### 2015-03-18 U_v16.tex
doc

\documentclass[a4paper,french,english,10pt]{article}
\usepackage{a4wide}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{lmodern}
%\usepackage{ae}

%\usepackage{refcheck}

%\usepackage{geometry}
%\geometry{verbose,a4paper,tmargin=3cm,bmargin=3cm,lmargin=3cm,rmargin=3cm,headheight=3cm,headsep=3cm}
\usepackage{babel}
\usepackage{color}
\usepackage{xcolor}
\usepackage{comment}
\usepackage{amsmath,amsthm, amssymb, mathrsfs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{epsfig}
%\usepackage{esint}R
\usepackage{amsfonts}
\usepackage{latexsym}
\usepackage{amscd}
 % \usepackage[all]{xy}
\usepackage{fancyhdr}
%\usepackage[affil-it]{authblk}
%\usepackage[nottoc, notlof, notlot,numbib]{tocbibind}
%\usepackage{refcheck}

 %Macros pour faciliter la frappe(?)
\newcommand\ljr{l_{jr}}
\newcommand\njr{\mathbf{n}_{jr}}
\newcommand\tnjr{\mathbf{\tilde{n}}_{j,r}}
\newcommand\uu{\mathbf{u}}
\newcommand\vv{\mathbf{v}}

\newcommand\Cjr{\mathbf{C}_{jr}}
\newcommand\al{\widehat{\alpha}_{jr}}
\newcommand\be{\widehat{\beta}_{jr}}
\newcommand\si{\sigma}
\newcommand\eps{\varepsilon}
\newcommand{\id}{\widehat{I}_d}
\newcommand{\cotan}{\cot} 
\newcommand{\U}{\uu}
\newcommand{\dx}{\partial_x}
\newcommand{\dy}{\partial_y}
\newcommand{\dz}{\partial_z}
\newcommand{\dt}{\partial_t}
\newcommand{\ds}{\displaystyle}
\newcommand{\f}{f(\x,\V,t)}
\newcommand{\I}{I(\x,\mathbf{\Omega},\nu,t)}
\newcommand{\alp}{\mathbf{\alpha}}
\newcommand\alj{\widehat{\alpha}_{jr}}
\newcommand\ali{\widehat{\alpha}_{ir}}
\newcommand\bei{\widehat{\beta}_{ir}}
\newcommand\bej{\widehat{\beta}_{jr}}
\newcommand\lir{l_{ir}}
\newcommand\nir{\mathbf{n}_{ir}}
\newcommand\tui{\tilde{\uu}_i}
\newcommand\tuj{\tilde{\uu}_j}
\newcommand\tur{\tilde{\uu}_r}
\newcommand\tuhr{\tilde{\uu}_{h,r}}
\newcommand\tuhj{\tilde{\uu}_{h,j}}
\newcommand\tpj{\tilde{E}_j}
\newcommand\tpi{\tilde{E}_i}
\newcommand\Fj{\uj}
\newcommand\ui{\uu_i}
\newcommand\tu{\tilde{\uu}}

\newcommand\x{\mathbf{x}}
\newcommand\xj{\mathbf{x}_j}
\newcommand\xr{\mathbf{x}_r}

\newcommand\pej{\bar{p}_j}
\newcommand\uej{\bar{\uu}_j}
\newcommand\uer{\bar{\uu}_r}

\newcommand\pj{\bar{p}_j}
\newcommand\uj{\uu_j}
\newcommand\ur{\uu_r}

\newcommand\fj{\mathbf{f}_j}
\newcommand\fr{\mathbf{f}_r}

\newcommand\cc{\mathbf{c}}
\newcommand\bb{\mathbf{b}}

\newcommand\cj{\cc_j}
\newcommand\br{\bb_r}
\newcommand\diam{\mbox{diam}}

\newcommand\ff{\mathbf{f}}
\newcommand\gf{\mathbf{g}}
\newcommand\V{\mathbf{V}}
\newcommand\W{\mathbf{W}}
\newcommand\G{\mathbf{G}}
\newcommand\F{\mathbf{F}}
\newcommand\nvhp{\|\V^\eps(0)\|_{H^3(\Omega)}}
 % Fin des macros pour faciliter la frappe

\newtheorem{theorem}{Theorem}[section]
\newtheorem{theor}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{pro}[theorem]{Proposition}
\newtheorem{algo}[theorem]{Algorithm}
\newtheorem{hyp}[theorem]{Hypothesis}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{coro}[theorem]{Corollary}
\newtheorem{definition}{Definition}[section]
\newtheorem{remark}[theorem]{Remark}

\begin{document}

\title{Proof of uniform convergence for a cell-centered  AP discretization  of the hyperbolic heat equation 
 on general meshes}

\author{Christophe Buet\thanks{Electronic address: 
\texttt{christophe.buet@cea.fr},
CEA, DAM, DIF,  F-91297 Arpajon Cedex, France}
,
Bruno Despr\'es\thanks{Electronic address: 
\texttt{despres@ann.jussieu.fr}, Laboratoire Jacques-Louis Lions,
  Universit\'e Pierre et Marie Curie,
  75252 Paris Cedex 05,
  France},
Emmanuel Franck\thanks{Electronic address: \texttt{emmanuel.franck@ipp.mpg.de}, Max-Planck-Institut f\"ur Plasmaphysik, Boltzmannstra\ss e 2
D-85748 Garching, Germany},
Thomas Leroy\thanks{Electronic address: \texttt{thomas.leroy@cea.fr},
CEA, DAM, DIF, F-91297 Arpajon Cedex,France,
and Laboratoire Jacques-Louis Lions,
  Universit\'e Pierre et Marie Curie,
  75252 Paris Cedex 05,
  France}
}

%\date{Version 2}
\maketitle

\begin{abstract} 
We prove the uniform  AP convergence on unstructured
meshes in 2D of a  generalization, see \cite{glaceap},      of the Gosse-Toscani 
 1D scheme  for the hyperbolic heat equation. 
This   scheme 
 is also a nodal  extension in 2D  of the Jin-Levermore scheme described in \cite{jinlev} for the  1D case.
In 2D, the proof  is performed using a new diffusion scheme.
\end{abstract}

%\tableofcontents
%\newpage

\section{Introduction}

We address the convergence analysis  on unstructured meshes
of diffusion
asymptotic preserving schemes for the discretization
of a problem with a stiff parameter denoted as $\eps\leq 1$.
The model problem considered in this work
is  the hyperbolic heat equation in the domain 
$t\geq 0$ and  $x\in \Omega\subset \mathbb R^n$
\begin{equation} \label{eq:mod1}
P^\varepsilon: \qquad 
\left\{\begin{array}{ll}
\ds\partial_t p^{\eps}+\frac{1}{\eps}\operatorname{div}(\uu^{\eps})=0,
& p^{\eps}\in \mathbb R, \\
\\
\ds\partial_t \uu^{\eps}+\frac{1}{\eps}\nabla
p^{\eps}=-\frac{\sigma}{\eps^2}\uu^{\eps},
& \uu^{\eps}  \in \mathbb R^n
 \end{array}\right.
\end{equation}
discretized with $P^0$ finite volume schemes.
This problem is representative
of many  transport problem such
as transfer and neutron transport,  for which the small parameter
$\eps$ is the ratio of two very different sound velocities and
$\sigma$ is the absorption or the opacity.
For simplicity both $\eps$ and  $\sigma>0$ are kept constant in space in this study.
The system (\ref{eq:mod1}) can also be introduced as a specific linearization
of a pressure-velocity system of partial differential equations
in the acoustic regime. In this work we will need the following well known energy estimates concerning 
the Cauchy problem for the partial differential equation (\ref{eq:mod1}): 
\begin{proposition}\label{bee}
If $\Omega= \mathbb R^n$ or $\Omega= \mathbb T^n$ and if the initial data $\V_0=(p_0,\uu_0) \in H^p( \Omega)$ then
\begin{equation}\label{bee1}
\vert\vert \V \vert \vert_{H^p( \Omega)}\leq \vert\vert \V_0 \vert \vert_{H^p( \Omega)}
\end{equation}
 and moreover 
\begin{equation}\label{bee2}
\frac{\sigma}{\eps^2}\vert\vert \uu \vert \vert^2_{L^2([0,T];H^p( \Omega))}\leq \vert\vert \V_0 \vert \vert^2_{H^p( \Omega)}.
\end{equation}
\end{proposition}
We will consider well prepared data in the sense that:
 $p^\eps(t=0)$
is independent of $\eps$ and is sufficiently smooth;
the initial velocity satisfies the equality in the second equation
of (\ref{eq:mod1}) at leading order. It writes 
\begin{equation} \label{eq:iniwp}
p^\eps(t=0)=p_0 \mbox{ and } 
\mathbf u^\eps(0)=-\frac\eps\sigma \nabla p_0.
\end{equation}
For such well prepared data, it can be easily shown that
the formal limit of $P^\varepsilon$ for small $\eps$ is
\begin{equation} \label{eq:mod2}
P^0: \qquad
\partial_t p - \frac1\sigma \Delta p=0. 
\end{equation}

\begin{remark}\label{sigmanotzero}
We do not consider the regime $\sigma \rightarrow 0$, since it introduces a singularity both
  in the initial data of the hyperbolic heat equation and in the limit parabolic equation.
\end{remark}

 Before addressing the main difficulty of this work  which is the discretization on  
  unstructured meshes, we briefly recall 
the  now well known notion 
of an asymptotic preserving technique \cite{jinbase}-\cite{jinreview}
which  is illustrated in the figure \ref{fig:diag1}.
For the simplicity of the presentation,
we will consider mainly semi-discrete numerical methods, this is why
the time step does not show up.
In  figure \ref{fig:diag1} the parameter $h$ designs a numerical method
with characteristic length $h\leq 1$:
so we assume  a numerical method $P_h^\varepsilon$ for the discretization
of $P^\varepsilon$.  
\begin{definition}[Uniform AP] \label{defAPu}
If  $P_h^\varepsilon$ is consistent with $P^\varepsilon$
uniformly with respect to $\varepsilon$, 
then we  say that the  scheme $P_h^\varepsilon$
is  uniformly AP  (uniformly asymptotic preserving).  
\end{definition}

However the design of such methods and  the numerical proof
of this property is difficult. This is why it has been proposed
in \cite{jinbase} to rely on the simpler necessary condition,
where the limit as $\eps\rightarrow 0$  of $P_h^\varepsilon$
is called the limit diffusion scheme $P_h^0$.

 \begin{figure}[h]
 \begin{center}
 \begin{tabular}{cc}
 \scalebox{.4}{\input{diag1.pdf_t}} 
 \end{tabular}
 \end{center}
 \caption{The AP (asymptotic diagram)
 diagram}
 \label{fig:diag1}
 \end{figure}

\begin{definition}[AP] \label{defAP}
 If $P_h^0$ is 
consistent with the limit model $P^0$, then we say that 
the scheme $P_h^\varepsilon$
is  AP (asymptotic preserving).
\end{definition}

This property is simpler to analyze than the uniform AP. It explains
why it has been very fruitful in the past.
In 1D, many AP schemes have been designed for some PDE and physical problems: S.
Jin, C. D. Levermore \cite{jinlev} or L. Gosse, G. Toscani \cite{Gosse} for the
hyperbolic heat equation, M. Lemou, L. Mieussens, N. Crouseilles
\cite{lemou}-\cite{MMvlasov}-\cite{couplingRad} for some kinetic equations, L.
Gosse \cite{GosseSn}, C. Buet and co-workers \cite{buet} or S. Jin and C. D.
Levermore \cite{SnJin} for $S_N$ equations and C. Berthon, R. Turpault
\cite{ber1}-\cite{ber3}-\cite{ber4} for generic systems and a non linear
radiative transfer model. Recently some asymptotic preserving schemes for linear
systems and non linear radiative transfer model have been designed in 2D
\cite{glaceap}-\cite{cras}-\cite{FVCA6}. However for this type of schemes it is
 difficult to obtain convergence estimates due to the competition between
the two parameters $\eps$ and $h$. To our knowledge this type of
proof are only given for uniform grids \cite{glaceap} (consistence and
stability, Lax theorem), \cite{Gosse} ($L^1$ and BV estimates), \cite{mmcv}
($L^2$ estimates).
The goal of this work is to prove the uniform AP property on unstructured 
grids.

To this end we adapt a strategy developed in 
 \cite{cveps} in a slightly different context.
It relies on the derivation of a priori estimates attached to the AP diagram in figure
\ref{fig:diag1}. To have a more global perspective
on this strategy,  let us assume 
some natural abstract a priori  estimates for a given norm
which is in our work based on   $\|f\|=\|f\|_{L^2([0,T]\times \Omega ) }$
where $T>0$ is a given final time, $\Omega=\mathbb{R}$, in 1D or $\Omega=[0,1]^2$ with periodic boundary conditions in 2D.
We assume four positive constants $a,b,c,d>0$ and another universal constant
 $C$ such that 
\begin{equation}\label{eq:mod3}
\| P^\varepsilon - P^0 \| \leq
C \varepsilon ^{a},
\end{equation}
\begin{equation}\label{eq:mod7}
\| P_h^\varepsilon - P^\varepsilon   \|_{ {\rm naive}} \leq
C \varepsilon ^{-b}h^c,
\end{equation}
\begin{equation}\label{eq:mod4}
\| P_h^0 - P^0   \| \leq
C h^d.
\end{equation}
The first inequality expresses that $P^0$ is indeed the limit of
$P^\varepsilon$. 
The second inequality is typically
based on  non AP error bounds. This is why we refer
to it as the naive error bound. 
The third inequality is the AP property.
A fourth inequality for
$\| P_h^\eps-P_h^0\|$ 
is of course
required to close the diagram.
We assume that it can be obtained in a form similar to 
(\ref{eq:mod3})
\begin{equation}\label{eq:mod3-bis}
\| P^\varepsilon_h - P^0_h \| \leq
C  \varepsilon ^{e}, \qquad e>0.
\end{equation}

\begin{pro} \label{prop:1}
 Assume that all these inequalities are at 
hand and that $d\geq c$ and $e\geq a$.
 Then the uniform AP holds with a rate at least
$O\left(h{^\frac{ac}{a+b}  } \right)$.
\end{pro}
\begin{proof}
The triangular inequality writes
$$
\| P_h^\varepsilon - P^\varepsilon   \|
\leq
\min
\left(
\| P_h^\varepsilon - P^\varepsilon   \|_{ {\rm naive}},
\| P_h^\eps-P_h^0\|+
\| P_h^0 - P^0   \| +
\| P^\varepsilon - P^0 \|
\right)
$$
which yields, using $\min(x,y+z)\leq \min(x,y)+\min(x,z)$ and   $e\geq a$.
\begin{equation} \label{eq:toutdebut}
\| P_h^\varepsilon - P^\varepsilon   \|
\leq
C\left(
\min
\left(
 \varepsilon ^{-b}h^c,
\eps^a
\right)+h^d+
\min\left(
 \varepsilon ^{-b}h^c,
\eps^e
\right)\right)
\leq C\left(
2\min  
\left(
 \varepsilon ^{-b}h^c,
\eps^a
\right) +h^d\right).
\end{equation}

We define a  threshold value $\varepsilon_{\rm thresh} $
by  $\varepsilon_{\rm thresh}  ^{-b}h^c=
\eps_{\rm thresh}^a$. So either $\eps\leq \varepsilon_{\rm thresh} $
so that $\min
\left(
 \varepsilon ^{-b}h^c,
\eps^a
\right)\leq \varepsilon_{\rm thresh} =h^{\frac{ac}{a+b}  }$, or 
$\eps\geq \varepsilon_{\rm thresh} $ and the same bound is obtained by 
taking the other term as the minimum.
And since $d\geq c$, one gets the abstract bound
$
\| P_h^\varepsilon - P^\varepsilon   \|
\leq
3Ch^{\frac{ac}{a+b}  }
$ which ends the proof.
\end{proof}

The structure of these  inequalities explains our strategy: that is we
prove separately each of these inequalities 
(\ref{eq:mod3}-\ref{eq:mod3-bis}) with care, so that
the inequalities $d\geq c$ and $e\geq a$  are true.
This part of the proof relies on specific hyperbolic
and parabolic numerical methods. Even if it is technical, 
the first three inequalities 
(\ref{eq:mod3}-\ref{eq:mod4}) do not yield additional difficulties
with respect to the state of the art. The proof of  inequality  (\ref{eq:mod3-bis})
is provided in 1D, and can be probably  be generalized 
straightforwardly on cartesian meshes in 2D and 3D.
On the other hand  our researches on proving 
   (\ref{eq:mod3-bis})
for  $\| P_h^\eps-P_h^0\|$  show 
a fundamental  obstruction in dimension greater than one on unstructured meshes   which was not expected
initially. 
%Indeed the study of this  inequality  is based
%on  comparison principles and a priori estimates. 
Since the main difficulty is related
to $P_h^0$, 
it motivates the definition
of a new  diffusion scheme. 
To this end we remark that another diffusion scheme is naturally
 defined
from $P_h^\varepsilon$ by {killing}
the derivative $\partial_t v_h$ in the discrete version
of the second equation of (\ref{eq:mod1}).
 {Killing} at the continuous level
the $\partial_t v$ is absolutely
equivalent to taking the formal limit $\varepsilon \rightarrow 0^+$.
But at the discrete level, 
it appears that it generates a new family of diffusion 
schemes, where
both parameters $h$ and $\eps$ are present. We 
call them Diffusion Asymptotic schemes, $DA_h^\varepsilon$.
By construction $P_h^0=\lim_{\varepsilon\rightarrow 0} DA_h^\varepsilon$. This 
is summarized
in figure \ref{fig:diag5}.
Finally since the scheme $DA_h^\eps$  is
 still  an accurate discretization of $P^0$,
our proof of the uniform AP properties is based
on the new AP diagram  displayed in figure \ref{fig:diag4}.

 \begin{figure}[h]
 \begin{center}
 \begin{tabular}{cc}
 \scalebox{.3}{\input{diag5.pdf_t}} 
  \end{tabular}
 \end{center}
 \caption{Definition of the diffusion asymptotic scheme $DA_h^\varepsilon$.}
 \label{fig:diag5}
 \end{figure}

Our main theorem \ref{theor:main} in dimension 2
is based on this structure and it may be stated as follows:
{\bf The so-called JL-(b) scheme defined
in \cite{glaceap} for the discretization of the hyperbolic heat equation 
(\ref{eq:mod1}) (the scheme  is cell-centered with nodal based fluxes)
 is uniformly AP on unstructured meshes, with a rate
of convergence at least $O(h^\frac14)$ for sufficiently smooth initial data}.
This is an improvement with respect to \cite{glaceap} where only AP was proven.
To our knowledge this is the first time that such a result is obtained on general unstructured
multidimensional meshes.

More precisely the convergence estimate can be written as 
$$
%\|\V_h^\eps-\V^\eps\|
\mbox{\bf error}
\leq
C(T) \min \left(
\sqrt{\frac h \eps  } \; \; , \; \;
\eps \max\left(1, \sqrt{\frac \eps h } \right) +
h + 
%\left(h +\eps
%\right)+
\eps
\right)
$$
where  the first argument in the min function comes from the hyperbolic analysis 
and the second argument comes from the parabolic analysis. 
Some natural regularity 
assumptions 
 are  nevertheless 
imposed on the mesh in the hypothesis \ref{geometrie1d}.
This hypothesis is not very restrictive. For example
 meshes with angles greater
than $90$ degrees are allowed. If the mesh is made with triangles,
the hypothesis is fulfilled if all angles are greater
than $12$ degrees, see \cite{glaceap}.
It is interesting to notice that
the rate of uniform 
convergence is $O(h^\frac13)$ 
in dimension one. 
The difference essentially comes from the 
estimate of the reconstruction of the initial velocity which is needed
to rewrite a diffusion scheme as a non homogeneous hyperbolic scheme:
it is much simpler in dimension one (see equation \eqref{init_1D}) than in 
dimension two (see proposition \eqref{esti_initial_data}).
In this work we considered only semi-discrete numerical schemes, since it simplifies
a lot the notations and allow to focus on the main difficulties,
but the final estimates of convergence can be generalized to fully discrete schemes, using the a priori
estimates developed in \cite{de04}. 
For explicit schemes,
these estimates add a term proportional to the square root of the maximal time step allowed by the CFL
condition. Since our problem is an hyperbolic+relaxation problem, with a limit which is parabolic,
this additional term can be computed and is of the order between $h$ (for purely hyperbolic)
to $h^2$ (for purely parabolic). We refer to  \cite{glaceap} for the detail of CFL condition in 1D and 2D.
Concerning the implicit fully discrete version of the semi-discrete scheme, the same kind
of error terms  can be analyzed. This is confirmed by he numerical results of section \ref{sec::num}, 
which show an even better rate of convergence.

 \begin{figure}[h]
 \begin{center}
 \begin{tabular}{cc}
 \scalebox{.4}{\input{diag4.pdf_t}} 
  \end{tabular}
 \end{center}
 \caption{The new AP diagram, where the previous branch is still
 displayed in dashed lines. 
 }
 \label{fig:diag4}
 \end{figure}

%More important for applications is the fact that 
%The fact that the finite volume scheme is nodal based and not edge based
%has been stressed in \cite{glaceap}. This fact is important if one has in mind to

We think that some of our results can have an interest for the 
development and  use of such methods in research or industrial codes with complex non linear 
physics   on unstructured meshes.
Indeed for such codes  cell-centered Finite Volume schemes %well adapted
are a natural solution in terms of  data structure.
The point is the following: the scheme studied in this work
is the only cell-centered  one  we know in 2D 
to compute
the solutions of problems which admit  diffusion limits in certain regimes and for which it is possible to prove the AP property.
Since the structure of this cell-centered scheme is nodal based, it strongly questions the ability
of standard Finite Volume methods with edge-based fluxes to recover asymptotic diffusion regimes.
As demonstrated in this work, nodal based Finite Volume techniques do not suffer from this drawback.

%It is another
%open problem to identify alternative finite volume schemes, valid  on unstructured meshes,
%which can be used to compute the solution of such problems with uniform accuracy.
%If ever edge based finite volume techniques are indeed
%strongly limited for such problems, as was suggested in \cite{glaceap}, it is a good reason
%to still continue to develop nodal based finite volume techniques.

This work is organized as follows.
Section \ref{sec:2}
is dedicated to the discretization 
of the model problem in dimension one on irregular grids.
The convergence is proved in 
theorem \ref{theor:1d}
with order
$h^{\frac13}$ in the $L^2$ space-time norm.
In the next section, the nodal solvers for the hyperbolic equation are defined, and the various a priori
estimates proved. 
The main theorem of uniform AP for the JL-(b) scheme
with a rate $O(h^\frac14)$
is proved at the end of the section.
Section \ref{sec::num}
  provides numerical results that sustain the fact
that the convergence order depends on the relative value of $\eps$ and $h$.,
and so is mixed hyperbolic/parabolic. 
Our final remarks will be gathered in a conclusion.

All our results and numerical methods in 2D can be generalized in 3D 
provided a convenient definition of the nodal corner vector is used as in \cite{de10}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Analysis in 1D} \label{sec:2}

%\subsection{The JL-(b) scheme}

The model problem in dimension one writes
\begin{equation}\label{chaleur22}
P^\varepsilon: \qquad
 \left \{
\begin{array}{lll}
\partial_t p^{\eps} + \frac{1}{\eps}\partial_x u^{\eps} =0, \\
\partial_t u^{\eps} + \frac{1}{\eps}\partial_x p^{\eps} =
-\frac{\sigma}{\eps^2}u^{\eps}.
\end{array}
\right.
\end{equation}
As stressed already in (\ref{eq:iniwp}), we consider well-prepared data
$
p^\varepsilon(t=0)=p_0 $  and  $u_0^\varepsilon=-\frac\varepsilon \sigma \partial_{x}p_0$.
The equations (\ref{chaleur22}) 
admit the formal diffusion limit when $\eps$ tends to $0$:
\begin{equation}\label{difffff}
P^0: \qquad 
\dt p -\frac{1}{\sigma}\partial_{xx}p=0.
\end{equation}
A useful variable will be  the scaled gradient  
\begin{equation} \label{eq:diff-v}
v=-\frac{1}{\sigma}\dx p.
\end{equation}
%%%%

\subsection{Notations}
We denote $x_{j+1/2}$ the nodes, the cells $j$ are the intervals $[x_{j-1/2},x_{j+1/2}]$, thus $\Delta x_j=x_{j+1/2}-x_{j-1/2}$, $x_j$ is the center of the cell $j$ that is $x_j =\frac12(x_{j+1/2}+x_{j-1/2})$, and $\Delta x_{j+1/2}=x_{j+1}-x_j=\frac12(\Delta x_{j+1}+\Delta x_{j})$. Natural assumptions on the mesh are summarized below:

\begin{hyp}[Regularity of the mesh in 1D] \label{geometrie1d}
 We consider there exists 
a universal constant $C>0$ independent of the mesh size
$h=\sup_{j\in \mathbb Z} \Delta x_j $
so that one has 
$$
Ch \leq \Delta x_j \leq h \qquad \forall j \in \mathbb{Z}.
$$
\end{hyp}

The semi-discrete
JL(b) scheme,   derived in  \cite{glaceap} in 2D,
can also be written in 1D on irregular meshes as 
\begin{equation}\label{schema1}
P^\varepsilon_h: \qquad
\left\{
\begin{array}{lll}
\displaystyle\frac{d}{dt}p^{\eps}_j +\frac{u_{j+\frac12 }^{\eps} -
u_{j-\frac12 }^{\eps} }{\eps\Delta x_j} = 0,\\
\displaystyle\frac{d}{dt}u^{\eps}_j+\frac{p_{j+\frac12 }^{\eps}-
p_{j-\frac12 }^{\eps}}{\eps\Delta x_j} = -\frac{\sigma}{\eps^2} \frac{
u_{j+\frac12 }^{\eps}+u_{j-\frac12 }^{\eps}}{2 } ,
\end{array}
\right.
\end{equation}
with  the fluxes  $p_{j+\frac12 }^{\eps}$ and $u_{j+\frac12 }^{\eps}$
are the solutions of the well-posed linear system
\begin{equation} \label{eq:fflux}
j\in \mathbb Z: \qquad
\left\{
\begin{array}{cl}
\displaystyle
p_{j+\frac12 }^{\eps}+u_{j+\frac12 }^{\eps}
+\frac{\sigma \Delta x_j}{2\eps}
 u_{j+\frac12 }^{\eps}
&=
p^{\eps}_j+u^{\eps}_j ,\vspace{2mm}
\\
\displaystyle
-p_{j+\frac12 }^{\eps} +u_{j+\frac12 }^{\eps}
+\frac{\sigma \Delta x_{j+1}}{2\eps} 
u_{j+\frac12 }^{\eps} 
&=
-p^{\eps}_{j+1}+u^{\eps}_{j+1}.
\end{array}
\right.
\end{equation}
This scheme is the same
as the Gosse-Toscani scheme\footnote{A 
long and tedious computation  shows that the  scheme is strictly
equivalent to 
  the   Gosse-Toscani's scheme, described in    \cite{Gosse} but only for
uniform meshes, which writes in terms of $w^{\eps} ,v^{\eps} =p^{\eps} \pm u^{\eps} $
\begin{equation*} \label{hhe:diagnum}
\left\{
\begin{array}{ll}
\displaystyle\frac{d w_j}{dt}
+\frac{ M_{j- \frac12} }{\varepsilon}
\frac{  w_j^{\eps}  -  w_{j-1}^{\eps} }{\Delta  x_j}=
\frac{1  }{\varepsilon\Delta  x_j}(1-M_{j-
\frac12})(v_j^{\eps}  -w_j^{\eps}  )=
 M_{j- \frac12}  
\frac{\Delta  x_{j- \frac12}}{\Delta  x_j}\frac{ \sigma }{2\varepsilon^2}
(v_j^{\eps} -w_j^{\eps} ),   \\
\displaystyle\frac{ dv_j^{\eps}  }{dt}
-\frac{  M_{j+ \frac12} }{\varepsilon}
\frac{  v_{j+1} ^{\eps} - v_j^{\eps} }{\Delta  x_j}=\frac{1  }{\varepsilon\Delta  x_j}(1-M_{j+
\frac12})(w_j ^{\eps}  -v_j^{\eps}  )
=
 M_{j+ \frac12} \frac{\Delta  x_{j+ \frac12}}{\Delta  x_j}
\frac{ \sigma}{2\varepsilon^2} (w_j^{\eps} -v_j^{\eps} )
\end{array}
\right.
\end{equation*}
with 
%\begin{equation} \label{eq:64num}
$M_{j+ \frac12} =\frac {2  \varepsilon }{\sigma\Delta  x_{j+ \frac12} + 2 
\varepsilon }
$%\end{equation}
and $ \Delta  x_{j+ \frac12}=\frac{\Delta  x_{j}+\Delta  x_{j+1}}{2}$. 
By writing
\begin{equation*} \label{hhe:toto}
\left\{
\begin{array}{ll}
M_{j- \frac12}
( w_{j-1}^{\eps}  - w_j^{\eps}    ) = M_{j- \frac12}w_{j-1} -M_{j+ \frac12}w_j + (M_{j+
\frac12}-M_{j- \frac12}) w_j^{\eps} \\
 M_{j+ \frac12} (  v_{j+1}^{\eps}  - v_j^{\eps} )=M_{j+ \frac12}
v_{j+1}^{\eps}  -M_{j- \frac12}v_j^{\eps}  -
(M_{j+ \frac12}-M_{j- \frac12})v_j^{\eps} 
\end{array}
\right.
\end{equation*}
then  in terms of $p^{\eps} $ an $u^{\eps} $ we have evidently
\begin{equation*} \label{eq:63num}
\left\{
\begin{array}{l}
\displaystyle\frac{dp_j^{\eps} }{dt }
+\frac{1}{\varepsilon}\frac{ M_{j+ \frac12}  u_{j+\frac12}^{\eps} 
-
M_{j- \frac12}  u_{j-\frac12}^{\eps}  }{\Delta  x_j}
=0,   \\
\\
\displaystyle\frac{du_j^{\eps} }{dt }
+\frac{1}{\varepsilon}\frac{ M_{j+ \frac12} p_{j+\frac12}^{\eps} 
-
M_{j- \frac12}  p_{j-\frac12} ^{\eps}  }{\Delta  x_j}
=-\frac12\left(
M_{j+ \frac12} 
\frac{\Delta  x_{j+ \frac12}}{\Delta  x_j}\frac{\sigma}{\varepsilon^2}
+
M_{j- \frac12} 
\frac{\Delta  x_{j- \frac12}}{\Delta  x_j}\frac{\sigma}{\varepsilon^2}
\right)
u_j^{\eps} 
 +\frac{M_{j+ \frac12} - M_{j- \frac12}}{\varepsilon \Delta  x_j} p_j^{\eps} 
\end{array}
\right.
\end{equation*} 
with  the fluxes given by
$p_{j+\frac12}^{\eps} =\frac{  p_j^{\eps}  +p_{j+1}^{\eps} }{2 }
+
\frac{  u_j^{\eps}  - u_{j+1}^{\eps} }{2 }
$ and $
\displaystyle u _{j+\frac12}= 
\frac{ u_j^{\eps}  + u_{j+1}^{\eps} }{2 }
+
\frac{ p_j^{\eps}  - p_{j+1}^{\eps} }{2 }$.
}.
Other  equivalent forms of $P_h^\eps$
  can be  obtained by various manipulations, as in (\ref{schema}).
The natural cellwise initialization is chosen
\begin{equation} \label{eq:initp1}
p_j^\eps(0)=p_0(x_j) \mbox{ and }
u_j^\eps(0)=-\frac\eps\sigma \partial_x p_0(x_j) \mbox{ for all }j\in \mathbb Z.
\end{equation}
Our goal is this section is to show that this scheme is AP.

When $\eps$ tends to $0$, 
 the scheme $P_h^\eps$ admits the 
diffusion limit scheme $P_h^0$
\begin{equation}\label{schemadifff}
P_h^0: \qquad
\displaystyle\Delta x_j\frac{d}{dt} p_j -\frac{1}{\sigma } \bigg(
\frac{p_{j+1}-p_j}{\Delta x_{j+\frac12 }}-\frac{p_j -p_{j-1}}{\Delta
x_{j-\frac12 }}\bigg)=0
\end{equation}

The natural cellwise initialization is
\begin{equation} \label{eq:intip0}
p_j(0)=p_0(x_j) \mbox{ for all }j\in \mathbb Z.
\end{equation}
Other quantities are 
\begin{equation} \label{eq:vv}
\left \{
\begin{array}{l}
\displaystyle v_{j+\frac12 }=-\frac{1}{\sigma}\frac{p_{j+1}-p_{j}}{\Delta
x_{j+\frac12 }},\\
\displaystyle v_j=\frac{v_{j+\frac12 }+v_{j-\frac12 }}{2}.
\end{array}
\right.
\end{equation}

Provided that the initial data is smooth, the initialization gives us 
\begin{equation}\label{init_1D}
 \| u_j^{\eps}(0)-\eps v_j(0)\|_{L^2(\mathbb{R})} \leq C h\eps .
\end{equation}

We denote by $\V^{\eps}(t)=\left(p^{\eps}(x_j,t),
u^{\eps}(x_j,t)\right)_{j\in \mathbb Z}$ the interpolation of the 
solution of the hyperbolic heat equations $P^\eps$ and by
$\V^{\eps}_h(t)=
\left(p_j^{\eps}(t), u_j^{\eps}(t)   \right)_{j\in \mathbb Z}$ the
solution of the JL-(b) scheme $P_h^\eps$. Similarly  we  reconstruct
similar quantities from the diffusion scheme: it yields 
$\W^\eps(t)=\left(p(x_j,t),\varepsilon v(x_j,t)\right)_{j\in \mathbb Z}$ 
which is the interpolation of the 
solution of the diffusion limit
$P^0$ (\ref{difffff})-(\ref{eq:diff-v}),
 and  $\W_h^\eps(t)=\left( p_j(t),  
\varepsilon v_j(t)   \right)_{j\in \mathbb Z}$ which is
the
solution of the diffusion scheme $P_h^0$ (\ref{schemadifff})-(\ref{eq:vv}). 
For simplicity we choose a final time $T>0$.
All  error estimates will be given for 
$t\leq T$, either
in the norm
$\|f(t)\|_{L^\infty([0,T];L^2(\mathbb{R}))}$, or mostly in the norm
$\|f\|_{L^2([0,T]\times \mathbb{R})}$

\subsection{Study of $\|P^\varepsilon-P^0  \|$}

In this section we prove a natural error estimate \cite{cveps}
between the solution of the
hyperbolic heat equations \eqref{chaleur22} and the solution of the diffusion
limit equation \eqref{difffff}.

\begin{proposition} \label{heqtode}
There exists a constant $C>0$ such that 
\begin{equation*}
\|\V^{\eps}-\W^\eps\|_{L^\infty([0,T];L^2(\mathbb{R}) )} \leq
C \eps  \|\partial_{xxx}p_0\|_{L^2(\mathbb{R})}.
\end{equation*}
\end{proposition}
\begin{proof}
We define $u^{\eps}=-\frac{\varepsilon}\sigma \partial_x p^{\eps}$ and
introduce $R^{\eps}$ such that the solution of the diffusion equation satisfies
\begin{equation}\label{modifdiff}
\left \{
\begin{array}{lll}
\dt p^{\eps} +\frac{1}{\eps}\partial_{x}u^{\eps}=0,\\
\partial_t u^{\eps} + \frac{1}{\eps}\partial_x p^{\eps} +\frac{\sigma}{\eps^2}u^{\eps} = R^{\eps}
\end{array}
\right.
\end{equation}
where
 $R^{\eps}=\dt u^{\eps}=-\frac{\varepsilon}\sigma \partial_{tx} p^{\eps}=
-\frac{\varepsilon}{\sigma^2} \partial_{xxx}p^{\eps}$. 
Note that 
$\|R^{\eps}(t)\|_{L^2(\mathbb{R})}\leq \|R^{\eps}(0)\|_{L^2(\mathbb{R})}$. 
Denoting $e^{\eps}=p-p^{\eps}$, $f^{\eps}=u-u^{\eps}$, we make the difference between the
systems \eqref{chaleur22} et \eqref{modifdiff}
\begin{equation}\label{diffmodif}
\left \{
\begin{array}{lll}
\dt e^{\eps} +\frac{1}{\eps}\partial_{x}f^{\eps}=0,\\
\partial_t f^{\eps} +\frac{1}{\eps}\partial_x e^{\eps} +\frac{\sigma}{\eps^2}f^{\eps} = R^{\eps}.
\end{array}
\right.
\end{equation}
Since data are well-prepared, one has $e^{\eps}(0)=f^{\eps}(0)=0$.
Consider
$\|\V^{\eps}-\W^\eps\|_{L^2(\mathbb{R})}^2=\|e^{\eps}\|_{L^2(\mathbb{R})}
^2+\|f^{\eps}\|_{L^2(\mathbb{R})}^2$.
Adding the first equation of
\eqref{diffmodif} multiplied by $e^{\eps}$ and the second multiplied by $f^{\eps}$ and integrating
on $\mathbb{R}$,
 we find out that:
$\frac12 \frac{d}{dt}\|\V^{\eps}-\W^\eps\|_{L^2(\mathbb{R})}^2 \leq
\int_{\mathbb{R}}R^{\eps}f^{\eps} dx \leq  \|R^{\eps}\|_{L^2(\mathbb{R})}
\|\V^{\eps}-\W^\eps\|_{L^2(\mathbb{R})}
.$
  The proof is ended by integration between 0 and T.

\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Stability  estimates for $P_h^\varepsilon$ and $P_h^0$}

These estimates characterize the dissipation rate 
of both schemes.

\begin{proposition}\label{prodentrgosse}
The  scheme $P_h^\eps$
is stable in $L^2$ norm. Moreover, 
\begin{equation}\label{estiuepsflux}
\sqrt{
\int_0^T \left( \sum \Delta x_{j+\frac12}  ( u_{j+\frac12 }^\eps)^2 \right)dt
}
\leq
\frac{\eps}{\sqrt{\sigma}}
 \|\V^{\eps}_h(0)\|_{L^2(\mathbb{R})}
\end{equation}
and
\begin{equation}\label{estiuepsflux2}
 \sqrt{
\int_0^T
\left(
\sum_{j\in \mathbb{Z}} 
{
(u_{j+\frac12 }^{\eps}-u^{\eps}_j)^2 }
 +\sum_{j\in \mathbb{Z}} 
{
(u_{j-\frac12 }^{\eps}-u^{\eps}_j)^2 }
\right)dt }
\leq \sqrt \eps  \|\V^{\eps}_h(0)\|_{L^2(\mathbb{R})}.
\end{equation}
\end{proposition}
\begin{remark}
The strategy of the proof of many estimates in this work
consists to analyze the balance
between the dissipation of the fluxes and the physical dissipation (all 
 source terms like 
$-\frac\sigma{\eps^2}u$) on the one hand, and some truncation errors
on the other hand.
This is why it is  convenient
to reformulate $P_h^\eps$
so that   the pressure fluxes 
$p_{j+\frac12 }^{\eps}$ and $p_{j-\frac12 }^{\eps}$ are eliminated in the second
equation of (\ref{schema1}). This elimination is technically convenient since
all dissipation terms are expressed using the same variable, namely $u$.
It will simplify a lot the comparisons between
all kinds of dissipation terms and other errors terms.
\end{remark}

\begin{proof}
According to the above remark we obtain  
the formulation 
(\ref{schema}) 
which is 
equivalent to $P_h^\eps$
\begin{equation}\label{schema}
\left\{
\begin{array}{lll}
\displaystyle\Delta x_j\frac{d}{dt}p^{\eps}_j +\frac{u_{j+\frac12 }^{\eps} -
u_{j-\frac12 }^{\eps} }{\eps} = 0,\\
\displaystyle\Delta x_j\frac{d}{dt}u^{\eps}_j-\frac{u_{j+\frac12 }^{\eps}+
u_{j-\frac12 }^{\eps}}{\eps} +\frac{2}{\eps}u_j^{\eps}=0, \\
\displaystyle 
\left( 2
+\frac{\sigma \Delta x_{j+\frac12}
 }{\eps}
\right) u_{j+\frac12 }^{\eps}

=p^{\eps}_j-p^{\eps}_{j+1}+u^{\eps}_j+u^{\eps}_{j+1}
.
\end{array}
\right.
\end{equation}
Consider now the discrete quadratic energy
$E(t)=\frac12 \sum_j \Delta x_j ((p^{\eps}_j)^2+(u^{\eps}_j)^2)$.
 Multiplying the first equation of \eqref{schema} by $p_j^{\eps}$ and the second
equation by $u_j^{\eps}$ and adding on all the cells, one finds
\begin{equation*}
 E'(t)=-\sum_{j\in \mathbb{Z}} \frac{
u_{j+\frac12 }^{\eps}-u_{j-\frac12 }^{\eps}}{\eps}p^{\eps}_j + \sum_{j\in
\mathbb{Z}} \frac{
u_{j+\frac12 }^{\eps}+u_{j-\frac12 }^{\eps}}{\eps}u^{\eps}_j
-\frac{2}{\eps}\sum_j (u^{\eps}_j)^2.
\end{equation*}
Since $
\sum_{j}(
u_{j+\frac12 }^{\eps}-u_{j-\frac12 }^{\eps})p^{\eps}_j =
\sum_{j} u_{j+\frac12 }^{\eps}(p^{\eps}_j-p^{\eps}_{j+1})$, one
has  by using the third equation of \eqref{schema} and rearranging the
terms
\begin{equation}\label{prodentrgosseeq}
E'(t)+\sum_{j\in \mathbb{Z}} \frac{
(u_{j+\frac12 }^{\eps}-u^{\eps}_j)^2 }{\eps}+\sum_{j\in \mathbb{Z}} \frac{
(u_{j-\frac12 }^{\eps}-u^{\eps}_j)^2 }{\eps} +
\frac{\sigma}{\eps^2}\sum_{j\in \mathbb{Z}} \Delta x_{j}
\frac{(u_{j+\frac12 }^{\eps})^2+(u_{j-\frac12 }^{\eps})^2}{2}= 0.
\end{equation}
Integrating  \eqref{prodentrgosseeq} between 0 and t, one finds  $E(t)\leq E(0)$, that is the $L^2$ stability of $P_h^\eps$.
The estimate  (\ref{estiuepsflux}) 
comes from 
$\Delta x_{j+\frac12}=\frac12( \Delta x_{j}+\Delta x_{j+1})$. The estimate 
 (\ref{estiuepsflux2}) is directly deduced from
(\ref{prodentrgosseeq}).
\end{proof}

Some similar bounds hold 
for  the quantities relatives to the diffusion scheme (\ref{schemadifff}).
First, multiplying the diffusion scheme by $p_j$ and adding on all the cells,
one has the $L^2$ stability in the sense
\begin{equation*}
\frac12 \frac{d}{dt}\sum_j \Delta x_jp_j^2=-\frac{1}{\sigma}\sum_j
\frac{(p_{j+1}-p_j)^2}{\Delta x_{j+\frac12 }}.
\end{equation*}
Thus 
the following estimate holds for
 the function 
$\bar{v}_h=\left( v_{j+\frac12}  \right)_j$ defined by
(\ref{eq:vv})

\begin{equation}\label{l2}
 \|\bar{v}_{h}\|_{L^2([0,T]\times\mathbb{R})}
=
\sqrt{
\int_0^T \sum_j \Delta x_{j+\frac12} (v_{j+\frac12} )^2
}
\leq
C\|p_0\|_{L^2(\mathbb R)}, \qquad C>0.
\end{equation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Study of $\| P_h^\varepsilon - P^\varepsilon   \|_{ {\rm naive}}$}

In this section we  
prove the 
convergence of $P_h^\varepsilon $ to  $P^\varepsilon $. We still denote $V^\eps(t)=(p^\eps,u^\eps)$.
\begin{proposition}\label{cv1d}
There exist a constant $C(T)>0$ independent of $\eps$ and $h$ 
 such that the following estimate holds 
\begin{equation*}
\|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
\leq C(T) 
\sqrt \frac{h}\eps 
\left\| \V^{\eps}(0)
\right\|_{H^1(\mathbb{R})}.
\end{equation*}

\end{proposition}

\begin{proof}
In order to establish this estimate, we will use the method introduced by C.
Mazeran \cite{Mazeran} in his PhD thesis.
It  starts with an estimate for the time derivative of
$\mathscr{E}=\frac12 \|\mathbf V_h^\eps - \mathbf V^\eps  \|^2_{L^2(\mathbb{R})}$.
For the sake of simplicity,for any quantity $q$,   $q'$ stands indifferently for  $\frac{d}{dt}q $ or $\partial_t q $. One has 
\begin{equation*}\label{esti}
\begin{array}{l}
\mathscr{E}'(t) = \underbrace{\frac12 
\int_{\mathbb{R}}((p_{h}^{\eps})^2+(u_{h}^{\eps})^2)'dx}_{D_1}+
\underbrace{\frac12 
\int_{\mathbb{R}}((p^{\eps})^2+(u^{\eps})^2)'dx}_{D_2} \\
\hspace{0.8cm}
+ \underbrace{\int_{\mathbb{R}}
(-(p_{h}^{\eps})'p^\eps-(u_{h}^{\eps})'u^\eps)dx}_{D_3} + \underbrace{\int_{\mathbb{R}}
(-p_{h}^{\eps}(p^{\eps})'-u_{h}^{\eps}(u^{\eps})'dx}_{D_4}
\end{array}
\end{equation*}
We will successively estimate each of those terms,
the fundamental idea being that
$D_1\leq 0$ and $D_2\leq 0$ are used to control 
spurious contributions in $D_3$ and $D_4$.
First $D_1$ corresponds to the
entropy production of the scheme. Thanks to the proof of
the proposition \ref{prodentrgosse},
one has
\begin{equation*}
 D_1 = -\frac{1}{\eps}\sum_{j\in \mathbb{Z}}
(u_{j+\frac12 }^{\eps}-u^{\eps}_j)^2 -\frac{1}{\eps} \sum_{j\in
\mathbb{Z}}(u_{j-\frac12 }^{\eps}-u^{\eps}_j)^2-
\frac{\sigma}{\eps^2}\sum_{j\in \mathbb{Z}} \Delta x_{j}
\frac{(u_{j+\frac12 }^{\eps})^2+(u_{j-\frac12 }^{\eps})^2}{2}\leq 0.
\end{equation*}
One also directly obtains
\begin{equation*}
 D_2 = -\sum_{j\in \mathbb{Z}} \Delta x_j \frac{ \sigma }{\eps^2} \: \bigg(
\frac{1}{\Delta x_j}{\int_{x_{j-\frac12}}^{x_{j+\frac12}}}(u^{\eps})^2 dx \bigg)
\leq 0.
\end{equation*}
For $D_4$, one gets  directly
\begin{eqnarray*}
 D_4 &=& \sum_{j\in \mathbb{Z}} p^{\eps}_j
\frac{u^{\eps}(x_{j+\frac12 })-u^{\eps}(x_{j-\frac12 })}{\eps} +
\sum_{j\in \mathbb{Z}} u^{\eps}_j 
\frac{p^{\eps}(x_{j+\frac12 })-p^{\eps}(x_{j-\frac12 })}{\eps} +
\sum_{j\in \mathbb{Z}} \frac{\sigma}{\eps^2} u^{\eps}_j 
{\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx 
\end{eqnarray*}
In this method the third term
 $D_3$ is more complicated to study
\begin{equation*}
\begin{array}{l}
 D_3 = \sum_{j\in \mathbb{Z}}
\frac{u_{j+\frac12 }^{\eps}-u_{j-\frac12 }^{\eps}}{\eps} \: \bigg(
\frac{1}{\Delta x_j} {\int_{x_{j-\frac12}}^{x_{j+\frac12}}}
 p^{\eps}(x) dx \bigg)
+\sum_{j\in \mathbb{Z}}
\frac{p_{j+\frac12 }^{\eps}-p_{j-\frac12 }^{\eps}}{\eps} \: \bigg(
\frac{1}{\Delta x_j} 
{\int_{x_{j-\frac12}}^{x_{j+\frac12}}}
 u^{\eps}(x) dx \bigg) \\
\hspace{0.8cm}+\sum_{j\in \mathbb{Z}} \Delta x_j  \frac{\sigma}{\eps^2}
\frac{u_{j+\frac12 }^{\eps}+u_{j-\frac12 }^{\eps}}{2}\: \bigg(
\frac{1}{\Delta x_j} {\int_{x_{j-\frac12}}^{x_{j+\frac12}}}
 u^{\eps}(x) dx \bigg).
\end{array}
\end{equation*}
 It is  decomposed in several pieces.
We add and subtract in each fluxes  the value of the unknowns in the
cell. We also add and subtract to the two first  integrals the value of the
unknowns on the edge. Denoting by $\delta_{j }^\pm
\left( g \right) =\frac{1}{\Delta
x_j} {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} g(x) dx -g(x_{j\pm\frac12 })$,
 one gets after rearrangements
\begin{equation*}
\begin{array}{lll}
 D_3 &=& \underset{j\in \mathbb{Z}}{\sum}
\frac{u_{j+\frac12 }^{\eps}-u_j^{\eps}}{\eps} \delta_{j}^+\left(p^{\eps}\right)+
\underset{j\in \mathbb{Z}}{\sum}
\frac{u^{\eps}_j-u_{j-\frac12 }^{\eps}}{\eps}\delta_{j}^-\left(p^{\eps}\right)
\\
& +& \underset{j\in \mathbb{Z}}{\sum}
\frac{p_{j+\frac12 }^{\eps}-p_{j}^{\eps}}{\eps} 
\delta_{j}^+\left(u^{\eps}\right)
+\underset{j\in \mathbb{Z}}{\sum}
\frac{p^{\eps}_j-p_{j-\frac12 }^{\eps}}{\eps} 
\delta_{j}^-\left(u^{\eps}\right) \\
&-&\underset{j\in \mathbb{Z}}{\sum} 
\frac{u^{\eps}(x_{j+\frac12 })-u^{\eps}(x_{j-\frac12 })}{\eps} 
p^{\eps}_j
-
\underset{j\in \mathbb{Z}}{\sum} 
\frac{p^{\eps}(x_{j+\frac12 })-p^{\eps}(x_{j-\frac12 })}{\eps}
u^{\eps}_j  \\
&+& \underset{j\in \mathbb{Z}}{\sum} \Delta x_j  \frac{\sigma}{\eps^2}
\frac{u_{j+\frac12 }^{\eps}+u_{j-\frac12 }^{\eps}}{2}\: \bigg(
\frac{1}{\Delta x_j} {\int_{x_{j-\frac12}}^{x_{j+\frac12}}}u^{\eps}(x) dx \bigg)
\end{array}
\end{equation*}
Using the fluxes' definition (\ref{eq:fflux}), one can 
eliminate the pressure fluxes. With
 a Young's inequality 
$ab\leq \alpha a^2+\frac1{4\alpha }b^2$ where $\alpha>0$, one gets 
$$
\underset{j\in \mathbb{Z}}{\sum}
\frac{p_{j+\frac12 }^{\eps}-p_{j}^{\eps}}{\eps}
\delta_{j }^+\left( u^{\eps}\right) 
= \sum_{j\in \mathbb{Z}} \frac{1}{\eps} (
u^{\eps}_j-u_{j+\frac12 }^{\eps})\delta_{j }^+\left( u^{\eps}\right) 
 -\frac{\sigma}{2\eps^2}
\sum_{j\in \mathbb{Z}}\Delta x_j 
u_{j+\frac12 }^{\eps}
\delta_{j }^+\left( u^{\eps}\right) 
$$
$$
\leq \alpha \sum_{j\in \mathbb{Z}}
\frac{(u_{j+\frac12 }^{\eps}-u_j^{\eps})^2}{\eps}
+
\left( \frac{1}{4\alpha\eps}+
\frac{\sigma}{2\eps^2}
\right)
\sum_{j\in \mathbb{Z}}
\delta_{j}^+\left(u^{\eps}\right)^2+
\frac\sigma{8\eps^2}
\sum_{j\in \mathbb{Z}}
\Delta x_j^2 \left( u_{j+\frac12 }^{\eps}\right)^2.
$$
Using this expression in $D_3$ and  using again Young's inequality, one gets for 
arbitrary  $\alpha>0$
\begin{eqnarray*}
 D_3 &\leq& \alpha \sum_{j\in \mathbb{Z}}
\frac{(u_{j+\frac12 }^{\eps}-u_j^{\eps})^2}{\eps} + \alpha \sum_{j\in
\mathbb{Z}} \frac{(u_{j-\frac12 }^{\eps}-u_j^{\eps})^2}{\eps} \\
&+&\sum_{j\in \mathbb{Z}} \bigg(
\left( \frac{1}{2\alpha\eps}+\frac{\sigma}{2\eps^2}\right)
\left( 
\delta_{j}^+\left(u^{\eps}\right)^2+
\delta_{j}^-\left(u^{\eps}\right)^2
\right)
+\frac{\delta_{j}^+\left(p^{\eps}\right)^2
+\delta_{j}^-\left(p^{\eps}\right)^2
}{2\eps\alpha} \bigg) \\
&+& \sum_{j\in \mathbb{Z}} \frac{1}{8\eps} \sigma \Delta x_j^2
\frac{(u_{j-\frac12 }^{\eps})^2 + (u_{j+\frac12 }^{\eps})^2}{\eps}+
\sum_{j\in \mathbb{Z}} \Delta x_j  \frac{\sigma}{\eps^2}
\frac{u_{j+\frac12 }^{\eps}+u_{j-\frac12 }^{\eps}}{2}\: \bigg(
\frac{1}{\Delta x_j} {\int_{x_{j-\frac12}}^{x_{j+\frac12}}}u^{\eps}(x) dx \bigg) \\
&-& \sum_{j\in \mathbb{Z}} u^{\eps}_j 
\frac{p^{\eps}(x_{j+\frac12 })-p^{\eps}(x_{j-\frac12 })}{\eps} -
\sum_{j\in \mathbb{Z}} p^{\eps}_j
\frac{u^{\eps}(x_{j+\frac12 })-u^{\eps}(x_{j-\frac12 })}{\eps}
\end{eqnarray*}
We now sum  all  bounds contributing to $\mathscr{E}'(t)$ and we get:
\begin{eqnarray*}
\mathscr{E}'(t)  & \leq & (-1+\alpha) \sum_{j\in \mathbb{Z}}
\frac{(u_{j+\frac12 }^{\eps}-u_j^{\eps})^2+(u_{j-\frac12 }^{\eps}-u_j^{
\eps})^2}{\eps} \\
&+&\sum_{j\in \mathbb{Z}} \bigg(
\left( \frac{1}{2\alpha\eps}+\frac{\sigma}{2\eps^2}\right)
\left ( \delta_{j}^+(u^{\eps})^2+\delta_{j}^-(u^{\eps})^2\right )
+\frac{\delta_{j}^+(p^{\eps})^2+\delta_{j}^-(p^{\eps}
)^2}{2\eps\alpha} \bigg) \\
&+& \sum_{j\in \mathbb{Z}} \frac{1}{8\eps} \sigma \Delta x_j^2
\frac{(u_{j-\frac12 }^{\eps})^2+ (u_{j+\frac12 }^{\eps})^2}{\eps}\\
&+& \sum_{j\in \mathbb{Z}} \Delta x_j  \frac{\sigma}{\eps^2}
\frac{u_{j+\frac12 }^{\eps}+u_{j-\frac12 }^{\eps}}{2}\: \bigg(
\frac{1}{\Delta x_j} {\int_{x_{j-\frac12}}^{x_{j+\frac12}}}
 u^{\eps}(x) dx \bigg) 
-\sum_{j\in \mathbb{Z}} \Delta x_j \frac{\sigma}{2\eps}
\frac{(u_{j-\frac12 }^{\eps})^2+(u_{j+\frac12 }^{\eps})^2}{\eps} \\
&+& \sum_{j\in \mathbb{Z}} \Delta x_j  \frac{\sigma}{\eps^2} u^{\eps}_j \:
\bigg( \frac{1}{\Delta x_j} {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg) -
\sum_{j\in \mathbb{Z}} \Delta x_j \frac{ \sigma  }{\eps^2} \: \bigg(
\frac{1}{\Delta x_j} {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} (u^{\eps})^2(x) dx \bigg).
\end{eqnarray*} 
We now examine
 the sum of all terms in the two last lines of the RHS of the above inequality , which we denote $S$. 
One finds
$$
S
=-
\sum_{j\in \mathbb{Z}} \Delta x_j \frac{\sigma}{2\eps^2}
\left[
{
\left(u_{j-\frac12 }^{\eps}-\frac{1}{\Delta x_j}
{\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx\right)^2+
\left(u_{j+\frac12 }^{\eps}
-\frac{1}{\Delta x_j} {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx
\right)^2}\right]
$$
$$
+\frac{\sigma}{2\eps^2} \sum_{j\in \mathbb{Z}}\bigg( 
{\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)\bigg( u_j^{\eps}-u_{j+\frac12 }^{\eps} +
u_j^{\eps}-u_{j-\frac12 }^{\eps}\bigg)
$$
$$ \leq \frac{\sigma}{2\eps^2} \sum_{j\in \mathbb{Z}}\bigg( 
{\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)\bigg( u_j^{\eps}-u_{j+\frac12 }^{\eps} +
u_j^{\eps}-u_{j-\frac12 }^{\eps}\bigg).
$$
Using another Young's inequality, one has for all $\widehat{\alpha}>0$
\begin{eqnarray*}
S \leq \frac{\sigma^2}{8\widehat{\alpha}\eps^3} \sum_{j\in \mathbb{Z}}\bigg(
{\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2+ \widehat{\alpha} \sum_{j\in
\mathbb{Z}} \frac{(u^{\eps}_j-u_{j+\frac12 }^{\eps})^2 +
(u^{\eps}_j-u_{j-\frac12 }^{\eps})^2}{\eps} .
\end{eqnarray*}
For example by choosing $\alpha=\frac12$ and $\widehat{\alpha}=\frac12$, and coming back to $\mathscr{E}'(t) $ we get
we obtain
\begin{eqnarray} \label{eq:eqn1}
\mathscr{E}'(t)  & \leq & \sum_{j\in \mathbb{Z}} \bigg(
\left( \frac{1}{\eps}+\frac{\sigma}{2\eps^2}\right)\left ( 
\delta_{j}^+(u^{\eps})^2+\delta_{j}^-(u^{\eps})^2\right )
+\frac{1}{\eps}\left (
\delta_{j}^+(p^{\eps})^2+\delta_{j}^-(p^{\eps}
)^2\right ) \bigg) \\
&+& \underset{j\in \mathbb{Z}}{\sum} \frac{1}{8\eps} \sigma \Delta x_j^2
\frac{(u_{j-\frac12 }^{\eps})^2+(
u_{j+\frac12 }^{\eps})^2}{\eps}+\frac{\sigma^2}{4\eps^3} \sum_{j\in
\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2.
\end{eqnarray} 
To estimate the contributions on the first line we use the following fact:
for any quantity $q$, one can use  $q(x_{j-\frac12})=q(x)+\int_x^{x_{j-\frac12}}\frac{d}{ds}q(s)ds$
 and integrate this
expression in the cell $\Delta x_j$; we
get $ \sum_{j\in \mathbb{Z}} \delta_{j}^\pm(q)^2\leq
h \| q \|_{H^1(\mathbb{R})}^2$. 
Therefore
the first terms on the right hand side of (\ref{eq:eqn1}) can be estimated as
$$
\left( \frac{1}{\eps}+\frac{\sigma}{2\eps^2}\right)
\int_0^t 
\sum_{j\in \mathbb{Z}} 
\left ( 
\delta_{j}^+(u^{\eps})^2+\delta_{j}^-(u^{\eps})^2\right )dt
\leq h \left( \frac{1}{\eps}+\frac{\sigma}{2\eps^2}\right)
\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) }.
$$

Since $\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) }\leq t \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$ and also 
$
\frac{\sigma}
{\eps^2}\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) }\leq  \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$
by (\ref{bee1} ) and (\ref{bee2} ), one gets that
\begin{equation} \label{eq:sm1}
\left( \frac{1}{\eps}+\frac{\sigma}{2\eps^2}\right)
\int_0^t 
\sum_{j\in \mathbb{Z}} 
\left ( 
\delta_{j}^+(u^{\eps})^2+\delta_{j}^-(u^{\eps})^2\right )dt
\leq  h  \left( \frac{t}\eps+\frac{1}{2}\right)
\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{equation}
A similar and simpler formula for the next terms is
\begin{equation} \label{eq:sm2}
 \frac{1}{\eps}\int_0^t 
 \sum_{j\in \mathbb{Z}} 
 \left (
\delta_{j}^+(p^{\eps})^2+\delta_{j}^-(p^{\eps}
)^2\right ) \leq   \frac{ h t}\eps 
\|  p^\eps  \|^2_{  H^1(\mathbb R) }
\leq     \frac{ h t}\eps 
\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{equation}
Next, using the assumption \eqref{geometrie1d} on the mesh and estimate \eqref{estiuepsflux}, one can find a constant $C\geq0$ such that the next term can be  bounded like 
\begin{equation} \label{eq:sm3}
 \int_0^T \underset{j\in \mathbb{Z}}{\sum} \frac{1}{8\eps} \sigma \Delta x_j^2
\frac{(u_{j-\frac12 }^{\eps})^2+(
u_{j+\frac12 }^{\eps})^2}{\eps} \leq C h \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2.
\end{equation}
Finally the last term in (\ref{eq:eqn1}) can be bounded using a
Cauchy-Schwarz inequality 
$$
\frac{\sigma^2}{4\eps^3} \sum_{j\in
\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2
\leq 
\frac{\sigma^2}{4\eps^3}
h \|  \mathbf u^\eps  \|^2_{  L^2(\mathbb R) }
$$
so that
\begin{equation} \label{eq:sm4}
\frac{\sigma^2}{4\eps^3} 
\int_0^t 
 \sum_{j\in
\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2
\leq 
\frac{\sigma^2}{4\eps^3}
h \|  \mathbf u^\eps  \|^2_{  L^2([0,t]\times \mathbb R) }
\leq 
\frac{\sigma}{4\eps}
h  \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2
\end{equation}
by means of the energy identity.
 So using (\ref{eq:sm1}-\ref{eq:sm4}) we obtain for all time $t\leq T$:
\begin{eqnarray*}
\mathscr{E}(t) \leq
\mathscr{E}(0)+h
\left( \frac{t}{\eps}+\frac{1}2 + \frac{t}{\eps}+C+\frac{\sigma
}{4\eps}\right)\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{eqnarray*}
The initialization stage is consistent so 
 $\mathscr{E}(0)\leq Ch^2\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$.
 Making use of the  initial remark \ref{sigmanotzero}, one   obtains 
\begin{equation*}\label{esti1}
\|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
\leq C(T) \sqrt{ \frac{h}{\eps}}
\| \V^{\eps}( 0)
\|_{H^1(\mathbb{R})}, \qquad C(T)\geq0.
\end{equation*}
The proof is ended.
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Study of $\| P_h^0 - P^0  \|$}

We  first 
 recall a fundamental   error estimate \cite{FV}
for the diffusion limit scheme, assuming smooth initial data.
\eqref{schemadifff}. 
\begin{proposition}\label{ds1d}
There exists a constant $C(T)>0$ such that
\begin{equation*}
\|\W_h^\eps-\W^\eps\|_{L^{\infty}([0,T];L^2(\mathbb{R}))} \leq
C(T)h \| \partial_{xxx}p_0 \|_{L^2(\mathbb{R})  }.
\end{equation*}
\end{proposition}

\begin{proof}
We  use the method of Gallouet and al \cite{FV}, which
is based on  a notion of consistency for finite volumes schemes.
We set
$$
s_j=\partial_{xx}p(x_j)-\frac{\partial_xp(x_{j+\frac12}  )
-
\partial_xp(x_{j-\frac12}  )
}{\Delta x_j}
\mbox{ and }
r_{j+\frac12}=\partial_{x}p(x_{j+\frac12})-\frac{p(x_{j+1}  )
-
p(x_{j}  )
}{\Delta x_{j+\frac12}},
$$
so that one has the identity
$$
 \frac{d}{dt} p(x_j)
-\frac{1}{\sigma\Delta x_j}\bigg(\frac{p(x_{j+1})-p(x_{j})}{\Delta
x_{j+\frac12 }}-\frac{p(x_{j})-p(x_{j-1})}{\Delta
x_{j-\frac12 }}\bigg)=
\frac{s_j}\sigma+
\frac{r_{j+\frac12}-r_{j-\frac12}}{\sigma \Delta x_j}.
$$
We next  introduce the difference
$e_j=p(x_j)-p_j$ which satisfies
$$
 \frac{d}{dt} e_j
-\frac{1}{\sigma\Delta x_j}\bigg(\frac{e_{j+1}-e_{j}}{\Delta
x_{j+\frac12 }}-\frac{e_{j}-e_{j-1}}{\Delta
x_{j-\frac12 }}\bigg)=
\frac{s_j}\sigma+
\frac{r_{j+\frac12}-r_{j-\frac12}}{\sigma \Delta x_j}
$$
with $e_j(0)=0$ for all $j$.
By multiplying this equation by $e_j$
and  denoting by $\|e_h\|_{L^2(\mathbb{R})}^2= \sum_j \Delta x_je_j^2$,
one finds that 
\begin{equation*}\label{fgfg}
\frac12 \frac{d}{dt}\|e_h\|_{L^2(\mathbb{R})}^2 +\frac{1}{\sigma} \sum_j
\frac{(e_{j+1}-e_{j})^2}{\Delta
x_{j+\frac12 }}=
\sigma^{-1}\sum_j \Delta x_j s_j e_j+\sigma^{-1}\sum_jr_{j+\frac12 }(e_j-e_{j+1}).
\end{equation*}
The Cauchy-Schwarz inequality yields 
\begin{equation*}
\sum_jr_{j+\frac12 }(e_j-e_{j+1})\leq \frac{1}{2} \sum_j
\frac{(e_{j+1}-e_{j})^2}{\Delta x_{j+\frac12 }}+\frac{1}{2}\sum_j\Delta
x_{j+\frac12 }r_{j+\frac12 }^2.
\end{equation*}
One finds out with natural notations
\begin{equation} \label{eq:eee}
\frac12 \frac{d}{dt} \|e_h\|_{L^2(\mathbb{R})}^2+
\frac{1}{2 \sigma} \sum_j
\frac{(e_{j+1}-e_{j})^2}{\Delta x_{j+\frac12 }}\leq
\sigma^{-1}\| s_h\|_{L^2(\mathbb{R})} \|e_h\|_{L^2(\mathbb{R})}+
\frac12 \|r_h\|^2_{L^2(\mathbb{R})}.
\end{equation}
Using the  definitions of  the truncation errors $s_h$ and $r_h$, these
quantites can be   
bounded independently of the time of observation $T$ 
\begin{equation} \label{eq:bsr}
\|s_h\|_{L^2([0,T]\times\mathbb{R})}+
\|r_h\|_{L^2([0,T]\times\mathbb{R})}  \leq C h \bigg(
 \|\partial_{xxx}p_0   \| _{L^2(\mathbb{R})}+\|\partial_{xx}p_0\| _{L^2(\mathbb{R})} \bigg).
\end{equation}
Rescaling  for convenience $\widehat s_h=\frac1hs_h$ for any quantity
$s$, one gets the bound
$$
\frac12 \frac{d}{dt} \|\widehat e_h\|_{L^2(\mathbb{R})}^2
\leq
\| \widehat s_h\|_{L^2(\mathbb{R})} \|\widehat e_h\|_{L^2(\mathbb{R})}+
\frac{1}{2\sigma} \|\widehat r_h\|^2_{L^2(\mathbb{R})}
\leq
\frac12
\left(\| \widehat s_h\|_{L^2(\mathbb{R})}^2+ \frac{1}{\sigma} \|\widehat r_h\|^2_{L^2(\mathbb{R})}  \right)+\frac12 
 \|\widehat e_h\|^2_{L^2(\mathbb{R})}
$$
where the term in parenthesis is bounded due to (\ref{eq:bsr}).
The Gronwall's inequality guarantees the boundedness of
$\|\widehat e_h\|_{L^2(\mathbb{R})}$ at any time.
Therefore
\begin{equation} \label{eq:e2}
\| e_h\|_{L^\infty([0,T];\mathbb{R})}\leq C(T) h 
\left(  \|\partial_{xx}p_0   \| _{L^2(\mathbb{R})}+
 \|\partial_{xxx}p_0   \| _{L^2(\mathbb{R})}
\right).
\end{equation}
The other term 
that we consider  is
$
f_h=\eps\left(v(x_j)-v_j    \right)_{j\in \mathbb Z}=-\eps
\left(\frac{\partial_x p(x_j)}{\sigma}- v_j  \right)_{j\in \mathbb Z}$.
We notice that (\ref{eq:eee}) and (\ref{eq:e2}) yields
$$
\left\| 
\frac{e_{j+1}-e_{j}}{\Delta x_{j+\frac12 }} \right\|_{
L^2([0,T]\times\mathbb{R})
}
\leq C(T) h 
\left(  \|\partial_{xx}p_0   \| _{L^2(\mathbb{R})}+
 \|\partial_{xxx}p_0   \| _{L^2(\mathbb{R})}
\right)
$$
which implies after some  manipulations
$$
\left\| 
\frac{p_{j+1}-p_{j}}{\Delta x_{j+\frac12 }} -\partial_x p (x_{j+\frac12}) \right\|_{
L^2([0,T]\times\mathbb{R})
}
\leq C(T) h 
\left(  \|\partial_{xx}p_0   \| _{L^2(\mathbb{R})}+
 \|\partial_{xxx}p_0   \| _{L^2(\mathbb{R})}
\right).
$$
The definition (\ref{eq:vv}) of $v_j$ 
implies 
the bound
\begin{equation} \label{eq:f2}
\|f_h\|_{
L^2([0,T]\times\mathbb{R})
}\leq C(T) h \eps \left(  \|\partial_{xx}p_0   \| _{L^2(\mathbb{R})}+
 \|\partial_{xxx}p_0   \| _{L^2(\mathbb{R})}
\right).
\end{equation}
Finally, 
$\|\W_h^\eps-\W^\eps\|_{L^2([0,T]\times\mathbb{R})}^2=
\|e_h\|_{L^2([0,T]\times\mathbb{R})}^2+\|f_h\|_{L^2([0,T]\times\mathbb{R
})}^2
$ 
is bounded using (\ref{eq:e2}) and (\ref{eq:f2}).
It ends the proof.
\end{proof}

\subsection{Study of $\| P_h^\varepsilon - P^0_h  \|$}

In this section we 
 prove an error estimate between the solution of the
scheme \eqref{schema} and the solution of the diffusion scheme
\eqref{schemadifff}.
It is necessary  to use some comparison
estimates between the initial data of $P_h^\eps$ and $P_h^0$.

\begin{proposition} \label{gttods}
There exists a constant $C(T)>0$ such that the following estimate holds
\begin{equation*}
\|\V_h^{\eps}-\W^\eps_h\|_{L^2([0,T]\times\mathbb R)} \leq
C(T)  \eps.
\end{equation*}
\end{proposition}
\begin{proof}
We define $R_j$ and $S_{j+\frac12 }$ such that the solution of
\eqref{schemadifff} satisfies the various relations 
which are generalizations of (\ref{schema}) and (\ref{eq:vv}) 
 \begin{equation}\label{schemadiff3}
\left\{
\begin{array}{lll}
\displaystyle 
\Delta x_j\frac{d}{dt} p_j
+\frac{u_{j+\frac12 }-u_{j-\frac12 }}{\eps }=0,\\
\\
\displaystyle 
\Delta x_j\frac{d}{dt} u_j
-\frac{u_{j+\frac12 }+u_{j-\frac12 }}{\eps}+\frac{2}{\eps }u_j=\Delta x_j R_j,\\
\\
\displaystyle 
p_j-p_{j+1}+u_j+u_{j+1} =2u_{j+\frac12 } +\sigma \Delta x_{j+\frac12 }
\frac{u_{j+\frac12 } }{\eps}+\Delta x_{j+\frac12}S_{j+\frac12 } , \\
\displaystyle 
u_{j+\frac12}= -\frac\eps\sigma \frac{p_{j+1}-p_j}{\Delta x_{j+\frac12}}, \\
\displaystyle 
u_j=\frac{u_{j+\frac12}+u_{j-\frac12}}{2}.
\end{array}
\right.
\end{equation}
A simple computation using the  last two identities
yields
\begin{equation*}
R_j= \frac{d}{dt} u_j
\mbox{ and }
S_{j+\frac12 }= \frac1{\Delta x_{j+\frac12} }\left(
u_j+u_{j+1} -2u_{j+\frac12 }\right).
\end{equation*}
Thanks to the estimate \eqref{l2} and as the scheme is linear, $\frac{d}{dt} u_j$
satisfies the estimate 
$$
\|R\|_{L^2([0,T]\times \mathbb{R})}=\bigg\|\frac{d}{dt} u_j\bigg\|_{L^2([0,T]\times \mathbb{R})}\leq
C\eps\bigg\|\frac{d}{dt} p_h(0)\bigg\|_{L^2(\mathbb{R})}.
$$
The definition of $\dt p_h(0)$ is from (\ref{schemadifff}-\ref{eq:intip0}),
which
implies that $\|\frac{d}{dt} p_h(0)\|_{L^2(\mathbb{R})}\leq C 
\| p(t=0)\|_{H^2(\mathbb{R})}$. So one has the bound
\begin{equation} \label{eq:p5}
\|R\|_{L^2([0,T]\times \mathbb{R})}\leq C \eps
\| p(0)\|_{H^2(\mathbb{R})}.
\end{equation}
It is seen in proposition \ref{pro:H1}
that 
\begin{equation}\label{eq:xx}
\| S\|_{L^2(\mathbb{R})} \leq \eps  
\| p(0)\|_{H^2(\mathbb{R})}.
\end{equation}
We now introduce the differences
\begin{equation*}
e_j= p_j-p_{j}^{\eps} ,\quad
f_j = u_j-u_j^{\eps} \mbox{ and }
f_{j+\frac12 }= u_{j+\frac12 }-u_{j+\frac12 }^{\eps}.
\end{equation*}
Let us  look at the difference between the scheme \eqref{schema} and
\eqref{schemadiff3}. We get
\begin{equation*}\label{diff222}
\left\{
\begin{array}{lll}
\Delta x_j\frac{d}{dt} e_j
+\frac{f_{j+\frac12 }-f_{j-\frac12 }}{\eps}=0,\\
\\
\Delta x_j\frac{d}{dt} f_j
-\frac{f_{j+\frac12 }+f_{j-\frac12 }}{\eps}+\frac{2}{\eps}f_j=
\Delta x_j
R_j,\\
\\
e_j-e_{j+1}+f_j+f_{j+1} -2f_{j+\frac12 } -\sigma \Delta x_{j+\frac12 }
\frac{f_{j+\frac12 } }{\eps}=\Delta x_{j+\frac12}S_{j+\frac12 } .
\end{array}
\right.
\end{equation*}
We use the notation
$\|\V_h^{\eps}-\W^\eps_h\|_{L^2(\mathbb R)}^2=\sum_j \Delta x_j
(e_j^2+f_j^2)$.
Using the same kind of proof than for the $L^2$ stability of 
proposition \ref{prodentrgosse}, one gets that
\begin{eqnarray*}
\frac12 \frac{d}{dt}\|\V_h^{\eps}-\W^\eps_h\|_{L^2(\mathbb R)}
^2 \leq \sum_j \Delta x_j R_jf_j -\sum_j\Delta x_{j+\frac12}
\frac{f_{j+\frac12 }}{\eps}S_{j+\frac12 }
-\frac{\sigma}{\eps^2}\sum_{j\in \mathbb{Z}} \Delta
x_{j+\frac12}f_{j+\frac12 }^2.
\end{eqnarray*}
Using a Young's inequality on the second 
term of the right side of this inequality,
one finds out that 
\begin{eqnarray*}
\frac12 \frac{d}{dt}\|\V_h^{\eps}-\W^\eps_h\|_{L^2(\mathbb R)}
^2 \leq \sum_j \Delta x_j R_jf_j  +
\frac1{4\sigma  }
\sum_j \Delta x_{j+\frac12} 
{S_{j+\frac12 }^2}
.
\end{eqnarray*}
Using the Cauchy-Schwarz inequality, we thus have
\begin{eqnarray*}
\frac12 \frac{d}{dt}\|\V_h^{\eps}-\W^\eps_h\|_{L^2(\mathbb R)}
^2 \leq \frac12 \|\V_h^{\eps}-\W^\eps_h\|_{L^2(\mathbb R)}^2 +
C\bigg( \| R\|_{L^2(\mathbb R)}^2 +\| S \|_{L^2(\mathbb R)}^2\bigg).
\end{eqnarray*}
Integrating between 0 and t and using a Gronwall's inequality, one finds
for $t\leq T$
\begin{equation*}
\|\V_h^{\eps}(t)-\W^\eps_h(t)\|_{L^2(\mathbb R)}^2 \leq 
\exp(t) \left( \|\V_h^{\eps}(0)-\W^\eps_h(0)\|_{L^2(\mathbb R)}^2 
+ C (
 \| R\|_{L^2([0,T]\times\mathbb R)}^2 + \|
S\|_{L^2([0,T]\times\mathbb R)}^2
) \right)
\end{equation*}
Finally, using the previous estimates (\ref{eq:p5}-\ref{eq:xx})
and the well-preparedness of the data (\ref{eq:initp1},\ref{eq:intip0},\ref{init_1D}), one gets
$
\|\V_h^{\eps}-\W^\eps_h\|_{L^2([0,T]\times\mathbb{R})} \leq C(T) \eps$. 
The proof is ended.
\end{proof}

\begin{proposition}\label{pro:H1}
The bound (\ref{eq:xx}) holds.
\end{proposition}

\begin{proof}

Using the definition of $u_j$
and $u_{j+\frac12 }$, one has 
$$
S_{j+\frac12 }=\frac{\eps}{2}\left( \frac{ \Delta x_j}{\Delta x_{j+\frac12}}
\frac{d}{dt} p_j - \frac{\Delta x_{j+1}}{\Delta x_{j+\frac12}} \frac{d}{dt} p_{j+1} \right)
$$
 at all time.
Moreover, $z_h=\frac{d}{dt} p_h$ is solution of
$P_h^0$:
$$
\Delta x_j\frac{d}{dt} z_j -\frac{1}{\sigma } \bigg(
\frac{z_{j+1}-z_j}{\Delta x_{j+\frac12 }}-\frac{z_j -z_{j-1}}{\Delta
x_{j-\frac12 }}\bigg)=0,
$$
with initial condition
\begin{equation}\label{eq:zz}
z_j(0)=\frac{d}{dt} p_0(x_j)=
\frac1 {\Delta x_j \sigma } \bigg(
\frac{p_0(x_{j+1})-p_0(x_j)}{\Delta x_{j+\frac12 }}-\frac{p_0(x_j)
 -p_0(x_{j-1}  )}{\Delta
x_{j-\frac12 }}\bigg).
\end{equation}
One gets from a Taylor expansion with integral residue
that
$$
\left|
\frac{p_0( x_{j+1}) -p_0(x_j)}{\Delta x_{j+\frac12 }}- 
\partial_x p _0(x_j)
\right|\leq 
 \int_{x_j}^{x_{j+1}  } \left|\partial_{xx}p_0(y)   \right| dy .$$ 
Similarly one has the bound
$
\left|
 \frac{p_0( x_{j}) -p_0(x_{j-1})}{\Delta x_{j+\frac12 }}-
\partial_x p _0(x_j)\right|
\leq
 \int_{x_{j-1}}^{x_{j}  } \left|\partial_{xx}p_0(y)   \right| dy $.
Therefore $|z_j(0)|\leq
\frac1 {\Delta x_j \sigma }  \int_{x_{j-1}}^{x_{j+1}  } \left|\partial_{xx}p_0(y)  
 \right| dy $ from which the bound
$
\sqrt{ \sum_j \Delta x_j z_j^2(0) }
\leq \sigma^{-1}\|p_0\|_{H^2(\mathbb{R})}$
is deduced.
Since the scheme $P_h^0$ being stable in $L^2$, this bound is true at any time.
Considering (\ref{eq:zz}) the discrete second derivative
attached to $P_h^0$ is bounded at any time, which ends the proof
of the claim.
\end{proof}

\subsection{End of the proof of uniform AP property}

\begin{theorem} \label{theor:1d}
Assuming a sufficiently smooth well prepared initial data,
the scheme $P_h^\eps$ converges to $P^\eps$ at order at least 
$\frac13$ in $L^2([0,T]\times \mathbb{R}   )$, uniformly with respect to $\eps$
\end{theorem}
\begin{proof}
All the previous estimates
show that (\ref{eq:mod3}-\ref{eq:mod4})  are true
with
$a=1$, $b=c=\frac12$ and $d=1$.
Moreover $\|P_h^\varepsilon-P_h^0  \|\leq C(T) \eps $
by proposition (\ref{gttods}) which means this term has the same
scaling as $\|P^\varepsilon-P^0  \|\approx C(T) \eps$.
So it can be  incorporated 
in  estimate (\ref{eq:mod3}) with $a=1$.
Using the general
method described at the beginning of this work in proposition \ref{prop:1}, 
one  obtains the convergence
estimate of convergence
$
\|\mathbf V_h^\eps -\mathbf V^\eps   \|_{L^2([0,T]\times \mathbb{R}   )  }
\leq C(T) h^{ q }
$
with the order of convergence
$
q=\frac{ac}{a+b}=\frac13$.
\end{proof} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The 2D case}

In this section we prove the uniform 
convergence of the solution of the diffusion
AP 
 scheme introduced in \cite{glaceap} to the solution
of the hyperbolic heat equation.
The structure of our proof  
is globally the same
as in the previous section. However two major  difficulties
will be treated: a) the first one 
consists in  the adaptation to our problem
 of a  combination of specific finite volumes 
techniques for hyperbolic and parabolic equations;
b) the second one is to derive new bounds for the scheme $\mathbf{DA}_h^\eps$.

The model problem is the hyperbolic heat equation in the domain
$\Omega= ]0,1[^2$
with periodic boundary conditions and  well-prepared data
\begin{equation*}\label{HHE!}
\mathbf P^\eps: \qquad 
\left\{\begin{array}{l}
\ds\partial_t p^{\eps}+\frac{1}{\eps}\operatorname{div}(\uu^{\eps})=0,\\
\\
\ds\partial_t \uu^{\eps}+\frac{1}{\eps}\nabla
p^{\eps}=-\frac{\sigma}{\eps^2}\uu^{\eps},\\
\\
p^{\eps}(t=0)=p_0\mbox{,  }\uu^{\eps}(t=0)=\uu^{\eps}_0=
-\frac{\eps}\sigma
\nabla p_0.
 \end{array}\right.
\end{equation*}
When $\eps$ tends to zero,
this problem  admits the following diffusion  limit
\begin{equation*}\label{HHE!lim}
\mathbf P^0: \qquad
\ds\partial_t p-\frac{1}{\sigma}\operatorname{div}(\nabla{p})=0
, \qquad 
p(t=0)=p_0.  
\end{equation*}
The rescaled gradient is 
$
\mathbf v=-\frac{1}{\sigma} \nabla{p}$.
We will admit the following proposition, the proof of which can be easily obtained 
by a method similar to the one of proposition
\ref{heqtode}.

\begin{proposition}\label{heqtode2d}
The error between the two solutions
can be  upper bounded by
\begin{equation}\label{ine3}
| p^\epsilon-p\|_{   L^\infty([0,T];H^n(\Omega))  }+
\| \uu^\eps 
 \|_{   L^\infty([0,T]; H^n(\Omega))  }
 \leq
C \eps
\|p_0 \|_{H^{3+n}(\Omega)},
\qquad n \in \mathbb N.
\end{equation}
\end{proposition}
\begin{proof}
The structure of the 
proof in the $L^\infty( [0,T];L^2(\Omega))$ norm is the same as the one
of proposition \ref{heqtode}.
Since the coefficients of the problem are constant, similar bounds are obtained
at any order of derivation which proves the estimate for any $n>0$.
\end{proof}

\subsection{Definition of $\mathbf P_h^\eps$}

Let us consider an unstructured mesh in dimension 2. The mesh is defined
by a finite number of vertices $\xr$ and cells $\Omega_{j}$. We
denote $\xj$ a point  chosen arbitrarily inside $\Omega_j$.
For simplicity we will call this point the center of the cell.
 By convention the vertices
are listed counter-clockwise $\x_{r-1},\xr,\x_{r+1}$
with
coordinates $\xr=(x_{r},y_{r})$. 
We note  $l_{jr}\njr$ the vector as follows
\begin{equation}\label{eq:not}
l_{jr}=\frac12 \mbox{dist}\left( \x_{r-1},\x_{r+1}\right) 
\mbox{ and }
\njr=\frac{1}{2l_{jr}}\left(
\x_{r+1}-\x_{r-1}
\right)^\perp.
\end{equation}
This notion of a corner vector can be done also in any dimension
using the abstract definition \cite{de10}.
The scalar product of two vectors is denoted as
$(\x,\mathbf{y})$.

\begin{figure}[ht!]
\begin{center}
\scalebox{0.7}{\includegraphics{atoc.pdf}}
\end{center}

\caption{Notation for node formulation. The corner length $l_{jr}$ 
and the corner normal $\njr$ are defined in equation (\ref{eq:not}).
The point $\x_j$ is an arbitrary point inside the cell, typically
the centroid of the cell or an averaged of the corners.
}
\end{figure}

The numerical approximation  
 of the problem  $\mathbf P^\eps$ that we study 
 is the JL-(b) scheme defined
in   \cite{glaceap}
\begin{equation}\label{eq:4}
\mathbf P_h^\eps:
\qquad \left\{ 
\begin{array}{l}
\displaystyle \mid\Omega_{j}\mid\frac{d}{dt} p_{j}^{\eps}+\frac{1}{\varepsilon}
\sum_{r}(l_{jr}\ur^{\eps},\njr)=0\\
\displaystyle \mid
\Omega_{j}\mid\frac{d}{dt}\uj^{\eps}+\frac{1}{\varepsilon}
\sum_{r} l_{jr} \njr    p_{jr}^{\eps}=-\frac{\sigma}{\varepsilon^{2}}\sum_{r}\widehat{
\beta}_{jr}\ur^{\eps},
\end{array}
\right.
\end{equation}
with initial data $p_j^{\eps}(0)=p_0(\mathbf{x}_j)$ and $\mathbf{u}_j^{\eps}(0) = -\eps\sigma^{-1}\nabla p_0(\mathbf{x}_j)$.
The fluxes are defined by the so-called 
corner problem 
\begin{equation}\label{eq:5}
\left\{ \begin{array}{l}
\displaystyle 
p_{jr}^{\eps}-p_j^\eps=
\njr,    \uj^{\eps}-\ur^{\eps}
)-\frac{\sigma}{\varepsilon}( \xr -\xj, \ur^{\eps}), 
\\
\sum_{j}\ljr
p_{jr}^{\eps}\njr=0.
 \end{array}\right.
\end{equation}
This corner problem has been introduced in 
\cite{glaceap} as a multidimensional version
of the 1D Jin-Levermore technique   \cite{jinlev}.
Its solution is provided by the solution
of the  linear system
\begin{equation*} \label{eq:5bis}
\displaystyle \left( \sum_{j}\alj+ 
\sum_{j}\frac{\sigma}{\varepsilon}\bej\right)\ur^{
\eps}= \sum_{j}\ljr
p_j^{\eps}\njr+\sum_j\alj\uj^{\eps},
\end{equation*}
 where the geometry of the mesh serves to define the  
  matrices  
$\alj$ and $\bej$ 
\begin{equation}\label{eq:6}
\alj=\ljr\njr\otimes\njr,\mbox{ and
}\bej=\ljr\njr\otimes(\xr-\xj) .
\end{equation}
We will use the notations
$A_j=\sum_r\alj$, $A_r=\sum_j\alj$ and
$B_r=\sum_j\bej$. 
By comparison with the scheme $P_h^\eps$ in dimension one, one see at once
that the multi-dimensional scheme (\ref{eq:4}-\ref{eq:6})  is  more 
tricky than the 1D scheme (\ref{schema1}-\ref{eq:fflux}).

Starting from (\ref{eq:4}) and taking into account of the definitions of
the fluxes (\ref{eq:5}) and also the identity $\sum_r l_{jr} \njr=0$,
the scheme $\mathbf P_h^\eps$ can also be rewritten as
\begin{equation}\label{eq:4bis}
\mathbf P_h^\eps:
\qquad
\left\{ 
\begin{array}{l}
\displaystyle \mid\Omega_{j}\mid\frac{d}{dt} p_{j}^{\eps}+\frac{1}{\varepsilon}
\sum_{r}(l_{jr}\ur^{\eps},\njr)=0\\
\displaystyle \mid
\Omega_{j}\mid\frac{d}{dt}\uj^{\eps}+\frac{1}{\varepsilon}
\sum_{r}l_{jr} (\njr,\uu_r^{\eps} -\uu_j^{\eps})\njr=0
\end{array}
\right.
\end{equation}
When $\eps \rightarrow 0$
the scheme $\mathbf P_h^\eps$ admits the limit diffusion scheme 
$\mathbf P_h^0$ 
\begin{equation}\label{diffglace}
\mathbf P_h^0:
\qquad\left\{ \begin{array}{l}
\displaystyle \left| \Omega_j 
\right| \frac{d}{dt} p_j+ 
\sum_{r} l_{jr}\bigg( 
\vv_r,\njr\bigg)=0,\\
\displaystyle \vv_r=\frac{1}{\sigma} B_r^{-1}
\sum_{j}l_{jr}p_j\njr,
\end{array}\right.
\end{equation}
with $B_r=\sum_{j}l_{jr}\njr\otimes(\xr-\xj)$.
We  define additionally $\vv_j$ by a kind of mean
$$
\left( \sum_r \alj \right) \vv_j=\sum_r \alj
\vv_r.
$$
This is well defined since the matrix
$\sum_r \alj$ is  symetric positive by definition of the $\alj$.

\subsection{Definition of $\mathbf{DA}_h^\eps$}

We define now that is  call thereafter the "diffusion approximation" 
scheme.
We just neglect the time derivative
in the second equation, that we make
 $\partial_t\uj^{\eps}=0$ for (\ref{eq:4bis}). It
leads to the scheme
\begin{equation}\label{das}
\mathbf{DA}_h^\eps:
\quad
\left\{ 
\begin{array}{l}
\displaystyle \mid\Omega_{j}\mid\frac{d}{dt} p_{j}^{\eps}+\frac{1}{\varepsilon}
\sum_{r}(l_{jr}\ur^{\eps},\njr)=0\\
\frac{1}{\varepsilon} \sum_{r}l_{jr} (\njr,\uu_r^{\eps} -\uu_j^{\eps})\njr=0\\
\displaystyle \left( \sum_{j}\alj+ 
\sum_{j}\frac{\sigma}{\varepsilon}\bej\right)\ur^{
\eps}= \sum_{j}\ljr
p_j^{\eps}\njr+\sum_j\alj\uj^{\eps}
\end{array}
\right.
\end{equation}
This  scheme depends of
two parameters, the size of the mesh $h$ and the small parameter 
$\eps$.
We notice that
$\mathbf{DA}_h^\eps\neq \mathbf P_h^0$ for $\eps> 0$, and that 
$\lim_{\eps\rightarrow 0^+} \mathbf{DA}_h^\eps = \mathbf P_h^0$.
The initial data for \eqref{das} is $p_j^{\eps}(0)=p_0(\mathbf{x}_j)$. There is no 
need of initial data for $(u_j^{\eps}(0))$, which will be obtained 
 as a function of $(p_j^{\eps}(0))$ by solving a linear system.

\subsection{Mesh assumptions}

 \begin{figure}[h!]
 \begin{center}
 \scalebox{0.8}{\includegraphics{vr.pdf}}
 \end{center}
 \caption{Definition of the control volume $V_r$ around
 vertex $\mathbf{x}_r$.
 The control volume  around the vertex $\mathbf{x}_r$
 is defined by the closed loop
 that joins the center of the cells ($\mathbf{x}_j$'s) and the middle
 of the edges ($\mathbf{x}_{j+\frac12}$'s).}
 \label{figcv}
 \end{figure}

The characteristic length of the mesh is 
\begin{equation*} \label{eq:d6}
h=\max_j \left( \mbox{diam}(\Omega_j)  \right).
\end{equation*}
By definition  there exists  a constant $C>0$ such that 
\begin{equation} \label{eq:d7}
l_{jr}\leq Ch , \qquad \forall j,r.
\end{equation}
The control volume $V_r$ 
around the vertex $\mathbf x_r$ is 
defined by the closed loop
$
\dots, \mathbf{x}_{j-\frac12}, \mathbf{x}_j,\mathbf{x}_{j+\frac12},\dots$.
Here  the $\mathbf{x}_j$'s are the center of the cells, and the 
$\mathbf{x}_{j+\frac12}$'s are the middle of the edges around the vertices
$\mathbf{x}_r$.
A typical example is depicted in  figure \ref{figcv}.

Additional geometrical assumptions are always
necessary in dimension greater than one to guarantee
some minimal regularity of the mesh.
We make  the usual assumptions
 listed below from 1 to 3.
The two last items are more specific.

\begin{hyp}\label{geometrie}
Our geometrical assumptions  will be the following
\begin{enumerate}
\item The mesh is regular in the sense that
there are
two constants $C_1,C_2>0$ such that
\begin{equation} \label{eq:d5}
C_1 h^2 \leq \left| \Omega_j \right| \leq C_2 h^2, \quad \forall j\qquad
\mbox{ uniformly with respect to  }h.
\end{equation}
and that 
\begin{equation} \label{eq:d5.2}
C_1 h^2 \leq \vert V_r \vert \leq C_2 h^2, \quad \forall r\qquad
\mbox{ uniformly with respect to  }h.
\end{equation}
We recall that $V_r$ is the volume control (centered on $\x_r$) and $\Omega_j$
is the cell $j$.
\item The numbers of cells which share  a node $r$ is
bounded independently of $h$, which means there exists 
$P\in \mathbb N$ independent of $h$ such that
\begin{equation}\label{nbmr} 
\sum_j \delta_{jr}\leq P.
\end{equation}
For example, for a structured mesh of quadrangular cells $P=4$.

 \item For  each cell of the mesh, the  number of edges is
bounded independently of $h$, or equivalently the numbers of vertices for a cell
 is bounded independently of $h$.

\item 
A consequence of the items 1-3 
is that there exists 
 a constant
$\beta >0 $ such that 
\begin{equation}\label{geom4}
(A_j\uu, \uu)\geq \beta h (\uu,\uu).
\end{equation}
It can be proved with a geometrical  identity that we borrow
 from \cite{de10}  (proposition 8).

\item  The matrix $B_r$ is positive and that there exists a
constant $\alpha >0 $ independent of r such that 
\begin{equation}\label{geom3}
(B_r \uu, \uu)=(B^s_r \uu, \uu)\geq \alpha \vert
V_r\vert (\uu,\uu)
\end{equation}
where $B^s_r=\frac12 (B_r+B_r^t)$ is the symmetric part of $B_r$.
Square meshes satisfy (\ref{geom3}).
This assumption is however not trivial to check in the general case.
We point out  \cite{glaceap} where
 sufficient conditions such that (\ref{geom3}) is satisfied
can be found; in particular it is shown 
that  triangular meshes with all angles greater than $12$ degrees
satisfy it. 
\end{enumerate}
\end{hyp}

We  use the convention that the quadratic norm
of any cell centered quantity $f=(f_j)_{j\in {\rm Cells}}$ is
$\|f\|_{L^2(\Omega)}=\sqrt{\sum_j |\Omega_j| |f_j|^2   }$, while the quadratic
norm of any vertex based quantity $g=(g_r)_{r\in {\rm Vertices}}$ is
$\|g\|_{L^2(\Omega)}=\sqrt{\sum_r |V_r| |g_r|^2   }$.
Useful  quantities  are
\begin{itemize}
\item $\mathbf V_h^\eps=\left(p^\eps_j, \uu^\eps_j \right)_
{j\in {\rm Cells}}$ is the solution of $\mathbf P_h^\eps$.
\item 
$\mathbf V^\eps=\left(p^\eps(\x_j), \uu^\eps(\x_j)  \right)_
{j\in {\rm Cells}}$ is the solution of $\mathbf P^\eps$,
\item $\mathbf W_h^\eps=\left(p^\eps_j, \uu^\eps_j \right)_
{j\in {\rm Cells}}$ is the solution of $\mathbf{DA}_h^\eps$.
Notice that an abuse of notations is been made with the solution
of $\mathbf P_h^\eps$.
\item $\mathbf W^\eps= \left(p(\x_j),-\frac\eps\sigma \nabla p(\x_j)  \right)_
{j\in {\rm Cells}} $ is the solution of $\mathbf P^0$.
\end{itemize}
With these notations,  (\ref{ine3}) is rewritten as
\begin{equation} \label{eq:enc22}
\|\W^\eps-\mathbf V^\eps\|
_{ L^2([0,T]\times L^2(\Omega)   ) } \leq C \eps.
\end{equation}

\subsection{Study of $\| \mathbf 
P_h^\varepsilon -\mathbf P^\varepsilon \|_{\rm naive}$}

In this part, we exploit the hyperbolic nature
of both 
$\mathbf P^\varepsilon$ and $\mathbf P_h^\varepsilon $.
We first prove the $L^{2}$ stability of  the scheme JL-(b) defined 
in (\ref{eq:4},\ref{eq:5}).

\begin{pro}[Stability] \label{propesti} Under the geometrical assumption (\ref{geom3}), the
semi-discrete general JL-(b) scheme defined by (\ref{eq:4},\ref{eq:5})  is
stable in the $L^2$ norm in the sense that $\frac{d}{dt}
 \vert\vert \V^{\eps}_{h}(t)
\vert\vert \leq 0$.
 Moreover we have the bounds
\begin{equation}\label{gggg}
\frac{\sigma}{\eps^2}\vert\vert \uu_r^{\eps} \vert\vert_{L^2([0,T]\times \Omega)}\leq
C 
\vert\vert
V^{\eps}_h(0)\vert\vert_{L^2( \Omega)}, \qquad C>0,
\end{equation}
\begin{equation}\label{gs}
\int_0^T\sum_j \sum_r
l_{jr}(\njr,(\uj^\eps-\ur^\eps))^{2} dt\leq C  \eps \vert\vert
\mathbf V^{\eps}_h(0)\vert\vert^2_{L^2( \Omega)}. 
\qquad C>0.
\end{equation}
\end{pro}

\begin{proof}
We define the functions $p^{\eps}_h$ and $\uu^{\eps}_h$  by
$p^{\eps}_h=p_j$ and $\uu^{\eps}_h=\uj$  on $\Omega_j$.
We set for convenience $E(t)= \vert\vert \V^{\eps}_{h}(t)
\vert\vert^2$.
 One has
$$
E^{'}(t)=\displaystyle \frac12  \int_{\Omega} \frac{d}{dt}( \mid
p^{\eps}_{h} \mid^{2}+
(\uu^{\eps}_{h},\uu^{\eps}_{h}))=\int_{\Omega}
p^{\eps}_{h}\frac{d}{dt}p^{\eps}_{h}+(\uu^{\eps}_{h},\frac{d}{dt
}\uu^{\eps}_{h})
=\displaystyle \sum_{j} \left| \Omega_j \right|
p_{j}^{\eps}\frac{d}{dt} p_{j}^{\eps}+(\uj^{\eps},\frac{d}{dt}\uj^{\eps}).
$$
Using the definition of scheme 
\begin{equation}\label{eq:ds1}
\displaystyle E^{'}(t)=-\frac{1}{\varepsilon}
\sum_{j}\sum_{r}l_{jr}p_{j}^{\eps}(\ur^{\eps},\njr)
-\frac{1}{\varepsilon
}\sum_{j}\sum_{r}(l_{jr}p_{j,r}^{\eps} \njr,\uj^{\eps})
-\frac{\sigma}{\varepsilon^{2}}
\sum_{j}\sum_r (\widehat{\beta}_{jr}\ur^{\eps},\uj^{\eps}).
\end{equation}
Using (\ref{eq:5}) we expand the second term of the previous equation 
\begin{equation}\label{eq:ds2}
\displaystyle
\sum_{j}\sum_{r}(
l_{jr}p_{j,r}^{\eps}\njr
,\uj^{\eps})=\sum_{j}\sum_{r}l_{jr}p_{j}^{\eps}
(\uj^{\eps},\njr)+\sum_{j}\sum_{r}(\widehat {\alpha}_{jr}(\uj^{\eps}
-\ur^{\eps}),\uj^{\eps})-\frac{\sigma}{\varepsilon}\sum_{j}\sum_{r}({
\widehat\beta}_{jr}\ur^{\eps},\uj^{\eps}).
\end{equation}
Since $\sum_{r}l_{jr}\njr=0$ the first term of (\ref{eq:ds2}) is
zero.
Summing on r the second equation of (\ref{eq:5}) and permuting the sums, we show
that $0=
 \displaystyle \sum_{j}\sum_{r}l_{jr}p_{jr}(\ur,\njr)$ which yields that
\begin{equation}\label{eq:ds3}
0=
 \displaystyle \sum_{j}\sum_{r}l_{jr}p_{j}^{\eps}(\ur^{\eps},\njr)-
\sum_{j}\sum_{r}((\widehat
{\alpha}_{jr}+\frac{\sigma}{\varepsilon}\widehat
{\beta}_{jr})\ur^{\eps},\ur^{\eps})
+\sum_{j}\sum_{r}(\widehat{\alpha}_{jr}\uj^{\eps},\uu_{r
}^{\eps}).
\end{equation}
Plugging (\ref{eq:ds2}) and (\ref{eq:ds3}) in (\ref{eq:ds1}) and permuting the
sums in $E'(t)$ gives
\begin{equation*}\label{rresti}
E^{'}(t)=\displaystyle -\frac{1}{\varepsilon}
\sum_{j}\sum_{r}( \widehat{\alpha}_{jr}(\uj^{\eps}-\ur^{\eps}),\uj^{\eps}
-\ur^{\eps})- \frac{\sigma}{\varepsilon^{2}}
\sum_{r}\sum_{j}(\widehat {\beta}_{jr}\ur^{\eps},\ur^{\eps})
\end{equation*}
which gives
\begin{equation}\label{eq:ds4}
\displaystyle
E^{'}(t)+\frac{1}{\varepsilon}\sum_{r}\sum_{j}l_{jr}(\njr,(\uu^{\eps}
_{j}-\ur^{\eps}))^{2}+ \frac{\sigma}{\varepsilon^{2}}
\sum_{r}(B_r\ur^{\eps},\ur^{\eps})= 0.
\end{equation}
By geometrical assumption  (\ref{geom3}) we have $E^{'}(t)\leq 0$, that is the
$L^2$ stability, and
by integrating this equality on $[0,T]$ we obtain
\begin{equation*}\label{eq:ds5}
\displaystyle
E(T)+\int_0^T\frac{1}{\varepsilon}\sum_{r}\sum_{j}l_{jr}(\njr,
(\uj^{\eps}-\ur^{\eps}))^{2}+ \int_0^T\frac{\sigma}{\varepsilon^{2}}
\sum_{r}(B_r\ur^{\eps},\ur^{\eps})=E(0)
\end{equation*}
Using again the geometrical assumption  (\ref{geom3}) for the terms
$(B_r\ur^{\eps},\ur^{\eps})$ we have
\begin{equation*}\label{eq:ds6}
\displaystyle
E(T)+\int_{0}^T\frac{1}{\varepsilon}\sum_{r}\sum_{j}l_{jr}(\njr,
(\uj^{\eps}-\ur^{\eps}))^{2}+ \alpha
\int_{0}^T\frac{\sigma}{\varepsilon^{2}} \sum_{r}\vert V_r\vert
\ \vert\ur^{\eps}\vert^2\leq E(0)
\end{equation*}
which gives (\ref{gggg}) and (\ref{gs}).
\begin{comment}
The last inequality can be obtained as follows.
One has
$$
\begin{array}{ll}
\vert\vert \uu_j^{\eps} \vert\vert_{L^2( \Omega)}&
\leq 
C \sum_j h^2 \vert\mathbf u_j ^\eps \vert^2
\\
& \leq 
C h  \sum_j \sum_r l_{jr} 
( \mathbf n_{jr}, \mathbf{u}_j^\eps    )^2
\\
& \leq 
C h  \sum_j \sum_r l_{jr} 
2 ( \mathbf n_{jr}, \mathbf u_r ^\eps    )^2
+
C h  \sum_j \sum_r l_{jr} 
2 ( \mathbf n_{jr}, \mathbf u_j ^\eps  - \mathbf u_r ^\eps    )^2 \\
&
\leq C
\vert\vert \uu_r^{\eps} \vert\vert_{L^2(\Omega)} 
+
C h  \sum_j \sum_r l_{jr} 
2 ( \mathbf n_{jr}, \mathbf u_j ^\eps  - \mathbf u_r ^\eps    )^2 .
\end{array}
$$
Using inequalities  (\ref{gggg}) and (\ref{gs}), one gets
$$
\vert\vert \uu_j^{\eps} \vert\vert_{L^2( [0,T]\times \Omega)}^2
\leq C 
\vert\vert \uu_r^{\eps} \vert\vert_{L^2( [0,T]\times \Omega)}^2
+C\int_0^T 
h  \sum_j \sum_r l_{jr} 
 ( \mathbf n_{jr}, \mathbf u_j ^\eps  - \mathbf u_r ^\eps    )^2 
\leq 
C ( \eps^2  + h \eps) \vert\vert
\mathbf V^{\eps}_h(0)\vert\vert^2_{L^2( \Omega)}.
$$
\end{comment}
The proof is ended.
\end{proof}

Our goal now is to prove the following result 
which will be the consequence
of propositions \ref{pro:conv1} to \ref{pro:conv2}.
This part is the more technical one of the paper, but is essential
to be able to use the general strategy of proposition
\ref{prop:1} with convenient exponents. 
As one will see below, the convergence estimate
(\ref{eq:veps2}) is not trivial. It indicates that, 
for a problem with $O(\varepsilon^{-2})$ terms, a scheme 
converges, with $h$, with  at rate $O(\varepsilon^{-\frac12})$ with respect to
$\eps$.

\begin{proposition}[Convergence]\label{ein_prosit}
There exist a constant $C(T, \sigma)>0$ 
      such that the following estimate holds
\begin{equation} \label{eq:veps2}
\|\V^{\eps}_h-\V^{\eps}\|_{L^\infty( [0,T]\times L^2  (\Omega) )}\leq
C(T, \sigma)\|  \mathbf V ^\eps (0) \|_  { H^3(\Omega)  }
\sqrt{\frac h \eps}.
\end{equation}
\end{proposition}
In the whole proof, we will use a constant $C>0$ large enough.
 Like in 1D, we use the method introduced by Mazeran \cite{Mazeran}. 
We introduce
$\mathscr{E}(t)=\frac12 \|\V^{\eps}-\V^{\eps}_h\|_{L^2(\Omega)}^2$.
As for the 1D proof and for the sake of simplicity, for any quantity $q$,   $q'$ stands indifferently for  $\frac{d}{dt}q $ or $\partial_t q $.

\begin{pro} \label{pro:conv1}
One has the formula
\begin{equation} \label{eq:ee1}
\begin{aligned}
\mathscr{E}'(t) &=
-\frac{1}{\eps}\sum_{j,r}l_{j,r}(\mathbf{n}_{j,r},\mathbf{u}_j^{\eps}-\mathbf{u}
_r^{\eps})^2 \\
&+ \frac{1}{\eps} \sum_j \sum_r \bigg(
l_{j,r}(\mathbf{u}_r^{\eps}-\mathbf{u}_j^{\eps}),\mathbf{n}_{j,r} \bigg)
\delta_{j,r}(p^{\eps}) +\frac{1}{\eps} \sum_j \sum_r \bigg( 
 l_{j,r}\mathbf{n}_{j,r} ( p_{jr}^{\eps}  - p_j^{\eps}) \: , \:
\delta_{j,r}(\uu^{\eps}) \bigg) \\
&+\frac{1}{\eps}\sum_j \sum_r  |\Gamma_{j,r} | p_j^{\eps} (\mathbf{n}_{j,r} ,
\tilde{\delta}_{j,r}(\uu^{\eps}) ) + \frac{1}{\eps}\sum_j \sum_r |\Gamma_{j,r} | \bigg(
\mathbf{u}_j^{\eps} , \mathbf{n}_{j,r} \tilde{\delta}_{j,r}(p^{\eps}) \bigg) \\
&+\frac{\sigma}{\eps^2} \sum_r \sum_j 
\bigg(\widehat{\beta}_{j,r}\mathbf{u}_r^{\eps}  \: , \:
\frac{1}{|\Omega_j|}\int_{\Omega_j} \uu^{\eps} d\x \bigg)
+\frac{\sigma}{\eps^2}\sum_j\bigg(  \mathbf{u}_j^{\eps} ,
\int_{\Omega_j}\uu^{\eps}d\x \bigg) \\
&-\frac{\sigma}{\eps^2}\sum_j\int_{\Omega_j}(\uu^{\eps},\uu^{\eps}
)d\x -\frac{\sigma}{\eps^2}\sum_{r}
(B_{r}\mathbf{u}_r^{\eps},\textbf{u}_r^{\eps})
\end{aligned}
\end{equation}
where  the extra notations are:
$\delta_{j,r}(f)= \frac{1}{|\Omega_j|}\int_{\Omega_j} f d\x
-f(\x_{r})$ is an interpolation error term that compares mean values and point 
values;
$\Gamma_{j,r}=[\x_{r},\x_{r+1}]$ is the edge
oriented toward the outside of the cell $j$, with
length $|\Gamma_{j,r} | $; and $\tilde{\delta}_{j,r}(h)=
\frac1{|\Gamma_{j,r}| } \int_{\Gamma_{j,r}} h d s
-\frac{h(\textbf{x}_{r})+h(\textbf{x}_{r+1})}{2}$ is another
interpolation error contribution that compares the  mean value and the mid sum,
on the edge.
\end{pro}

\begin{proof}
We first consider  the time  derivative
\begin{equation*} \label{eq:eetoile}
\begin{array}{l}
\mathscr{E}'(t)
=\underbrace{\int_{\Omega}(p_h^{\eps}(p_h^{\eps})'+(\uu_h^{\eps},(\textbf{u}
_h^{\eps})'))d\x}_{D_1}+ \underbrace{
\int_{\Omega}(p^{\eps}(p^{\eps})'+(\textbf{u}^{\eps},(\textbf{u}^{\eps})'))d\x}_{
D_2} \\
\hspace{0.8cm}+ \underbrace{\int_{\Omega}
(-(p_h^{\eps})'p^{\eps}-((\textbf{u}_h^{\eps})',\textbf{u}^{\eps}))d\x}_{D_3} 
+ \underbrace{\int_{\Omega}
(-p_h^{\eps}(p^{\eps})'-(\textbf{u}_h^{\eps},(\textbf{u}^{\eps})'))d\x}_{D_4}.
\end{array}
\end{equation*}
One has thanks to  (\ref{eq:ds4})
$$
D_1
=-\frac{1}{\eps}\sum_{j,r}l_{j,r}(\textbf{n}_{j,r},\textbf{u}_j^{\eps}-\textbf{u}
_r^{\eps})^2-\frac{\sigma}{\eps^2}\sum_{r}
( B_r\textbf{u}_r^{\eps},\textbf{u}_r^{\eps}).
$$
One also directly has
\begin{equation*}
D_2 =
-\frac{\sigma}{\eps^2}\int_{\Omega}(\uu^{\eps},\uu^{\eps})d\x =
-\frac{\sigma}{\eps^2}\sum_j\int_{\Omega_j}(\uu^{\eps},\uu^{\eps}
)d\x.
\end{equation*}
Then,  using the  definition (\ref{eq:4},\ref{eq:5}) of the scheme we have
\begin{equation*}
\begin{array}{l}
D_3 = \frac{1}{\eps} \sum_j \sum_r \bigg(
l_{j,r}\textbf{u}_r^{\eps},\textbf{n}_{j,r} \bigg) 
\frac{1}{|\Omega_j|}\int_{\Omega_j} p^{\eps} dx \\
\hspace{1cm}+\frac{1}{\eps} \sum_j \bigg( \sum_r
l_{jr} \mathbf n_{jr} p_{j,r}^{\eps}+\frac{\sigma}{\eps} \sum_r
\widehat{\beta}_{j,r}\textbf{u}_r^{\eps}  \: , \:
\frac{1}{|\Omega_j|}\int_{\Omega_j} \uu^{\eps} d\x \bigg) 
\end{array}
\end{equation*}
Since $\sum_r l_{jr} \mathbf n_{jr}=0$,  we can write
\begin{equation*}
\begin{array}{ll}
D_3= &  \frac{1}{\eps} \sum_j \sum_r \bigg(
l_{j,r}(\textbf{u}_r^{\eps}-\textbf{u}_j^{\eps}),\textbf{n}_{j,r} \bigg) 
\frac{1}{|\Omega_j|}\int_{\Omega_j} p^{\eps} dx \\
& + \frac{1}{\eps} \sum_j \bigg( \sum_r 
l_{jr} \mathbf n_{jr} (p_{j,r}^{\eps}
-
p_j^{\eps})  \: , \: \frac{1}{|\Omega_j|}\int_{\Omega_j}
\uu^{\eps} d\x \bigg) \\
& +\frac{\sigma}{\eps^2} \bigg( \sum_r \sum_j\widehat{\beta}_{j,r}\textbf{u}_r^{\eps} 
\: , \: \frac{1}{|\Omega_j|}\int_{\Omega_j} \uu^{\eps} d\x \bigg) .
\end{array}
\end{equation*}
One gets
\begin{equation*}
\begin{array}{l}
D_3 =\frac{1}{\eps} \sum_j \sum_r \bigg(
l_{j,r}(\textbf{u}_r^{\eps}-\textbf{u}_j^{\eps}),\textbf{n}_{j,r} \bigg)
\delta_{j,r}(p^{\eps})+\frac{1}{\eps} \sum_j \sum_r \bigg(

l_{jr} \mathbf n_{jr} (p_{j,r}^{\eps}
-
p_j^{\eps}) \: ,
\:\delta_{j,r}(\uu^{\eps}) \bigg) \\
\hspace{0.6cm}+ \frac{1}{\eps} \sum_j \sum_r \bigg(
l_{j,r}(\textbf{u}_r^{\eps}-\textbf{u}_j^{\eps}),\textbf{n}_{j,r} \bigg)
p^{\eps}(\x_r)+ \frac{1}{\eps} \sum_j \sum_r \bigg(  
l_{jr} \mathbf n_{jr} (p_{j,r}^{\eps}
-
p_j^{\eps})  \: , \:  \uu^{\eps}(\textbf{x}_{r}) \bigg) \\
\hspace{0.6cm}+\frac{\sigma}{\eps^2} \bigg( \sum_r \sum_j
\widehat{\beta}_{j,r}\textbf{u}_r^{\eps}  \: , \:
\frac{1}{|\Omega_j|}\int_{\Omega_j} \uu^{\eps} d\x \bigg) .
\end{array}
\end{equation*}
We have the identities $\sum_{j,r}\ljr \njr 
=0$
and  $\sum_j  l_{jr} \mathbf n_{jr} p_{j,r}^{\eps}=0$ by definition
(\ref{eq:5}).
Therefore one can simplify the third and fourth term
in the previous expression and get 
\begin{equation*}
\begin{aligned}
D_3  & =  \frac{1}{\eps} \sum_j \sum_r \bigg(
l_{j,r}(\textbf{u}_r^{\eps}-\textbf{u}_j^{\eps}),\textbf{n}_{j,r} \bigg)
\delta_{j,r}(p^{\eps})+\frac{1}{\eps} \sum_j \sum_r \bigg( 
l_{jr} \mathbf n_{jr} (p_{j,r}^{\eps}
-
p_j^{\eps}) \: , \:
\delta_{j,r}(\uu^{\eps}) \bigg) \\
& - \frac{1}{\eps} \sum_j \sum_r \bigg(
l_{j,r}\textbf{u}_j^{\eps},\textbf{n}_{j,r} \bigg) p^{\eps}(\x_r)- \frac{1}{\eps}
\sum_j \sum_r \bigg( l_{j,r}p_j^{\eps}\textbf{n}_{j,r} \: ,\:
\uu^{\eps}(\textbf{x}_{r}) \bigg)\\
 & + \frac{\sigma}{\eps^2} \bigg( \sum_r
\sum_j\widehat{\beta}_{j,r}\textbf{u}_r^{\eps}  \: , \:
\frac{1}{|\Omega_j|}\int_{\Omega_j} \uu^{\eps} d\x \bigg) .
\end{aligned}
\end{equation*}
We now look at $D_4$. By definition, one has
\begin{equation*}
D_4= \frac{1}{\eps}\sum_j p_j^{\eps} \sum_r \int_{\Gamma_{j,r}}
(\uu^{\eps},\tnjr)d\sigma + \frac{1}{\eps}\sum_j
\bigg( \textbf{u}_j^{\eps} , \bigg( \sum_r \int_{\Gamma_{j,r}} p^{\eps}
\tnjr d\sigma
+\frac{\sigma}{\eps}\int_{\Omega_j}\uu^{\eps} d\x\bigg) \bigg)
\end{equation*}
where $\tnjr$ is the normal to the edge
$\Gamma_{j,r}=[\x_{r},\x_{r+1}]$ oriented toward the outside of the cell $j$. 
This expression needs an important manipulation which
is to approximate the integral on edges by corner values.
This necessary manipulation is one of the ideas that was introduced
in \cite{Mazeran} in order to proceed to the numerical
analysis of such corner based finite volume schemes.
This is why  interpolation terms  $\tilde{\delta}_{j,r}(h)= 
\frac1{|\Gamma_{jr}|}\int_{\Gamma_{j,r}} h
- \frac{h(\textbf{x}_{r})+h(\textbf{x}_{r+1})}{2}$ are introduced.
One gets after an algebraic manipulation 
\begin{equation*}
\begin{aligned}
D_4 &= \frac{1}{\eps}\sum_j \sum_r |\Gamma_{j,r}|   p_j^{\eps} \bigg( \tnjr
,\tilde{\delta}_{j,r}(\uu^{\eps}) \bigg) +\frac{1}{\eps}\sum_j \sum_r
|\Gamma_{j,r}| 
\bigg( \textbf{u}_j^{\eps} ,
\tnjr\tilde{\delta}_{j,r}(p^{\eps})\bigg) +
\frac{\sigma}{\eps^2}\sum_j\bigg(  \textbf{u}_j^{\eps} ,
\int_{\Omega_j}\uu^{\eps} \bigg)\\
&+ \frac{1}{\eps}\sum_j \sum_r  |\Gamma_{j,r}| p_j^{\eps} \bigg(
\tnjr ,\frac{\uu^{\eps}(\textbf{x}_{r})+\uu^{\eps}(\textbf{x}_{r+1})}{2}
\bigg) + \frac{1}{\eps}\sum_j \sum_r |\Gamma_{j,r}| \bigg( \textbf{u}_j^{\eps} ,
\tnjr
\frac{p^{\eps}(\textbf{x}_{r})+p^{\eps}(\textbf{x}_{r+1})}{2}\bigg) 
\end{aligned}
\end{equation*}
By definition (\ref{eq:not}),
$\njr\ljr=\frac{\tilde{n}_{j,r}|\Gamma_{j,r}|+\tilde{n}_{j,r-1}|\Gamma_{j,r-1}|}
{2}$, so one can see that 
$$
\sum_j \sum_r |\Gamma_{j,r}|  p_j^{\eps} \bigg(
\tnjr ,\frac{\uu^{\eps}(\textbf{x}_{r})+\uu^{\eps}(\textbf{x}_{r+1})}{2}
\bigg)= \sum_j \sum_r  l_{jr} p_j^{\eps} \big( \njr ,\uu^{\eps}(\textbf{x}_{r}) \big).
$$ 
It yields a slightly simpler expression
$$
\begin{aligned}
D_4 &= \frac{1}{\eps}\sum_j \sum_r |\Gamma_{j,r}|   p_j^{\eps} \bigg( \tnjr
,\tilde{\delta}_{j,r}(\uu^{\eps}) \bigg) +\frac{1}{\eps}\sum_j \sum_r
|\Gamma_{j,r}| 
\bigg( \textbf{u}_j^{\eps} ,
\tnjr\tilde{\delta}_{j,r}(p^{\eps})\bigg) +
\frac{\sigma}{\eps^2}\sum_j\bigg(  \textbf{u}_j^{\eps} ,
\int_{\Omega_j}\uu^{\eps} \bigg)\\
&+ \frac{1}{\eps}
\sum_j \sum_r  l_{jr} p_j^{\eps} \big( \njr ,\uu^{\eps}(\textbf{x}_{r}) \big)
 + \frac{1}{\eps}\sum_j \sum_r \ljr p^{\eps}(\textbf{x}_{r})\big(\njr ,\textbf{u}_j^{\eps}\big) 
\end{aligned}
$$
One can now compute the sum  $D_3+D_4$
\begin{equation*}
\begin{aligned}
D_3+D_4 &= \frac{1}{\eps} \sum_j \sum_r \bigg(
l_{j,r}(\textbf{u}_r^{\eps}-\textbf{u}_j^{\eps}),\textbf{n}_{j,r} \bigg)
\delta_{j,r}(p^{\eps}) +\frac{1}{\eps} \sum_j \sum_r \bigg( 
 l_{j,r}\textbf{n}_{j,r}  (p_{j,r}^{\eps}- p_j^{\eps})  \: , \:
\delta_{j,r}(\uu^{\eps}) \bigg) \\
&+\frac{1}{\eps}\sum_j \sum_r  |\Gamma_{jr}|
p_j^{\eps}
\bigg(\textbf{n}_{j,r},\tilde{\delta}_{j,r}(\uu^{\eps}) \bigg) +
\frac{1}{\eps}\sum_j \sum_r  |\Gamma_{jr}| \bigg( \textbf{u}_j^{\eps} , \textbf{n}_{j,r}
\tilde{\delta}_{j,r}(p^{\eps})\bigg)\\
&+\frac{\sigma}{\eps^2} \bigg( \sum_r \sum_j \widehat{\beta}_{j,r}\textbf{u}_r^{\eps}
 \: , \: \frac{1}{|\Omega_j|}\int_{\Omega_j} \uu^{\eps} d\x \bigg)
+\frac{\sigma}{\eps^2}\sum_j \bigg(  \textbf{u}_j^{\eps} ,
\int_{\Omega_j}\uu^{\eps} d\x\bigg).
\end{aligned}
\end{equation*}
One finally gets after rearrangement
the final result (\ref{eq:ee1}) for $\mathscr{E}'(t)
=D_1+D_2+D_3 +D_4$.
\end{proof}

Before going further in the examination of each term in the right hand side of
(\ref{eq:ee1}), it is worthwhile to notice that terms like $\delta_{jr}(\dots)$ and 
$\widetilde \delta_{jr}(\dots)$ 
are small in some  sense. For this  we recall the results taken from \cite{Mazeran}, chapter 4:

\begin{pro} \label{pro:interp}
For any funtion $q$ in $ H^3(\Omega)$,   using  Sobolev embeddings,
one has the inequalities
\begin{equation}\label{}
 \vert \delta_{jr}(q) \vert
 \leq 
  C  \| q \| _{ H^1(\Omega_j) }
\end{equation}
and
\begin{equation}
\vert \widetilde \delta_{jr}(q)\vert
\leq  
  C h^{3/2}  \| q \| _{ H^3(\Omega_j) }
\end{equation}
\end{pro}

Our aim is to now examine each term in the right hand side of
(\ref{eq:ee1}). Its  first line is already non positive.
We  look at the second line of (\ref{eq:ee1})  which we call
$E_1$. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{pro}
One has
the bound with a constant $C$proportional to $  \|  \mathbf V ^\eps (0) \|^2_  { H^1(\Omega)  }$  
\begin{equation} \label{eq:bound1}
\int_0^T E_1(t)dt \leq 
\frac{\gamma}{\eps}\int_0^T\sum_{j,r}l_{j,r}(\textbf{n}_{j,r},\textbf{u}_j^{\eps}-\textbf{u}
_r^{\eps})^2 
+Ch(  \frac T {\gamma } +1).
\end{equation}
\end{pro}
\begin{proof}
We use a Young's inequality 
$ab\leq \frac\gamma2 a^2+\frac1{2\gamma} b^2$,with some positive constant$\gamma$ which will be defined later,   for the second term
and the definition of the fluxes (\ref{eq:5}) for the third term: we get
\begin{equation*}
\begin{aligned}
E_1 &\leq  \frac{\gamma }{2 \eps}\sum_{j,r}l_{j,r}(\textbf{n}_{j,r},\textbf{u}_j^{\eps}
-\textbf{u}_r^{\eps})^2 + \frac{1}{2\gamma\eps} \sum_j \sum_r l_{j,r}
\delta_{j,r}(p^{\eps})^2 \\
&+\frac{1}{\eps} \sum_j \sum_r \bigg(
\widehat{\alpha}_{j,r}(\textbf{u}_j^{\eps}-\textbf{u}_r^{\eps}) \: , \:
\delta_{j,r}(\uu^{\eps}) \bigg) -\frac{1}{\eps} \sum_j \sum_r \bigg(
\frac{\sigma}{\eps} \widehat{\beta}_{j,r}\textbf{u}_r^{\eps}\: , \:
\delta_{j,r}(\uu^{\eps} )\bigg) \\
\end{aligned}
\end{equation*}
 By definition of $\widehat{\alpha}_{j,r}$,
one rewrites
 $$
\sum_j \sum_r \bigg(
\widehat{\alpha}_{j,r}(\textbf{u}_j^{\eps}-\textbf{u}_r^{\eps}) \: , \:
\delta_{j,r}(\uu^{\eps}) \bigg) = \sum_j \sum_r 
\ljr(\njr , \textbf{u}_j^{\eps}-\textbf{u}_r^{\eps} )(\njr ,
  \delta_{j,r}(\uu^{\eps})).
$$ 
Another use of Young's inequality with the same coefficient $\gamma$ for this term
yields

\begin{equation*}
\begin{aligned}
E_1 &\leq  \frac{\gamma }{ \eps}\sum_{j,r}l_{j,r}(\textbf{n}_{j,r},\textbf{u}_j^{\eps}
-\textbf{u}_r^{\eps})^2 + \frac{1}{2\gamma\eps} \sum_j \sum_r l_{j,r}
\delta_{j,r}(p^{\eps})^2 \\
&+\frac{1}{2\gamma\eps} \sum_j \sum_r 
\
\delta_{j,r}(\uu^{\eps})^2 -\frac{1}{\eps} \sum_j \sum_r \bigg(
\frac{\sigma}{\eps} \widehat{\beta}_{j,r}\textbf{u}_r^{\eps}\: , \:
\delta_{j,r}(\uu^{\eps} )\bigg) \\
\end{aligned}
\end{equation*}

We now look at the last term of (\ref{eq:bound1}), which we call $W$.
One has, by definition of $\widehat{\beta}_{j,r}$
\begin{equation*}
W=-\frac{1}{\eps} \sum_j \sum_r \bigg( \frac{\sigma}{\eps}
\widehat{\beta}_{j,r}\textbf{u}_r^{\eps}\: , \: \delta_{j,r}(\uu^{\eps} )\bigg)
= -\frac{\sigma}{\eps^2} \sum_j \sum_r
\bigg((\ljr)^{\frac12 }\njr\otimes(\xr -\xj)
\textbf{u}_r^{\eps}\: , \: (\ljr)^{\frac12 }\delta_{j,r}(\uu^{\eps})
\bigg)
\end{equation*}
 Using the Cauchy-Schwarz inequality, we get
\begin{equation*}
\vert W \vert \leq \frac{\sigma}{\eps^2} \bigg(\sum_j \sum_r
\ljr  \bigg| 
\njr\otimes(\xr -\xj)
\textbf{u}_r^{\eps}
 \bigg|^2 \bigg)^{\frac12 } \bigg(\sum_j \sum_r
 \ljr  | \delta_{j,r}(\uu^{\eps})| ^2 \bigg)^{\frac12 } \\
\end{equation*}
Using the assumptions of the mesh, there exist a 
constant $C>0$ such that $|\xr -\xj|\leq Ch$.
 Using successively assumptions \eqref{eq:d5.2},\eqref{nbmr} and 
\eqref{geom3}, we get
\begin{equation*}\label{esti_beta}
\vert W \vert
\leq C \frac{\sigma h}{\eps^2}
\bigg( \sum_r \big( B_{r}\textbf{u}_r^{\eps},\textbf{u}_r^{\eps}\big)\bigg)^{\frac12} \bigg(\sum_j \sum_r    | \delta_{j,r}(\uu^{\eps})|^2 \bigg)^{\frac12 }.
\end{equation*}
and therefore
\begin{equation}\label{eq:bound2}
\vert W \vert
\leq C \frac{\sigma h}{2\eps^2}
\bigg( \sum_r \big( B_{r}\textbf{u}_r^{\eps},\textbf{u}_r^{\eps}\big)  +\sum_j \sum_r    | \delta_{j,r}(\uu^{\eps})|^2 \bigg).
\end{equation}
so that
\begin{equation} \label{eq:bound1bis}
\begin{aligned}
E_1 &\leq \frac{\gamma }{\eps}
\sum_{j,r}l_{j,r}(\textbf{n}_{j,r},\textbf{u}_j^{\eps}-\textbf{u}
_r^{\eps})^2 + \frac{1}{2\gamma\eps} \sum_j \sum_r l_{j,r}
\delta_{j,r}(p^{\eps})^2 \\
&+\frac{1}{2 \gamma \eps} \sum_j \sum_r l_{j,r}\bigg( \textbf{n}_{j,r} \: , \:
\delta_{j,r}(\uu^{\eps}) \bigg)^2 + C \frac{\sigma h}{2\eps^2}
\bigg( \sum_r \big( B_{r}\textbf{u}_r^{\eps},\textbf{u}_r^{\eps}\big)  +\sum_j \sum_r    | \delta_{j,r}(\uu^{\eps})|^2 \bigg)\\
\end{aligned}
\end{equation}

Furthermore, using the  classical interpolation results of proposition \ref{pro:interp} , there exists another constant $C\geq0$ such that 
\[
\sum_j \sum_r ( \delta_{j,r}\uu^{\eps})^2 \leq C \vert \vert \uu^\eps \vert\vert^2_{H^1(\Omega)}
.
\]
and
\[
\sum_j \sum_r l_{j,r} ( \delta_{j,r}p^{\eps})^2 \leq C h \vert \vert p^\eps \vert\vert^2_{H^1(\Omega)}
.
\]

So we obtain, after redefinition of all the constants $C$

$$
\int_0^T E_1 dt\leq 
\int_0^T \frac{\gamma}{\eps}
\sum_{j,r}l_{j,r}(\textbf{n}_{j,r},\textbf{u}_j^{\eps}-\textbf{u}
_r^{\eps})^2 
+\frac {Ch }{2\gamma \eps}\bigg(\vert \vert \uu^\eps \vert\vert^2_{H^1(\Omega)} +\vert \vert p^\eps \vert\vert^2_{H^1(\Omega)}  \bigg)
+C \frac{h\sigma}{2\eps^2}
\bigg(\sum_r \big( B_{r}\mathbf{u}_r^{\eps},\mathbf{u}_r^{\eps}\big) +  \vert \vert \uu^\eps \vert\vert^2_{H^1(\Omega)}\bigg)dt.
$$

Using  energy estimate (\ref{bee1})  for the the second  term of the rhs of the above inequality,    (\ref{gggg}) for the third term   and   (\ref{bee2}) for the last term,
one gets finally after simplifications and up to another redefinition  of the constant $C$(which is proportional to the $H^1(\Omega)$ norm of the initial data $\V_0$ and  is independent of the parameter $\sigma$)
\begin{equation} \label{eq:si1}
\int_0^T E_1(t)dt \leq 
\frac{\gamma}{\eps}\int_0^T\sum_{j,r}l_{j,r}(\textbf{n}_{j,r},\textbf{u}_j^{\eps}-\textbf{u}
_r^{\eps})^2 
+Ch(  \frac 1 {\gamma } +1).
\end{equation}
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Now we consider the third line 
of  $\mathscr{E}'(t)$, which we call $E_2$.

\begin{pro} \label{pro:e2}
One has the bound
\begin{equation} \label{eq:si2}
\int_0^T E_2(t) dt \leq  \frac{CTh}{\eps} .
\end{equation}

where the constant $C$ depends   on $\|  \mathbf V ^\eps (0) \|^2_  { H^3(\Omega)  }$
\end{pro}
\begin{proof}
$E_2=A+B$ is made of two contributions.
Making use of the second set of inequalities
of proposition \ref{pro:interp}, one gets concerning the first one
$$
| A|= \left |
\frac{1}{\eps}\sum_j \sum_r  |\Gamma_{j,r} | p_j^{\eps} (\mathbf{n}_{j,r} ,
\tilde{\delta}_{j,r}(\uu^{\eps}) ) 
\right |
\leq 
\frac{C}{\eps}  \sum_j h^{5/2} | p_j  ^\eps |
 \|  \mathbf V ^\eps (t) \|_  { H^3(\Omega_j)  }.
$$
And using the inequality $ab\leq \frac{1}{2}(a^2+b^2)$

$$
| A|\leq 
\frac{C_1}{\eps}  \sum_j h^{3} | p_j  ^\eps |^2 + \frac{C_2}{\eps} \sum_j h^{2} 
 \|  \mathbf V ^\eps (t) \|^2_  { H^3(\Omega_j)  }
 \leq 
\frac{hC_3}{\eps} \|  \mathbf V_h ^\eps (t) \|^2_  { L^2(\Omega)  } + \frac{C_2h^2}{\eps}  
 \|  \mathbf V ^\eps (t) \|^2_  { H^3(\Omega)  }.
$$
The $L^2$ stability  (\ref{gggg})  of the scheme $\mathbf P_h ^\eps$ yields
that $\|  \mathbf V_h ^\eps (t) \|^2_  { L^2(\Omega)  }\leq
\|  \mathbf V_h ^\eps (0) \|^2_  { L^2(\Omega)  }\leq\|  \mathbf V ^\eps (0) \|^2_  { L^2(\Omega)  }+C \|  \mathbf V ^\eps (0) \|^2_  { H^1(\Omega)  } $.
And with  the basic energy estimate (\ref{bee1}) , and since $h$ is bounded, we obtain with a constant $C_4$ proportional to  $   \|  \mathbf V ^\eps (0) \|^2_  { H^3(\Omega)  }$ 
$$\int_0^T\vert A \vert dt \leq C_4 \frac{hT}{\eps}.$$

For the  second contribution$$
B=\frac{1}{\eps}\sum_j \sum_r |\Gamma_{j,r} | \bigg(
\mathbf{u}_j^{\eps} , \mathbf{n}_{j,r} \tilde{\delta}_{j,r}(p^{\eps}) \bigg),
$$
by similar calculations we obtain
$$\int_0^T\vert B \vert dt \leq C_5 \frac{hT}{\eps},$$
with a constant $C_5$ proportional to $  \|  \mathbf V ^\eps (0) \|^2_  { H^3(\Omega)  }$. Taking $C=2\max(C_4,C_5)$ yields (\ref{eq:si2}).
\end{proof}

We now study the two last lines of $\mathscr{E}'(t)$, which we call S. 
\begin{pro}  \label{pro:conv2}
There exists a constant $C>0$ proportional to $  \|  \mathbf V ^\eps (0) \|^2_  { H^1(\Omega)  }$ such that one has for all $\hat \gamma>0$ 
\begin{equation} \label{eq:bound3}
\begin{aligned}
\int_0^TSdt&\leq  C\left(  { h^2} +\frac{h}{ \widehat \gamma \eps}\right)
 +
 \frac{\sigma\hat \gamma}{2\eps}\int_0^T\sum_r \sum_j \ljr \bigg(  \njr  \: , \:
\mathbf{u}_r^{\eps}-\mathbf{u}_j^{\eps} \bigg)^2 dt
\end{aligned}
\end{equation}
\end{pro}

\begin{proof}
These two last lines 
write 
\begin{equation*}
\begin{aligned}
S &= \frac{\sigma}{\eps^2} \sum_r \sum_j  \bigg(
\widehat{\beta}_{j,r}\textbf{u}_r^{\eps}  \: , \:
\frac{1}{|\Omega_j|}\int_{\Omega_j} \textbf{u}^{\eps} d\x \bigg)
+\frac{\sigma}{\eps^2}\sum_j\bigg(  \textbf{u}_j^{\eps} ,
\int_{\Omega_j}\textbf{u}^{\eps} \bigg) \\
&-\frac{\sigma}{\eps^2}\sum_j\int_{\Omega_j}(\textbf{u}^{\eps},\textbf{u}^{\eps}
)d\x -\frac{\sigma}{\eps^2}\sum_{j}\sum_{r}
(\widehat{\beta}_{j}
\textbf{u}_r^{\eps},\textbf{u}_r^{\eps}).
\end{aligned}
\end{equation*}
Using the Cauchy-Schwarz inequality on the third term
 $\int (\textbf{u}^{\eps},\textbf{u}^{\eps})$, one gets
\begin{equation*}
\begin{aligned}
S &\leq \frac{\sigma}{\eps^2} \sum_r \sum_j  \bigg(
\widehat{\beta}_{j,r}\textbf{u}_r^{\eps}  \: , \:
\frac{1}{|\Omega_j|}\int_{\Omega_j} \uu^{\eps}d\x \bigg) +\frac{\sigma}{\eps^2}\sum_j\bigg(  \textbf{u}_j^{\eps} ,
\int_{\Omega_j}\textbf{u}^{\eps} \bigg) \\
&- \frac{\sigma}{\eps^2}\sum_j \frac{1}{|\Omega_j|}\bigg(
\int_{\Omega_j}\textbf{u}^{\eps}d\x \bigg)^2 -\frac{\sigma}{\eps^2}\sum_{j}
\sum_{r}
(\widehat{\beta}_{j}    
\textbf{u}_r^{\eps},\textbf{u}_r^{\eps}),
\end{aligned}
\end{equation*}
which can be written
\begin{equation*}
S \leq -\frac{\sigma}{\eps^2} \sum_r \sum_j  \bigg(
\widehat{\beta}_{j,r}\textbf{u}_r^{\eps}  \: , \:
\textbf{u}_r^{\eps}-\frac{1}{|\Omega_j|}\int_{\Omega_j} \textbf{u}^{\eps} d\x
\bigg) - \frac{\sigma}{\eps^2}\sum_j\bigg( \int_{\Omega_j}\textbf{u}^{\eps}d\x ,
 \frac{1}{|\Omega_j|}  \int_{\Omega_j}\textbf{u}^{\eps}d\x -\uj^{\eps}
\bigg) .
\end{equation*}
We can rewrite this inequality on the form
\begin{equation*}
\begin{aligned}
S \leq &-\frac{\sigma}{\eps^2} \sum_r \sum_j  \bigg( \widehat{\beta}_{j,r}\bigg(
\textbf{u}_r^{\eps}- \frac{1}{|\Omega_j|}\int_{\Omega_j} \textbf{u}^{\eps} d\x\bigg) 
\: , \: \textbf{u}_r^{\eps}-\frac{1}{|\Omega_j|}\int_{\Omega_j}
\textbf{u}^{\eps} d\x \bigg) \\
&-\frac{\sigma}{\eps^2} \sum_r \sum_j  \bigg( \widehat{\beta}_{j,r}
\frac{1}{|\Omega_j|}\int_{\Omega_j} \textbf{u}^{\eps} d\x  \: , \:
\textbf{u}_r^{\eps}-\frac{1}{|\Omega_j|}\int_{\Omega_j} \textbf{u}^{\eps} d\x
\bigg)\\
&-\frac{\sigma}{\eps^2}\sum_j\bigg( \int_{\Omega_j}\textbf{u}^{\eps}d\x , 
\frac{1}{|\Omega_j|}  \int_{\Omega_j}\textbf{u}^{\eps}d\x -\textbf{u}^{\eps}_j
\bigg).
\end{aligned}
\end{equation*}
One has, using the geometric identity 
$\sum_r \be =|\Omega_j| I_d$ which can be found in \cite{glaceap,de10},
\begin{equation*}
 \begin{aligned}
  \sum_r \sum_j  \bigg( \widehat{\beta}_{j,r}
\frac{1}{|\Omega_j|}\int_{\Omega_j} \textbf{u}^{\eps} d\x  \: , \:
\textbf{u}_r^{\eps}-\frac{1}{|\Omega_j|}\int_{\Omega_j} \textbf{u}^{\eps} d\x
\bigg) &= \sum_r \sum_j  \bigg( \widehat{\beta}_{j,r}
\frac{1}{|\Omega_j|}\int_{\Omega_j} \textbf{u}^{\eps} d\x  \: , \:
\textbf{u}_r^{\eps}-\textbf{u}_j^{\eps} \bigg) \\
&-\sum_j  \bigg( \int_{\Omega_j} \textbf{u}^{\eps} d\x  \: , \:
\frac{1}{|\Omega_j|}\int_{\Omega_j} \textbf{u}^{\eps} d\x-\textbf{u}_j^{\eps}
\bigg).
 \end{aligned}
\end{equation*}
We thus get
\begin{equation}\label{eq:s1}
\begin{array}{ll | r}
S\leq &-\frac{\sigma}{\eps^2} \sum_r \sum_j  \bigg( \widehat{\beta}_{j,r}\bigg(
\textbf{u}_r^{\eps}- \frac{1}{|\Omega_j|}\int_{\Omega_j} 
\textbf{u}^{\eps} d\x\bigg ) 
\: , \: \textbf{u}_r^{\eps}-\frac{1}{|\Omega_j|}\int_{\Omega_j}
\textbf{u}^{\eps} d\x \bigg)
&=S_1
 \\
&-\frac{\sigma}{\eps^2} \sum_r \sum_j  \bigg( \widehat{\beta}_{j,r}
\frac{1}{|\Omega_j|}\int_{\Omega_j} \textbf{u}^{\eps} d\x  \: , \:
\textbf{u}_r^{\eps}-\textbf{u}_j^{\eps} \bigg). &=S_2
\end{array}
\end{equation}
We add and subtract at each average on the cell the nodal value. 
We recall the notation  
$\delta_{j,r}(\textbf{u}^{\eps})=\frac{1}{|\Omega_j|}\int_{\Omega_j}
\uu^{\eps} d\x-\textbf{u}^{\eps}(\textbf{x}_r)$.
We get for the term under the first sum in (\ref{eq:s1})
$$
\bigg( \widehat{\beta}_{j,r}\bigg(
\textbf{u}_r^{\eps}- \frac{1}{|\Omega_j|}\int_{\Omega_j} 
\textbf{u}^{\eps} d\x\bigg ) 
\: , \: \textbf{u}_r^{\eps}-\frac{1}{|\Omega_j|}\int_{\Omega_j}
\textbf{u}^{\eps} d\x \bigg)
$$
$$
=\bigg( \widehat{\beta}_{j,r}\bigg(
\textbf{u}_r^{\eps}- u^\eps(\x_r)
\bigg ) 
\: , \: \textbf{u}_r^{\eps}-u^\eps(\x_r)
 \bigg)
-
\bigg( \widehat{\beta}_{j,r}\bigg(
\textbf{u}_r^{\eps}- u^\eps(\x_r)
\bigg ) 
\: , \: \delta_{j,r}(\textbf{u}^{\eps})
 \bigg)
$$
\begin{equation} \label{eq:bb1}
-
\bigg( 
\widehat{\beta}_{j,r} \delta_{j,r}(\textbf{u}^{\eps})
\: , \:
\textbf{u}_r^{\eps}- u^\eps(\x_r)
 \bigg)
+
\bigg( 
\widehat{\beta}_{j,r} \delta_{j,r}(\textbf{u}^{\eps})
\: , \:
 \delta_{j,r}(\textbf{u}^{\eps})
 \bigg).
\end{equation}
The first of these quantities is purely nodal, so one has
$$
\sum_j \sum_r \bigg( \widehat{\beta}_{j,r}\bigg(
\textbf{u}_r^{\eps}- u^\eps(\x_r)
\bigg ) 
\: , \: \textbf{u}_r^{\eps}-u^\eps(\x_r)
 \bigg)
$$
\begin{equation} \label{eq:ss2}
=
 \sum_r \bigg( B_{r}\bigg(
\textbf{u}_r^{\eps}- u^\eps(\x_r)
\bigg ) 
\: , \: \textbf{u}_r^{\eps}-u^\eps(\x_r)
 \bigg)\geq \alpha \sum_r |V_r| | 
 \textbf{u}_r^{\eps}-
 u^\eps(\x_r) |^2
\end{equation}
with the help of (\ref{geom3}).

The second and third term in the identity (\ref{eq:bb1}) can be bounded
by a Young's inequality with a convenient constant
so that all terms containing $ \textbf{u}_r^{\eps}-u^\eps(\x_r)$
are controlled by (\ref{eq:ss2}).
So we obtain concerning $S_1$ defined in (\ref{eq:s1})
\begin{equation*} \label{eq:ss4}
S_1
\leq C\frac{h^2\sigma }{\eps^2}\sum_r \sum_j  \left|  \delta_{j,r}(\textbf{u}^{\eps}) \right|^2.
\end{equation*}
Using the standard interpolation result stressed in proposition \ref{pro:interp},
one has in dimension two
$| \delta_{j,r}(\textbf{u}^{\eps}) |
 \leq C_1  \|\uu^\eps(t)\|^2_{H^1(\Omega_j)} $. 
So, taking into account energy estimate (\ref{bee2})
we have for the first term
\begin{equation*} \label{eq:ss6}
\int_0^T S_1dt \leq C_2 h^2  \|\V^\eps(0\|^2_{H^1(\Omega)}.
\end{equation*}
We now consider the second term called  $S_2$ in (\ref{eq:s1})
\begin{equation*} \label{eq:ss5}
S_2=-\frac{\sigma}{\eps^2} \sum_r \sum_j  \bigg( \widehat{\beta}_{j,r}
\frac{1}{|\Omega_j|}\int_{\Omega_j} \uu^{\eps} d\x  \: , \:
\textbf{u}_r^{\eps}-\textbf{u}_j^{\eps} \bigg) .
\end{equation*}
Using $(\vec{a}\otimes\vec{b}\:\vec{c},\vec{d}) 
= (\vec{b},\vec{c})(\vec{a},\vec{d})$, one has 
\begin{equation*}
S_2 = -\frac{\sigma}{\eps^2} \sum_r
\sum_j \ljr \bigg( (\x_r-\x_j), \frac{1}{|\Omega_j|}\int_{\Omega_j}
\uu^{\eps} d\x \bigg) \bigg(  \njr  \: , \:
\textbf{u}_r^{\eps}-\textbf{u}_j^{\eps} \bigg)
\end{equation*}
Using the  Young's inequality  $ab \leq \frac{\widehat \gamma \eps }2 a^2+\frac1{2\widehat \gamma \eps } b^2 $, we get
$$\int_0^T
S_2 dt \leq \frac{\widehat{\gamma} \sigma}{2\eps}\int_0^T\sum_r \sum_j \ljr \bigg( 
\njr  \: , \: \textbf{u}_r^{\eps}-\textbf{u}_j^{\eps} \bigg)^2 dt\\
+
\int_0^T\frac{\sigma}{2\widehat{\gamma}  \eps^3}\sum_r \sum_j \ljr \bigg( (\x_r-\x_j),
\frac{1}{|\Omega_j|}\int_{\Omega_j} \uu^{\eps} d\x \bigg) ^2dt
$$
Using one more time the energy estimate (\ref{bee2}) the second term in the right hand side of the above inequality  is bounded by $\frac{C_3h}{\widehat{\gamma}\eps}\|\V^\eps(0)\|^2_{ L^2(\Omega)}$.

Thus 
$$
\int _0^TS dt \leq 
C_2 h^2  \|\V^\eps(0)\|^2_{H^1(\Omega)}
+
\frac{\widehat{\gamma} \sigma}{2\eps}\int_0^T\sum_r \sum_j \ljr \bigg( 
\njr  \: , \: \textbf{u}_r^{\eps}-\textbf{u}_j^{\eps} \bigg)^2 dt\\
+
\frac{C_3h}{\widehat{\gamma}\eps}\|\V^\eps(0)\|^2_{ L^2(\Omega)}
$$

One finally obtains
the claim
 with a new constant $C\geq0$ proportional to $\|\V^\eps(0)\|^2_{H^1(\Omega)} $.
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proof}[End of the proof of the proposition (\ref{ein_prosit})]
One gets
$$
\mathscr{E}(T) \leq \mathscr{E}(0)
-\frac1\eps \int_0^T \sum_{j,r}l_{j,r}(\textbf{n}_{j,r},\textbf{u}_j^{\eps}-\textbf{u}
_r^{\eps})^2 +
\int_0^T E_1(t)dt + \int_0^T E_2(t)dt
+\int_0^T S(t)dt
$$
where integrals are estimated in 
(\ref{eq:bound1}), (\ref{eq:si2}) and   
(\ref{eq:bound3}).  Using $\mathscr{E}(0)=O(h)$,  it yields with some new constant $C$
$$
\begin{array}{ll}
\mathscr{E}(T)& \leq Ch  \\
& 
\displaystyle 
-\frac1\eps \int_0^T \sum_{j,r}l_{j,r}(\textbf{n}_{j,r},\textbf{u}_j^{\eps}-\textbf{u}
_r^{\eps})^2\\
  & 
    \displaystyle            +            \frac{\gamma}{\eps}
     \int_0^T \sum_{j,r}l_{j,r}(\textbf{n}_{j,r},\textbf{u}_j^{\eps}-\textbf{u}
_r^{\eps})^2 
+Ch(  \frac 1 {\gamma } +1) \\
& \displaystyle  + C T
\frac{h}{\eps}  \\
&
 \displaystyle +C(h^2+\frac{h}{ \widehat \gamma \eps})
 +
 \frac{\sigma\hat \gamma}{2\eps} \int_0^T \sum_r \sum_j \ljr \bigg(  \njr  \: , \:
\mathbf{u}_r^{\eps}-\mathbf{u}_j^{\eps} \bigg)^2
 \end{array}.
$$
Therefore
$$
\mathscr{E}(T)\leq
Ch\left( 2 + \frac{1}{\gamma} +\frac T \eps +h +\frac{1}{\eps \widehat{\gamma}}
\right)-
\frac{1}{\eps}\bigg( 1-\frac1{\gamma} - \frac{\sigma \widehat{\gamma}}{2}
\bigg)\int_0^T \sum_{j,r}l_{j,r}\bigg(\textbf{n}_{j,r},\textbf{u}_j^{\eps}-\textbf{u}_r^{\eps} \bigg)^2 dt.
$$
This estimate is fundamental, since it 
shows the competition between different kind of error terms
and the dissipation of the fluxes.
Choosing by example $\widehat{\gamma}<\frac{1}{\sigma}$ and $\gamma<\frac12$, the last
term is non positive, which means that
the dissipation of the fluxes is dominant in some sense. We choose $\widehat{\gamma}=\frac{1}{\sigma}$ and $\gamma=\frac12$, the last term  vanishes thus
$$
\mathscr{E}(T)\leq
Ch\left( 3 +\frac T \eps +h +\frac{\sigma}{\eps}
\right)$$
 Rereading the proof one can check that the constant $C$ is proportional to  $\|\V^\eps(0)\|^2_{H^3(\Omega)} $, and  if $\sigma=0$ one recovers the result of Mazeran \cite{Mazeran}, chapter 4. The proof was more difficult to obtain due to the non standard discretization of the source term and its incorporation in  the approximate nodal Riemann solver.

 Since $h$ and $\eps$ can be taken less than 1, elementary comparison
principles 
yield
$\ds
\mathscr{E}(t) 
\leq C' (T,\sigma)\nvhp \frac{h}{\eps}$.
The proof is ended. 
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Study of $\|\mathbf {DA}_h^\eps - \mathbf P^0\|$}

We consider the semi-discrete scheme (\ref{das}) wherein for  convenience we
made the following change of unknowns
\begin{equation} \label{eq:barn}
\bar{\uu_r^{\eps}}=\frac{\uu_r^{\eps}}{\eps}
\mbox{ and }
\bar{\uu_j^{\eps}}=\frac{\uu_j^{\eps}}{\eps}.
\end{equation} 
But in order to keep  a simple
notation we dropped the superscript $\eps$ and the bars. Thus the scheme
(\ref{das}) is now written as:

\begin{equation}\label{das:1}
\left\{ 
\begin{array}{l}
\displaystyle \mid\Omega_{j}\mid\frac{d}{dt} p_{j}+
\sum_{r}(l_{jr}\ur,\njr)=0\\
 \sum_{r}l_{jr} (\njr,\uu_r -\uu_j)\njr=0\\
 \left( \eps\sum_{j}\alj+  \sigma B_r\right)\ur=
\sum_{j}\ljr p_j\njr+\eps\sum_j\alj\uj
\end{array}
\right.
\end{equation}
\begin{remark}
If wet set $\eps=0$ we naturally recover the limit diffusion scheme (\ref{diffglace}).
\end{remark}

\subsubsection*{Well-posedness}

What we mean about well-posedness is the following:
if we are able to write the
last two relations of (\ref{das:1}) as a non singular linear system with the $\uu_r$'s and
$\uu_j$'s as unknowns, then we have a unique solution in terms of the $p_j$'s. 
This notion is the relevant one for numerical discretization.

Let us denote $Y=(\{\uu_j\}, \{\uu_r\})$  the vector of unknowns. We can write
 the last
two relations of (\ref{das:1}) as
$MY=b$ where $M$ is a $(J+R)^2$ square matrix, $J$ is the number of cells  and $R$.
One can observe that unless $\eps=0$, $M$ is not a blockwise
triangular matrix.
One has
$$(MY,Y)=\sum_r \left (\sigma B_r \uu_r, \uu_r\right ) 
+\eps\sum_j\sum_r \ljr \left( \uu_r- \uu_j,  \njr\right )^2$$
Assume  $(MY,Y)=0$: in this case   the geometrical assumption  (\ref{geom3}) implies that all
the $\uu_r$ are null and therefore it remains to study 
$
\sum_j\sum_r \ljr \left(  \uu_j,  \njr\right )^2=0
$ that is
$ \sum_j\left (\uu_j, C_j\uu_j\right )=0$ where $
C_j=\sum_r l_{jr} \mathbf n_{jr} \otimes \mathbf n_{jr}$.
 Since  the $C_j$ are all invertible
unless the mesh is degenerate, all the $\uu_j$ are null: we have proved the
invertibility of the matrix $M$ and thus the scheme (\ref{das:1}) exists and is
uniquely defined.

\subsubsection*{Stability}
The $L^2$ norm of the solution is defined as
$
E(t)=
\displaystyle \frac12  \sum_j \vert \Omega_j\vert p_j^2$.

\begin{pro}\label{das_stab} Under the geometrical assumption (\ref{geom3}), the
diffusion approximation scheme (\ref{das:1})  is stable in the $L^2$
norm, in the sense that $E'(t)\leq 0$. Moreover we have
\begin{equation}\label{das:gggg}
\vert\vert \uu_r \vert\vert_{L^2([0,T]\times \Omega)}\leq
C  \left\|  \left( p_j(0)\right)_j \right\|_{L^2(\Omega)}
\end{equation}
and
\begin{equation}\label{das:gs}
\eps \int_{[0,T]}\sum_j \sum_r
l_{jr}(\njr,(\uj-\ur))^{2} \leq  
 \left\|  \left( p_j(0)\right)_j \right\|_{L^2(\Omega)}.
\end{equation}
\end{pro}

\begin{proof}
One has
$$
E^{'}(t)= \sum_j \vert \Omega_j\vert p_j \frac{d}{dt}p_j
= -\sum_j  p_j \sum_{r}(l_{jr}\ur,\njr) 
 =\sum_r \left (\uu_r, \sum_{j}l_{jr}\njr p_j\right ) .
$$

 Now using the last equation of (\ref{das:1}),  one finds
\begin{equation*}\label{das:4}
E^{'}(t)= -\sum_r \left (\uu_r, \left( \eps\sum_{j}\alj+ 
\sigma B_r\right)\ur-
\eps\sum_j\alj\uj\right )
\end{equation*}
We expand the right hand side  of the previous equation 
\begin{equation*}\label{das:5}
E^{'}(t)= -\sum_r \left (\sigma B_r \uu_r, \uu_r\right ) 
-\eps \sum_r\left( \uu_r, \sum_j \alj(\uu_r -\uu_j\right ).
\end{equation*}
Permuting the sums in the second term of the right hand side , we show that
\begin{equation}\label{das:6}
E^{'}(t)= -\sum_r \left (\sigma B_r \uu_r, \uu_r\right ) 
-\eps\sum_j\sum_r \left( \uu_r,  \alj(\uu_r -\uu_j)\right ).
\end{equation}
Using the definition of the $\uu_j$, second line of (\ref{das:1}), one has
\begin{equation}\label{das:7}
\sum_j 
\left( \uu_j,  \sum_r \alj(\uu_r -\uu_j)\right)=0. 
\end{equation}
Combining (\ref{das:7})$\times \eps$  with (\ref{das:6}) and using the definition of
the matrices $\alj$ one has finally
\begin{equation*}\label{das:8}
E^{'}(t)= -\sum_r \left (\sigma B_r \uu_r, \uu_r\right ) 
-\eps\sum_j\sum_r \ljr \left( \uu_r- \uu_j,  \njr\right )^2.
\end{equation*}
By the geometrical assumption  (\ref{geom3}) we have $E^{'}(t)\leq 0$, that is
the $L^2$ stability.
By integrating this equality on $[0,T]$ we obtain
\begin{equation*}\label{eq:ds5bis}
\displaystyle
E(T) + \int_{[0,T]}\sum_r \left (\sigma B_r \uu_r, \uu_r\right ) 
 +\int_{[0,T]}\eps\sum_j\sum_r \ljr \left( \uu_r- \uu_j,  \njr\right )^2=E(0)
\end{equation*}
Using again the geometrical assumption  (\ref{geom3}) for the terms
$(B_r\ur,\ur)$ we have
\begin{equation*}\label{eq:ds6bis}
E(T) + \alpha \int_{[0,T]}\sum_r  \vert V_r\vert \  \vert\vert\uu_r\vert\vert^2 
+ \int_{[0,T]}\eps\sum_j\sum_r \ljr \left( \uu_r- \uu_j,  \njr\right )^2\leq
E(0)
\end{equation*}
which gives (\ref{das:gggg}) and (\ref{das:gs}).
\end{proof}

\subsubsection*{Consistency}

For convenience   we set
\begin{equation*} \label{eq:con1}
\pej=p(\x_j,t)\ \ \uej=-\frac{1}{\sigma}\nabla p(\x_j,t)\ \
\uer=-\frac{1}{\sigma}\nabla p(\x_r,t)
\end{equation*}
where $p(x,t)$ is the solution of the diffusion equation. 
 We define the consistency error 
by inserting these quantities into the three equations of
(\ref{das:1}). 
It yields 
\begin{equation*} \label{eq:d2.2}
\left\{ 
\begin{array}{l}
a_j=\displaystyle \frac{d}{dt} \pej+
\frac{1}{\mid\Omega_{j}\mid}\sum_{r}(l_{jr}\uer,\njr)\\
 \br=\frac{1}{\vert V_r\vert}\left (   \sigma B_r \uer- \sum_{j}\ljr
\pej\njr+ \eps\sum_j\alj(\uer-\uej)\right ), \\
\cj= \frac{1}{h}\sum_{r}l_{jr} (\njr,\uer -\uej)\njr=0.
\end{array}
\right.
\end{equation*}

\begin{lemma}\label{consistency}
Assume  the geometrical  assumptions (\ref{geometrie}).
Assume $p_0\in H^{4}(\Omega)$.
Then there exists a constant $C>0$ such that the following 
estimates hold
\begin{equation} \label{eq:d20}
\left| a_j\right|\leq C h
\quad
 \mbox{for all } j  ,
\end{equation}
\begin{equation} \label{eq:d21}
\left|  \br\right|  \leq C(h+\eps), \quad
\mbox{for all } r   .
\end{equation}
and
\begin{equation} \label{eq:d22}
\left| \cj\right| \leq C h, \quad
\mbox{for all } j   .
\end{equation}
\end{lemma}

\begin{proof} 
Since $p_0\in H^{4}(\Omega)$, one has that $p(t)\in H^{4}(\Omega)$ 
which turns into the fact that $\nabla p(t)\in L^\infty(\Omega)$ and $\nabla ^2p(t)\in L^\infty(\Omega)$ by means of 
Sobolev embeddings. It is sufficient to justify 
the Taylor expansions done hereafter.
By construction
$$
\partial_t p(\xj,t)=\frac{1}{\sigma}\frac{\int_{\Omega_j} \partial_t
p(x,t)dx}{\left| \Omega_j \right|}+O(h)=
\frac{1}{\sigma}\frac{\int_{\Omega_j} \Delta p dx}{\left| \Omega_j
\right|}+O(h)=
\frac1{\sigma \left| \Omega_j \right|}\int_{\partial \Omega_j} \partial_n p d\sigma
+O(h).
$$
By definition of $l_{jr} \njr$ one has
$$
 \sum_r l_{jr}\left(\njr, \nabla p (\xr,t) \right)=
\sum_k \int_{\partial\Omega_{jk}} \left(
\frac{  \nabla p\left(x_{jk}^+ \right)+ \nabla p\left(x_{jk}^- \right)   }2,
\mathbf{n}_j \right) d\sigma 
$$
where $n_j=\tilde{n}_{j,r}$ defined in the previous part and the nodes $x_{jk}^+$ and $x_{jk}^-$ are the end of the edge
$\partial\Omega_{jk}=\Omega_j\bigcap\Omega_k$. Note that  $\partial \Omega_j =
\bigcup\partial\Omega_{jk} $.
Therefore
$$
a_j=O(h) + \frac{1}{\sigma}\frac1{\left| \Omega_j \right|}
\sum_k \int_{\partial\Omega_{jk}} \left(
\nabla p- \frac{  \nabla p\left(x_{jk}^+ \right)+ \nabla p\left(x_{jk}^- \right)
  }2, \mathbf{n}_j \right) d\sigma 
$$
Since the function under the integral is approximated by the trapezoidal rule, 
the error of integration
 is $O(h^2)$
$$
\left| \int_{\partial\Omega_{jk}} \left(
\nabla p- \frac{  \nabla p\left(x_{jk}^+ \right)+ \nabla p\left(x_{jk}^- \right)
  }2, \mathbf{n}_j \right) d\sigma   \right| \leq C h^2 \left|
\partial\Omega_{jk}\right|\leq Ch^3.
$$
After division by $\mid \Omega_j \mid$ and using the lower bound of the
regularity hypothesis (\ref{eq:d5}),
one gets that $a_j=O(h)$.
Now we write  $\br=\br^a+\br^b$  with
$$
\br^a = 
\frac1{\vert V_r \vert}\left(  \left( \sigma \sum_j l_{jr}\njr\otimes
\left(\xr - \xj    \right)  \right)  
 \bigg(-\frac{\nabla p (\xr,t)}{\sigma}\bigg) -   \sum_j  l_{jr}\njr
p(\xj,t)\right)
$$
$$
= \frac1{\vert V_r \vert} \sum_j  
\bigg(
  \big( \xj - \xr  , \nabla p (\xr,t)   \big)  
  -    p(\xj,t)  
\bigg)
l_{jr}\njr
$$
and 
$$
\br^b = 
\frac\eps{\sigma \vert V_r \vert} \left(  \sum_j l_{jr}\njr\otimes \njr \left( \nabla p
(\xj,t)  - \nabla p (\xr,t)\right )\right )
$$
A simple Taylor expansion shows that
$$
     p(\xj,t)+
\left(\xr - \xj  , \nabla p (\xr,t)  \right) 
  = p(\xr,t)+O_{jr}(h^2).
$$
So
$
\br ^a= 
\frac1{\vert V_r \vert}  \sum_j O_{jr}(h^2)  l_{jr}\njr =O(h)
$
due to (\ref{eq:d7}), (\ref{eq:d5.2}). 
Another Taylor expansion shows that 
$ \nabla p (\xj,t)-\nabla p (\xr,t)=O_{jr}(h)$
so that 
$\vert \vert \br^b\vert \vert=O(\eps)$ and
$| \br|=O(h+\eps)$.
 We finally obtain with similar arguments
$ \vert \cj  \vert=O( h)$. 
It ends the proof of the lemma.
\end{proof}

\subsubsection*{Convergence}

Let us define three  error variables 
$$
e_j= p_j -\pej
\mbox{ , }
\fr = \ur -\uer
\mbox{ and }
\fj = \uj -\uej
$$ 
The numerical error is 
$
E(t)=\frac12  \| e \|_{L^2(\Omega)}^2=
 \sum_j \left| \Omega_j \right| \left(    p_j
-p(\xj,t)\right)^2 $. 
We will also consider
$
F(t)=
\| \ff \|_{L^2([0,t]\times \Omega)}^2=
 \int_0^t \sum_r \left| V_r \right| |\fr|^2,
$
and 
$
\| \gf \|_{L^2([0,t]\times \Omega)}^2=  \int_0^t
\sum_j
 \left| \Omega_j \right| \   \left| \fj  \right|^2 $.
\begin{theorem} \label{theor:main0}
Assume $p \in W^{3, \infty} (\Omega)$ and assume that geometrical conditions
(\ref{geometrie}) are verified.
There  exists a  constant
$C(T)>0$ such that 
\begin{equation} \label{eq:dconv1}
 \| e \|_{L^\infty(  [0,T]: L^2(\Omega) )}
 \leq C(T)(h+\eps),
\end{equation}
\begin{equation} \label{eq:dconv2}
 \| \ff \|_{L^2([0,T]\times \Omega)} \leq C(T) (h+\eps)  
 ,
\end{equation}
\begin{equation} \label{eq:dconv3}
\eps \int_0^T \sum_j \sum_r    \ljr \left( \fr  -
\fj ,\njr \right)^2\leq C(T) (h+\eps)^2, 
 \end{equation}
and 
\begin{equation} \label{eq:dconv4}
\| \gf \|_{L^2([0,T]\times \Omega)} \leq C(T) (h+\eps)\sqrt{(1+\frac
h\eps )} . 
\end{equation}

\end{theorem}

\begin{proof}
By construction
\begin{equation*}\label{eq:d30}
\left\{ 
\begin{array}{l}
\displaystyle \mid\Omega_{j}\mid e'_{j}+
\sum_{r}(l_{jr}\fr,\njr)=-\mid\Omega_{j}\mid a_j\\
 \left( \eps\sum_{j}\alj+  \sigma B_r\right)\fr-
\sum_{j}\ljr e_j\njr-\eps\sum_j\alj\fj=-\mid
V_r\mid\br , \\
 \sum_{r}l_{jr} (\njr,\fr -\fj)\njr=-h\cj.
\end{array}
\right.
\end{equation*}
By proceeding as for the results of stability one has the identity
$$
E'(t)= \sum_j |\Omega_j| e_j e_j'=
\sum_j  e_j\left(
- \left( \sum_r l_{jr}\left(\njr, \fr  
   \right)\right)
- \left| \Omega_j \right| a_j 
\right)
$$ 
$$
=- \sum_r \sum_j (  l_{jr}  \mathbf n_{jr} e_j , \mathbf f_r)
- \sum_j\left| \Omega_j \right| e_j a_j 
$$
$$= -\sum_r \left (\fr, \left( \eps\sum_{j}\alj+  \sigma
B_r\right)\fr- \eps\sum_j\alj\fj\right )
- \sum_j \left| \Omega_j \right| a_j e_j
- \sum_r \left| V_r \right| \br \fr
$$
$$= -\sum_r \left (\sigma B_r \fr, \fr\right ) 
-\eps \sum_r\left( \fr, \sum_j \alj(\fr -\fj\right )
- \sum_j \left| \Omega_j \right| a_j e_j
- \sum_r \left| V_r \right| \br \fr
$$
$$= -\sum_r \left (\sigma B_r \fr, \fr\right ) 
-\eps\sum_j\sum_r \ljr \left( \fr- \fj,  \njr\right )^2
- \sum_j \left| \Omega_j \right| a_j e_j
- \sum_r \left| V_r \right| \br \fr +\eps\sum_j h \fj\cj.
$$
Using a Young's inequality and the Cauchy-Schwarz inequality, one gets
\begin{equation} \label{eq:yi}
\begin{aligned}
E'(t) \leq & ||e||_{L^2(\Omega)}\ ||a||_{L^2(\Omega)} +
\left(
\frac{\mu}{2} ||\ff ||^2_{L^2(\Omega)} + \frac{1}{2\mu} ||\bb||^2_{L^2(\Omega)} 
\right)
-  \alpha \|  \ff \|^2_{L^2(\Omega)}\\
&
  -\eps\sum_j\sum_r \ljr \left( \fr- \fj,  \njr\right )^2 
+\frac{\eps}{2h}\left (\eta||\gf ||^2_{L^2(\Omega)}
+\frac{1}{\eta}||\cc||^2_{L^2(\Omega)} \right )
\end{aligned}
\end{equation}
where $ \mu,\eta >0$ are two arbitrary coefficients that will be 
specified later. 
Now using  (\ref{geom4})
we have
$$
\vert \Omega_j\vert \ \vert \fj \vert^2\leq C h\sum_r\ljr(\njr,\fj)^2.
$$
Therefore
$$
\vert \Omega_j\vert \ \vert\fj \vert^2\leq 
Ch \left(2\sum_r\ljr(\njr,\fj-\fr)^2+2\sum_r \ljr \vert 
\fr \vert^2\right ).
$$
So 
there exists two constant $C_1$ and $C_2$ such that
\begin{equation}\label{gl2}
\vert\vert\gf \vert\vert^2_{L^2(\Omega)} \leq 
C_1 h\sum_{jr}\ljr(\njr,\fj-\fr)^2 +  C_2\vert\vert\ff \vert\vert^2_{L^2(\Omega)}.
\end{equation}
So from (\ref{eq:yi}) we  obtain 
$$
E'(t) \leq  ||e||_{L^2(\Omega)}\ ||a||_{L^2(\Omega)} +
 \frac{1}{2\mu} ||\bb||^2_{L^2(\Omega)} 
+( \frac{\mu}{2} +\frac{C_2\eps\eta}{2h}- \alpha) \|  \ff \|^2_{L^2(\Omega)}
$$
$$
+ (\frac{C_1}{2}\eta -1)\eps\sum_j\sum_r \ljr \left( \fr- \fj,  \njr\right )^2 
+\frac{\eps}{2h\eta} ||\cc||^2, \qquad \forall \mu,\eta >0.
$$
Let us choose $\mu=\frac{\alpha}{2}$ and $\eta =\min(\frac{1}{C_1},\frac{\alpha h}{C_2
\eps})$, so that
\begin{equation*} \label{eq:d40}
\begin{aligned}
E'(t) \leq & \sqrt{2}\sqrt{E(t)}\ ||a||_{L^2(\Omega)}  - \frac{\alpha}{4}  F'(t)
- \frac{\eps}{2}\sum_j\sum_r \ljr \left( \fr- \fj,  \njr\right )^2\\
& +  \frac{1}{2 \alpha} ||\bb||^2_{L^2(\Omega)} +\max(\frac{\eps C_1}{2h},\frac{C_2
\eps^2}{\alpha h^2}) ||\cc||^2_{L^2(\Omega)} .
\end{aligned}
\end{equation*}
where we have used  $\frac1{\min(a,b)}=\max(\frac1a, \frac1b)$.
By the consistency estimates (\ref{eq:d20}-\ref{eq:d21}-\ref{eq:d22}) 
 and since the domain $\Omega$ is bounded, one finds a constant C such that
\begin{equation} \label{eq:d40bis}
E'(t) \leq  E(t)  - \frac{\alpha}{4}  F'(t)
- \frac{\eps}{2}\sum_j\sum_r \ljr \left( \fr- \fj,  \njr\right )^2
+  C\left (h+\eps\right )^2. 
\end{equation}
Thus 
$$
E'(t) \leq  E(t)  
+  C\left (h+\eps\right )^2. 
$$
By construction $E(0)=O(h^2)$ for a smooth initial data.
 So by the Gr\"onwall lemma 
$
E(t)\leq C(t) (h+\eps)^2
$
which gives (\ref{eq:dconv1}).
Integrating  (\ref{eq:d40bis}) in the time interval $[0,t]$,  we find that for any 
for $t\leq T$
$$
E(t)+  \frac{\alpha}{4}  F(t)+\int_0^t \frac{\eps}{2}\sum_j\sum_r \ljr \left(
\fr- \fj,  \njr\right )^2
\leq
 E(0)+ \int_0^t \left(  E(t)+ C(h+\eps)^2  \right) dt \leq C'(T) (h+\eps)^2.
$$
It shows   
the  estimates (\ref{eq:dconv2}) and (\ref{eq:dconv3}).
Using   (\ref{gl2}) 
one gets
\begin{equation*}\label{gl3}
\int_0^T \vert\vert\gf \vert\vert^2_{L^2(\Omega)} \leq 
C_1 h\int_0^T\sum_{jr}\ljr(\njr,\fj-\fr)^2 +  C_2\int_0^T\vert\vert\ff \vert\vert^2_{L^2(\Omega)}\leq
C"(T)(h+\eps)^2(1+\frac h\eps)
\end{equation*}
from which (\ref{eq:dconv4}) follows.
The proof is finished.
\end{proof}

\begin{corollary}
From (\ref{eq:dconv1}) and (\ref{eq:dconv2})
we deduce
\begin{equation} \label{eq:enc1}
\| \mathbf W_h^\eps  -\W^\eps \|_{L^2([0,T]\times  \Omega)   )   }\leq C(T) (h+\eps).
\end{equation}
\end{corollary}
\subsubsection*{$L^\infty$ stability of the derivative}

This estimate is needed in the next section.

\begin{pro}
Consider a smooth enough initial $p_0$.
One has
\begin{equation*} \label{eq:der1}
\bigg\|  \frac{d}{dt} p_h  \bigg\|_{ L^\infty([0,T];L^2(\Omega)   )  }
\leq C \max\left(1,\sqrt{\frac{\eps} {h} }
\right),  
\end{equation*}
and
\begin{equation}\label{e:qder2}
\bigg\|( \frac{d}{dt} \mathbf u_r  )_r \bigg\|_{L^2([0,T] \times  \Omega)   }
\leq C \max\left(1,\sqrt{\frac{\eps} {h} }
\right).
\end{equation}
\end{pro}
\begin{proof}
Let us denote the time derivative of any $f$
as $\tilde f=\partial_t f$.
By linearity of the system (\ref{das:1}), one has
\begin{equation*}\label{das:1:der}
\left\{ 
\begin{array}{l}
\displaystyle \mid\Omega_{j}\mid \frac{d}{dt} \tilde p_{j}+
\sum_{r}(l_{jr}  \tilde\uu_r,\njr)=0\\
 \sum_{r}l_{jr} (\njr, \tilde\uu_r - \tilde\uu_j)\njr=0\\
 \left( \eps\sum_{j}\alj+  \sigma B_r\right) \tilde\uu_r=
\sum_{j}\ljr  \tilde p_j\njr+\eps\sum_j\alj \tilde\uu_j
\end{array}
\right.
\end{equation*}
The $L^2$ stability property yields
$$
\|  \tilde p_h(t)\|^2_{L^\infty([0,T];L^2(\Omega)  )   } 
+\int_0^t \sum_r ( B_r \tilde\uu_r, \tilde\uu_r )dt
\leq
\|  \tilde p(0)\|_{L^2(\Omega)} 
$$
where this last quantity can be estimated
with the first equation of (\ref{das:1}):
the square of the norm in (\ref{e:qder2}) is also bounded by
the same quantity.
 It remains to bound $\|  \tilde p(0)\|_{L^2(\Omega)  )  } $.
At $t=0$ one has 
$$
\frac{d}{dt} p_j=\frac1\sigma \frac1{|\Omega_j|}
\sum_r l_{jr}  ( \nabla p(\x_r) ,\njr)
- \frac1\sigma \frac1{|\Omega_j|}
\sum_r l_{jr}  ( \mathbf q_r ,\njr).
$$
Using the same consistency arguments as before, the first
term in the right hand side is bounded in $L^2$ uniformly
with respect to $h$ and $\eps$. The second one is bounded in $L^2$ 
by a term of order 
$C\frac{h \sqrt {\max( h^2, \eps h)}}{h^2}=C
\max\left(1,\sqrt{\frac{\eps} {h} }
\right)$. The proof is ended.
\end{proof}

\begin{pro}\label{esti_initial_data}
One has that
\begin{equation*} \label{eq:iner1}
\bigg\| \left(  \uu_r +\frac1\sigma \nabla p(\x _r)\right)(t=0)\bigg\|_
{ L^2(\Omega) }\leq C \sqrt {h\max( h, \eps )}
\end{equation*}
and
\begin{equation} \label{eq:iner10}
\bigg\| \left(  \uu_j +\frac1\sigma \nabla p(\x _j)\right)(t=0)\bigg\|_
{ L^2(\Omega) }\leq C  
 \sqrt{ \frac{h}\eps} \max(  h, \eps).  
\end{equation}
\end{pro}
\begin{proof}
Let us write $\mathbf q_r= \uu_r +\frac1\sigma \nabla p(\x _r)$
and $\mathbf s_j= \uu_j +\frac1\sigma \nabla p(\x _j)$.
These quantities are solution
of the system
$$
\left\{
\begin{array}{ccll}
 \left( \eps\sum_{j}l_{jr} \njr\otimes \njr  +  \sigma B_r\right) \mathbf q_r
& -
\eps \sum_{j}l_{jr} \njr\otimes \njr \mathbf s_j& =
\mathbf  d_r^1+\mathbf  d_r^2 , & \forall r,  \\
- \eps \sum_{r}l_{jr} (\njr, \mathbf q_r )\njr & +  
\eps  \sum_{r}l_{jr} (\njr, \mathbf s_j )\njr& =\mathbf  d_j,
&
 \forall j, 
\end{array}
\right.
$$
where the right hand sides are
$$
\mathbf  d_r^1=
\sum_{j}\ljr   p(\mathbf x_j)\njr+ \sum_j l_{jr}  (\x_r -\x_j, \nabla p(\x_r))\njr,
$$
$$
\mathbf  d_r^2=\eps\sum_j l_{jr}  \left( \njr, \nabla p(\x_r)
- \nabla p(\x_j) \right)
\njr    
$$
and
$$
\mathbf  d_j=-\eps\sum_r l_{jr}  \left( \njr, \nabla p(\x_r)
- \nabla p(\x_j) \right).
$$
Taking the scalar product of the first line by $\mathbf q_r$
and of the second line by   $\mathbf s_j$, one gets the identity
$$
\sigma \sum_r \left(B_r \mathbf q_r, \mathbf q_r    \right)
+ \eps \sum_{jr} l_{jr}
\left( \njr, \mathbf q_r - \mathbf s_j  \right)^2
$$
$$
=
\sum_r \left( \mathbf d_r^1, \mathbf q_r   \right)+  
\eps \sum_{jr} l_{jr}
\left( \njr, \mathbf q_r - \mathbf s_j  \right)
\left( \njr, 
 \nabla p(\x_r)
- \nabla p(\x_j)
 \right).
$$
A Young's inequality yields
\begin{equation} \label{eq:y1}
\sigma \sum_r \left(B_r \mathbf q_r, \mathbf q_r    \right)
+\frac\eps2
 \sum_{jr} l_{jr}
\left( \njr, \mathbf q_r - \mathbf s_j  \right)^2\leq 
\sum_r \left( \mathbf d_r^1, \mathbf q_r   \right)+
 \frac\eps2  \sum_{jr} l_{jr}
\left( \njr, 
 \nabla p(\x_r)
- \nabla p(\x_j)
 \right)^2.
\end{equation}
One gets
$$
\left| \mathbf d_r^1 \right| \leq Ch^2
\mbox{ and }
  \sum_{jr} l_{jr}
\left( \njr, 
 \nabla p(\x_r)
- \nabla p(\x_j)
 \right)^2\leq Ch.
$$
So (\ref{eq:y1}) implies
\begin{equation*} \label{eq:qq1}
\|\mathbf q\|_{L^2(\Omega)}^2\leq Ch 
\|\mathbf q\|_{L^2(\Omega)}+C\varepsilon h.
\end{equation*}  
It means that $\|\mathbf q\|_{L^2(\Omega)}$ is below the maximal root
of the polynomial $p(x)=x^2-Chx-C\eps h$, that is
for some constant $K >0$
\begin{equation} \label{eq:iner11}
\|\mathbf q\|_{L^2(\Omega)}\leq x^+=\frac{Ch+\sqrt{C^2h^2+4C\eps h  }}{2}
\leq K \sqrt{ \max(h^2 , h \eps  )}.
\end{equation}
It yields the proof of the first inequality.

Concerning the second inequality, we note that 
$$
\|\mathbf s\|_{L^2(\Omega)}^2\leq 
2 \|\mathbf q\|_{L^2(\Omega)}^2+ 
Ch \sum_{jr} l_{jr}
\left( \njr, \mathbf q_r - \mathbf s_j  \right)^2
$$
which can be upper bounded using (\ref{eq:y1}) and (\ref{eq:iner11}). We obtain 
$$
\|\mathbf s\|_{L^2(\Omega)}^2
\leq C  { \max(h^2 , h \eps  )}
+ C \frac{h}\eps
h  \sqrt{\max(h^2, h\eps)  } 
$$
The numbers  $h$ and $\eps$ can be considered less than 1.
There are two cases:
\begin{itemize}
\item Either $h<\eps$:  so
$
\|\mathbf s\|_{L^2(\Omega)}^2
\leq \widetilde C  h\eps    
$ for another constant $\widetilde C$.
\item 
Or $\eps\leq h$: so 
$
\|\mathbf s\|_{L^2(\Omega)}^2
\leq \widetilde C \frac{h^3}\eps $
 for another constant $\widetilde C$.
\end{itemize}
So we can writes
$$
\|\mathbf s\|_{L^2(\Omega)}
\leq C \sqrt{ \frac{h}\eps} \max(  h, \eps), \qquad C>0.
$$
The proof of (\ref{eq:iner10}) is ended.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Study of $\| \mathbf P_h^\varepsilon - \mathbf {DA}_h^\eps  \|$}

In this section we prove that for fixed step mesh, the discrete
solution of the heat equation  scheme tends to the discrete solution of the diffusion
equation scheme when $\eps$ tends to zero. Indeed, we will prove the following result:
\begin{proposition}\label{jlbtodas}
Assume a smooth initial data.
There exists a constant $C(T)>0$ such that the following estimate holds:
\begin{equation} \label{eq:ww1}
\|\V_h^{\eps}-\mathbf W_h^\eps\|_{L^2([0,T] \times \Omega))} \leq
C(T)\left(\eps
\max\left(1,\sqrt{\frac{\eps} {h} }
\right)+ \big( h^2+\eps^2\big)\right).
\end{equation}
\end{proposition}
\begin{proof}
We introduce $\mathbf{R}_j= \frac{d}{dt} \mathbf u_j$  such that the solution $\V_h$ of the
diffusion scheme \eqref{das} satisfies
\begin{equation}\label{schemP11diff}
\left\{\begin{array}{l}
\ds \mid \Omega_j \mid\frac{d}{dt} p_j+\frac{1}{\eps}\sum_r(\ljr\njr,\ur)=0,\\
\ds \mid \Omega_j \mid\frac{d}{dt}\uj+\frac{1}{\eps}\sum_r(\ljr p_j\njr
+\alj(\uj-\ur)) =|\Omega_j| \mathbf{R}_j,\\
\ds \left(A_r+\frac{\si}{\eps}B_r\right) \ur-\sum_j\ljr
p_j\njr-\sum_j\alj  \uj=0 .
\end{array}\right.
\end{equation}
By definition $\|\mathbf{R}\|_{L^2(\Omega)}= \|\frac{d}{dt}
\uj\|_{L^2(\Omega)}$. Using the third line of \eqref{das}, one has
$\uj=A_j^{-1}\sum_r \alj\ur$ and thus $\|\frac{d}{dt}
\uj\|_{L^2(\Omega)}\leq C \|\frac{d}{dt} \ur\|_{L^2(\Omega)}$. 
Using
(\ref{e:qder2}) (and taking care
that a rescaling by a factor $\eps$
was systematically used
in the previous section, see (\ref{eq:barn})), one gets
for a smooth initial data
\begin{equation*}\label{dddd}
\|\mathbf{R}\|_{L^2([0,T]\times\Omega)}\leq C
\eps \max\left(1, \sqrt{\frac\eps h}   \right).
\end{equation*}
We denote by $e_j=p_j-p_j^{\eps}, \;
\fj =\uj-\uj^{\eps}$ and
$\fr =\ur-\ur^{\eps}$. One finds, making the
difference between the schemes \eqref{schemP11diff} and \eqref{eq:4}:
\begin{equation*}\label{schemP11diff2}
\left\{\begin{array}{l}
\ds \mid \Omega_j \mid\frac{d}{dt} e_j+\frac{1}{\eps}\sum_r(\ljr\njr,\fr )=0,\\
\ds \mid \Omega_j \mid\frac{d}{dt} \fj +\frac{1}{\eps}\sum_r(\ljr e_j\njr
+\alj(\fj -\fr )) =|\Omega_j| \mathbf{R}_j,\\
\ds \left(A_r+\frac{\si}{\eps}B_r\right) \fr -\sum_j\ljr
e_j\njr-\sum_j\alj  \fj =0.
\end{array}\right.
\end{equation*}
 We are going to write an inequality satisfied  by $E(t)=
\| e(t)\|_{L^2(\Omega)  } ^2+\|\mathbf f(t)\|_{L^2(\Omega)  }^2
$, knowing that  $e(0)=0  $. Using the
same kind of proof than for the $L^2$ stability of the JL-(b) scheme
(proposition \ref{propesti}), one can show that
 \begin{equation*}
\frac12 \frac{d}{dt}
E(t) \leq \sum_j
| \Omega_j | 
(\mathbf{R}_j,\fj ) \leq \|\mathbf f\|_{L^2(\Omega)}  \| \mathbf R\|
_{L^2(\Omega)} \leq \sqrt{E(t)}
\| \mathbf R\|
_{L^2(\Omega)} .
\end{equation*}
So one has for $t\leq T$ 
$$
\sqrt{  E(t)}\leq \sqrt{E(0)}+
C t\|\mathbf  R\|_{L^2([0,T]\times \Omega)}
=
\| \mathbf f (0)\|_{L^2(\Omega)  } +
Ct\|\mathbf  R\|_{L^2([0,T]\times \Omega)}.
$$
One has 
 $\|\mathbf f(0)\|_{L^2(\Omega)  }= O(\sqrt{h\eps}\max(h,\eps)   )$
by virtue of (\ref{eq:iner10}) (taking care that there is a rescaling
by a factor $\eps$, see (\ref{eq:barn})).
In any case, one has
$\|\mathbf f(0)\|_{L^2(\Omega)  }\leq C(h^2+\eps^2)$.
Since
$
\|\V_h^{\eps}-\mathbf W_h^\eps\|_{L^2([0,T] \times \Omega))} =\sqrt{\int_0^TE(t)dt}
$, 
the proof is ended.
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\subsection{End of the proof of the uniform AP property in 2D}
We have the following
result of uniform convergence.
\begin{theorem} \label{theor:main}
We assume the initial data is smooth. Under the geometrical assumptions
(\ref{geometrie}) in 2D,  there exists a constant
C(T)>0 independent of $\eps$, such that the following estimate holds:
\begin{equation*}\label{est2}
\|\V^{\eps}-\V^{\eps}_h\|_{L^2([0,T]\times\Omega)}\leq
C(T)h^{\frac{1}{4}}.
\end{equation*}
\end{theorem}

\begin{proof}
The proof is a slight adaptation of our initial proposition
\ref{prop:1}, where we use the norm
$\|\cdot\|=\|\cdot\|_{L^2([0,T]\times\Omega)   ) }$.
Indeed one has
$$
\|\V_h^\eps-\V^\eps\|\leq
\min \left(
\|\V_h^\eps-\V^\eps\|_{\rm naive},
\|\V_h^\eps-\mathbf{W}^\eps_h\|
+
\|\mathbf{W}^\eps_h-\W^\eps\|
+
\|\W^\eps-\V^\eps\|
\right)
$$
where each estimates are given in order in 
(\ref{eq:veps2}), (\ref{eq:ww1}), (\ref{eq:enc1}) and (\ref{eq:enc22}).
Therefore
$$
\|\V_h^\eps-\V^\eps\|\leq
C(T) \min \left(
\sqrt{\frac h \eps  } \; \; , \; \;
\eps \max\left(1, \sqrt{\frac \eps h } \right) +
h + \left(h +\eps
\right)+\eps
\right)
$$
$$
\leq  C(T) \min \left(
\sqrt{\frac h \eps  } \; \; , \; \;
\eps 
\right)+
C(T) \min \left(
\sqrt{\frac h \eps  } \; \; , \; \;
\sqrt{\frac {\eps^3} h }
\right)
$$
$$
\leq
C(T) \min \left(
\eps^{-\frac12   } h^{\frac12  }\; \; , \; \;
\eps 
\right)+C(T) h^{- \frac12  }
 \min \left(
\eps^{-\frac12   } h \; \; , \; \;
\eps^{\frac 32} 
\right).
$$
The first contribution is estimated with
$a=1$ and $b=c=\frac12$ as in 1D and as in the inequality (\ref{eq:toutdebut}) of proposition \ref{prop:1}:
it yields a contribution $O(h^ \frac13 )$.
The second contribution can also be estimated in the context of  proposition \ref{prop:1}.
One gets  a convergence rate  
$O \left( \frac{ac}{a+b}-\frac12 \right)$ where now $a=\frac32$, $b=\frac12$ and $c=1$:
that is $O(h^ \frac14 )$.
The worst case is 
$O(h^ \frac14 )$
which ends the proof.
\end{proof}

\section{Numerical illustration}\label{sec::num}

To illustrate the theory and have a more quantitative version of the error estimates
studied in this work, we consider the academic square $\Omega=[0,1]^2$ and discretize the hyperbolic heat equation
of a mesh made with random quads. 
A random quad mesh is made of quads where the vertices are moved
randomly around their initial position, by a factor between 10\% and 30\%.
We use the fully implicit time discretization version of the 2D scheme
detailed in this work. The solution of the linear systems is computed via
an iterative GMRES algorithm, which converges smoothly in our numerical experiments.
The reference analytical solution used in our tests is designed by separation of variables.
A solution of (\ref{eq:mod1}) is
$$
p= f+\frac{\eps^2}\sigma \partial_t f
\mbox{ and }
\mathbf u= -\frac\eps \sigma \nabla f,
$$
with $f$ solution of 
$
\partial_t f +\frac{\eps^2}\sigma \partial_t^2 f -\frac1\sigma \Delta f=0$.
We add periodic boundary conditions and consider
$$
f(t,x,y)=\alpha(t)\cos (\pi x ))\cos( \pi y ).
$$
The function $\alpha$ is determined as the solution of
$$
\alpha'(t)+ \frac{\eps^2}\sigma\alpha''(t)+\frac{2\pi}\sigma \alpha=0
$$
whith $\alpha'(0)=0$ and $\alpha(0)=1$.
For small $\eps$, which is the case we are interested in, the solution is computed as follows.
First determine 
$$
\lambda_1=-
\frac{
\sigma \left( \sqrt{1-\frac{\eps^2}{\sigma^2}  8 \pi^2  } +1\right)
}{2 \eps^2  }
\mbox{ and }
\lambda_2=
\frac{
\sigma \left( \sqrt{1-\frac{\eps^2}{\sigma^2}  8 \pi^2  } -1\right)
}{2 \eps^2  }.
$$
Then 
$$
\alpha(t)=\frac{\lambda_2}{\lambda_2-\lambda_1}e^{\lambda_2 t  }
-
\frac{\lambda_1}{\lambda_2-\lambda_1}e^{\lambda_1 t  }
$$
from which $p(t)$ and $\mathbf u(t)$ are easily recovered.

We decide that an exact relation is enforced between
$\eps$ and $h=\frac1N$, so that the error can be expressed as a function of $h$ solely.
The relation between $\eps$ and $h$ writes
$\eps=0.01 (40h)^\gamma$ for $\gamma \in\{0,\frac14, \frac12, 1, 2  \}$.
The error between the exact solution and the numerical solution is computed numerically
in function of $h=\frac1N$, for different values of $\gamma$, and the results of some of these numerical experiments is
displayed in figure \ref{fig1}. The results correspond  to the  time $T = 0.02$ using the time step 
$\Delta t = 0.2 h^2$.

\begin{figure}
\begin{center}
\includegraphics[width=9cm,angle=-90]{sortie_enfin.eps}
\end{center}
\caption{The error is plotted in log scale versus the number of cells per direction for the test problem described
in section \ref{sec::num}.
Each curve corresponds to a value of $\gamma\in\{0,\frac14, \frac12, 1, 2  \}$, plus 
a reference line for order one. One sees that the order of convergence is an increasing function
of $\gamma$.}
\label{fig1}
\end{figure}

As predicted by  the theory, the scheme is uniformly AP and the error behavior is a continuous function of $\gamma$
between the  hyperbolic and parabolic limits. However the results are much better, in the sense
the order is greater than the theoretical prediction since
the order is approximatively 1 for $\gamma=0$ (hyperbolic limit)
and 2 for $\gamma=2$ (parabolic regime).
The reason is probably that the theory is based on worst case estimates, as it is often the case for the numerical analysis
of finite volume schemes \cite{FV}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}

The proof that was given of the uniform AP property is quite technical.
It relies on specific hyperbolic and parabolic estimates for linear
nodal finite volume schemes on general meshes.
We observe that the multidimensional case yields an additional contribution in the error
that ultimately slightly degrades the convergence rate.
It is an open problem to determine if these inequalities are optimal.
The numerical results indicate that it is probably not the case.

{\footnotesize 
\begin{thebibliography}{abcde}

\bibitem{ber1} C. Berthon, P. Charrier, R. Turpault \emph{An HLLC scheme
to solve the $M^1$ model of radiative transfer in two dimensions} J. Scie.
Comput., J. Sci. Comput., 31, no. 3, pp 347-389, 2007.

\bibitem{ber3} C. Berthon, P. LeFloch, R. Turpault  \emph{Late-time relaxation limits of nonlinear hyperbolic systems. A general framework}, Math. of Comput., 82 , pp. 831-860, 2013.

\bibitem{ber4} C. Berthon, R. Turpault \emph{Asymptotic preserving HLL
schemes}, Numerical Methods for Partial Differential Equations, 27 (6)  pp
1396-1422, 2011.

\bibitem{buet} C. Buet, S. Cordier,   B. Lucquin-Desreux, S. Mancini, 
\emph{Diffusion limit of the lorentz model: asymptotic preserving schemes.}
ESAIM: M2AN vol. 36, 4, pp 631-655, 2002.

\bibitem{glaceap} C. Buet, B. Despr\'es, E. Franck \emph{Design of
asymptotic preserving schemes for the hyperbolic heat equation on unstructured
meshes} Numerish Mathematik, Volume 122, Issue 2, pp 227-278,  2012.

\bibitem{cras} C. Buet, B. Despr\'es, E. Franck, \emph{An asymptotic
preserving scheme with the maximum principle for the $M_1$ model on distorted
meshes}, C.R. Acad. Sci., Paris, S\'er. I, Math., Vol 350,  11-12
pp 633-638,  2012.

\bibitem{FVCA6} C. Buet, B. Despr\'es, E. Franck, \emph{Asymptotic
preserving finite volumes discretization for non-linear moment model on
unstructured meshes}, Finite Volumes for Complex Applications VI Problems,
Perspectives, Springer Proceedings in Mathematics Volume 4, pp 467-474, 2011.

\bibitem{MMvlasov} N. Crouseilles, M. Lemou \emph{An asymptotic preserving
scheme based on a micro-macro decomposition for collisional Vlasov equations:
diffusion and high-field scaling limits}, Kinetic and related models 4, 2 
pp 441-477, 2011.

\bibitem{couplingRad} N. Crouseilles, M. Roger \emph{A dynamic multi-scale
model for transient radiative transfer calculations} Journal of Quantitative
Spectroscopy and Radiative Transfer , pp 110-121, 2013.

\bibitem{de04} B. Despr\'es,  \emph{Lax theorem and finite volume
schemes},
Math. Comput 0, 73:1203-1234, 2004.

\bibitem{de10} B. Despr\'es,  \emph{Weak consistency of the cell-centered
Lagrangian GLACE scheme on general
meshes in any dimension}, Comput. Methods Appl. Mech. Engrg. 199, pp 
2669-2679, 2010.

\bibitem{FV} R. Eymard, T. Gallouet, R. Herbin, \emph{The finite volume
method}, Handbook for Numerical Analysis, Ph. Ciarlet J.L. Lions eds, North
Holland, 715-1022, 2000.

\bibitem{cveps} F. Golse, S. Jin, C. D. Levermore \emph{The convergence
of numerical transfer schemes in diffusive regimes I: discrete-ordinate method},
SIAM J. Numer. Anal. 36, pp 1333-1369, 1999.

\bibitem{Gosse} L. Gosse, G. Toscani \emph{An asymptotic-preserving
well-balanced scheme for the hyperbolic heat equations} C. R. Acad. Sci
Paris,Ser. I 334, pp  337-342, , 2000.

\bibitem{GosseSn} L. Gosse \emph{Transient radiative transfer in the grey
case: Well-balanced and asymptotic-preserving schemes built on Cases's
elementary solutions} Journal of Quantitative Spectroscopy and Radiative
Transfer 112, pp 1995-2012, 2011.

\bibitem{jinbase} S. Jin, \emph{Efficient Asymptotic-Preserving (AP)
Schemes for Some Multiscale Kinetic Equations},  SIAM J. Sci. Comp. 21, 441-454,
1999.

\bibitem{jinreview} S. Jin, \emph{Asymptotic preserving (AP) schemes for
multiscale kinetic and hyperbolic equations: a review}, Lecture Notes for Summer
School on \og Methods and Models of Kinetic Theory\fg\, (M and MKT), Porto
Ercole (Grosseto, Italy),  2010.

\bibitem{jinlev} S. Jin, D. Levermore \emph{Numerical schemes for
hyperbolic conservation laws with stiff relaxation terms.} JCP 126, pp 449-467,
1996.

\bibitem{SnJin} S. Jin, D. Levermore \emph{The discrete-ordinate method in
diffusive regime.} Transport Theory and Statistical Physics, vol. 20, issue 5,
pp 413-439, 1991.

\bibitem{lemou} M. Lemou, L.Mieussens \emph{A new asymptotic preserving
scheme based on micro-macro formulation for linear kinetic equations in the
diffusion limit.} SIAM J. Sci. COMPUT. Vol. 31, 1, pp 334-368, 2008.

\bibitem{mmcv} J. G. Liu, L. Mieussens \emph{Analysis of an Asymptotic
Preserving Scheme for Linear Kinetic Equations in the Diffusion Limit} SIAM J.
Numer. Anal,  48(4), pp 1474-1491, 2010.

\bibitem{Mazeran} C. Mazeran \emph{Sur la structure mathematique et
l'approximation numerique de l'hydrodynamique lagrangienne bidimentionnelle}
 PhD, University Bordeaux 1, 2007.
\end{thebibliography}

}

\end{document}

### 2015-03-18 resultatap/gamma2.tex
doc

%!PS-Adobe-2.0
%%Title: gamma2.tex
%%Creator: gnuplot 4.6 patchlevel 3
%%CreationDate: Thu Jun 26 08:55:47 2014
%%DocumentFonts: (atend)
%%BoundingBox: 50 50 402 338
%%Orientation: Portrait
%%Pages: (atend)
%%EndComments
%%BeginProlog
/gnudict 256 dict def
gnudict begin
%
% The following true/false flags may be edited by hand if desired.
% The unit line width and grayscale image gamma correction may also be changed.
%
/Color false def
/Blacktext false def
/Solid false def
/Dashlength 1 def
/Landscape false def
/Level1 false def
/Rounded false def
/ClipToBoundingBox false def
/SuppressPDFMark false def
/TransparentPatterns false def
/gnulinewidth 5.000 def
/userlinewidth gnulinewidth def
/Gamma 1.0 def
/BackgroundColor {-1.000 -1.000 -1.000} def
%
/vshift -46 def
/dl1 {
  10.0 Dashlength mul mul
  Rounded { currentlinewidth 0.75 mul sub dup 0 le { pop 0.01 } if } if
} def
/dl2 {
  10.0 Dashlength mul mul
  Rounded { currentlinewidth 0.75 mul add } if
} def
/hpt_ 31.5 def
/vpt_ 31.5 def
/hpt hpt_ def
/vpt vpt_ def
/doclip {
  ClipToBoundingBox {
    newpath 50 50 moveto 402 50 lineto 402 338 lineto 50 338 lineto closepath
    clip
  } if
} def
%
% Gnuplot Prolog Version 4.6 (September 2012)
%
%/SuppressPDFMark true def
%
/M {moveto} bind def
/L {lineto} bind def
/R {rmoveto} bind def
/V {rlineto} bind def
/N {newpath moveto} bind def
/Z {closepath} bind def
/C {setrgbcolor} bind def
/f {rlineto fill} bind def
/g {setgray} bind def
/Gshow {show} def   % May be redefined later in the file to support UTF-8
/vpt2 vpt 2 mul def
/hpt2 hpt 2 mul def
/Lshow {currentpoint stroke M 0 vshift R 
	Blacktext {gsave 0 setgray show grestore} {show} ifelse} def
/Rshow {currentpoint stroke M dup stringwidth pop neg vshift R
	Blacktext {gsave 0 setgray show grestore} {show} ifelse} def
/Cshow {currentpoint stroke M dup stringwidth pop -2 div vshift R 
	Blacktext {gsave 0 setgray show grestore} {show} ifelse} def
/UP {dup vpt_ mul /vpt exch def hpt_ mul /hpt exch def
  /hpt2 hpt 2 mul def /vpt2 vpt 2 mul def} def
/DL {Color {setrgbcolor Solid {pop []} if 0 setdash}
 {pop pop pop 0 setgray Solid {pop []} if 0 setdash} ifelse} def
/BL {stroke userlinewidth 2 mul setlinewidth
	Rounded {1 setlinejoin 1 setlinecap} if} def
/AL {stroke userlinewidth 2 div setlinewidth
	Rounded {1 setlinejoin 1 setlinecap} if} def
/UL {dup gnulinewidth mul /userlinewidth exch def
	dup 1 lt {pop 1} if 10 mul /udl exch def} def
/PL {stroke userlinewidth setlinewidth
	Rounded {1 setlinejoin 1 setlinecap} if} def
3.8 setmiterlimit
% Default Line colors
/LCw {1 1 1} def
/LCb {0 0 0} def
/LCa {0 0 0} def
/LC0 {1 0 0} def
/LC1 {0 1 0} def
/LC2 {0 0 1} def
/LC3 {1 0 1} def
/LC4 {0 1 1} def
/LC5 {1 1 0} def
/LC6 {0 0 0} def
/LC7 {1 0.3 0} def
/LC8 {0.5 0.5 0.5} def
% Default Line Types
/LTw {PL [] 1 setgray} def
/LTb {BL [] LCb DL} def
/LTa {AL [1 udl mul 2 udl mul] 0 setdash LCa setrgbcolor} def
/LT0 {PL [] LC0 DL} def
/LT1 {PL [4 dl1 2 dl2] LC1 DL} def
/LT2 {PL [2 dl1 3 dl2] LC2 DL} def
/LT3 {PL [1 dl1 1.5 dl2] LC3 DL} def
/LT4 {PL [6 dl1 2 dl2 1 dl1 2 dl2] LC4 DL} def
/LT5 {PL [3 dl1 3 dl2 1 dl1 3 dl2] LC5 DL} def
/LT6 {PL [2 dl1 2 dl2 2 dl1 6 dl2] LC6 DL} def
/LT7 {PL [1 dl1 2 dl2 6 dl1 2 dl2 1 dl1 2 dl2] LC7 DL} def
/LT8 {PL [2 dl1 2 dl2 2 dl1 2 dl2 2 dl1 2 dl2 2 dl1 4 dl2] LC8 DL} def
/Pnt {stroke [] 0 setdash gsave 1 setlinecap M 0 0 V stroke grestore} def
/Dia {stroke [] 0 setdash 2 copy vpt add M
  hpt neg vpt neg V hpt vpt neg V
  hpt vpt V hpt neg vpt V closepath stroke
  Pnt} def
/Pls {stroke [] 0 setdash vpt sub M 0 vpt2 V
  currentpoint stroke M
  hpt neg vpt neg R hpt2 0 V stroke
 } def
/Box {stroke [] 0 setdash 2 copy exch hpt sub exch vpt add M
  0 vpt2 neg V hpt2 0 V 0 vpt2 V
  hpt2 neg 0 V closepath stroke
  Pnt} def
/Crs {stroke [] 0 setdash exch hpt sub exch vpt add M
  hpt2 vpt2 neg V currentpoint stroke M
  hpt2 neg 0 R hpt2 vpt2 V stroke} def
/TriU {stroke [] 0 setdash 2 copy vpt 1.12 mul add M
  hpt neg vpt -1.62 mul V
  hpt 2 mul 0 V
  hpt neg vpt 1.62 mul V closepath stroke
  Pnt} def
/Star {2 copy Pls Crs} def
/BoxF {stroke [] 0 setdash exch hpt sub exch vpt add M
  0 vpt2 neg V hpt2 0 V 0 vpt2 V
  hpt2 neg 0 V closepath fill} def
/TriUF {stroke [] 0 setdash vpt 1.12 mul add M
  hpt neg vpt -1.62 mul V
  hpt 2 mul 0 V
  hpt neg vpt 1.62 mul V closepath fill} def
/TriD {stroke [] 0 setdash 2 copy vpt 1.12 mul sub M
  hpt neg vpt 1.62 mul V
  hpt 2 mul 0 V
  hpt neg vpt -1.62 mul V closepath stroke
  Pnt} def
/TriDF {stroke [] 0 setdash vpt 1.12 mul sub M
  hpt neg vpt 1.62 mul V
  hpt 2 mul 0 V
  hpt neg vpt -1.62 mul V closepath fill} def
/DiaF {stroke [] 0 setdash vpt add M
  hpt neg vpt neg V hpt vpt neg V
  hpt vpt V hpt neg vpt V closepath fill} def
/Pent {stroke [] 0 setdash 2 copy gsave
  translate 0 hpt M 4 {72 rotate 0 hpt L} repeat
  closepath stroke grestore Pnt} def
/PentF {stroke [] 0 setdash gsave
  translate 0 hpt M 4 {72 rotate 0 hpt L} repeat
  closepath fill grestore} def
/Circle {stroke [] 0 setdash 2 copy
  hpt 0 360 arc stroke Pnt} def
/CircleF {stroke [] 0 setdash hpt 0 360 arc fill} def
/C0 {BL [] 0 setdash 2 copy moveto vpt 90 450 arc} bind def
/C1 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 0 90 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C2 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 90 180 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C3 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 0 180 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C4 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 180 270 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C5 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 0 90 arc
	2 copy moveto
	2 copy vpt 180 270 arc closepath fill
	vpt 0 360 arc} bind def
/C6 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 90 270 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C7 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 0 270 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C8 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 270 360 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C9 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 270 450 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C10 {BL [] 0 setdash 2 copy 2 copy moveto vpt 270 360 arc closepath fill
	2 copy moveto
	2 copy vpt 90 180 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C11 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 0 180 arc closepath fill
	2 copy moveto
	2 copy vpt 270 360 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C12 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 180 360 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C13 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 0 90 arc closepath fill
	2 copy moveto
	2 copy vpt 180 360 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C14 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 90 360 arc closepath fill
	vpt 0 360 arc} bind def
/C15 {BL [] 0 setdash 2 copy vpt 0 360 arc closepath fill
	vpt 0 360 arc closepath} bind def
/Rec {newpath 4 2 roll moveto 1 index 0 rlineto 0 exch rlineto
	neg 0 rlineto closepath} bind def
/Square {dup Rec} bind def
/Bsquare {vpt sub exch vpt sub exch vpt2 Square} bind def
/S0 {BL [] 0 setdash 2 copy moveto 0 vpt rlineto BL Bsquare} bind def
/S1 {BL [] 0 setdash 2 copy vpt Square fill Bsquare} bind def
/S2 {BL [] 0 setdash 2 copy exch vpt sub exch vpt Square fill Bsquare} bind def
/S3 {BL [] 0 setdash 2 copy exch vpt sub exch vpt2 vpt Rec fill Bsquare} bind def
/S4 {BL [] 0 setdash 2 copy exch vpt sub exch vpt sub vpt Square fill Bsquare} bind def
/S5 {BL [] 0 setdash 2 copy 2 copy vpt Square fill
	exch vpt sub exch vpt sub vpt Square fill Bsquare} bind def
/S6 {BL [] 0 setdash 2 copy exch vpt sub exch vpt sub vpt vpt2 Rec fill Bsquare} bind def
/S7 {BL [] 0 setdash 2 copy exch vpt sub exch vpt sub vpt vpt2 Rec fill
	2 copy vpt Square fill Bsquare} bind def
/S8 {BL [] 0 setdash 2 copy vpt sub vpt Square fill Bsquare} bind def
/S9 {BL [] 0 setdash 2 copy vpt sub vpt vpt2 Rec fill Bsquare} bind def
/S10 {BL [] 0 setdash 2 copy vpt sub vpt Square fill 2 copy exch vpt sub exch vpt Square fill
	Bsquare} bind def
/S11 {BL [] 0 setdash 2 copy vpt sub vpt Square fill 2 copy exch vpt sub exch vpt2 vpt Rec fill
	Bsquare} bind def
/S12 {BL [] 0 setdash 2 copy exch vpt sub exch vpt sub vpt2 vpt Rec fill Bsquare} bind def
/S13 {BL [] 0 setdash 2 copy exch vpt sub exch vpt sub vpt2 vpt Rec fill
	2 copy vpt Square fill Bsquare} bind def
/S14 {BL [] 0 setdash 2 copy exch vpt sub exch vpt sub vpt2 vpt Rec fill
	2 copy exch vpt sub exch vpt Square fill Bsquare} bind def
/S15 {BL [] 0 setdash 2 copy Bsquare fill Bsquare} bind def
/D0 {gsave translate 45 rotate 0 0 S0 stroke grestore} bind def
/D1 {gsave translate 45 rotate 0 0 S1 stroke grestore} bind def
/D2 {gsave translate 45 rotate 0 0 S2 stroke grestore} bind def
/D3 {gsave translate 45 rotate 0 0 S3 stroke grestore} bind def
/D4 {gsave translate 45 rotate 0 0 S4 stroke grestore} bind def
/D5 {gsave translate 45 rotate 0 0 S5 stroke grestore} bind def
/D6 {gsave translate 45 rotate 0 0 S6 stroke grestore} bind def
/D7 {gsave translate 45 rotate 0 0 S7 stroke grestore} bind def
/D8 {gsave translate 45 rotate 0 0 S8 stroke grestore} bind def
/D9 {gsave translate 45 rotate 0 0 S9 stroke grestore} bind def
/D10 {gsave translate 45 rotate 0 0 S10 stroke grestore} bind def
/D11 {gsave translate 45 rotate 0 0 S11 stroke grestore} bind def
/D12 {gsave translate 45 rotate 0 0 S12 stroke grestore} bind def
/D13 {gsave translate 45 rotate 0 0 S13 stroke grestore} bind def
/D14 {gsave translate 45 rotate 0 0 S14 stroke grestore} bind def
/D15 {gsave translate 45 rotate 0 0 S15 stroke grestore} bind def
/DiaE {stroke [] 0 setdash vpt add M
  hpt neg vpt neg V hpt vpt neg V
  hpt vpt V hpt neg vpt V closepath stroke} def
/BoxE {stroke [] 0 setdash exch hpt sub exch vpt add M
  0 vpt2 neg V hpt2 0 V 0 vpt2 V
  hpt2 neg 0 V closepath stroke} def
/TriUE {stroke [] 0 setdash vpt 1.12 mul add M
  hpt neg vpt -1.62 mul V
  hpt 2 mul 0 V
  hpt neg vpt 1.62 mul V closepath stroke} def
/TriDE {stroke [] 0 setdash vpt 1.12 mul sub M
  hpt neg vpt 1.62 mul V
  hpt 2 mul 0 V
  hpt neg vpt -1.62 mul V closepath stroke} def
/PentE {stroke [] 0 setdash gsave
  translate 0 hpt M 4 {72 rotate 0 hpt L} repeat
  closepath stroke grestore} def
/CircE {stroke [] 0 setdash 
  hpt 0 360 arc stroke} def
/Opaque {gsave closepath 1 setgray fill grestore 0 setgray closepath} def
/DiaW {stroke [] 0 setdash vpt add M
  hpt neg vpt neg V hpt vpt neg V
  hpt vpt V hpt neg vpt V Opaque stroke} def
/BoxW {stroke [] 0 setdash exch hpt sub exch vpt add M
  0 vpt2 neg V hpt2 0 V 0 vpt2 V
  hpt2 neg 0 V Opaque stroke} def
/TriUW {stroke [] 0 setdash vpt 1.12 mul add M
  hpt neg vpt -1.62 mul V
  hpt 2 mul 0 V
  hpt neg vpt 1.62 mul V Opaque stroke} def
/TriDW {stroke [] 0 setdash vpt 1.12 mul sub M
  hpt neg vpt 1.62 mul V
  hpt 2 mul 0 V
  hpt neg vpt -1.62 mul V Opaque stroke} def
/PentW {stroke [] 0 setdash gsave
  translate 0 hpt M 4 {72 rotate 0 hpt L} repeat
  Opaque stroke grestore} def
/CircW {stroke [] 0 setdash 
  hpt 0 360 arc Opaque stroke} def
/BoxFill {gsave Rec 1 setgray fill grestore} def
/Density {
  /Fillden exch def
  currentrgbcolor
  /ColB exch def /ColG exch def /ColR exch def
  /ColR ColR Fillden mul Fillden sub 1 add def
  /ColG ColG Fillden mul Fillden sub 1 add def
  /ColB ColB Fillden mul Fillden sub 1 add def
  ColR ColG ColB setrgbcolor} def
/BoxColFill {gsave Rec PolyFill} def
/PolyFill {gsave Density fill grestore grestore} def
/h {rlineto rlineto rlineto gsave closepath fill grestore} bind def
%
% PostScript Level 1 Pattern Fill routine for rectangles
% Usage: x y w h s a XX PatternFill
%	x,y = lower left corner of box to be filled
%	w,h = width and height of box
%	  a = angle in degrees between lines and x-axis
%	 XX = 0/1 for no/yes cross-hatch
%
/PatternFill {gsave /PFa [ 9 2 roll ] def
  PFa 0 get PFa 2 get 2 div add PFa 1 get PFa 3 get 2 div add translate
  PFa 2 get -2 div PFa 3 get -2 div PFa 2 get PFa 3 get Rec
  TransparentPatterns {} {gsave 1 setgray fill grestore} ifelse
  clip
  currentlinewidth 0.5 mul setlinewidth
  /PFs PFa 2 get dup mul PFa 3 get dup mul add sqrt def
  0 0 M PFa 5 get rotate PFs -2 div dup translate
  0 1 PFs PFa 4 get div 1 add floor cvi
	{PFa 4 get mul 0 M 0 PFs V} for
  0 PFa 6 get ne {
	0 1 PFs PFa 4 get div 1 add floor cvi
	{PFa 4 get mul 0 2 1 roll M PFs 0 V} for
 } if
  stroke grestore} def
%
/languagelevel where
 {pop languagelevel} {1} ifelse
 2 lt
	{/InterpretLevel1 true def}
	{/InterpretLevel1 Level1 def}
 ifelse
%
% PostScript level 2 pattern fill definitions
%
/Level2PatternFill {
/Tile8x8 {/PaintType 2 /PatternType 1 /TilingType 1 /BBox [0 0 8 8] /XStep 8 /YStep 8}
	bind def
/KeepColor {currentrgbcolor [/Pattern /DeviceRGB] setcolorspace} bind def
<< Tile8x8
 /PaintProc {0.5 setlinewidth pop 0 0 M 8 8 L 0 8 M 8 0 L stroke} 
>> matrix makepattern
/Pat1 exch def
<< Tile8x8
 /PaintProc {0.5 setlinewidth pop 0 0 M 8 8 L 0 8 M 8 0 L stroke
	0 4 M 4 8 L 8 4 L 4 0 L 0 4 L stroke}
>> matrix makepattern
/Pat2 exch def
<< Tile8x8
 /PaintProc {0.5 setlinewidth pop 0 0 M 0 8 L
	8 8 L 8 0 L 0 0 L fill}
>> matrix makepattern
/Pat3 exch def
<< Tile8x8
 /PaintProc {0.5 setlinewidth pop -4 8 M 8 -4 L
	0 12 M 12 0 L stroke}
>> matrix makepattern
/Pat4 exch def
<< Tile8x8
 /PaintProc {0.5 setlinewidth pop -4 0 M 8 12 L
	0 -4 M 12 8 L stroke}
>> matrix makepattern
/Pat5 exch def
<< Tile8x8
 /PaintProc {0.5 setlinewidth pop -2 8 M 4 -4 L
	0 12 M 8 -4 L 4 12 M 10 0 L stroke}
>> matrix makepattern
/Pat6 exch def
<< Tile8x8
 /PaintProc {0.5 setlinewidth pop -2 0 M 4 12 L
	0 -4 M 8 12 L 4 -4 M 10 8 L stroke}
>> matrix makepattern
/Pat7 exch def
<< Tile8x8
 /PaintProc {0.5 setlinewidth pop 8 -2 M -4 4 L
	12 0 M -4 8 L 12 4 M 0 10 L stroke}
>> matrix makepattern
/Pat8 exch def
<< Tile8x8
 /PaintProc {0.5 setlinewidth pop 0 -2 M 12 4 L
	-4 0 M 12 8 L -4 4 M 8 10 L stroke}
>> matrix makepattern
/Pat9 exch def
/Pattern1 {PatternBgnd KeepColor Pat1 setpattern} bind def
/Pattern2 {PatternBgnd KeepColor Pat2 setpattern} bind def
/Pattern3 {PatternBgnd KeepColor Pat3 setpattern} bind def
/Pattern4 {PatternBgnd KeepColor Landscape {Pat5} {Pat4} ifelse setpattern} bind def
/Pattern5 {PatternBgnd KeepColor Landscape {Pat4} {Pat5} ifelse setpattern} bind def
/Pattern6 {PatternBgnd KeepColor Landscape {Pat9} {Pat6} ifelse setpattern} bind def
/Pattern7 {PatternBgnd KeepColor Landscape {Pat8} {Pat7} ifelse setpattern} bind def
} def
%
%
%End of PostScript Level 2 code
%
/PatternBgnd {
  TransparentPatterns {} {gsave 1 setgray fill grestore} ifelse
} def
%
% Substitute for Level 2 pattern fill codes with
% grayscale if Level 2 support is not selected.
%
/Level1PatternFill {
/Pattern1 {0.250 Density} bind def
/Pattern2 {0.500 Density} bind def
/Pattern3 {0.750 Density} bind def
/Pattern4 {0.125 Density} bind def
/Pattern5 {0.375 Density} bind def
/Pattern6 {0.625 Density} bind def
/Pattern7 {0.875 Density} bind def
} def
%
% Now test for support of Level 2 code
%
Level1 {Level1PatternFill} {Level2PatternFill} ifelse
%
/Symbol-Oblique /Symbol findfont [1 0 .167 1 0 0] makefont
dup length dict begin {1 index /FID eq {pop pop} {def} ifelse} forall
currentdict end definefont pop
Level1 SuppressPDFMark or 
{} {
/SDict 10 dict def
systemdict /pdfmark known not {
  userdict /pdfmark systemdict /cleartomark get put
} if
SDict begin [
  /Title (gamma2.tex)
  /Subject (gnuplot plot)
  /Creator (gnuplot 4.6 patchlevel 3)
  /Author (despres)
%  /Producer (gnuplot)
%  /Keywords ()
  /CreationDate (Thu Jun 26 08:55:47 2014)
  /DOCINFO pdfmark
end
} ifelse
end
%%EndProlog
%%Page: 1 1
gnudict begin
gsave
doclip
50 50 translate
0.100 0.100 scale
0 setgray
newpath
(Helvetica) findfont 140 scalefont setfont
BackgroundColor 0 lt 3 1 roll 0 lt exch 0 lt or or not {gsave BackgroundColor C clippath fill grestore} if
1.000 UL
LTb
938 448 M
63 0 V
2274 0 R
-63 0 V
854 448 M
( 1e-05) Rshow
1.000 UL
LTb
938 675 M
31 0 V
2306 0 R
-31 0 V
938 808 M
31 0 V
2306 0 R
-31 0 V
938 902 M
31 0 V
2306 0 R
-31 0 V
938 975 M
31 0 V
2306 0 R
-31 0 V
938 1035 M
31 0 V
2306 0 R
-31 0 V
938 1086 M
31 0 V
2306 0 R
-31 0 V
938 1130 M
31 0 V
2306 0 R
-31 0 V
938 1168 M
31 0 V
2306 0 R
-31 0 V
938 1203 M
63 0 V
2274 0 R
-63 0 V
-2358 0 R
( 0.0001) Rshow
1.000 UL
LTb
938 1430 M
31 0 V
2306 0 R
-31 0 V
938 1563 M
31 0 V
2306 0 R
-31 0 V
938 1657 M
31 0 V
2306 0 R
-31 0 V
938 1730 M
31 0 V
2306 0 R
-31 0 V
938 1790 M
31 0 V
2306 0 R
-31 0 V
938 1840 M
31 0 V
2306 0 R
-31 0 V
938 1884 M
31 0 V
2306 0 R
-31 0 V
938 1923 M
31 0 V
2306 0 R
-31 0 V
938 1957 M
63 0 V
2274 0 R
-63 0 V
-2358 0 R
( 0.001) Rshow
1.000 UL
LTb
938 2185 M
31 0 V
2306 0 R
-31 0 V
938 2317 M
31 0 V
2306 0 R
-31 0 V
938 2412 M
31 0 V
2306 0 R
-31 0 V
938 2485 M
31 0 V
2306 0 R
-31 0 V
938 2545 M
31 0 V
2306 0 R
-31 0 V
938 2595 M
31 0 V
2306 0 R
-31 0 V
938 2639 M
31 0 V
2306 0 R
-31 0 V
938 2677 M
31 0 V
2306 0 R
-31 0 V
938 2712 M
63 0 V
2274 0 R
-63 0 V
-2358 0 R
( 0.01) Rshow
1.000 UL
LTb
938 448 M
0 63 V
0 2201 R
0 -63 V
938 308 M
( 10) Cshow
1.000 UL
LTb
1290 448 M
0 31 V
0 2233 R
0 -31 V
1496 448 M
0 31 V
0 2233 R
0 -31 V
1642 448 M
0 31 V
0 2233 R
0 -31 V
1755 448 M
0 31 V
0 2233 R
0 -31 V
1847 448 M
0 31 V
0 2233 R
0 -31 V
1925 448 M
0 31 V
0 2233 R
0 -31 V
1993 448 M
0 31 V
0 2233 R
0 -31 V
2053 448 M
0 31 V
0 2233 R
0 -31 V
2107 448 M
0 63 V
0 2201 R
0 -63 V
0 -2341 R
( 100) Cshow
1.000 UL
LTb
2458 448 M
0 31 V
0 2233 R
0 -31 V
2664 448 M
0 31 V
0 2233 R
0 -31 V
2810 448 M
0 31 V
0 2233 R
0 -31 V
2923 448 M
0 31 V
0 2233 R
0 -31 V
3016 448 M
0 31 V
0 2233 R
0 -31 V
3094 448 M
0 31 V
0 2233 R
0 -31 V
3162 448 M
0 31 V
0 2233 R
0 -31 V
3222 448 M
0 31 V
0 2233 R
0 -31 V
3275 448 M
0 63 V
0 2201 R
0 -63 V
0 -2341 R
( 1000) Cshow
1.000 UL
LTb
1.000 UL
LTb
938 2712 N
938 448 L
2337 0 V
0 2264 V
-2337 0 V
Z stroke
LCb setrgbcolor
112 1580 M
currentpoint gsave translate -270 rotate 0 0 M
(L2 Error) Cshow
grestore
LTb
LCb setrgbcolor
2106 98 M
(N) Cshow
LTb
1.000 UP
1.000 UL
LTb
% Begin plot #1
1.000 UL
LT0
LCb setrgbcolor
2624 2579 M
(gamma=2) Rshow
LT0
2708 2579 M
399 0 V
1642 2525 M
205 -309 V
146 -214 V
114 -166 V
92 -130 V
146 -210 V
113 -153 V
239 -323 V
% End plot #1
% Begin plot #2
stroke
LT1
LCb setrgbcolor
2624 2439 M
(gamma=1) Rshow
LT1
2708 2439 M
399 0 V
-1465 86 R
205 -261 V
146 -188 V
114 -147 V
92 -119 V
146 -193 V
113 -144 V
93 -121 V
146 -188 V
% End plot #2
% Begin plot #3
stroke
LT2
LCb setrgbcolor
2624 2299 M
(gamma=0.5) Rshow
LT2
2708 2299 M
399 0 V
1642 2525 M
205 -232 V
146 -165 V
114 -127 V
92 -104 V
146 -163 V
113 -123 V
93 -101 V
146 -157 V
% End plot #3
% Begin plot #4
stroke
LT3
LCb setrgbcolor
2624 2159 M
(gamma=0.25) Rshow
LT3
2708 2159 M
399 0 V
1642 2525 M
205 -216 V
146 -151 V
114 -114 V
92 -93 V
146 -144 V
113 -107 V
239 -216 V
% End plot #4
% Begin plot #5
stroke
LT4
LCb setrgbcolor
2624 2019 M
(gamma=0) Rshow
LT4
2708 2019 M
399 0 V
1642 2525 M
205 -199 V
146 -136 V
114 -99 V
92 -80 V
146 -121 V
113 -88 V
93 -71 V
146 -107 V
% End plot #5
% Begin plot #6
stroke
LT5
LCb setrgbcolor
2624 1879 M
( order one ) Rshow
LT5
2708 1879 M
399 0 V
1642 2618 M
10 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -6 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -6 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -6 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -6 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -6 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -6 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -6 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -6 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -6 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -6 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -6 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
% End plot #6
stroke
LTb
938 2712 N
938 448 L
2337 0 V
0 2264 V
-2337 0 V
Z stroke
1.000 UP
1.000 UL
LTb
stroke
grestore
end
showpage
%%Page: 2 2
gnudict begin
gsave
doclip
50 50 translate
0.100 0.100 scale
0 setgray
newpath
(Helvetica) findfont 140 scalefont setfont
BackgroundColor 0 lt 3 1 roll 0 lt exch 0 lt or or not {gsave BackgroundColor C clippath fill grestore} if
1.000 UL
LTb
938 448 M
63 0 V
2274 0 R
-63 0 V
854 448 M
( 1e-05) Rshow
1.000 UL
LTb
938 675 M
31 0 V
2306 0 R
-31 0 V
938 808 M
31 0 V
2306 0 R
-31 0 V
938 902 M
31 0 V
2306 0 R
-31 0 V
938 975 M
31 0 V
2306 0 R
-31 0 V
938 1035 M
31 0 V
2306 0 R
-31 0 V
938 1086 M
31 0 V
2306 0 R
-31 0 V
938 1130 M
31 0 V
2306 0 R
-31 0 V
938 1168 M
31 0 V
2306 0 R
-31 0 V
938 1203 M
63 0 V
2274 0 R
-63 0 V
-2358 0 R
( 0.0001) Rshow
1.000 UL
LTb
938 1430 M
31 0 V
2306 0 R
-31 0 V
938 1563 M
31 0 V
2306 0 R
-31 0 V
938 1657 M
31 0 V
2306 0 R
-31 0 V
938 1730 M
31 0 V
2306 0 R
-31 0 V
938 1790 M
31 0 V
2306 0 R
-31 0 V
938 1840 M
31 0 V
2306 0 R
-31 0 V
938 1884 M
31 0 V
2306 0 R
-31 0 V
938 1923 M
31 0 V
2306 0 R
-31 0 V
938 1957 M
63 0 V
2274 0 R
-63 0 V
-2358 0 R
( 0.001) Rshow
1.000 UL
LTb
938 2185 M
31 0 V
2306 0 R
-31 0 V
938 2317 M
31 0 V
2306 0 R
-31 0 V
938 2412 M
31 0 V
2306 0 R
-31 0 V
938 2485 M
31 0 V
2306 0 R
-31 0 V
938 2545 M
31 0 V
2306 0 R
-31 0 V
938 2595 M
31 0 V
2306 0 R
-31 0 V
938 2639 M
31 0 V
2306 0 R
-31 0 V
938 2677 M
31 0 V
2306 0 R
-31 0 V
938 2712 M
63 0 V
2274 0 R
-63 0 V
-2358 0 R
( 0.01) Rshow
1.000 UL
LTb
938 448 M
0 63 V
0 2201 R
0 -63 V
938 308 M
( 10) Cshow
1.000 UL
LTb
1290 448 M
0 31 V
0 2233 R
0 -31 V
1496 448 M
0 31 V
0 2233 R
0 -31 V
1642 448 M
0 31 V
0 2233 R
0 -31 V
1755 448 M
0 31 V
0 2233 R
0 -31 V
1847 448 M
0 31 V
0 2233 R
0 -31 V
1925 448 M
0 31 V
0 2233 R
0 -31 V
1993 448 M
0 31 V
0 2233 R
0 -31 V
2053 448 M
0 31 V
0 2233 R
0 -31 V
2107 448 M
0 63 V
0 2201 R
0 -63 V
0 -2341 R
( 100) Cshow
1.000 UL
LTb
2458 448 M
0 31 V
0 2233 R
0 -31 V
2664 448 M
0 31 V
0 2233 R
0 -31 V
2810 448 M
0 31 V
0 2233 R
0 -31 V
2923 448 M
0 31 V
0 2233 R
0 -31 V
3016 448 M
0 31 V
0 2233 R
0 -31 V
3094 448 M
0 31 V
0 2233 R
0 -31 V
3162 448 M
0 31 V
0 2233 R
0 -31 V
3222 448 M
0 31 V
0 2233 R
0 -31 V
3275 448 M
0 63 V
0 2201 R
0 -63 V
0 -2341 R
( 1000) Cshow
1.000 UL
LTb
1.000 UL
LTb
938 2712 N
938 448 L
2337 0 V
0 2264 V
-2337 0 V
Z stroke
LCb setrgbcolor
112 1580 M
currentpoint gsave translate -270 rotate 0 0 M
(L2 Error) Cshow
grestore
LTb
LCb setrgbcolor
2106 98 M
(N) Cshow
LTb
1.000 UP
1.000 UL
LTb
% Begin plot #1
1.000 UL
LT0
LCb setrgbcolor
2624 2579 M
(gamma=2) Rshow
LT0
2708 2579 M
399 0 V
1642 2525 M
205 -309 V
146 -214 V
114 -166 V
92 -130 V
146 -210 V
113 -153 V
239 -323 V
% End plot #1
% Begin plot #2
stroke
LT1
LCb setrgbcolor
2624 2439 M
(gamma=1) Rshow
LT1
2708 2439 M
399 0 V
-1465 86 R
205 -261 V
146 -188 V
114 -147 V
92 -119 V
146 -193 V
113 -144 V
93 -121 V
146 -188 V
% End plot #2
% Begin plot #3
stroke
LT2
LCb setrgbcolor
2624 2299 M
(gamma=0.5) Rshow
LT2
2708 2299 M
399 0 V
1642 2525 M
205 -232 V
146 -165 V
114 -127 V
92 -104 V
146 -163 V
113 -123 V
93 -101 V
146 -157 V
% End plot #3
% Begin plot #4
stroke
LT3
LCb setrgbcolor
2624 2159 M
(gamma=0.25) Rshow
LT3
2708 2159 M
399 0 V
1642 2525 M
205 -216 V
146 -151 V
114 -114 V
92 -93 V
146 -144 V
113 -107 V
239 -216 V
% End plot #4
% Begin plot #5
stroke
LT4
LCb setrgbcolor
2624 2019 M
(gamma=0) Rshow
LT4
2708 2019 M
399 0 V
1642 2525 M
205 -199 V
146 -136 V
114 -99 V
92 -80 V
146 -121 V
113 -88 V
93 -71 V
146 -107 V
% End plot #5
% Begin plot #6
stroke
LT5
LCb setrgbcolor
2624 1879 M
( order one ) Rshow
LT5
2708 1879 M
399 0 V
1642 2618 M
10 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -6 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -6 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -6 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -6 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -6 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -6 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -6 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -6 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -6 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -6 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -6 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
% End plot #6
stroke
LTb
938 2712 N
938 448 L
2337 0 V
0 2264 V
-2337 0 V
Z stroke
1.000 UP
1.000 UL
LTb
stroke
grestore
end
showpage
%%Trailer
%%DocumentFonts: Helvetica
%%Pages: 2
%!PS-Adobe-2.0
%%Title: gamma2.tex
%%Creator: gnuplot 4.6 patchlevel 3
%%CreationDate: Thu Jun 26 08:57:03 2014
%%DocumentFonts: (atend)
%%BoundingBox: 50 50 402 338
%%Orientation: Portrait
%%Pages: (atend)
%%EndComments
%%BeginProlog
/gnudict 256 dict def
gnudict begin
%
% The following true/false flags may be edited by hand if desired.
% The unit line width and grayscale image gamma correction may also be changed.
%
/Color false def
/Blacktext false def
/Solid true def
/Dashlength 1 def
/Landscape false def
/Level1 false def
/Rounded false def
/ClipToBoundingBox false def
/SuppressPDFMark false def
/TransparentPatterns false def
/gnulinewidth 5.000 def
/userlinewidth gnulinewidth def
/Gamma 1.0 def
/BackgroundColor {-1.000 -1.000 -1.000} def
%
/vshift -46 def
/dl1 {
  10.0 Dashlength mul mul
  Rounded { currentlinewidth 0.75 mul sub dup 0 le { pop 0.01 } if } if
} def
/dl2 {
  10.0 Dashlength mul mul
  Rounded { currentlinewidth 0.75 mul add } if
} def
/hpt_ 31.5 def
/vpt_ 31.5 def
/hpt hpt_ def
/vpt vpt_ def
/doclip {
  ClipToBoundingBox {
    newpath 50 50 moveto 402 50 lineto 402 338 lineto 50 338 lineto closepath
    clip
  } if
} def
%
% Gnuplot Prolog Version 4.6 (September 2012)
%
%/SuppressPDFMark true def
%
/M {moveto} bind def
/L {lineto} bind def
/R {rmoveto} bind def
/V {rlineto} bind def
/N {newpath moveto} bind def
/Z {closepath} bind def
/C {setrgbcolor} bind def
/f {rlineto fill} bind def
/g {setgray} bind def
/Gshow {show} def   % May be redefined later in the file to support UTF-8
/vpt2 vpt 2 mul def
/hpt2 hpt 2 mul def
/Lshow {currentpoint stroke M 0 vshift R 
	Blacktext {gsave 0 setgray show grestore} {show} ifelse} def
/Rshow {currentpoint stroke M dup stringwidth pop neg vshift R
	Blacktext {gsave 0 setgray show grestore} {show} ifelse} def
/Cshow {currentpoint stroke M dup stringwidth pop -2 div vshift R 
	Blacktext {gsave 0 setgray show grestore} {show} ifelse} def
/UP {dup vpt_ mul /vpt exch def hpt_ mul /hpt exch def
  /hpt2 hpt 2 mul def /vpt2 vpt 2 mul def} def
/DL {Color {setrgbcolor Solid {pop []} if 0 setdash}
 {pop pop pop 0 setgray Solid {pop []} if 0 setdash} ifelse} def
/BL {stroke userlinewidth 2 mul setlinewidth
	Rounded {1 setlinejoin 1 setlinecap} if} def
/AL {stroke userlinewidth 2 div setlinewidth
	Rounded {1 setlinejoin 1 setlinecap} if} def
/UL {dup gnulinewidth mul /userlinewidth exch def
	dup 1 lt {pop 1} if 10 mul /udl exch def} def
/PL {stroke userlinewidth setlinewidth
	Rounded {1 setlinejoin 1 setlinecap} if} def
3.8 setmiterlimit
% Default Line colors
/LCw {1 1 1} def
/LCb {0 0 0} def
/LCa {0 0 0} def
/LC0 {1 0 0} def
/LC1 {0 1 0} def
/LC2 {0 0 1} def
/LC3 {1 0 1} def
/LC4 {0 1 1} def
/LC5 {1 1 0} def
/LC6 {0 0 0} def
/LC7 {1 0.3 0} def
/LC8 {0.5 0.5 0.5} def
% Default Line Types
/LTw {PL [] 1 setgray} def
/LTb {BL [] LCb DL} def
/LTa {AL [1 udl mul 2 udl mul] 0 setdash LCa setrgbcolor} def
/LT0 {PL [] LC0 DL} def
/LT1 {PL [4 dl1 2 dl2] LC1 DL} def
/LT2 {PL [2 dl1 3 dl2] LC2 DL} def
/LT3 {PL [1 dl1 1.5 dl2] LC3 DL} def
/LT4 {PL [6 dl1 2 dl2 1 dl1 2 dl2] LC4 DL} def
/LT5 {PL [3 dl1 3 dl2 1 dl1 3 dl2] LC5 DL} def
/LT6 {PL [2 dl1 2 dl2 2 dl1 6 dl2] LC6 DL} def
/LT7 {PL [1 dl1 2 dl2 6 dl1 2 dl2 1 dl1 2 dl2] LC7 DL} def
/LT8 {PL [2 dl1 2 dl2 2 dl1 2 dl2 2 dl1 2 dl2 2 dl1 4 dl2] LC8 DL} def
/Pnt {stroke [] 0 setdash gsave 1 setlinecap M 0 0 V stroke grestore} def
/Dia {stroke [] 0 setdash 2 copy vpt add M
  hpt neg vpt neg V hpt vpt neg V
  hpt vpt V hpt neg vpt V closepath stroke
  Pnt} def
/Pls {stroke [] 0 setdash vpt sub M 0 vpt2 V
  currentpoint stroke M
  hpt neg vpt neg R hpt2 0 V stroke
 } def
/Box {stroke [] 0 setdash 2 copy exch hpt sub exch vpt add M
  0 vpt2 neg V hpt2 0 V 0 vpt2 V
  hpt2 neg 0 V closepath stroke
  Pnt} def
/Crs {stroke [] 0 setdash exch hpt sub exch vpt add M
  hpt2 vpt2 neg V currentpoint stroke M
  hpt2 neg 0 R hpt2 vpt2 V stroke} def
/TriU {stroke [] 0 setdash 2 copy vpt 1.12 mul add M
  hpt neg vpt -1.62 mul V
  hpt 2 mul 0 V
  hpt neg vpt 1.62 mul V closepath stroke
  Pnt} def
/Star {2 copy Pls Crs} def
/BoxF {stroke [] 0 setdash exch hpt sub exch vpt add M
  0 vpt2 neg V hpt2 0 V 0 vpt2 V
  hpt2 neg 0 V closepath fill} def
/TriUF {stroke [] 0 setdash vpt 1.12 mul add M
  hpt neg vpt -1.62 mul V
  hpt 2 mul 0 V
  hpt neg vpt 1.62 mul V closepath fill} def
/TriD {stroke [] 0 setdash 2 copy vpt 1.12 mul sub M
  hpt neg vpt 1.62 mul V
  hpt 2 mul 0 V
  hpt neg vpt -1.62 mul V closepath stroke
  Pnt} def
/TriDF {stroke [] 0 setdash vpt 1.12 mul sub M
  hpt neg vpt 1.62 mul V
  hpt 2 mul 0 V
  hpt neg vpt -1.62 mul V closepath fill} def
/DiaF {stroke [] 0 setdash vpt add M
  hpt neg vpt neg V hpt vpt neg V
  hpt vpt V hpt neg vpt V closepath fill} def
/Pent {stroke [] 0 setdash 2 copy gsave
  translate 0 hpt M 4 {72 rotate 0 hpt L} repeat
  closepath stroke grestore Pnt} def
/PentF {stroke [] 0 setdash gsave
  translate 0 hpt M 4 {72 rotate 0 hpt L} repeat
  closepath fill grestore} def
/Circle {stroke [] 0 setdash 2 copy
  hpt 0 360 arc stroke Pnt} def
/CircleF {stroke [] 0 setdash hpt 0 360 arc fill} def
/C0 {BL [] 0 setdash 2 copy moveto vpt 90 450 arc} bind def
/C1 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 0 90 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C2 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 90 180 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C3 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 0 180 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C4 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 180 270 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C5 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 0 90 arc
	2 copy moveto
	2 copy vpt 180 270 arc closepath fill
	vpt 0 360 arc} bind def
/C6 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 90 270 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C7 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 0 270 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C8 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 270 360 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C9 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 270 450 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C10 {BL [] 0 setdash 2 copy 2 copy moveto vpt 270 360 arc closepath fill
	2 copy moveto
	2 copy vpt 90 180 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C11 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 0 180 arc closepath fill
	2 copy moveto
	2 copy vpt 270 360 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C12 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 180 360 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C13 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 0 90 arc closepath fill
	2 copy moveto
	2 copy vpt 180 360 arc closepath fill
	vpt 0 360 arc closepath} bind def
/C14 {BL [] 0 setdash 2 copy moveto
	2 copy vpt 90 360 arc closepath fill
	vpt 0 360 arc} bind def
/C15 {BL [] 0 setdash 2 copy vpt 0 360 arc closepath fill
	vpt 0 360 arc closepath} bind def
/Rec {newpath 4 2 roll moveto 1 index 0 rlineto 0 exch rlineto
	neg 0 rlineto closepath} bind def
/Square {dup Rec} bind def
/Bsquare {vpt sub exch vpt sub exch vpt2 Square} bind def
/S0 {BL [] 0 setdash 2 copy moveto 0 vpt rlineto BL Bsquare} bind def
/S1 {BL [] 0 setdash 2 copy vpt Square fill Bsquare} bind def
/S2 {BL [] 0 setdash 2 copy exch vpt sub exch vpt Square fill Bsquare} bind def
/S3 {BL [] 0 setdash 2 copy exch vpt sub exch vpt2 vpt Rec fill Bsquare} bind def
/S4 {BL [] 0 setdash 2 copy exch vpt sub exch vpt sub vpt Square fill Bsquare} bind def
/S5 {BL [] 0 setdash 2 copy 2 copy vpt Square fill
	exch vpt sub exch vpt sub vpt Square fill Bsquare} bind def
/S6 {BL [] 0 setdash 2 copy exch vpt sub exch vpt sub vpt vpt2 Rec fill Bsquare} bind def
/S7 {BL [] 0 setdash 2 copy exch vpt sub exch vpt sub vpt vpt2 Rec fill
	2 copy vpt Square fill Bsquare} bind def
/S8 {BL [] 0 setdash 2 copy vpt sub vpt Square fill Bsquare} bind def
/S9 {BL [] 0 setdash 2 copy vpt sub vpt vpt2 Rec fill Bsquare} bind def
/S10 {BL [] 0 setdash 2 copy vpt sub vpt Square fill 2 copy exch vpt sub exch vpt Square fill
	Bsquare} bind def
/S11 {BL [] 0 setdash 2 copy vpt sub vpt Square fill 2 copy exch vpt sub exch vpt2 vpt Rec fill
	Bsquare} bind def
/S12 {BL [] 0 setdash 2 copy exch vpt sub exch vpt sub vpt2 vpt Rec fill Bsquare} bind def
/S13 {BL [] 0 setdash 2 copy exch vpt sub exch vpt sub vpt2 vpt Rec fill
	2 copy vpt Square fill Bsquare} bind def
/S14 {BL [] 0 setdash 2 copy exch vpt sub exch vpt sub vpt2 vpt Rec fill
	2 copy exch vpt sub exch vpt Square fill Bsquare} bind def
/S15 {BL [] 0 setdash 2 copy Bsquare fill Bsquare} bind def
/D0 {gsave translate 45 rotate 0 0 S0 stroke grestore} bind def
/D1 {gsave translate 45 rotate 0 0 S1 stroke grestore} bind def
/D2 {gsave translate 45 rotate 0 0 S2 stroke grestore} bind def
/D3 {gsave translate 45 rotate 0 0 S3 stroke grestore} bind def
/D4 {gsave translate 45 rotate 0 0 S4 stroke grestore} bind def
/D5 {gsave translate 45 rotate 0 0 S5 stroke grestore} bind def
/D6 {gsave translate 45 rotate 0 0 S6 stroke grestore} bind def
/D7 {gsave translate 45 rotate 0 0 S7 stroke grestore} bind def
/D8 {gsave translate 45 rotate 0 0 S8 stroke grestore} bind def
/D9 {gsave translate 45 rotate 0 0 S9 stroke grestore} bind def
/D10 {gsave translate 45 rotate 0 0 S10 stroke grestore} bind def
/D11 {gsave translate 45 rotate 0 0 S11 stroke grestore} bind def
/D12 {gsave translate 45 rotate 0 0 S12 stroke grestore} bind def
/D13 {gsave translate 45 rotate 0 0 S13 stroke grestore} bind def
/D14 {gsave translate 45 rotate 0 0 S14 stroke grestore} bind def
/D15 {gsave translate 45 rotate 0 0 S15 stroke grestore} bind def
/DiaE {stroke [] 0 setdash vpt add M
  hpt neg vpt neg V hpt vpt neg V
  hpt vpt V hpt neg vpt V closepath stroke} def
/BoxE {stroke [] 0 setdash exch hpt sub exch vpt add M
  0 vpt2 neg V hpt2 0 V 0 vpt2 V
  hpt2 neg 0 V closepath stroke} def
/TriUE {stroke [] 0 setdash vpt 1.12 mul add M
  hpt neg vpt -1.62 mul V
  hpt 2 mul 0 V
  hpt neg vpt 1.62 mul V closepath stroke} def
/TriDE {stroke [] 0 setdash vpt 1.12 mul sub M
  hpt neg vpt 1.62 mul V
  hpt 2 mul 0 V
  hpt neg vpt -1.62 mul V closepath stroke} def
/PentE {stroke [] 0 setdash gsave
  translate 0 hpt M 4 {72 rotate 0 hpt L} repeat
  closepath stroke grestore} def
/CircE {stroke [] 0 setdash 
  hpt 0 360 arc stroke} def
/Opaque {gsave closepath 1 setgray fill grestore 0 setgray closepath} def
/DiaW {stroke [] 0 setdash vpt add M
  hpt neg vpt neg V hpt vpt neg V
  hpt vpt V hpt neg vpt V Opaque stroke} def
/BoxW {stroke [] 0 setdash exch hpt sub exch vpt add M
  0 vpt2 neg V hpt2 0 V 0 vpt2 V
  hpt2 neg 0 V Opaque stroke} def
/TriUW {stroke [] 0 setdash vpt 1.12 mul add M
  hpt neg vpt -1.62 mul V
  hpt 2 mul 0 V
  hpt neg vpt 1.62 mul V Opaque stroke} def
/TriDW {stroke [] 0 setdash vpt 1.12 mul sub M
  hpt neg vpt 1.62 mul V
  hpt 2 mul 0 V
  hpt neg vpt -1.62 mul V Opaque stroke} def
/PentW {stroke [] 0 setdash gsave
  translate 0 hpt M 4 {72 rotate 0 hpt L} repeat
  Opaque stroke grestore} def
/CircW {stroke [] 0 setdash 
  hpt 0 360 arc Opaque stroke} def
/BoxFill {gsave Rec 1 setgray fill grestore} def
/Density {
  /Fillden exch def
  currentrgbcolor
  /ColB exch def /ColG exch def /ColR exch def
  /ColR ColR Fillden mul Fillden sub 1 add def
  /ColG ColG Fillden mul Fillden sub 1 add def
  /ColB ColB Fillden mul Fillden sub 1 add def
  ColR ColG ColB setrgbcolor} def
/BoxColFill {gsave Rec PolyFill} def
/PolyFill {gsave Density fill grestore grestore} def
/h {rlineto rlineto rlineto gsave closepath fill grestore} bind def
%
% PostScript Level 1 Pattern Fill routine for rectangles
% Usage: x y w h s a XX PatternFill
%	x,y = lower left corner of box to be filled
%	w,h = width and height of box
%	  a = angle in degrees between lines and x-axis
%	 XX = 0/1 for no/yes cross-hatch
%
/PatternFill {gsave /PFa [ 9 2 roll ] def
  PFa 0 get PFa 2 get 2 div add PFa 1 get PFa 3 get 2 div add translate
  PFa 2 get -2 div PFa 3 get -2 div PFa 2 get PFa 3 get Rec
  TransparentPatterns {} {gsave 1 setgray fill grestore} ifelse
  clip
  currentlinewidth 0.5 mul setlinewidth
  /PFs PFa 2 get dup mul PFa 3 get dup mul add sqrt def
  0 0 M PFa 5 get rotate PFs -2 div dup translate
  0 1 PFs PFa 4 get div 1 add floor cvi
	{PFa 4 get mul 0 M 0 PFs V} for
  0 PFa 6 get ne {
	0 1 PFs PFa 4 get div 1 add floor cvi
	{PFa 4 get mul 0 2 1 roll M PFs 0 V} for
 } if
  stroke grestore} def
%
/languagelevel where
 {pop languagelevel} {1} ifelse
 2 lt
	{/InterpretLevel1 true def}
	{/InterpretLevel1 Level1 def}
 ifelse
%
% PostScript level 2 pattern fill definitions
%
/Level2PatternFill {
/Tile8x8 {/PaintType 2 /PatternType 1 /TilingType 1 /BBox [0 0 8 8] /XStep 8 /YStep 8}
	bind def
/KeepColor {currentrgbcolor [/Pattern /DeviceRGB] setcolorspace} bind def
<< Tile8x8
 /PaintProc {0.5 setlinewidth pop 0 0 M 8 8 L 0 8 M 8 0 L stroke} 
>> matrix makepattern
/Pat1 exch def
<< Tile8x8
 /PaintProc {0.5 setlinewidth pop 0 0 M 8 8 L 0 8 M 8 0 L stroke
	0 4 M 4 8 L 8 4 L 4 0 L 0 4 L stroke}
>> matrix makepattern
/Pat2 exch def
<< Tile8x8
 /PaintProc {0.5 setlinewidth pop 0 0 M 0 8 L
	8 8 L 8 0 L 0 0 L fill}
>> matrix makepattern
/Pat3 exch def
<< Tile8x8
 /PaintProc {0.5 setlinewidth pop -4 8 M 8 -4 L
	0 12 M 12 0 L stroke}
>> matrix makepattern
/Pat4 exch def
<< Tile8x8
 /PaintProc {0.5 setlinewidth pop -4 0 M 8 12 L
	0 -4 M 12 8 L stroke}
>> matrix makepattern
/Pat5 exch def
<< Tile8x8
 /PaintProc {0.5 setlinewidth pop -2 8 M 4 -4 L
	0 12 M 8 -4 L 4 12 M 10 0 L stroke}
>> matrix makepattern
/Pat6 exch def
<< Tile8x8
 /PaintProc {0.5 setlinewidth pop -2 0 M 4 12 L
	0 -4 M 8 12 L 4 -4 M 10 8 L stroke}
>> matrix makepattern
/Pat7 exch def
<< Tile8x8
 /PaintProc {0.5 setlinewidth pop 8 -2 M -4 4 L
	12 0 M -4 8 L 12 4 M 0 10 L stroke}
>> matrix makepattern
/Pat8 exch def
<< Tile8x8
 /PaintProc {0.5 setlinewidth pop 0 -2 M 12 4 L
	-4 0 M 12 8 L -4 4 M 8 10 L stroke}
>> matrix makepattern
/Pat9 exch def
/Pattern1 {PatternBgnd KeepColor Pat1 setpattern} bind def
/Pattern2 {PatternBgnd KeepColor Pat2 setpattern} bind def
/Pattern3 {PatternBgnd KeepColor Pat3 setpattern} bind def
/Pattern4 {PatternBgnd KeepColor Landscape {Pat5} {Pat4} ifelse setpattern} bind def
/Pattern5 {PatternBgnd KeepColor Landscape {Pat4} {Pat5} ifelse setpattern} bind def
/Pattern6 {PatternBgnd KeepColor Landscape {Pat9} {Pat6} ifelse setpattern} bind def
/Pattern7 {PatternBgnd KeepColor Landscape {Pat8} {Pat7} ifelse setpattern} bind def
} def
%
%
%End of PostScript Level 2 code
%
/PatternBgnd {
  TransparentPatterns {} {gsave 1 setgray fill grestore} ifelse
} def
%
% Substitute for Level 2 pattern fill codes with
% grayscale if Level 2 support is not selected.
%
/Level1PatternFill {
/Pattern1 {0.250 Density} bind def
/Pattern2 {0.500 Density} bind def
/Pattern3 {0.750 Density} bind def
/Pattern4 {0.125 Density} bind def
/Pattern5 {0.375 Density} bind def
/Pattern6 {0.625 Density} bind def
/Pattern7 {0.875 Density} bind def
} def
%
% Now test for support of Level 2 code
%
Level1 {Level1PatternFill} {Level2PatternFill} ifelse
%
/Symbol-Oblique /Symbol findfont [1 0 .167 1 0 0] makefont
dup length dict begin {1 index /FID eq {pop pop} {def} ifelse} forall
currentdict end definefont pop
Level1 SuppressPDFMark or 
{} {
/SDict 10 dict def
systemdict /pdfmark known not {
  userdict /pdfmark systemdict /cleartomark get put
} if
SDict begin [
  /Title (gamma2.tex)
  /Subject (gnuplot plot)
  /Creator (gnuplot 4.6 patchlevel 3)
  /Author (despres)
%  /Producer (gnuplot)
%  /Keywords ()
  /CreationDate (Thu Jun 26 08:57:03 2014)
  /DOCINFO pdfmark
end
} ifelse
end
%%EndProlog
%%Page: 1 1
gnudict begin
gsave
doclip
50 50 translate
0.100 0.100 scale
0 setgray
newpath
(Helvetica) findfont 140 scalefont setfont
BackgroundColor 0 lt 3 1 roll 0 lt exch 0 lt or or not {gsave BackgroundColor C clippath fill grestore} if
1.000 UL
LTb
938 448 M
63 0 V
2274 0 R
-63 0 V
854 448 M
( 1e-05) Rshow
1.000 UL
LTb
938 675 M
31 0 V
2306 0 R
-31 0 V
938 808 M
31 0 V
2306 0 R
-31 0 V
938 902 M
31 0 V
2306 0 R
-31 0 V
938 975 M
31 0 V
2306 0 R
-31 0 V
938 1035 M
31 0 V
2306 0 R
-31 0 V
938 1086 M
31 0 V
2306 0 R
-31 0 V
938 1130 M
31 0 V
2306 0 R
-31 0 V
938 1168 M
31 0 V
2306 0 R
-31 0 V
938 1203 M
63 0 V
2274 0 R
-63 0 V
-2358 0 R
( 0.0001) Rshow
1.000 UL
LTb
938 1430 M
31 0 V
2306 0 R
-31 0 V
938 1563 M
31 0 V
2306 0 R
-31 0 V
938 1657 M
31 0 V
2306 0 R
-31 0 V
938 1730 M
31 0 V
2306 0 R
-31 0 V
938 1790 M
31 0 V
2306 0 R
-31 0 V
938 1840 M
31 0 V
2306 0 R
-31 0 V
938 1884 M
31 0 V
2306 0 R
-31 0 V
938 1923 M
31 0 V
2306 0 R
-31 0 V
938 1957 M
63 0 V
2274 0 R
-63 0 V
-2358 0 R
( 0.001) Rshow
1.000 UL
LTb
938 2185 M
31 0 V
2306 0 R
-31 0 V
938 2317 M
31 0 V
2306 0 R
-31 0 V
938 2412 M
31 0 V
2306 0 R
-31 0 V
938 2485 M
31 0 V
2306 0 R
-31 0 V
938 2545 M
31 0 V
2306 0 R
-31 0 V
938 2595 M
31 0 V
2306 0 R
-31 0 V
938 2639 M
31 0 V
2306 0 R
-31 0 V
938 2677 M
31 0 V
2306 0 R
-31 0 V
938 2712 M
63 0 V
2274 0 R
-63 0 V
-2358 0 R
( 0.01) Rshow
1.000 UL
LTb
938 448 M
0 63 V
0 2201 R
0 -63 V
938 308 M
( 10) Cshow
1.000 UL
LTb
1290 448 M
0 31 V
0 2233 R
0 -31 V
1496 448 M
0 31 V
0 2233 R
0 -31 V
1642 448 M
0 31 V
0 2233 R
0 -31 V
1755 448 M
0 31 V
0 2233 R
0 -31 V
1847 448 M
0 31 V
0 2233 R
0 -31 V
1925 448 M
0 31 V
0 2233 R
0 -31 V
1993 448 M
0 31 V
0 2233 R
0 -31 V
2053 448 M
0 31 V
0 2233 R
0 -31 V
2107 448 M
0 63 V
0 2201 R
0 -63 V
0 -2341 R
( 100) Cshow
1.000 UL
LTb
2458 448 M
0 31 V
0 2233 R
0 -31 V
2664 448 M
0 31 V
0 2233 R
0 -31 V
2810 448 M
0 31 V
0 2233 R
0 -31 V
2923 448 M
0 31 V
0 2233 R
0 -31 V
3016 448 M
0 31 V
0 2233 R
0 -31 V
3094 448 M
0 31 V
0 2233 R
0 -31 V
3162 448 M
0 31 V
0 2233 R
0 -31 V
3222 448 M
0 31 V
0 2233 R
0 -31 V
3275 448 M
0 63 V
0 2201 R
0 -63 V
0 -2341 R
( 1000) Cshow
1.000 UL
LTb
1.000 UL
LTb
938 2712 N
938 448 L
2337 0 V
0 2264 V
-2337 0 V
Z stroke
LCb setrgbcolor
112 1580 M
currentpoint gsave translate -270 rotate 0 0 M
(L2 Error) Cshow
grestore
LTb
LCb setrgbcolor
2106 98 M
(N) Cshow
LTb
1.000 UP
1.000 UL
LTb
% Begin plot #1
1.000 UL
LT0
LCb setrgbcolor
2624 2579 M
(gamma=2) Rshow
LT0
2708 2579 M
399 0 V
1642 2525 M
205 -309 V
146 -214 V
114 -166 V
92 -130 V
146 -210 V
113 -153 V
239 -323 V
% End plot #1
% Begin plot #2
stroke
LT1
LCb setrgbcolor
2624 2439 M
(gamma=1) Rshow
LT1
2708 2439 M
399 0 V
-1465 86 R
205 -261 V
146 -188 V
114 -147 V
92 -119 V
146 -193 V
113 -144 V
93 -121 V
146 -188 V
% End plot #2
% Begin plot #3
stroke
LT2
LCb setrgbcolor
2624 2299 M
(gamma=0.5) Rshow
LT2
2708 2299 M
399 0 V
1642 2525 M
205 -232 V
146 -165 V
114 -127 V
92 -104 V
146 -163 V
113 -123 V
93 -101 V
146 -157 V
% End plot #3
% Begin plot #4
stroke
LT3
LCb setrgbcolor
2624 2159 M
(gamma=0.25) Rshow
LT3
2708 2159 M
399 0 V
1642 2525 M
205 -216 V
146 -151 V
114 -114 V
92 -93 V
146 -144 V
113 -107 V
239 -216 V
% End plot #4
% Begin plot #5
stroke
LT4
LCb setrgbcolor
2624 2019 M
(gamma=0) Rshow
LT4
2708 2019 M
399 0 V
1642 2525 M
205 -199 V
146 -136 V
114 -99 V
92 -80 V
146 -121 V
113 -88 V
93 -71 V
146 -107 V
% End plot #5
% Begin plot #6
stroke
LT5
LCb setrgbcolor
2624 1879 M
( order one ) Rshow
LT5
2708 1879 M
399 0 V
1642 2618 M
10 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -6 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -6 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -6 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -6 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -6 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -6 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -6 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -6 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -6 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -6 V
10 -7 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
10 -6 V
11 -7 V
11 -7 V
10 -7 V
11 -7 V
11 -7 V
% End plot #6
stroke
LTb
938 2712 N
938 448 L
2337 0 V
0 2264 V
-2337 0 V
Z stroke
1.000 UP
1.000 UL
LTb
stroke
grestore
end
showpage
%%Trailer
%%DocumentFonts: Helvetica
%%Pages: 1

### 2015-03-19 Answers_for_reviewers.tex
first corrections

\documentclass[a4paper,french,english,10pt]{article}
\usepackage{a4wide}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
%\usepackage{geometry}
%\geometry{verbose,a4paper,tmargin=3cm,bmargin=3cm,lmargin=3cm,rmargin=3cm,headheight=3cm,headsep=3cm}
\usepackage{babel}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{epsfig}
%\usepackage{esint}
\usepackage{color}
\usepackage{amsfonts}
\usepackage{amssymb,latexsym}
\usepackage{amscd}
\usepackage{multirow}
\usepackage{amsthm}
\usepackage[pdftex,bookmarks=true,bookmarksopen=true,colorlinks=true,linkbordercolor=white, citecolor=blue, linkcolor=red]{hyperref}

\usepackage{comment}

\newcommand{\dr}{\partial_R}
\newcommand{\ds}{\displaystyle}
\newcommand{\dz}{\partial_Z}
\newcommand{\dphi}{\partial_{\phi}}
\newcommand{\ephi}{\mathbf{e}_{\phi}}
\newcommand{\dt}{\partial_t}
\newcommand{\lp}{\triangle_{pol}}
\newcommand{\lpp}{\triangle_{pol}^2}
\newcommand{\gradp}{\nabla_{pol}}
\newcommand{\lpm}{\triangle_{pol}^{-1}}
\newcommand{\gs}{\triangle^{*}}
\newcommand{\U}{\mathbf{U}}
\newcommand{\V}{\mathbf{V}}
\newcommand{\vv}{\mathbf{v}}
\newcommand{\vB}{\mathbf{B}}
\newcommand{\vJ}{\mathbf{J}}
\newcommand{\vE}{\mathbf{E}}
\newcommand{\rot}{\nabla \times}
\newcommand{\er}{\mathbf{e}_R}
\newcommand{\ez}{\mathbf{e}_Z}
\newcommand{\eps}{\varepsilon}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\begin{document}

\title{Answers for the Reviewers  for the paper "Proof of uniform convergence for a cell-centered AP discretization of the hyperbolic heat equation on general meshes"}

\author{Emmanuel Franck\footnotemark[1] \footnotemark[2],
C. Buet \footnotemark[3], 
B. Despr\'es\footnotemark[4], 
T. Leroy\footnotemark[4] \footnotemark[3]
}
 \footnotetext[1]{INRIA Nancy Grand-Est & IRMA Strasbourg}
 \footnotetext[3]{CEA, DAM, DIF, F-91297 Arpajon Cedex,France}
 \footnotetext[4]{Laboratoire Jacques-Louis Lions,
  Universit\'e Pierre et Marie Curie,
  75252 Paris Cedex 05,
  France}
\footnotetext[2]{Email adress: emmanuel.franck@inria.fr}

\maketitle

\section{Answers for the report 2M}
\begin{itemize}
\item Comments and suggestions
\begin{itemize}
\item 1: We have added two subsections : "Precisions on AP discretizations" and "Organisation of the proof"
\end{itemize}
\item Minor issues and Typos
\begin{itemize}
\item 1: We have replaced $P^0$ by "first order"
\item 2 : we have corrected this sentence 
\item 3 : we have corrected this sentence 
\item 4 : we have corrected this sentence. (17) correspond to the scheme not the smooth data.
\item 5 : we have corrected this sentence. 
\item 6 : we have corrected your two remarks in this page 
\item 7 : we have corrected this sentence. 
\item 8: We have replaced $\gamma$ by $\tau$ in the numeric part.
\item 9: The date for the L. Gosse paper have been modified. for the S. Jin article we have copy the reference written on the website of S. Jin 
\end{itemize}
\end{itemize}
\end{document}

### 2015-03-19 Corrected_version.tex
first corrections

--- 2015-03-18 U_v16.tex
@@
 \end{equation}
-discretized with $P^0$ finite volume schemes.
+discretized with first order finite volume schemes.
 This problem is representative
@@
 \end{remark}
-
+\subsection{Precision of AP discretizations}
  Before addressing the main difficulty of this work  which is the discretization on  
@@
 
+\subsection{Organization of the proof}
 The structure of these  inequalities explains our strategy: that is we
@@
 The strategy of the proof of many estimates in this work
-consists to analyze the balance
+consists in analyzing the balance
 between the dissipation of the fluxes and the physical dissipation (all 
@@
 Some similar bounds hold 
-for  the quantities relatives to the diffusion scheme (\ref{schemadifff}).
+for  the quantities related to the diffusion scheme (\ref{schemadifff}).
 First, multiplying the diffusion scheme by $p_j$ and adding on all the cells,
@@
  recall a fundamental   error estimate \cite{FV}
-for the diffusion limit scheme, assuming smooth initial data.
-\eqref{schemadifff}. 
+for the diffusion limit scheme \eqref{schemadifff}, assuming smooth initial data.
+. 
 \begin{proposition}\label{ds1d}
@@
 is deduced.
-Since the scheme $P_h^0$ being stable in $L^2$, this bound is true at any time.
+Since the scheme $P_h^0$ is stable in $L^2$, this bound is true at any time.
 Considering (\ref{eq:zz}) the discrete second derivative
@@
 \end{equation*}
- where the geometry of the mesh serves to define the  
+ where the geometry of the mesh is sued to define the  
   matrices  
@@
 $B_r=\sum_j\bej$. 
-By comparison with the scheme $P_h^\eps$ in dimension one, one see at once
+By comparison with the scheme $P_h^\eps$ in dimension one, one sees at once
 that the multi-dimensional scheme (\ref{eq:4}-\ref{eq:6})  is  more 
@@
 \begin{proposition}[Convergence]\label{ein_prosit}
-There exist a constant $C(T, \sigma)>0$ 
+There exists a constant $C(T, \sigma)>0$ 
       such that the following estimate holds
@@
 The relation between $\eps$ and $h$ writes
-$\eps=0.01 (40h)^\gamma$ for $\gamma \in\{0,\frac14, \frac12, 1, 2  \}$.
+$\eps=0.01 (40h)^\tau$ for $\tau \in\{0,\frac14, \frac12, 1, 2  \}$.
 The error between the exact solution and the numerical solution is computed numerically
-in function of $h=\frac1N$, for different values of $\gamma$, and the results of some of these numerical experiments is
+in function of $h=\frac1N$, for different values of $\tau$, and the results of some of these numerical experiments is
 displayed in figure \ref{fig1}. The results correspond  to the  time $T = 0.02$ using the time step 
@@
 in section \ref{sec::num}.
-Each curve corresponds to a value of $\gamma\in\{0,\frac14, \frac12, 1, 2  \}$, plus 
+Each curve corresponds to a value of $\tau\in\{0,\frac14, \frac12, 1, 2  \}$, plus 
 a reference line for order one. One sees that the order of convergence is an increasing function
@@
 well-balanced scheme for the hyperbolic heat equations} C. R. Acad. Sci
-Paris,Ser. I 334, pp  337-342, , 2000.
+Paris,Ser. I 334, pp  337-342, , 2002.
 

### 2015-03-19 Corrected_version.tex
adding corrections

@@
 \begin{proof}
-We define $u^{\eps}=-\frac{\varepsilon}\sigma \partial_x p^{\eps}$ and
+We define $v=-\frac{\varepsilon}\sigma \partial_x p$ with $p$ the diffusion solution of (\ref{difffff}) and
 introduce $R^{\eps}$ such that the solution of the diffusion equation satisfies
@@
 \begin{array}{lll}
-\dt p^{\eps} +\frac{1}{\eps}\partial_{x}u^{\eps}=0,\\
-\partial_t u^{\eps} + \frac{1}{\eps}\partial_x p^{\eps} +\frac{\sigma}{\eps^2}u^{\eps} = R^{\eps}
+\dt p +\frac{1}{\eps}\partial_{x}v=0,\\
+\partial_t v+ \frac{1}{\eps}\partial_x p +\frac{\sigma}{\eps^2}v = R^{\eps}
 \end{array}
@@
 where
- $R^{\eps}=\dt u^{\eps}=-\frac{\varepsilon}\sigma \partial_{tx} p^{\eps}=
--\frac{\varepsilon}{\sigma^2} \partial_{xxx}p^{\eps}$. 
+ $R^{\eps}=\dt v=-\frac{\varepsilon}\sigma \partial_{tx} p=
+-\frac{\varepsilon}{\sigma^2} \partial_{xxx}p$. 
 Note that 
 $\|R^{\eps}(t)\|_{L^2(\mathbb{R})}\leq \|R^{\eps}(0)\|_{L^2(\mathbb{R})}$. 
-Denoting $e^{\eps}=p-p^{\eps}$, $f^{\eps}=u-u^{\eps}$, we make the difference between the
+Denoting $e^{\eps}=p-p^{\eps}$, $f^{\eps}=v-u^{\eps}$, we make the difference between the
 systems \eqref{chaleur22} et \eqref{modifdiff}
@@
 \leq h \left( \frac{1}{\eps}+\frac{\sigma}{2\eps^2}\right)
-\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) }.
-$$
-
-Since $\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) }\leq t \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$ and also 
+\|  u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) }.
+$$
+
+Since $\| u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) }\leq t \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$ and also 
 $
 \frac{\sigma}
-{\eps^2}\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) }\leq  \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$
+{\eps^2}\| u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) }\leq  \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$
 by (\ref{bee1} ) and (\ref{bee2} ), one gets that
@@
 \frac{\sigma^2}{4\eps^3}
-h \|  \mathbf u^\eps  \|^2_{  L^2(\mathbb R) }
+h \|  u^\eps  \|^2_{  L^2(\mathbb R) }
 $$
@@
 \frac{\sigma^2}{4\eps^3}
-h \|  \mathbf u^\eps  \|^2_{  L^2([0,t]\times \mathbb R) }
+h \| u^\eps  \|^2_{  L^2([0,t]\times \mathbb R) }
 \leq 
@@
 
-\begin{proposition}\label{pro:H1}
+\begin{lemma}\label{pro:H1}
 The bound (\ref{eq:xx}) holds.
-\end{proposition}
+\end{lemma}
 
@@
 \begin{equation}\label{ine3}
-| p^\epsilon-p\|_{   L^\infty([0,T];H^n(\Omega))  }+
-\| \uu^\eps 
+\| p^\epsilon-p\|_{   L^\infty([0,T];H^n(\Omega))  }+
+\| \mathbf{v} 
  \|_{   L^\infty([0,T]; H^n(\Omega))  }
@@
 p_{jr}^{\eps}-p_j^\eps=
-\njr,    \uj^{\eps}-\ur^{\eps}
+(\njr,    \uj^{\eps}-\ur^{\eps}
 )-\frac{\sigma}{\varepsilon}( \xr -\xj, \ur^{\eps}), 
@@
 a reference line for order one. One sees that the order of convergence is an increasing function
-of $\gamma$.}
+of $\tau$.}
 \label{fig1}
@@
 the order is approximatively 1 for $\gamma=0$ (hyperbolic limit)
-and 2 for $\gamma=2$ (parabolic regime).
+and 2 for $\gamma=2$ (parabolic regime).  We can find a closed result on the second order convergence for the parabolic regime in the paper \cite{TAHO} (1D linear problem).
 The reason is probably that the theory is based on worst case estimates, as it is often the case for the numerical analysis
@@
 
+\bibitem{TAHO} D. Aregba, M. Briani, R. Natalini, Time Asymptotic High Order Schemes for Dissipative BGK Hyperbolic Systems, arXiv:1207.6279.
+
 \bibitem{ber1} C. Berthon, P. Charrier, R. Turpault \emph{An HLLC scheme

### 2015-03-19 Answers_for_reviewers.tex
adding corrections
last corrections

@@
 \item 1: We have added two subsections : "Precisions on AP discretizations" and "Organisation of the proof"
+\item 3: We have added a sentence to explain why we use this formulation of the scheme and not the classical Gosse-Toscani scheme.
+For the remark about " the authors choose to renounce to the well- balanced property of the original 1D Gosse-Toscani scheme (except on uniform Cartesian grids) while retaining only its AP character" it is not clear that we say that.
+Indeed the scheme is well balanced for a subset of steady states (see annex of the paper "design of AP scheme ..."): the steady state associated to $u=Cts$ and $p$ linear.
+This property is perhaps impotent for the uniform convergence.
+At the end we renounce only to the steady states associated to $\nabla{u}=\nabla\times \phi$ with $\phi$ a potential.
+\item 4: We have correct this part introducing $v$ to obtain a not confusing proof.
+\item 5: We have replaced is $\mathbf{u}^{\eps}$ by $u^{\eps}$
+\item 6 : We have replaced the proposition 2.8 by the Lemma 2.8
+\item 7 : We have added the reference on the paper "Time asymptotic high order ..." at the end of the 2D in the numerical results.
+\item 8 : We have corrected the proposition 
+\item 9 : We have added the missing "("
 \end{itemize}

### 2015-03-19 Corrected_version.tex
last corrections

@@
   can be  obtained by various manipulations, as in (\ref{schema}).
+  We use another formulation of the Gosse-Toscani obtained using the Jin-Levemore scheme \cite{jinlev} and a discretization of the source term which use the fluxes.
+Contrary to the Gosse-Toscani scheme which use Riemann problem, this formulation based a basic algebraic computation is easier to write in 2D on unstructured meshes (the design is detailed in \cite{glaceap}).
+
 The natural cellwise initialization is chosen

### 2015-03-19 Corrected_version.tex
correction numérique
final correction manu

@@
 As demonstrated in this work, nodal based Finite Volume techniques do not suffer from this drawback.
+For linear wave equation the nodal scheme can be understand as some 1D Riemann problem written in some direction around each node.
+This a approximation of the 2D Riemann problem \cite{2Driemann}.
 
@@
 $$
-\alpha(t)=\frac{\lambda_2}{\lambda_2-\lambda_1}e^{\lambda_2 t  }
+\alpha(t)=\frac{\lambda_2}{\lambda_2-\lambda_1}e^{\lambda_1 t  }
 -
-\frac{\lambda_1}{\lambda_2-\lambda_1}e^{\lambda_1 t  }
+\frac{\lambda_1}{\lambda_2-\lambda_1}e^{\lambda_2 t  }
 $$
@@
 
-\bibitem{TAHO} D. Aregba, M. Briani, R. Natalini, Time Asymptotic High Order Schemes for Dissipative BGK Hyperbolic Systems, arXiv:1207.6279.
+\bibitem{TAHO} D. Aregba, M. Briani, R. Natalini, \emph{Time Asymptotic High Order Schemes for Dissipative BGK Hyperbolic Systems}, arXiv:1207.6279.
 
@@
 
+\bibitem{2DRiemann}  L. Gosse, \emph{A two-dimensional version of the Godunov scheme for scalar balance laws}. SIAM J. Numer. Anal. 52 (2014) 626?652.
+
 \bibitem{jinbase} S. Jin, \emph{Efficient Asymptotic-Preserving (AP)

### 2015-03-19 U_v16.tex
Test pour voir
Constantes_1D
Explicitation des constantes jusqu'à p12 incluse

@@
 \begin{hyp}[Regularity of the mesh in 1D] \label{geometrie1d}
- We consider there exists 
-a universal constant $C>0$ independent of the mesh size
+ We consider that there exists 
+a universal constant $C_{\mathcal{M}}>0$ independent of the mesh size
 $h=\sup_{j\in \mathbb Z} \Delta x_j $
@@
 $$
-Ch \leq \Delta x_j \leq h \qquad \forall j \in \mathbb{Z}.
+C_{\mathcal{M}} h \leq \Delta x_j \leq h \qquad \forall j \in \mathbb{Z}.
 $$
@@
 \end{equation}
-Our goal is this section is to show that this scheme is AP.
-
-When $\eps$ tends to $0$, 
+Our goal is this section is to show that this scheme is AP. When $\eps$ tends to $0$, 
  the scheme $P_h^\eps$ admits the 
@@
 \end{equation}
-
 The natural cellwise initialization is
@@
 \end{equation}
-
 Provided that the initial data is smooth, the initialization gives us 
@@
 \end{equation}
-
 We denote by $\V^{\eps}(t)=\left(p^{\eps}(x_j,t),
@@
 \|\V^{\eps}-\W^\eps\|_{L^\infty([0,T];L^2(\mathbb{R}) )} \leq
-C \eps  \|\partial_{xxx}p_0\|_{L^2(\mathbb{R})}.
+ \eps \frac{T}{\sigma^2} \|\partial_{xxx}p_0\|_{L^2(\mathbb{R})}.
 \end{equation*}
@@
 \begin{proof}
-We define $u^{\eps}=-\frac{\varepsilon}\sigma \partial_x p^{\eps}$ and
+We define $\widehat{u}^{\eps}=-\frac{\varepsilon}\sigma \partial_x p$, where $p$ is the solution of the diffusion equation\eqref{difffff} and we
 introduce $R^{\eps}$ such that the solution of the diffusion equation satisfies
@@
 \begin{array}{lll}
-\dt p^{\eps} +\frac{1}{\eps}\partial_{x}u^{\eps}=0,\\
-\partial_t u^{\eps} + \frac{1}{\eps}\partial_x p^{\eps} +\frac{\sigma}{\eps^2}u^{\eps} = R^{\eps}
+\dt p +\frac{1}{\eps}\partial_{x}\widehat{u}^{\eps}=0,\\
+\partial_t \widehat{u}^{\eps} + \frac{1}{\eps}\partial_x p +\frac{\sigma}{\eps^2}\widehat{u}^{\eps} = R^{\eps},
 \end{array}
@@
 where
- $R^{\eps}=\dt u^{\eps}=-\frac{\varepsilon}\sigma \partial_{tx} p^{\eps}=
--\frac{\varepsilon}{\sigma^2} \partial_{xxx}p^{\eps}$. 
+ $R^{\eps}=\dt \widehat{u}^{\eps}=-\frac{\varepsilon}\sigma \partial_{tx} p =
+-\frac{\varepsilon}{\sigma^2} \partial_{xxx}p$. 
 Note that 
 $\|R^{\eps}(t)\|_{L^2(\mathbb{R})}\leq \|R^{\eps}(0)\|_{L^2(\mathbb{R})}$. 
-Denoting $e^{\eps}=p-p^{\eps}$, $f^{\eps}=u-u^{\eps}$, we make the difference between the
+Denoting $e^{\eps}=p-p^{\eps}$, $f^{\eps}=\widehat{u}^{\eps}-u^{\eps}$, we make the difference between the
 systems \eqref{chaleur22} et \eqref{modifdiff}
@@
 \left\{
-\begin{array}{lll}
-\displaystyle\Delta x_j\frac{d}{dt}p^{\eps}_j +\frac{u_{j+\frac12 }^{\eps} -
+\begin{aligned}
+&\Delta x_j\frac{d}{dt}p^{\eps}_j +\frac{u_{j+\frac12 }^{\eps} -
 u_{j-\frac12 }^{\eps} }{\eps} = 0,\\
-\displaystyle\Delta x_j\frac{d}{dt}u^{\eps}_j-\frac{u_{j+\frac12 }^{\eps}+
+&\Delta x_j\frac{d}{dt}u^{\eps}_j-\frac{u_{j+\frac12 }^{\eps}+
 u_{j-\frac12 }^{\eps}}{\eps} +\frac{2}{\eps}u_j^{\eps}=0, \\
-\displaystyle 
+&
 \left( 2
@@
 \right) u_{j+\frac12 }^{\eps} 
-
 =p^{\eps}_j-p^{\eps}_{j+1}+u^{\eps}_j+u^{\eps}_{j+1}
 .
-\end{array}
+\end{aligned}
 \right.
@@
 \begin{proposition}\label{cv1d}
-There exist a constant $C(T)>0$ independent of $\eps$ and $h$ 
- such that the following estimate holds 
+Under assumption \ref{geometrie1d} on the mesh and assuming that the initial conditions satisfy \eqref{eq:initp1}, the following estimate holds 
 \begin{equation*}
 \|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
-\leq C(T) 
+\leq \sqrt{h\eps + 2t + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} }
 \sqrt \frac{h}\eps 
@@
 $\mathscr{E}=\frac12 \|\mathbf V_h^\eps - \mathbf V^\eps  \|^2_{L^2(\mathbb{R})}$.
-For the sake of simplicity,for any quantity $q$,   $q'$ stands indifferently for  $\frac{d}{dt}q $ or $\partial_t q $. One has 
+For the sake of simplicity, for any quantity $q$,   $q'$ stands indifferently for  $\frac{d}{dt}q $ or $\partial_t q $. One has 
 \begin{equation*}\label{esti}
@@
 \begin{equation*}
-\begin{array}{l}
- D_3 = \sum_{j\in \mathbb{Z}}
+\begin{aligned}
+ D_3 &= \sum_{j\in \mathbb{Z}}
 \frac{u_{j+\frac12 }^{\eps}-u_{j-\frac12 }^{\eps}}{\eps} \: \bigg(
@@
  u^{\eps}(x) dx \bigg) \\
-\hspace{0.8cm}+\sum_{j\in \mathbb{Z}} \Delta x_j  \frac{\sigma}{\eps^2}
+&+\sum_{j\in \mathbb{Z}} \Delta x_j  \frac{\sigma}{\eps^2}
 \frac{u_{j+\frac12 }^{\eps}+u_{j-\frac12 }^{\eps}}{2}\: \bigg(
@@
  u^{\eps}(x) dx \bigg).
-\end{array}
+\end{aligned}
 \end{equation*}
@@
 \begin{equation*}
-\begin{array}{lll}
- D_3 &=& \underset{j\in \mathbb{Z}}{\sum}
+\begin{aligned}
+ D_3 &= \underset{j\in \mathbb{Z}}{\sum}
 \frac{u_{j+\frac12 }^{\eps}-u_j^{\eps}}{\eps} \delta_{j}^+\left(p^{\eps}\right)+
@@
 \\
-& +& \underset{j\in \mathbb{Z}}{\sum}
+& + \underset{j\in \mathbb{Z}}{\sum}
 \frac{p_{j+\frac12 }^{\eps}-p_{j}^{\eps}}{\eps} 
@@
 \delta_{j}^-\left(u^{\eps}\right) \\
-&-&\underset{j\in \mathbb{Z}}{\sum} 
+&-\underset{j\in \mathbb{Z}}{\sum} 
 \frac{u^{\eps}(x_{j+\frac12 })-u^{\eps}(x_{j-\frac12 })}{\eps} 
-p^{\eps}_j
--
+p^{\eps}_j -
 \underset{j\in \mathbb{Z}}{\sum} 
@@
 u^{\eps}_j  \\
-&+& \underset{j\in \mathbb{Z}}{\sum} \Delta x_j  \frac{\sigma}{\eps^2}
+&+ \underset{j\in \mathbb{Z}}{\sum} \Delta x_j  \frac{\sigma}{\eps^2}
 \frac{u_{j+\frac12 }^{\eps}+u_{j-\frac12 }^{\eps}}{2}\: \bigg(
 \frac{1}{\Delta x_j} {\int_{x_{j-\frac12}}^{x_{j+\frac12}}}u^{\eps}(x) dx \bigg)
-\end{array}
+\end{aligned}
 \end{equation*}
@@
 arbitrary  $\alpha>0$
-\begin{eqnarray*}
- D_3 &\leq& \alpha \sum_{j\in \mathbb{Z}}
+\begin{equation*}
+\begin{aligned}
+ D_3 &\leq \alpha \sum_{j\in \mathbb{Z}}
 \frac{(u_{j+\frac12 }^{\eps}-u_j^{\eps})^2}{\eps} + \alpha \sum_{j\in
 \mathbb{Z}} \frac{(u_{j-\frac12 }^{\eps}-u_j^{\eps})^2}{\eps} \\
-&+&\sum_{j\in \mathbb{Z}} \bigg(
+&+\sum_{j\in \mathbb{Z}} \bigg(
 \left( \frac{1}{2\alpha\eps}+\frac{\sigma}{2\eps^2}\right)
@@
 }{2\eps\alpha} \bigg) \\
-&+& \sum_{j\in \mathbb{Z}} \frac{1}{8\eps} \sigma \Delta x_j^2
+&+ \sum_{j\in \mathbb{Z}} \frac{1}{8\eps} \sigma \Delta x_j^2
 \frac{(u_{j-\frac12 }^{\eps})^2 + (u_{j+\frac12 }^{\eps})^2}{\eps}+
@@
 \frac{1}{\Delta x_j} {\int_{x_{j-\frac12}}^{x_{j+\frac12}}}u^{\eps}(x) dx \bigg) \\
-&-& \sum_{j\in \mathbb{Z}} u^{\eps}_j 
+&- \sum_{j\in \mathbb{Z}} u^{\eps}_j 
 \frac{p^{\eps}(x_{j+\frac12 })-p^{\eps}(x_{j-\frac12 })}{\eps} -
 \sum_{j\in \mathbb{Z}} p^{\eps}_j
-\frac{u^{\eps}(x_{j+\frac12 })-u^{\eps}(x_{j-\frac12 })}{\eps}
-\end{eqnarray*}
+\frac{u^{\eps}(x_{j+\frac12 })-u^{\eps}(x_{j-\frac12 })}{\eps}.
+\end{aligned}
+\end{equation*}
 We now sum  all  bounds contributing to $\mathscr{E}'(t)$ and we get:
-\begin{eqnarray*}
-\mathscr{E}'(t)  & \leq & (-1+\alpha) \sum_{j\in \mathbb{Z}}
+\begin{equation*}
+\begin{aligned}
+\mathscr{E}'(t)  & \leq (-1+\alpha) \sum_{j\in \mathbb{Z}}
 \frac{(u_{j+\frac12 }^{\eps}-u_j^{\eps})^2+(u_{j-\frac12 }^{\eps}-u_j^{
 \eps})^2}{\eps} \\
-&+&\sum_{j\in \mathbb{Z}} \bigg(
+&+\sum_{j\in \mathbb{Z}} \bigg(
 \left( \frac{1}{2\alpha\eps}+\frac{\sigma}{2\eps^2}\right)
@@
 )^2}{2\eps\alpha} \bigg) \\
-&+& \sum_{j\in \mathbb{Z}} \frac{1}{8\eps} \sigma \Delta x_j^2
+&+ \sum_{j\in \mathbb{Z}} \frac{1}{8\eps} \sigma \Delta x_j^2
 \frac{(u_{j-\frac12 }^{\eps})^2+ (u_{j+\frac12 }^{\eps})^2}{\eps}\\
-&+& \sum_{j\in \mathbb{Z}} \Delta x_j  \frac{\sigma}{\eps^2}
+&+ \sum_{j\in \mathbb{Z}} \Delta x_j  \frac{\sigma}{\eps^2}
 \frac{u_{j+\frac12 }^{\eps}+u_{j-\frac12 }^{\eps}}{2}\: \bigg(
@@
 \frac{(u_{j-\frac12 }^{\eps})^2+(u_{j+\frac12 }^{\eps})^2}{\eps} \\
-&+& \sum_{j\in \mathbb{Z}} \Delta x_j  \frac{\sigma}{\eps^2} u^{\eps}_j \:
+&+ \sum_{j\in \mathbb{Z}} \Delta x_j  \frac{\sigma}{\eps^2} u^{\eps}_j \:
 \bigg( \frac{1}{\Delta x_j} {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg) -
@@
 \frac{1}{\Delta x_j} {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} (u^{\eps})^2(x) dx \bigg).
-\end{eqnarray*} 
+\end{aligned}
+\end{equation*} 
 We now examine
@@
 For example by choosing $\alpha=\frac12$ and $\widehat{\alpha}=\frac12$, and coming back to $\mathscr{E}'(t) $ we get
-we obtain
 \begin{eqnarray} \label{eq:eqn1}
@@
 \leq h \left( \frac{1}{\eps}+\frac{\sigma}{2\eps^2}\right)
-\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) }.
-$$
-
-Since $\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) }\leq t \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$ and also 
+\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R)) }.
+$$
+Since $\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) )}\leq t \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$ and also 
 $
 \frac{\sigma}
-{\eps^2}\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) }\leq  \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$
-by (\ref{bee1} ) and (\ref{bee2} ), one gets that
+{\eps^2}\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) )}\leq  \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$
+by (\ref{bee1}) and (\ref{bee2}), one gets that
 \begin{equation} \label{eq:sm1}
@@
 \end{equation}
-Next, using the assumption \eqref{geometrie1d} on the mesh and estimate \eqref{estiuepsflux}, one can find a constant $C\geq0$ such that the next term can be  bounded like 
+Next, using the assumption \eqref{geometrie1d} on the mesh and the estimate \eqref{estiuepsflux}, one controls the next term by 
 \begin{equation} \label{eq:sm3}
@@
 \frac{(u_{j-\frac12 }^{\eps})^2+(
-u_{j+\frac12 }^{\eps})^2}{\eps} \leq C h \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2.
+u_{j+\frac12 }^{\eps})^2}{\eps} \leq  \frac{h}{4C_{\mathcal{M}}} \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2.
 \end{equation}
@@
 \mathscr{E}(0)+h
-\left( \frac{t}{\eps}+\frac{1}2 + \frac{t}{\eps}+C+\frac{\sigma
+\left( \frac{t}{\eps}+\frac{1}2 + \frac{t}{\eps}+\frac{1}{4C_{\mathcal{M}}}+\frac{\sigma
 }{4\eps}\right)\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
 \end{eqnarray*}
-The initialization stage is consistent so 
- $\mathscr{E}(0)\leq Ch^2\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$.
+The initialization stage is consistent (equation \ref{eq:initp1}) so 
+ $\mathscr{E}(0)\leq h^2\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$.
  Making use of the  initial remark \ref{sigmanotzero}, one   obtains 
@@
 \|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
-\leq C(T) \sqrt{ \frac{h}{\eps}}
+\leq \sqrt{h\eps + 2t + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} } \sqrt{ \frac{h}{\eps}}
 \| \V^{\eps}( 0)
-\|_{H^1(\mathbb{R})}, \qquad C(T)\geq0.
+\|_{H^1(\mathbb{R})} .
 \end{equation*}
@@
  recall a fundamental   error estimate \cite{FV}
-for the diffusion limit scheme, assuming smooth initial data.
-\eqref{schemadifff}. 
+for the diffusion limit scheme \eqref{schemadifff}, assuming smooth initial data \eqref{eq:intip0}. 
 \begin{proposition}\label{ds1d}
@@
 x_{j+\frac12 }}=
-\sigma^{-1}\sum_j \Delta x_j s_j e_j+\sigma^{-1}\sum_jr_{j+\frac12 }(e_j-e_{j+1}).
+\frac{1}{\sigma}\sum_j \Delta x_j s_j e_j+\frac{1}{\sigma}\sum_jr_{j+\frac12 }(e_j-e_{j+1}).
 \end{equation*}
@@
 \frac{(e_{j+1}-e_{j})^2}{\Delta x_{j+\frac12 }}\leq
-\sigma^{-1}\| s_h\|_{L^2(\mathbb{R})} \|e_h\|_{L^2(\mathbb{R})}+
-\frac12 \|r_h\|^2_{L^2(\mathbb{R})}.
-\end{equation}
-Using the  definitions of  the truncation errors $s_h$ and $r_h$, these
-quantites can be   
-bounded independently of the time of observation $T$ 
+\frac{1}{\sigma}\| s_h\|_{L^2(\mathbb{R})} \|e_h\|_{L^2(\mathbb{R})}+
+\frac{1}{2\sigma} \|r_h\|^2_{L^2(\mathbb{R})}.
+\end{equation}
+Using the  definitions of  the truncation error $s_h$, one easilly obtains by using classical arguments $\|s_h\|_{L^2([0,T]\times\mathbb{R})}\leq \sqrt{2}h\|\partial_{xxx}p\|_{L^2([0,T]\times\mathbb{R})}$.
+Since $p$ satisfies the diffusion equation \eqref{difffff}, one gets $\|\partial_{xxx}p\|_{L^2([0,T]\times\mathbb{R})} \leq \sqrt{\sigma/2} \|\partial_{xx}p_0\|_{L^2(\mathbb{R})}$.
+The same manipulations on the second truncation error $r_h$ yields
 \begin{equation} \label{eq:bsr}
 \|s_h\|_{L^2([0,T]\times\mathbb{R})}+
-\|r_h\|_{L^2([0,T]\times\mathbb{R})}  \leq C h \bigg(
- \|\partial_{xxx}p_0   \| _{L^2(\mathbb{R})}+\|\partial_{xx}p_0\| _{L^2(\mathbb{R})} \bigg).
+\|r_h\|_{L^2([0,T]\times\mathbb{R})} \leq \sqrt{\sigma} h \bigg(
+ \|\partial_{xx}p_0   \| _{L^2(\mathbb{R})} +\|\partial_{x}p_0\| _{L^2(\mathbb{R})} \bigg).
 \end{equation}
@@
 \leq
-\| \widehat s_h\|_{L^2(\mathbb{R})} \|\widehat e_h\|_{L^2(\mathbb{R})}+
+\frac{1}{\sigma} \| \widehat s_h\|_{L^2(\mathbb{R})} \|\widehat e_h\|_{L^2(\mathbb{R})}+
 \frac{1}{2\sigma} \|\widehat r_h\|^2_{L^2(\mathbb{R})}
 \leq
-\frac12
-\left(\| \widehat s_h\|_{L^2(\mathbb{R})}^2+ \frac{1}{\sigma} \|\widehat r_h\|^2_{L^2(\mathbb{R})}  \right)+\frac12 
- \|\widehat e_h\|^2_{L^2(\mathbb{R})}
+\frac{1}{2\sigma}
+\left(\| \widehat s_h\|_{L^2(\mathbb{R})}^2+  \|\widehat r_h\|^2_{L^2(\mathbb{R})}  \right)+ \frac{1}{2\sigma}
+ \|\widehat e_h\|^2_{L^2(\mathbb{R})},
 $$
@@
 \begin{equation} \label{eq:e2}
-\| e_h\|_{L^\infty([0,T];\mathbb{R})}\leq C(T) h 
+\| e_h\|_{L^\infty([0,T];L^2(\mathbb{R}))}\leq h 
 \left(  \|\partial_{xx}p_0   \| _{L^2(\mathbb{R})}+
- \|\partial_{xxx}p_0   \| _{L^2(\mathbb{R})}
-\right).
+ \|\partial_{x}p_0   \| _{L^2(\mathbb{R})}
+\right)e^{T/2\sigma}.
 \end{equation}
@@
 $
-f_h=\eps\left(v(x_j)-v_j    \right)_{j\in \mathbb Z}=-\eps
-\left(\frac{\partial_x p(x_j)}{\sigma}- v_j  \right)_{j\in \mathbb Z}$.
+f_h=\eps\left(v(x_j)-v_j    \right)_{j\in \mathbb Z}= - \eps
+\left(  \frac{\partial_x p(x_j)}{\sigma} + v_j  \right)_{j\in \mathbb Z}$, where $v$ is defined in \eqref{eq:diff-v}.
 We notice that (\ref{eq:eee}) and (\ref{eq:e2}) yields
 $$
-\left\| 
-\frac{e_{j+1}-e_{j}}{\Delta x_{j+\frac12 }} \right\|_{
-L^2([0,T]\times\mathbb{R})
-}
-\leq C(T) h 
-\left(  \|\partial_{xx}p_0   \| _{L^2(\mathbb{R})}+
- \|\partial_{xxx}p_0   \| _{L^2(\mathbb{R})}
-\right)
+\int_0^T \sum_j
+\frac{(e_{j+1}-e_{j})^2}{\Delta x_{j+\frac12 }}\leq h^2
+\left(  \|\partial_{xx}p_0   \| _{L^2(\mathbb{R})}^2 +
+ \|\partial_{x}p_0   \| _{L^2(\mathbb{R})}^2 
+\right)\bigg( \sigma + Te^{T/\sigma} \bigg) ,
 $$
@@
 $$
-\left\| 
-\frac{p_{j+1}-p_{j}}{\Delta x_{j+\frac12 }} -\partial_x p (x_{j+\frac12}) \right\|_{
-L^2([0,T]\times\mathbb{R})
-}
-\leq C(T) h 
-\left(  \|\partial_{xx}p_0   \| _{L^2(\mathbb{R})}+
- \|\partial_{xxx}p_0   \| _{L^2(\mathbb{R})}
-\right).
+\int_0^T \sum_j \Delta x_{j+\frac12 } \bigg|
+\frac{p_{j+1}-p_{j}}{\Delta x_{j+\frac12 }} -\partial_x p (x_{j+\frac12})  \bigg|^2
+\leq 2 h^2
+\left(  \|\partial_{xx}p_0   \| _{L^2(\mathbb{R})}^2 +
+ \|\partial_{x}p_0   \| _{L^2(\mathbb{R})}^2 
+\right)\bigg( 3 \sigma + Te^{T/\sigma} \bigg).
 $$
@@
 L^2([0,T]\times\mathbb{R})
-}\leq C(T) h \eps \left(  \|\partial_{xx}p_0   \| _{L^2(\mathbb{R})}+
- \|\partial_{xxx}p_0   \| _{L^2(\mathbb{R})}
-\right).
-\end{equation}
-Finally, 
+}\leq  h \eps \bigg(  \|\partial_{xx}p_0   \| _{L^2(\mathbb{R})}+
+ \|\partial_{xxx}p_0   \| _{L^2(\mathbb{R})} \bigg) \sqrt{\frac12 + \frac{4}{\mathcal{C}_M}\bigg( 3 + \frac{T}{\sigma}e^{T/\sigma} \bigg) }
+,
+\end{equation}
+where the constant $\mathcal{C}_M$ is defined in assumption \ref{geometrie1d}. Finally, 
 $\|\W_h^\eps-\W^\eps\|_{L^2([0,T]\times\mathbb{R})}^2=

### 2015-03-20 Answers_for_reviewers.tex
final correction manu
correction thomas

@@
 }
- \footnotetext[1]{INRIA Nancy Grand-Est & IRMA Strasbourg}
+ \footnotetext[1]{INRIA Nancy Grand-Est and IRMA Strasbourg}
  \footnotetext[3]{CEA, DAM, DIF, F-91297 Arpajon Cedex,France}
@@
 \begin{itemize}
+\item Constant
+\begin{itemize}
+\item Page 5 we have modified the constant for the 1D regularity mesh
+\item We have correct the constant in the proposition 2.5 page 8
+\item 1 : we have corrected the constant in the proposition 2.2 page 7
+\item 2 :
+\item 3 :
+\item 4 :
+\item 5 : We have explicit the constant between the equation (32) and the end of the proof of the proposition 2.5
+\end{itemize}
+\begin{itemize}
 \item Comments and suggestions
@@
 \item 1: We have added two subsections : "Precisions on AP discretizations" and "Organisation of the proof"
+\item 2: we have added 2 sentences about the 2D Riemann problem and the nodal scheme. 
 \item 3: We have added a sentence to explain why we use this formulation of the scheme and not the classical Gosse-Toscani scheme.

### 2015-03-20 Corrected_version.tex
correction thomas

@@
 \begin{proposition} \label{heqtode}
-There exists a constant $C>0$ such that 
+There exists a constant which depend of the time such that 
 \begin{equation*}
 \|\V^{\eps}-\W^\eps\|_{L^\infty([0,T];L^2(\mathbb{R}) )} \leq
-C \eps  \|\partial_{xxx}p_0\|_{L^2(\mathbb{R})}.
+ \eps \frac{T}{\sigma^2} \|\partial_{xxx}p_0\|_{L^2(\mathbb{R})}.
 \end{equation*}
@@
 .
-\end{array}
+\end{aligned}
 \right.
@@
 \begin{proposition}\label{cv1d}
-There exist a constant $C(T)>0$ independent of $\eps$ and $h$ 
- such that the following estimate holds 
+Under assumption \ref{geometrie1d} on the mesh and assuming that the initial conditions satisfy \eqref{eq:initp1}, the following estimate holds
+
 \begin{equation*}
 \|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
-\leq C(T) 
+\leq \sqrt{h\eps + 2t + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} }
 \sqrt \frac{h}\eps 
@@
 \leq h \left( \frac{1}{\eps}+\frac{\sigma}{2\eps^2}\right)
-\|  u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) }.
-$$
-
-Since $\| u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) }\leq t \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$ and also 
-$
+\|  u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R)) }.
+$$
+
+Since $\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) )}\leq t \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$ and also 
 \frac{\sigma}
-{\eps^2}\| u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) }\leq  \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$
-by (\ref{bee1} ) and (\ref{bee2} ), one gets that
+{\eps^2}\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) )}\leq  \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$
+by (\ref{bee1}) and (\ref{bee2}), one gets that
 \begin{equation} \label{eq:sm1}
@@
 \end{eqnarray*}
-The initialization stage is consistent so 
- $\mathscr{E}(0)\leq Ch^2\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$.
+The initialization stage is consistent (equation \ref{eq:initp1}) so 
+ $\mathscr{E}(0)\leq h^2\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$.
  Making use of the  initial remark \ref{sigmanotzero}, one   obtains 
@@
 \|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
-\leq C(T) \sqrt{ \frac{h}{\eps}}
+\leq \sqrt{h\eps + 2t + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} } \sqrt{ \frac{h}{\eps}}
 \| \V^{\eps}( 0)
@@
  recall a fundamental   error estimate \cite{FV}
-for the diffusion limit scheme \eqref{schemadifff}, assuming smooth initial data.
-. 
+for the diffusion limit scheme \eqref{schemadifff}, assuming smooth initial data \eqref{eq:intip0}. 
 \begin{proposition}\label{ds1d}
@@
 \frac{(e_{j+1}-e_{j})^2}{\Delta x_{j+\frac12 }}\leq
-\sigma^{-1}\| s_h\|_{L^2(\mathbb{R})} \|e_h\|_{L^2(\mathbb{R})}+
-\frac12 \|r_h\|^2_{L^2(\mathbb{R})}.
-\end{equation}
-Using the  definitions of  the truncation errors $s_h$ and $r_h$, these
-quantites can be   
-bounded independently of the time of observation $T$ 
+\frac{1}{\sigma}\| s_h\|_{L^2(\mathbb{R})} \|e_h\|_{L^2(\mathbb{R})}+
+\frac{1}{2\sigma} \|r_h\|^2_{L^2(\mathbb{R})}.
+\end{equation}
+Using the  definitions of  the truncation error $s_h$, one easily obtains by using classical arguments $\|s_h\|_{L^2([0,T]\times\mathbb{R})}\leq \sqrt{2}h\|\partial_{xxx}p\|_{L^2([0,T]\times\mathbb{R})}$.
+Since $p$ satisfies the diffusion equation \eqref{difffff}, one gets $\|\partial_{xxx}p\|_{L^2([0,T]\times\mathbb{R})} \leq \sqrt{\sigma/2} \|\partial_{xx}p_0\|_{L^2(\mathbb{R})}$.
+The same manipulations on the second truncation error $r_h$ yields
 \begin{equation} \label{eq:bsr}
 \|s_h\|_{L^2([0,T]\times\mathbb{R})}+
-\|r_h\|_{L^2([0,T]\times\mathbb{R})}  \leq C h \bigg(
- \|\partial_{xxx}p_0   \| _{L^2(\mathbb{R})}+\|\partial_{xx}p_0\| _{L^2(\mathbb{R})} \bigg).
+\|r_h\|_{L^2([0,T]\times\mathbb{R})} \leq \sqrt{\sigma} h \bigg(
+ \|\partial_{xx}p_0   \| _{L^2(\mathbb{R})} +\|\partial_{x}p_0\| _{L^2(\mathbb{R})} \bigg).
 \end{equation}

### 2015-03-20 Corrected_version.tex
correction

@@
 \right) u_{j+\frac12 }^{\eps} 
-
 =p^{\eps}_j-p^{\eps}_{j+1}+u^{\eps}_j+u^{\eps}_{j+1}
@@
 Since $\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) )}\leq t \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$ and also 
-\frac{\sigma}
+$\frac{\sigma}
 {\eps^2}\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) )}\leq  \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$

### 2015-03-20 Answers_for_reviewers.tex
corrections

@@
 \begin{itemize}
-\item Constant
+\item A massive overuse of ?Constant C? and the issue of the estimates? time-dependence
 \begin{itemize}
@@
 \item 1 : we have corrected the constant in the proposition 2.2 page 7
-\item 2 :
+\item 8: in 1D we have explicit all the constant 
 \item 3 :
@@
 \item 5 : We have explicit the constant between the equation (32) and the end of the proof of the proposition 2.5
+\item 6 :
+\item 7 : The conflict for the notation have been corrected. For the solution there are not reference, we have construct this solution using a separation of the variable. we have added the details.
+\item 2-8: in 1D we have explicit all the constant. We obtain time-exponential rate as you expect.
 \end{itemize}

### 2015-03-20 Corrected_version.tex
corrections

@@
 with $f$ solution of 
-$
-\partial_t f +\frac{\eps^2}\sigma \partial_t^2 f -\frac1\sigma \Delta f=0$.
-We add periodic boundary conditions and consider
+\begin{equation}\label{telegraph}
+\partial_t f +\frac{\eps^2}\sigma \partial_t^2 f -\frac1\sigma \Delta f=0.
+\end{equation}
+ We propose to construct a solution for a subset of small $\eps$ to validate the uniform convergence.
+Firstly we consider that the solution is a periodic solution on the square $\left[0,2\right]\times\left[0,2\right]$.
+For this we use the separation of the variables.
+We consider the following function
 $$
@@
 $$
+and we propose to find the function $\alpha(t)$ such that $f(t,x,y)=\alpha(t)\cos (\pi x ))\cos( \pi y )$ is a periodic solution of (\ref{telegraph}).
 The function $\alpha$ is determined as the solution of
@@
 $$
-whith $\alpha'(0)=0$ and $\alpha(0)=1$.
+with $\alpha'(0)=0$ and $\alpha(0)=1$.
 For small $\eps$, which is the case we are interested in, the solution is computed as follows.

### 2015-03-20 Corrected_version.tex
Chgt constante + Lemma 2.8

@@
 \begin{equation}\label{init_1D}
- \| u_j^{\eps}(0)-\eps v_j(0)\|_{L^2(\mathbb{R})} \leq C h\eps .
+ \| u_j^{\eps}(0)-\eps v_j(0)\|_{L^2(\mathbb{R})} \leq C_0 h\eps .
 \end{equation}
@@
 \leq
-C\|p_0\|_{L^2(\mathbb R)}, \qquad C>0.
+\sqrt{\frac{\sigma}{2}}\|p_0\|_{L^2(\mathbb R)}, \qquad C>0.
 \end{equation}
@@
 \begin{proposition}\label{ds1d}
-There exists a constant $C(T)>0$ such that
+Under assumption \ref{geometrie1d}, the following estimate holds
 \begin{equation*}
 \|\W_h^\eps-\W^\eps\|_{L^{\infty}([0,T];L^2(\mathbb{R}))} \leq
-C(T)h \| \partial_{xxx}p_0 \|_{L^2(\mathbb{R})  }.
+h 
+\left(  \|\partial_{xx}p_0   \| _{L^2(\mathbb{R})}+
+ \|\partial_{x}p_0   \| _{L^2(\mathbb{R})}
+\right)  \bigg(  
+e^{T/2\sigma} + 
+\eps \sqrt{\frac12 + \frac{4}{\mathcal{C}_M}\bigg( 3 + \frac{T}{\sigma}e^{T/\sigma} \bigg) } \bigg).
 \end{equation*}
@@
 }\leq  h \eps \bigg(  \|\partial_{xx}p_0   \| _{L^2(\mathbb{R})}+
- \|\partial_{xxx}p_0   \| _{L^2(\mathbb{R})} \bigg) \sqrt{\frac12 + \frac{4}{\mathcal{C}_M}\bigg( 3 + \frac{T}{\sigma}e^{T/\sigma} \bigg) }
+ \|\partial_{xxx}p_0   \| _{L^2(\mathbb{R})} \bigg) \sqrt{\frac12 + \frac{4}{C_{\mathcal{M}}}\bigg( 3 + \frac{T}{\sigma}e^{T/\sigma} \bigg) }
 ,
 \end{equation}
-where the constant $\mathcal{C}_M$ is defined in assumption \ref{geometrie1d}. Finally, 
+where the constant $C_{\mathcal{M}}$ is defined in assumption \ref{geometrie1d}. Finally, 
 $\|\W_h^\eps-\W^\eps\|_{L^2([0,T]\times\mathbb{R})}^2=
@@
 \begin{equation*}
-\|\V_h^{\eps}-\W^\eps_h\|_{L^2([0,T]\times\mathbb R)} \leq
-C(T)  \eps.
-\end{equation*}
+\|\V_h^{\eps}-\W^\eps_h\|_{L^2([0,T]\times\mathbb R)} \leq  \eps e^{t/2} \bigg(  C_0h + \sqrt{ \frac{1}{\sigma C_{\mathcal{M}} } ( \frac12 + \frac{1}{\sigma^2} )} \|p_0\|_{H^2(\mathbb{R})} \bigg) ,
+\end{equation*}
+where $C_0$ is defined in \eqref{init_1D}.
 \end{proposition}
@@
 \end{equation*}
-Thanks to the estimate \eqref{l2} and as the scheme is linear, $\frac{d}{dt} u_j$
+Thanks to the estimate \eqref{l2} and since the scheme is linear, $\frac{d}{dt} u_h = (\frac{d}{dt} u_j)_{j\in\mathbb{Z}}$
 satisfies the estimate 
 $$
-\|R\|_{L^2([0,T]\times \mathbb{R})}=\bigg\|\frac{d}{dt} u_j\bigg\|_{L^2([0,T]\times \mathbb{R})}\leq
-C\eps\bigg\|\frac{d}{dt} p_h(0)\bigg\|_{L^2(\mathbb{R})}.
+\bigg\|\frac{d}{dt} u_h\bigg\|_{L^2([0,T]\times \mathbb{R})} = \sqrt{\int_0^T \sum_{j\in\mathbb{Z}} \Delta x_j u_j^2 }\leq
+\eps \sqrt{ \frac{\sigma}{2C_{\mathcal{M}} }} \bigg\|\frac{d}{dt} p_h(0)\bigg\|_{L^2(\mathbb{R})}.
 $$
@@
 which
-implies that $\|\frac{d}{dt} p_h(0)\|_{L^2(\mathbb{R})}\leq C 
-\| p(t=0)\|_{H^2(\mathbb{R})}$. So one has the bound
+implies that $\|\frac{d}{dt} p_h(0)\|_{L^2(\mathbb{R})}\leq \frac{1}{\sigma}
+\| p_0\|_{H^2(\mathbb{R})}$  (proposition \ref{pro:H1}). So one has the bound
 \begin{equation} \label{eq:p5}
-\|R\|_{L^2([0,T]\times \mathbb{R})}\leq C \eps
-\| p(0)\|_{H^2(\mathbb{R})}.
-\end{equation}
-It is seen in proposition \ref{pro:H1}
-that 
+\|R\|_{L^2([0,T]\times \mathbb{R})}\leq   \frac{\eps }{ \sqrt{ 2\sigma C_{\mathcal{M}} } } 
+\| p_0\|_{H^2(\mathbb{R})}.
+\end{equation}
+Using the definitions of $u_j$ \eqref{schemadiff3}, the $L^2$ norm of $S_h = (S_{j+\frac12})_{j\in\mathbb{Z}}$ is related to the $L^2$ norm of $\frac{d}{dt}u_j$.
+Using once again the proposition \ref{pro:H1}, one finds out that
 \begin{equation}\label{eq:xx}
-\| S\|_{L^2(\mathbb{R})} \leq \eps  
+\| S_h \|_{L^2(\mathbb{R})} \leq \eps  \frac{\sqrt{2}}{\sigma \sqrt{C_{\mathcal{M}}}}
 \| p(0)\|_{H^2(\mathbb{R})}.
@@
 \begin{eqnarray*}
-\frac12 \frac{d}{dt}\|\V_h^{\eps}-\W^\eps_h\|_{L^2(\mathbb R)}
-^2 \leq \frac12 \|\V_h^{\eps}-\W^\eps_h\|_{L^2(\mathbb R)}^2 +
-C\bigg( \| R\|_{L^2(\mathbb R)}^2 +\| S \|_{L^2(\mathbb R)}^2\bigg).
+ \frac{d}{dt}\|\V_h^{\eps}-\W^\eps_h\|_{L^2(\mathbb R)}
+^2 \leq  \|\V_h^{\eps}-\W^\eps_h\|_{L^2(\mathbb R)}^2 +
+ \| R\|_{L^2(\mathbb R)}^2 + \frac1{2\sigma}\| S \|_{L^2(\mathbb R)}^2 . 
 \end{eqnarray*}
@@
 \exp(t) \left( \|\V_h^{\eps}(0)-\W^\eps_h(0)\|_{L^2(\mathbb R)}^2 
-+ C (
- \| R\|_{L^2([0,T]\times\mathbb R)}^2 + \|
-S\|_{L^2([0,T]\times\mathbb R)}^2
-) \right)
++ 
+ \| R\|_{L^2([0,T]\times\mathbb R)}^2 +  \frac1{2\sigma} \|
+S\|_{L^2([0,T]\times\mathbb R)}^2 \right)
 \end{equation*}
@@
 $
-\|\V_h^{\eps}-\W^\eps_h\|_{L^2([0,T]\times\mathbb{R})} \leq C(T) \eps$. 
+\|\V_h^{\eps}-\W^\eps_h\|_{L^2([0,T]\times\mathbb{R})} \leq \eps e^{t/2} \big(  C_0h + \sqrt{ \frac{1}{\sigma C_{\mathcal{M}} } ( \frac12 + \frac{1}{\sigma^2} )} \|p_0\|_{H^2(\mathbb{R})} \big)$. 
 The proof is ended.
@@
 \begin{lemma}\label{pro:H1}
-The bound (\ref{eq:xx}) holds.
-\end{lemma}
+The bound $
+\sqrt{ \sum_j \Delta x_j (\frac{d}{dt}u_j)^2(t) }
+\leq \sigma^{-1}\|p_0\|_{H^2(\mathbb{R})}$
+ holds at any time.\end{lemma}
 
@@
 
-Using the definition of $u_j$
-and $u_{j+\frac12 }$, one has 
-$$
-S_{j+\frac12 }=\frac{\eps}{2}\left( \frac{ \Delta x_j}{\Delta x_{j+\frac12}}
-\frac{d}{dt} p_j - \frac{\Delta x_{j+1}}{\Delta x_{j+\frac12}} \frac{d}{dt} p_{j+1} \right)
-$$
- at all time.
-Moreover, $z_h=\frac{d}{dt} p_h$ is solution of
+By linearity of the diffusion scheme, $z_h=\frac{d}{dt} p_h$ is solution of
 $P_h^0$:

### 2015-03-20 U_v16.tex
Chgt constante + Lemma 2.8

@@
 \end{equation*}
-then  in terms of $p^{\eps} $ an $u^{\eps} $ we have evidently
+then  in terms of $p^{\eps} $ and $u^{\eps} $ we have evidently
 \begin{equation*} \label{eq:63num}
@@
 \leq
-C\|p_0\|_{L^2(\mathbb R)}, \qquad C>0.
+\sqrt{\frac{\sigma}{2}} \|p_0\|_{L^2(\mathbb R)}.
 \end{equation}
@@
 \begin{proposition}\label{ds1d}
-There exists a constant $C(T)>0$ such that
+Under assumption \ref{geometrie1d}, the following estimate holds
 \begin{equation*}
-\|\W_h^\eps-\W^\eps\|_{L^{\infty}([0,T];L^2(\mathbb{R}))} \leq
-C(T)h \| \partial_{xxx}p_0 \|_{L^2(\mathbb{R})  }.
+\|\W_h^\eps-\W^\eps\|_{L^{\infty}([0,T];L^2(\mathbb{R}))} \leq h 
+\left(  \|\partial_{xx}p_0   \| _{L^2(\mathbb{R})}+
+ \|\partial_{x}p_0   \| _{L^2(\mathbb{R})}
+\right)  \bigg(  
+e^{T/2\sigma} + 
+\eps \sqrt{\frac12 + \frac{4}{\mathcal{C}_M}\bigg( 3 + \frac{T}{\sigma}e^{T/\sigma} \bigg) } \bigg).
 \end{equation*}
@@
 which
-implies that $\|\frac{d}{dt} p_h(0)\|_{L^2(\mathbb{R})}\leq C 
-\| p(t=0)\|_{H^2(\mathbb{R})}$. So one has the bound
+implies that $\|\frac{d}{dt} p_h(0)\|_{L^2(\mathbb{R})}\leq \frac{1}{\sigma} 
+\| p_0\|_{H^2(\mathbb{R})}$ (proposition \ref{pro:H1}). So one has the bound
 \begin{equation} \label{eq:p5}
-\|R\|_{L^2([0,T]\times \mathbb{R})}\leq C \eps
-\| p(0)\|_{H^2(\mathbb{R})}.
-\end{equation}
-It is seen in proposition \ref{pro:H1}
-that 
+\|R\|_{L^2([0,T]\times \mathbb{R})}\leq   \frac{\eps }{ \sqrt{ 2\sigma C_{\mathcal{M}} } } 
+\| p_0\|_{H^2(\mathbb{R})}.
+\end{equation}
+Using the definitions of $u_j$ \eqref{schemadiff3}, the $L^2$ norm of $S_h = (S_{j+\frac12})_{j\in\mathbb{Z}}$ is related to the $L^2$ norm of $\frac{d}{dt}u_j$.
+Using once again the proposition \ref{pro:H1}, one finds out that
 \begin{equation}\label{eq:xx}
-\| S\|_{L^2(\mathbb{R})} \leq \eps  
+\| S_h \|_{L^2(\mathbb{R})} \leq \eps  \frac{\sqrt{2}}{\sigma \sqrt{C_{\mathcal{M}}}}
 \| p(0)\|_{H^2(\mathbb{R})}.
@@
 \begin{proposition}\label{pro:H1}
-The bound (\ref{eq:xx}) holds.
+The bound $
+\sqrt{ \sum_j \Delta x_j (\frac{d}{dt}u_j)^2(0) }
+\leq \sigma^{-1}\|p_0\|_{H^2(\mathbb{R})}$
+ holds at any time.
 \end{proposition}

### 2015-03-20 Corrected_version.tex
Corrections u->p

@@
 \end{equation}
-Using the definitions of $u_j$ \eqref{schemadiff3}, the $L^2$ norm of $S_h = (S_{j+\frac12})_{j\in\mathbb{Z}}$ is related to the $L^2$ norm of $\frac{d}{dt}u_j$.
-Using once again the proposition \ref{pro:H1}, one finds out that
+Using the definitions of $u_j$ \eqref{schemadiff3}, $S_{j+\frac12}$ can be written in terms of $\frac{d}{dt}p_j$ and $\frac{d}{dt}p_{j+1}$
+\begin{equation*}
+S_{j+\frac12} = \frac{\eps}{2} \bigg( \frac{\Delta x_{j} }{\Delta x_{j+\frac12} }\frac{d}{dt}p_j - \frac{\Delta x_{j+1} }{\Delta x_{j+\frac12} }\frac{d}{dt}p_{j+1} \bigg).
+\end{equation*}
+Using once again the proposition \ref{pro:H1}, one finds out that $S_h = (S_{j+\frac12})_{j\in\mathbb{Z}}$ satisfies
 \begin{equation}\label{eq:xx}
@@
 The bound $
-\sqrt{ \sum_j \Delta x_j (\frac{d}{dt}u_j)^2(t) }
+\sqrt{ \sum_j \Delta x_j (\frac{d}{dt}p_j)^2(t) }
 \leq \sigma^{-1}\|p_0\|_{H^2(\mathbb{R})}$

### 2015-03-23 Corrected_version.tex
add a remark on time rate

@@
  We propose to construct a solution for a subset of small $\eps$ to validate the uniform convergence.
-Firstly we consider that the solution is a periodic solution on the square $\left[0,2\right]\times\left[0,2\right]$.
+Firstly we consider that the solution is a periodic solution on the square $\left[0,2\right]\times\left[0,\frac{2}{L}\right]$.
 For this we use the separation of the variables.
@@
 $$
-f(t,x,y)=\alpha(t)\cos (\pi x ))\cos( \pi y ).
-$$
-and we propose to find the function $\alpha(t)$ such that $f(t,x,y)=\alpha(t)\cos (\pi x ))\cos( \pi y )$ is a periodic solution of (\ref{telegraph}).
+f(t,x,y)=\alpha(t)\cos (L \pi x ))\cos( L\pi y ).
+$$
+and we propose to find the function $\alpha(t)$ such that $f(t,x,y)=\alpha(t)\cos (L\pi x )\cos( L\pi y )$ is a periodic solution of (\ref{telegraph}).
 The function $\alpha$ is determined as the solution of
 $$
-\alpha'(t)+ \frac{\eps^2}\sigma\alpha''(t)+\frac{2\pi}\sigma \alpha=0
+\alpha'(t)+ \frac{\eps^2}\sigma\alpha''(t)+\frac{2L^2\pi^2}\sigma \alpha(t)=0
 $$
@@
 \frac{
-\sigma \left( \sqrt{1-\frac{\eps^2}{\sigma^2}  8 \pi^2  } +1\right)
+\sigma \left( \sqrt{1-\frac{\eps^2}{\sigma^2}  8L^2 \pi^2  } +1\right)
 }{2 \eps^2  }
@@
 \frac{
-\sigma \left( \sqrt{1-\frac{\eps^2}{\sigma^2}  8 \pi^2  } -1\right)
+\sigma \left( \sqrt{1-\frac{\eps^2}{\sigma^2}  8L^2 \pi^2  } -1\right)
 }{2 \eps^2  }.
@@
 The reason is probably that the theory is based on worst case estimates, as it is often the case for the numerical analysis
-of finite volume schemes \cite{FV}.
+of finite volume schemes \cite{FV}. Numerically we observe a time-linear rate for the numerical which shows that the time-exponential rate obtained using the Gronwall lemma is clearly not optimal.
 

### 2015-03-23 code_FVFSHS_2D_matter/AnaSol/AnalyticAdvectionSolution.cpp
ajout du code

@@ -1,0 +1,41 @@
+
+#include <iostream>
+#include <cassert>
+#include "ClassMesh.hpp"
+#include "math.h"
+#include "Functions.hpp"
+#include "AnalyticSolutions.hpp"
+#include "ParamPhys.hpp"
+
+double SolFonAdvection(Data & d,ParamPhysic & Param,Vertex p,double t,Vertex center){
+  /** fucntion which gives the advection analytical solution for p, t and center  **/ 
+  double res;
+
+
+  if(d.nTest==1){   
+    res=TransportSol(d,Param,p,t,center);
+    return res;
+  }
+
+    
+    else {
+      cout << "Pas de solution fondamentale associé a ce cas test"<<endl;exit(1);
+    }
+}
+
+double TransportSol(Data & d,ParamPhysic & Param,Vertex p,double t,Vertex center){
+   /** Analytical solution: advection of gaussian function  **/ 
+  R2 pp(0,0);
+  double res=0;
+  R2 a(0,0);
+  a.x=Param.Adv.velocity.x;
+  a.y=Param.Adv.velocity.y;
+  if(!strcmp(d.Typemodel,"M1")){ a.x=1.; a.y=0;}
+  pp.x=p.x-a.x*t;
+  pp.y=p.y-a.y*t;
+  res=(1/(4*(1.)*M_PI*0.01))*exp(-((pp-center).norme2()/(4*(1.)*0.01)));
+
+ 
+  return res;
+		  
+}

### 2015-03-23 code_FVFSHS_2D_matter/AnaSol/AnalyticDiffSolutions.cpp

@@ -1,0 +1,73 @@
+#include <iostream>
+#include <cassert>
+#include "ClassMesh.hpp"
+#include "math.h"
+#include "Functions.hpp"
+#include "AnalyticSolutions.hpp"
+#include "ParamPhys.hpp"
+
+
+double SolFonDiff(Data & d, ParamPhysic & Param,Vertex p,double t,Vertex center){
+   /** fucntion which gives the diffusion analytical solution for p, t and center  **/
+  double res;
+
+     
+  if(d.nTest==1){   
+    res=SolFonChaleur(d,Param,p,t,center);
+    return res;
+  }
+  
+  if(d.nTest==2){   
+    res=SolNeumannChaleur(d,Param,p,t);
+    return res;
+  }
+    
+    else {
+      cout << "Pas de solution fondamentale associé a ce cas test"<<endl;exit(1);
+    }
+}
+
+
+
+
+double SolFonChaleur(Data & d, ParamPhysic & Param,Vertex p,double t,Vertex center){
+   /** Analytical solution: fundamental solution of the heat equation for different diffusion coefficient
+ and with initial time =0.001  **/
+  double res=0;
+  double cD=0;
+  double t0=0.01;
+  if(Param.Model == 1 && Param.Diff.Coefdiff_value !=-1) {
+    cD=Param.Diff.Coefdiff_value;
+  }
+   if(Param.Model == 3 && Param.P1.sig_value !=-1) {
+     cD=1./Param.P1.sig_value;
+  }
+
+   if(Param.Model ==6 && Param.M1.sig_value !=-1) {
+     cD=1./(3.*Param.M1.sig_value);
+   }
+   res=(1./(4*cD*M_PI*(t+t0)))*exp(-((p-center).norme2()/(4*cD*(t+t0))))+1.;
+  return res;
+}
+
+
+double SolNeumannChaleur(Data & d, ParamPhysic & Param,Vertex p,double t){
+     /** Analytical solution: periodic solution of the heat equation for different diffusion coefficient**/
+  double res=0;
+   double cD=0;
+
+  if(Param.Model == 1 && Param.Diff.Coefdiff_value !=-1) {
+    cD=Param.Diff.Coefdiff_value;
+  }
+   if(Param.Model == 1 && Param.P1.sig_value !=-1) {
+    cD=1./Param.P1.sig_value;
+  }
[…]

### 2015-03-23 code_FVFSHS_2D_matter/AnaSol/AnalyticEulerSolutions.cpp

@@ -1,0 +1,249 @@
+
+#include <iostream>
+#include <cassert>
+#include "ClassMesh.hpp"
+#include "math.h"
+#include "Functions.hpp"
+#include "AnalyticSolutions.hpp"
+#include "ParamPhys.hpp"
+#include "HOfunctions.hpp"
+
+/////////////////////////Fonctions liées aux solutions fondamental/////////////
+
+
+
+double SolFonEuler(Data & d, ParamPhysic & Param,Vertex p,double t,Vertex center,int var){
+    /** function which gives the Euler analytical solution for p, t, center and the variable "var"  **/ 
+  double res=0;
+  R2 g(0,0);
+  g=GravityVector(d,Param.Euler);
+  R2 u(2.,0.);
+  double rho1=0,rho2=0,X=0,Y=0,p0=0,u0=0,v0=0,r=0,rho=0;
+ 
+  if(d.nTest==1){
+    if(var==0){
+      res=1.;
+    }
+    if(var==1){
+      res=0.;
+    }
+    if(var==2){
+      res=0.;
+    }
+    if(var==3){
+      res=-(1./(Param.Euler.gamma-1.))*(p,g)+6;
+    }
+  }
+
+  if(d.nTest==2){
+    if(var==0){
+      res=1.;
+    }
+    if(var==1){
+      res=0.;
+    }
+    if(var==2){
+      res=0.;
+    }
+    if(var==3){
+      res=-(1./(Param.Euler.gamma-1.))*(p,g)+6;
+    }
+  }
+  if(d.nTest==3){
+    if(var==0){
+      res=p.y+0.5;
+    }
+    if(var==1){
+      res=0.;
+    }
+    if(var==2){
+      res=0.;
+    }
+    if(var==3){
+      res=(1./(Param.Euler.gamma-1.))*(-(0.5*pow(p.y,2.)+0.5*p.y)*g.y+10);
+    }
+  }
+
+   if(d.nTest==4){
+    if(var==0){
+      res=p.y+0.5;
+    }
+    if(var==1){
+      res=0;
+    }
+    if(var==2){
+      res=0;
+    }
+    if(var==3){
[…]

### 2015-03-23 code_FVFSHS_2D_matter/AnaSol/AnalyticSolutionM1.cpp

@@ -1,0 +1,116 @@
+
+#include <iostream>
+#include <cassert>
+#include "ClassMesh.hpp"
+#include "math.h"
+#include "Functions.hpp"
+#include "AnalyticSolutions.hpp"
+#include "ParamPhys.hpp"
+
+
+double SolFonM1(Data & d, ParamPhysic & Param,Vertex p,double t,Vertex center,int var){
+ /** function which gives the M1 analytical solution for p, t, center and the variable "var"  **/  
+  double res=0;
+  
+  if(d.nTest==1){
+    res=CasTestM1Diff(d,Param,p,t,center,var);
+    return res;
+  }
+  if(d.nTest==2){
+    res=CasTestM1DiffPeriodic(d,Param,p,t,center,var);
+    return res;
+  }
+   if(d.nTest==3){
+    res=CasTestM1TransportSmooth(d,Param,p,t,center,var);
+    return res;
+  }
+  if(d.nTest==4){
+    res=CasTestM1Transport(d,Param,p,t,center,var);
+    return res;
+  }
+   
+
+    
+    else {
+      cout << "Pas de solution fondamentale associé a ce cas test"<<endl;exit(1);
+    }
+}
+
+double CasTestM1Diff(Data & d, ParamPhysic & Param,Vertex p, double t,Vertex center, int var ){
+   /** Analytical solution: M1 solution in the diffusion regime for eps<<1**/
+  double res;
+ 
+  if(var == 0) {
+     res=SolFonChaleur(d,Param,p,t,center);
+   }
+   if(var == 1) {
+     res=0.0000;
+   }
+   if(var == 2) {
+     res=0.0000;
+   }
+  
+  
+  return res;
+}
+
+double CasTestM1DiffPeriodic(Data & d, ParamPhysic & Param,Vertex p, double t,Vertex center,int var){
+    /** Analytical solution: periodic M1 solution in the diffusion regime for eps<<1**/
+  double res;
+  double co=0;
+
+  co=Param.M1.sig_value;
+   if(var == 0) {
+     res=SolNeumannChaleur(d,Param,p,t)+2;
+   }
+   if(var == 1) {
+     res=0.0000;
+   }
+   if(var == 2) {
+     res=0.0000;
+   }
+  
+  return res;
+}
+
[…]

### 2015-03-23 code_FVFSHS_2D_matter/AnaSol/AnalyticSolutions.cpp

@@ -1,0 +1,69 @@
+
+#include <iostream>
+#include <cassert>
+#include "ClassMesh.hpp"
+#include "math.h"
+#include "Functions.hpp"
+#include "AnalyticSolutions.hpp"
+#include "ParamPhys.hpp"
+
+/** This file contains the functions generic for all the models associated with the analytical solutions **/
+
+
+
+
+double SolFon(Data & d,ParamPhysic & Param,Vertex p,double t,Vertex center,int var){
+ /** The function Solfond five the analytical solution for a vertex "p", 
+      the time "t", the variable "var" with a center of the scheme given by "center **/
+  double res=0;
+  
+  
+ if(Param.Model == 1){   
+   res=SolFonDiff(d,Param,p,t,center);
+
+  }
+
+  if(Param.Model == 2){   
+    res=SolFonAdvection(d,Param,p,t,center);
+  }
+
+  if(Param.Model == 3){   
+    res=SolFonP1(d,Param,p,t,center,var);
+  }
+  
+  if(Param.Model == 5){   
+    res=SolFonEuler(d,Param,p,t,center,var);
+  }
+  if(Param.Model == 6){   
+    res=SolFonM1(d,Param,p,t,center,var);
+  }
+  return res;
+}
+
+
+
+
+int TraceSolfond(Data & d, ParamPhysic & Param){
+  /** This fucntion return 1 if we have a analytical solution 
+and 0 if there are not analytical solution **/
+  int p=0;
+
+  if(Param.Model == 1){
+    p=1;
+  }
+  if(Param.Model == 2){
+    p=1;
+  }
+  if(Param.Model == 3 && d.nTest < 5){
+    p=1;
+  }
+  if(Param.Model == 5 && d.nTest < 8){
+    p=1;
+  }
+  if(Param.Model == 6){
+    p=1;
+  }
+  	
+
+ return p;
+}

### 2015-03-23 code_FVFSHS_2D_matter/BC/BoundaryCondition.cpp

@@ -1,0 +1,95 @@
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "ClassMesh.hpp"
+#include "math.h"
+#include <cstdlib>
+#include "Variables.hpp"
+#include "Data.hpp"
+#include "BoundaryCondition.hpp"
+#include "Functions.hpp"
+#include "Tensor.hpp"
+#include "Functionsgeo.hpp"
+#include "AnalyticSolutions.hpp"
+#include "Diagnostics.hpp"
+#include "Functionsinit.hpp"
+#include "ParamPhys.hpp"
+
+ /** File which contains the function for the boundary conditions common to the models**/
+
+
+R2 Norext(Data & d,Mesh & Mh, int numGr){
+   /** Function which compute the external normal**/
+  R2 Next(0,0);
+  if(Mh.xr(numGr).lab==2) {
+    Next.x=-1;
+    Next.y=0; 
+  }
+  if(Mh.xr(numGr).lab==3) {
+    Next.x=0;
+    Next.y=1;
+  }
+  if(Mh.xr(numGr).lab==4) {
+    Next.x=1;
+    Next.y=0;   
+  }
+  if(Mh.xr(numGr).lab==5) {
+    Next.x=0;
+    Next.y=-1;
+  } 
+  if(Mh.xr(numGr).x==0 && Mh.xr(numGr).y==0) {
+    Next.x=-1;
+    Next.y=-1;
+  }
+  if(Mh.xr(numGr).x==d.Tx && Mh.xr(numGr).y==0) {
+    Next.x=1;
+    Next.y=-1;
+  }
+  if(Mh.xr(numGr).x==d.Tx && Mh.xr(numGr).y==d.Ty) {
+    Next.x=1;
+    Next.y=1;
+  }
+  if(Mh.xr(numGr).x==0 && Mh.xr(numGr).y==d.Ty) {
+    Next.x=-1;
+    Next.y=1;
+  }
+  return Next;
+}
+
+
+void BoundaryCondition(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,double time){
+ /** Function which initialize the phantom cells for the model given by Data and Param **/
+  if (Param.Model == 1) {
+    BoundaryConditionDiff(d,Mh,v,Param,time);
+  }
+
+  if (Param.Model == 2) {
+    BoundaryConditionAdvection(d,Mh,v,Param,time);
+  }
+
[…]

### 2015-03-23 code_FVFSHS_2D_matter/BC/BoundaryConditionAdvection.cpp

@@ -1,0 +1,78 @@
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "ClassMesh.hpp"
+#include "math.h"
+#include <cstdlib>
+#include "Variables.hpp"
+#include "Data.hpp"
+#include "BoundaryCondition.hpp"
+#include "Functions.hpp"
+#include "Tensor.hpp"
+#include "Functionsgeo.hpp"
+#include "AnalyticSolutions.hpp"
+#include "Diagnostics.hpp"
+#include "Functionsinit.hpp"
+
+void BoundaryConditionAdvection(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time){
+ /** Function which initialize the phantom cells for the advection model **/
+      switch(d.nTest)
+    {
+    case 1 : BCDirichlet_SolExact_Advection(d,Mh,v,Param,time);
+
+      break;}
+}
+
+
+
+
+
+void BCDirichlet_SolExact_Advection(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time){
+   /** Function which initialize the phantom cells with the exact solution **/
+  int in=0;
+  in=centerdomain(d,Mh);
+
+  for(int j=0;j<Mh.nc;j++){
+    if(Mh.cells[j].lab==-1){
+	  
+	    //cote gauche
+
+	    if((Mh.xj(j).x < 0) && (Mh.xj(j).y> 0 && Mh.xj(j).y< d.Ty)){
+	      v.var[0][j]=SolFon(d,Param,Mh.xj(j),time,Mh.xj(in),0);
+             
+	   }
+	    //cote droit
+	    if(Mh.xj(j).x> d.Tx && (Mh.xj(j).y> 0 && Mh.xj(j).y< d.Ty)){
+	      v.var[0][j]=SolFon(d,Param,Mh.xj(j),time,Mh.xj(in),0);
+	   }
+	    //cote bas
+	    if(Mh.xj(j).y< 0 && (Mh.xj(j).x> 0  && Mh.xj(j).x< d.Tx)){
+	      v.var[0][j]=SolFon(d,Param,Mh.xj(j),time,Mh.xj(in),0);
+	   }
+	    //cote haut
[…]

### 2015-03-23 code_FVFSHS_2D_matter/BC/BoundaryConditionDiff.cpp

@@ -1,0 +1,119 @@
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "ClassMesh.hpp"
+#include "math.h"
+#include <cstdlib>
+#include "Variables.hpp"
+#include "Data.hpp"
+#include "BoundaryCondition.hpp"
+#include "Functions.hpp"
+#include "Tensor.hpp"
+#include "Functionsgeo.hpp"
+#include "AnalyticSolutions.hpp"
+#include "Diagnostics.hpp"
+#include "Functionsinit.hpp"
+
+void BoundaryConditionDiff(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time){
+ /** Function which initialize the phantom cells for the diffusion model **/
+      switch(d.nTest)
+    {
+    case 1 : BCDirichlet_SolExact_diff(d,Mh,v,Param,time);
+
+      break;}
+}
+
+void BCDirichlet_SolExact_diff(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time){
+  /** Function which initialize the phantom cells with the exact solution **/
+  int in=0;
+  in=centerdomain(d,Mh);
+
+  for(int j=0;j<Mh.nc;j++){
+    if(Mh.cells[j].lab==-1){
+	  
+	    //cote gauche
+
+	    if((Mh.xj(j).x < 0) && (Mh.xj(j).y> 0 && Mh.xj(j).y< d.Ty)){
+	      v.var[0][j]=SolFon(d,Param,Mh.xj(j),time,Mh.xj(in),0);
+             
+	   }
+	    //cote droit
+	    if(Mh.xj(j).x> d.Tx && (Mh.xj(j).y> 0 && Mh.xj(j).y< d.Ty)){
+	      v.var[0][j]=SolFon(d,Param,Mh.xj(j),time,Mh.xj(in),0);
+	   }
+	    //cote bas
+	    if(Mh.xj(j).y< 0 && (Mh.xj(j).x> 0  && Mh.xj(j).x< d.Tx)){
+	      v.var[0][j]=SolFon(d,Param,Mh.xj(j),time,Mh.xj(in),0);
+	   }
+	    //cote haut
[…]

### 2015-03-23 code_FVFSHS_2D_matter/BC/BoundaryConditionM1.cpp

@@ -1,0 +1,239 @@
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "ClassMesh.hpp"
+#include "math.h"
+#include <cstdlib>
+#include "Variables.hpp"
+#include "Data.hpp"
+#include "BoundaryCondition.hpp"
+#include "Functions.hpp"
+#include "Tensor.hpp"
+#include "Functionsgeo.hpp"
+#include "AnalyticSolutions.hpp"
+#include "Diagnostics.hpp"
+#include "Functionsinit.hpp"
+
+void BoundaryConditionM1(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time){
+   /** Function which initialize the phantom cells for the M1 model.
+For triangular mesh only the Boundary conditions based on th exact solutions are written **/
+  if (d.Typemesh=='Q'){
+    switch(d.nTest)
+      {
+      case 1 : BC_Dirichlet_SolExact_M1(d,Mh,v,Param,time);
+    
+	break;
+	
+      case 2 : BC_Periodic_M1(d,Mh,v,Param,time);
+	
+	break;
+	
+      case 3 : BC_Periodic_M1(d,Mh,v,Param,time);
+	
+	break;
+	
+      case 4 :BC_Periodic_M1(d,Mh,v,Param,time);
+	
+	break;}
+  }
+  if (d.Typemesh=='T'){
+    BCDirichlet_P1(d,Mh,v,Param,time);
+  }
+}
+
+void BC_Neumann_M1(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time){
+/** Function which initialize the phantom cells to have Neumann condition **/
+  for(int j=0;j<Mh.nc;j++){
+    if(Mh.cells[j].lab==-1){
+      
+	  
+	    //cote gauche
+
+	    if((Mh.xj(j).x < 0) && (Mh.xj(j).y> 0 && Mh.xj(j).y< d.Ty)){
+	     v.var[0][j]=v.var[0][j+1];
[…]

### 2015-03-23 code_FVFSHS_2D_matter/BC/BoundaryConditionP1.cpp

@@ -1,0 +1,250 @@
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "ClassMesh.hpp"
+#include "math.h"
+#include <cstdlib>
+#include "Variables.hpp"
+#include "Data.hpp"
+#include "BoundaryCondition.hpp"
+#include "Functions.hpp"
+#include "Tensor.hpp"
+#include "Functionsgeo.hpp"
+#include "AnalyticSolutions.hpp"
+#include "Diagnostics.hpp"
+#include "Functionsinit.hpp"
+
+void BoundaryConditionP1(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time){
+ /** Function which initialize the phantom cells for the P1 model.
+For triangular mesh only the Boundary conditions based on th exact solutions are written **/
+  if (d.Typemesh=='Q'){
+    switch(d.nTest)
+      {
+      case 1 : BC_Periodic_P1(d,Mh,v,Param,time);
+	
+	break;
+	
+      case 2 : BC_Periodic_P1(d,Mh,v,Param,time);
+	
+	break;
+	
+      case 3 : BCDirichlet_P1(d,Mh,v,Param,time);
+	
+	break;
+      
+      case 4 :BC_Periodic_P1(d,Mh,v,Param,time);
+
+	break;
+
+      case 5 : BCNeumann_P1(d,Mh,v,Param,time);
+       
+	
+	break;
+
+      case 6 : BC_Periodic_P1(d,Mh,v,Param,time);
+       
+	
+	break;}
+  }
+
+  if (d.Typemesh=='T'){
+    BCDirichlet_P1(d,Mh,v,Param,time);
+  }
+}
+
+void BCNeumann_P1(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time){
+ /** Function which initialize the phantom cells to have Neumann condition **/
+  for(int j=0;j<Mh.nc;j++){
+    if(Mh.cells[j].lab==-1){
+      
+	  
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Diagnostics/Diagnostics.cpp

@@ -1,0 +1,181 @@
+
+#include <iostream>
+#include <cassert>
+#include "ClassMesh.hpp"
+#include "math.h"
+#include "Functions.hpp"
+#include "Diagnostics.hpp"
+#include "ParamPhys.hpp"
+
+/** File which contains the function associated to the diagnostics (norm Lp, error Lp, masse etc) for all the models **/
+
+
+
+double NormLP_Error_All_variables(Data & d, Mesh & Mh,variable & v,ParamPhysic & Param,double p,double t){
+       /** Function which compute the Lp error associated with all discrete quantities and 
+all analytical solutions for the different models **/
+  double res=0.;
+  int in=0;
+  double hx;
+  double a=0;
+  
+  hx=1/double(d.Nx);
+  if(Mh.nbnodelocal==4){
+    in=(Mh.nc+d.Nx)/2;}
+  if(Mh.nbnodelocal==3){
+    in=((Mh.nc+d.Nx*2)/2);}
+  if(!strcmp(d.NameMesh,"KershawMesh")){
+    for(int j=0;j<Mh.nc;j++){
+      if(Mh.xj(j).x<=1+d.Tx*(1./d.Nx) && Mh.xj(j).x>=1-d.Tx*(1./d.Nx)){
+	if(Mh.xj(j).y<=1+d.Ty*(1./d.Ny) && Mh.xj(j).y>=1-d.Ty*(1./d.Ny)){
+	  in=j;
+	}
+      }
+    }
+  }
+
+  if(d.dimsave==2){
+
+    for(int j=0;j<Mh.nc;j++){
+      if(Mh.cells[j].lab!=-1){
+	  for(int k=0;k<v.nbvar;k++){
+	    a=Mh.area(j)*(pow(Valabs(SolFon(d,Param,Mh.xj(j),t,Mh.xj(in),k)-v.var[k][j]),p)); 
+	    res=res+a;
+	  }
+	}
+      }
+      
+  }
+  
+  res=pow(res,1/p);
+  return res;	
+}
+
+double NormLP_Error_One_variable(Data & d, Mesh & Mh,variable & v,ParamPhysic & Param,double p,double t,int var){
+      /** Function which compute the Lp error associated with one discrete quantity and 
+one analytical solution for the different models **/
+  double res=0.;
+  int in=0;
+  double hx;
+  
+  hx=1/double(d.Nx);
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Diagnostics/Diagnostics_Euler.cpp

@@ -1,0 +1,108 @@
+
+#include <iostream>
+#include <cassert>
+#include "ClassMesh.hpp"
+#include "math.h"
+#include "Functions.hpp"
+#include "Diagnostics.hpp"
+
+
+/** File which contains the function associated to the diagnostics (norm Lp, error Lp, masse etc) specific to the Euler equations **/
+
+double NormLP_Velocity(Data & d, Mesh & Mh,variable & v,ParamPhysic & Param,double p,double t){
+  /** Function which compute the Lp norm associated with the discrete velocity for the Euler equations **/
+  double res=0.;
+  int in=0;
+  double hx;
+  double a1=0,a2=0;
+  double rho=0;
+  
+  hx=1/double(d.Nx);
+       if(Mh.nbnodelocal==4){
+	   in=(Mh.nc+d.Nx)/2;}
+	 if(Mh.nbnodelocal==3){
+	   in=((Mh.nc+d.Nx*2)/2);}
+	 if(!strcmp(d.NameMesh,"KershawMesh")){
+	   for(int j=0;j<Mh.nc;j++){
+	     if(Mh.xj(j).x<=1+d.Tx*(1./d.Nx) && Mh.xj(j).x>=1-d.Tx*(1./d.Nx)){
+	       if(Mh.xj(j).y<=1+d.Ty*(1./d.Ny) && Mh.xj(j).y>=1-d.Ty*(1./d.Ny)){
+		 in=j;
+	       }
+	     }
+	   }
+	 }
+
+	 if(d.dimsave==2){
+
+	     for(int j=0;j<Mh.nc;j++){
+	        if(Mh.cells[j].lab!=-1){
+		  rho=v.var[0][j];
+		  a1=Mh.area(j)*(pow(Valabs(v.var[1][j]/rho),p));
+		  a2=Mh.area(j)*(pow(Valabs(v.var[2][j]/rho),p));
+	       res=res+a1+a2;
+
+		}
+
+	   }
+	 }
+  
+  res=pow(res,1/p);
+     return res;
+
+}
+
+
+double NormLP_Error_All_variables_Euler(Data & d, Mesh & Mh,variable & v,ParamPhysic & Param,double p,double t){
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Flux/DynGazFonction.cpp

@@ -1,0 +1,297 @@
+
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "Flux.hpp"
+#include "Variables.hpp"
+#include "Functions.hpp"
+#include <stdio.h>
+#include "Tensor.hpp"
+#include "BoundaryCondition.hpp"
+#include "Functionsinit.hpp"
+#include "FunctionsAdvection.hpp"
+#include "ParamPhys.hpp"
+#include "HOfunctions.hpp"
+
+
+/** This file contains different functions useful for the discretization of the Euler equations **/
+
+double PressureLaw(Data & d,Mesh & Mh, variable & v,ParamEuler & Euler, int numCell){
+  /** This function compute the pressure law. Actuzlly only the perfect gas law is implemented **/
+  double res=0;
+
+    if(Euler.lp==1){
+      res=(Euler.gamma-1.)*v.var[0][numCell]*EnergyIn(d,Mh,v,Euler,numCell); 
+    }
+
+
+  return res;
+}
+
+double rhor(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamEuler & Euler,int numGr){
+  /** This function compute a value of rho at the node numGr. 
+This value is given by the value in the cell NumCell or by an average around the node numGr **/
+  int nbmeans=0,typerho=0;
+  int jG=0;
+  double m=0;
+  nbmeans=2;
+  typerho=1;
+  if(typerho==1){
+
+    if(nbmeans==1){
+      for(int j=0;j<tab.TabInv[numGr].taille;j++){
+	jG=tab.TabInv[numGr].TabCell[j];
+	m=m+Vjr(Mh,jG,numGr)*v.var[0][jG];
+      }
+
+      m=m/Vr(Mh,numGr,tab);
+    }
+    if(nbmeans==2){
+      for(int j=0;j<tab.TabInv[numGr].taille;j++){
+	jG=tab.TabInv[numGr].TabCell[j];
+	m=m+v.var[0][jG];
+      }
+    m=m/tab.TabInv[numGr].taille;
+    
+    }
+  }
+  if(typerho==2){
+    m=v.var[0][jG];
+  } 
+
+  return m;
+}
+
+
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Flux/Flux.cpp

@@ -1,0 +1,208 @@
+
+#include <iostream>
+#include <cmath>
+#include <cstdlib>
+#include "Flux.hpp"
+
+/**
+   Function which gives the flux associated with your model and your shceme (in Data)**/
+
+
+vectorflux ChoiceFluxN(Data & d ,int numCell,Mesh &  Mh, variable & v, TabConnecInv & tab,ParamPhysic & Param,R2 * ur){
+  /**  Function which gives the Nodal flux associated with your model and your scheme (in Data) **/
+vectorflux res(d);
+ 
+  if(Param.Model == 1){
+      switch(d.scheme){
+      case 1:
+	/** Linear Nodal diffusion scheme**/
+	res=FluxVertexDiff(d,numCell,Mh,v,tab,Param,ur);
+	break;
+	/** Nonlinear Nodal diffusion scheme aobtain using advection fluxes**/
+      case 2:
+	res=FluxVertexNlDiff(d,numCell,Mh,v,tab,Param,ur);
+      break;
+      default: cout <<" the scheme associated with the number"<<d.scheme<<" does not exist "<<endl;
+    }
+  
+  }
+
+  if(Param.Model == 2){
+    
+    switch(d.scheme){
+    case 1:
+      /** Linear Nodal advection scheme (order one and two)**/
+      res=FluxVertexadv(d,numCell,Mh,v,tab,Param);
+      break;
+    default: cout <<" the scheme associated with the number"<<d.scheme<<" does not exist "<<endl;
+    }
+  }
+  
+   if(Param.Model == 3){
+    
+    switch(d.scheme){
+    case 1:
+      /** Linear JL-(a) nodal scheme for P1 model **/
+      res=FluxVertexP1(d,numCell,Mh,v,tab,Param,ur);
+      break;
+    case 2:
+      /** Linear JL-(b) nodal scheme for P1 model **/
+      res=FluxVertexP1(d,numCell,Mh,v,tab,Param,ur);
+      break;  
+    case 3:
+      /** Linear JL-(b) nodal scheme with local source term for P1 model **/
+      res=FluxVertexP1Gosse(d,numCell,Mh,v,tab,Param,ur);
+      break;  
+    default: cout <<" the scheme associated with the number"<<d.scheme<<" does not exist "<<endl;
+    }
+  }
+
+   if(Param.Model == 4){
+     
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Flux/FluxAdvection.cpp

@@ -1,0 +1,34 @@
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "Flux.hpp"
+#include "Variables.hpp"
+#include "Functions.hpp"
+#include <stdio.h>
+#include "Tensor.hpp"
+#include "BoundaryCondition.hpp"
+#include "Functionsinit.hpp"
+#include "FunctionsAdvection.hpp"
+
+
+vectorflux FluxVertexadv(Data & d,int numCell,Mesh &  Mh,variable & v, TabConnecInv & tab,ParamPhysic & Param){
+  /**  Nodal advection fluxes  **/
+ vectorflux res(1);
+ R2 a(0,0); 
+  int numGr;
+  double s=0;
+  
+  for(int r=0;r<Mh.nbnodelocal;r++){
+    numGr=Mh(numCell,r);
+    a=AverageVelocityNode(d,Mh,v,tab,Param.Adv,numGr,numCell);
+    s=s+VertexUpwind(d,Mh,v,0,tab,Param,numCell,r,a);
+
+  }
+  
+  res.vflux[0]=-s;
+  return res;	
+
+
+}
+
+

### 2015-03-23 code_FVFSHS_2D_matter/Flux/FluxAdvectionEdge.cpp

@@ -1,0 +1,45 @@
+
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "Flux.hpp"
+#include "Variables.hpp"
+#include "Functions.hpp"
+#include <stdio.h>
+#include "Tensor.hpp"
+#include "BoundaryCondition.hpp"
+#include "Functionsinit.hpp"
+#include "FunctionsAdvection.hpp"
+
+vectorflux FluxEdgeAdv(Data & d,int numCell,Mesh &  Mh,variable & v, TabConnecInv & tab,ParamPhysic & Param){
+   /**  Edge advection fluxes  **/
+ vectorflux res(1);
+ R2 a(0.,0.); 
+ int k=0;
+ int r1=0,r2=0,numGr1=0,numGr2=0;
+ int numGr=0;
+ double s=0.;
+  
+  for(int r=0;r<Mh.nbnodelocal;r++){
+    numGr=Mh(numCell,r); 
+    r1=r;
+    if(r==Mh.nbnodelocal-1){
+      r2=0;
+    }
+    else{
+      r2=r+1;
+    }
+    numGr1=Mh(numCell,r1);
+    numGr2=Mh(numCell,r2);      
+
+    k=InverseEdge(Mh,numGr1,numGr2,numCell,tab);
+    a.x=0.5*(Param.Adv.a[numCell].x+Param.Adv.a[k].x);
+    a.y=0.5*(Param.Adv.a[numCell].y+Param.Adv.a[k].y);
+    s=s+EdgeUpwind(d,Mh,v,0,tab,Param,numCell,k,r,a);
+  }
+  
+  res.vflux[0]=-s;
+  return res;	
+
+
+}

### 2015-03-23 code_FVFSHS_2D_matter/Flux/FluxDiffVertex.cpp

@@ -1,0 +1,88 @@
+
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "Flux.hpp"
+#include "Variables.hpp"
+#include "Functions.hpp"
+#include <stdio.h>
+#include "Tensor.hpp"
+#include "BoundaryCondition.hpp"
+#include "Functionsinit.hpp"
+#include "FunctionsAdvection.hpp"
+
+/** Flux du schéma de diffusion GLACE linéaire**/
+vectorflux FluxVertexDiff(Data & d,int numCell,Mesh & Mh, variable & v, TabConnecInv & tab,ParamPhysic & Param,R2 * ur){
+   /**  Nodal fluxes for linear diffusion scheme   **/
+  vectorflux res(1);
+  R2 sol(0,0);
+  int numGr;
+  double s=0;
+  R2 stab(0,0);
+    
+  for(int r=0;r<Mh.nbnodelocal;r++){
+     numGr=Mh(numCell,r);
+
+     sol=ur[numGr];  
+
+     s=s+Mh.ljr(numCell,r)*(sol,Mh.njr(numCell,r));
+    
+  }
+    res.vflux[0]=-s;
+    return res;	
+}
+
+vectorflux FluxVertexNlDiff(Data & d,int numCell,Mesh &  Mh,variable & v, TabConnecInv & tab,ParamPhysic & Param,R2 * ur){
+   /**  Nodal fluxes for nonlinear diffusion scheme based on advection   **/
+ vectorflux res(1);
+ R2 sol(0,0);
+  int numGr;
+  double s=0;  
+  double cd=0;
+  tensor beta(d,'s');
+  double Er;
+
+    for(int r=0;r<Mh.nbnodelocal;r++){
+     numGr=Mh(numCell,r);
+     
+     cd=AverageCoefDiffNode(d,Mh,v,tab,Param.Diff,numGr,numCell);   
+     
+     Er=AverageQuantity(d,Mh,v,tab,Param,numGr,0);
+     sol=ur[numGr];
+       
+     s=s+VertexUpwind(d,Mh,v,0,tab,Param,numCell,r,sol/Er);
+  }
+
+    res.vflux[0]=-s;
+    return res;	
+}
+
+
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Flux/FluxEdgediff.cpp

@@ -1,0 +1,90 @@
+
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "Flux.hpp"
+#include "Variables.hpp"
+#include "Functions.hpp"
+#include <stdio.h>
+#include "Tensor.hpp"
+#include "BoundaryCondition.hpp"
+#include "Functionsinit.hpp"
+
+vectorflux FluxVF4Diff(Data & d,int numCell, Mesh & Mh,  variable & v,  TabConnecInv & tab,ParamPhysic & Param){
+   /**  Edge fluxes for linear diffusion scheme VF4   **/
+    double dis=0.;
+  double s=0.;
+  int k,A,B,C,D;
+  vectorflux res(1);
+  int **tabCellEdge=NULL;// table with the neighbour cell for each edge//  
+  Vertex p1,p2;
+
+
+  //We find the neighbour cell for each edge //
+  if(Mh.nbnodelocal==3){
+
+    A=Mh(numCell,0);
+    B=Mh(numCell,1);
+    C=Mh(numCell,2);
+
+    tabCellEdge = new int*[3];
+    for(int i=0;i<3;i++){
+      tabCellEdge[i]=new int[3];
+    }
+    
+    tabCellEdge[0][0]=InverseEdge(Mh,A,B,numCell,tab);
+    tabCellEdge[0][1]=A;
+    tabCellEdge[0][2]=B;
+    tabCellEdge[1][0]=InverseEdge(Mh,B,C,numCell,tab);
+    tabCellEdge[1][1]=B;
+    tabCellEdge[1][2]=C;
+    tabCellEdge[2][0]=InverseEdge(Mh,C,A,numCell,tab);
+    tabCellEdge[2][1]=C;
+    tabCellEdge[2][2]=A;
+  }
+  else if(Mh.nbnodelocal==4){
+    A=Mh(numCell,0);
+    B=Mh(numCell,1);
+    C=Mh(numCell,2);
+    D=Mh(numCell,3);
+
+    tabCellEdge = new int*[4];
+    for(int i=0;i<4;i++){
+      tabCellEdge[i]=new int[3];
+    }
+    
+    tabCellEdge[0][0]=InverseEdge(Mh,A,B,numCell,tab);
+    tabCellEdge[0][1]=A;
+    tabCellEdge[0][2]=B;
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Flux/FluxEuler.cpp

@@ -1,0 +1,271 @@
+
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "Flux.hpp"
+#include "Variables.hpp"
+#include "Functions.hpp"
+#include <stdio.h>
+#include "Tensor.hpp"
+#include "BoundaryCondition.hpp"
+#include "Functionsinit.hpp"
+#include "FunctionsAdvection.hpp"
+#include "ParamPhys.hpp"
+#include "Source.hpp"
+
+
+
+
+
+vectorflux FluxVertexEulerGosse(Data & d,int numCell,Mesh & Mh,variable & v,TabConnecInv & tab,ParamPhysic & Param,R2 * ur){
+  /**  Nodal Lagrange+remap JL-(b) fluxes with local source term for the Euler model **/
+  vectorflux res(4);
+  R2 sol(0.,0.);
+  R2 sol2(0.,0.);
+  double s[4]={0.,0.,0.,0.};
+  tensor alpha(d,'h');
+  tensor beta(d,'s');
+  int numGr;
+  double rjr=0;
+  R2 Gjr(0,0);
+  double pj=0;
+  R2 uj(0,0);
+  double Mr[2][2];
+  double temp=0;
+
+  Mr[0][0]=0;
+  Mr[0][1]=0;
+  Mr[1][0]=0;
+  Mr[1][1]=0;
+
+  uj.x=v.var[1][numCell]/v.var[0][numCell];
+  uj.y=v.var[2][numCell]/v.var[0][numCell];
+
+    for(int r=0;r<Mh.nbnodelocal;r++){
+    // calcul du flux nodale vr
+
+     numGr=Mh(numCell,r);
+     MrConstructE(d,numGr,Mh,v,tab,Param,Mr);
+     sol=ur[numGr];
+     sol2=ClassicalSolver(d,Mh,v,tab,Param,numGr);
+  
+     beta=inittensor(d,Mh,v,tab,'s',numGr,numCell);
+     alpha=inittensor(d,Mh,v,tab,'h',numGr,numCell);
+     rjr=WaveSpeed(d,Mh,v,numCell,numGr,tab,Param.Euler);
+      
+     pj=PressureLaw(d,Mh,v,Param.Euler,numCell);
+
+
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Flux/FluxVertexM1.cpp

@@ -1,0 +1,423 @@
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "Variables.hpp"
+#include "Flux.hpp"
+#include "Source.hpp"
+#include "BoundaryCondition.hpp"
+#include "Tensor.hpp"
+#include "FunctionsAdvection.hpp"
+#include "ParamPhys.hpp"
+
+
+/** Calcul de la pression q**/
+double q(Data & d, ParamM1 & M1,double E,double F1, double F2){
+    /**  function which compute the isotorpic pressure of the M1 model **/
+  double res;
+  R2 f;
+  if(E==0){
+    res=0;
+  }
+  else{
+    f.x=F1/(E);
+    f.y=F2/(E);
+      double khi=(3.+4.*(f,f))/(5.+2.*sqrt(4.-3.*(f,f)));
+      res=0.5*(1.-khi)*E;
+  }
+  return res;
+}
+
+/** Calcul du coefficient kr**/
+double coefk(Data & d, ParamM1 & M1,double E,double F1, double F2){
+    /**  function which compute the coefficienty k define by F=k U, with F the flux and U the velocity in the euler description **/
+  double res=0.;
+  R2 f(0,0);
+ 
+  if(E==0){
+    res=0;
+  }
+  else{
+    f.x=F1/(E);
+    f.y=F2/(E);
+    if(f.x==0 && f.y==0){
+       res=(4./3.)*E;
+     }
+     
+     else{
+       double khi=(3.+4.*(f,f))/(5.+2.*sqrt(4.-3.*(f,f)));
+         if(khi < (1./3.)+0.000001 && khi >(1./3.)-0.000001){
+        res=(4./3.)*E;
+       }
+       else{
+	res=(2.*E*(f,f))/(3.*khi-1.);
+       }     
+     }
+  }
+  return res;
+
+}
+
+void  Calcul_u(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab, ParamM1 & M1,R2 & u,int numCell){
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Flux/FluxVertexM1Matter.cpp

@@ -1,0 +1,88 @@
+#include <iostream>
+#include <cmath>
+#include <cstdlib>
+#include "Variables.hpp"
+#include "Flux.hpp"
+#include "Source.hpp"
+#include "BoundaryCondition.hpp"
+#include "Tensor.hpp"
+#include "FunctionsAdvection.hpp"
+
+
+
+void MatrixM1Matter(Data & d,Mesh & Mh,variable & v, TabConnecInv & tab,ParamPhysic & Param,int numGr,double &a11,double &a12,double &a21,double &a22,double &b1,double &b2){
+    /**  Nodal matrix for the classical scheme for the M1 model **/
+    tensor alpha(d,'h');
+    tensor beta(d,'s');
+    int numLrj=0, jG=0;
+    double rjr=0.;
+    double qj=0.;
+    R2  uj(0,0);
+    
+    for(int j=0;j<tab.TabInv[numGr].taille;j++){
+        jG=tab.TabInv[numGr].TabCell[j];
+        numLrj=NodeGtoL(Mh,jG,numGr);
+        
+        beta=inittensor(d,Mh,v,tab,'s',numGr,jG);
+        alpha=inittensor(d,Mh,v,tab,'h',numGr,jG);
+        
+        Calcul_u(d,Mh,v,tab,Param.M1,uj,jG);
+        qj=q(d,Param.M1,v.var[0][jG],v.var[1][jG],v.var[2][jG]);
+        rjr=(4./sqrt(3.))*(v.var[0][jG]/(3+(uj,uj)));
+        
+        a11=a11+Mh.ljr(jG,numLrj)*(rjr*alpha.ten[0][0]);
+        a12=a12+Mh.ljr(jG,numLrj)*(rjr*alpha.ten[0][1]);
+        a21=a21+Mh.ljr(jG,numLrj)*(rjr*alpha.ten[1][0]);
+        a22=a22+Mh.ljr(jG,numLrj)*(rjr*alpha.ten[1][1]);
+        
+        b1=b1+Mh.ljr(jG,numLrj)*(qj*Mh.njr(jG,numLrj).x+rjr*alpha.ten[0][0]*uj.x+rjr*alpha.ten[0][1]*uj.y);
+        b2=b2+Mh.ljr(jG,numLrj)*(qj*Mh.njr(jG,numLrj).y+rjr*alpha.ten[1][0]*uj.x+rjr*alpha.ten[1][1]*uj.y);
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Flux/FunctionsAdvection.cpp

@@ -1,0 +1,287 @@
+
+#include <iostream>
+#include <cmath>
+#include <cstdlib>
+#include "Variables.hpp"
+#include "ClassMesh.hpp"
+#include "Functions.hpp"
+#include "Initialisation.hpp"
+#include "Functionsinit.hpp"
+#include "FunctionsAdvection.hpp"
+#include <algorithm>
+#include "BoundaryCondition.hpp"
+
+using std::min;
+using std::max;
+using std::abs;
+
+/** File which contains the functions for the advetionf fluxes **/
+
+
+int EnsembleR(Data & d,Mesh & Mh, variable & v,ParamPhysic & Param,int r,int numCell, R2 a){
+  /** function which compute if the normal nodal velocity is positive or negative **/
+  int res=0;
+  double value;
+  int numGr=0;
+  
+  numGr=Mh(numCell,r);
+  value=Mh.ljr(numCell,r)*(a,Mh.njr(numCell,r));
+  if(value>0){
+    res=1;
+  }
+  if(value<0){
+    res=-1;
+  }
+  return res;
+
+}
+
+
+double variablekr(Data & d,Mesh & Mh, variable & v,int var,TabConnecInv & tab,ParamPhysic & Param,int numCell,int numGr, R2  a,int ordre){
+  /** nodal average the compute the nodal value of the unknown for the advection scheme **/
+  double dem=0;
+  double num=0;
+  double res=0;
+  int jG=0,r=0;
+  
+  for(int j=0;j<tab.TabInv[numGr].taille;j++){
+    jG=tab.TabInv[numGr].TabCell[j];
+    r=NodeGtoL(Mh,jG,numGr); 
+ 
+    if(EnsembleR(d,Mh,v,Param,r,jG,a)==1){
+      num=num+Mh.ljr(jG,r)*(a,Mh.njr(jG,r))*InterLineVertex(d,Mh,v,tab,Param,var,ordre,jG,r);
+      dem=dem+Mh.ljr(jG,r)*(a,Mh.njr(jG,r));
+      
+    } 
+  }
+
+  if(dem==0){
+      cout<<" "<<a<<" "<<Mh.njr(jG,r)<<endl;
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Functions/Functions.cpp

@@ -1,0 +1,185 @@
+
+
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "ClassMesh.hpp"
+#include "math.h"
+#include "Functions.hpp"
+#include "Data.hpp"
+#include "Functionsgeo.hpp"
+#include "Tensor.hpp"
+
+/** file which contains some functions uselful **/
+
+
+
+void WriteDataToMain(Data & d,ParamPhysic & Param){
+/** function which plot the parameters at the beginning of the run **/
+  
+  if(!strcmp(d.Typemodel,"Diffusion")){
+    cout<<"//////////Solve diffusion equation//////////"<<endl;
+    if(d.scheme==1 && d.Typescheme =='N'){
+      cout<<"//////////////////// Linear nodal scheme ////////////////////"<<endl;
+    }
+    if(d.scheme==1 && d.Typescheme =='E'){
+      cout<<"////////////////// Linear VF4 Edge scheme ////////////////////"<<endl;
+    }
+    if(d.scheme==2 && d.Typescheme =='N'){
+      cout<<"///////// Nonlinear nodal diffusion scheme ///////////"<<endl;}
+  }
+  
+  if(!strcmp(d.Typemodel,"P1")){
+      cout<<"////////////// Solve P1 model ///////////////"<<endl;
+      if(d.scheme==1){
+      cout<<"////////////////// Nodal JL-(a) scheme /////////////////"<<endl;}
+      if(d.scheme==2){
+	cout<<"//////////////// Nodal JL-(b) scheme /////////////////"<<endl;}
+      if(d.scheme==3){
+	cout<<"///////// Nodal JL-(b) with local source term //////////"<<endl;}    
+        
+      cout<<"//////////////// Eps : "<<Param.P1.eps_value<<"///////////////"<<endl;
+      cout<<"////////////// sigma : "<<Param.P1.sig_value<<"///////////////"<<endl;
+  }
+    
+  if(!strcmp(d.Typemodel,"Euler")){
+    cout<<"////////////// Solve Euler model ///////////////"<<endl;
+    if(d.scheme==1){
+      cout<<"////////////// Nodal Lagrange+remap JL-(a) scheme ///////////////"<<endl;}
+    if(d.scheme==2){
+      cout<<"////////////// Nodal Lagrange+remap JL-(b) scheme /////////////////"<<endl;}
+    if(d.scheme==3){
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Functions/Functionsinit.cpp

@@ -1,0 +1,97 @@
+
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "ClassMesh.hpp"
+#include "math.h"
+#include "Functions.hpp"
+#include "Data.hpp"
+#include "Functionsgeo.hpp"
+#include "Tensor.hpp"
+#include "Functionsinit.hpp"
+#include "Flux.hpp"
+#include "ParamPhys.hpp"
+
+/** File with fucntions which allows to initialize some quantities**/
+
+
+
+double CFL(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamPhysic & Param){
+  /** Function which initiliaze the time step for your schemeand test case **/
+double dt=0;
+ double hx=0,hy=0,h=0;
+  hx=1/double(d.Nx);
+  hy=1/double(d.Ny);
+  h=min(hx,hy);
+
+ if(d.Typetime=='S'){
+   if(Param.Model == 3 &&  d.scheme!=3){ //P1 model
+     dt=d.CFL*Param.P1.eps[0]*(pow(h,d.Total_order));
+   }
+   if(Param.Model == 3  &&  d.scheme==3){ // P1 Model
+     dt=d.CFL*Param.P1.sigma[0]*h*h;
+   }
+
+   if(Param.Model == 4){ // P1 matter Model
+     dt=d.CFL*Param.P1M.eps[0]*h;
+   }
+   
+   if(Param.Model == 5  &&  d.scheme==3){ // Euler Model
+     dt=d.CFL*h*h;
+   }
+  if(Param.Model == 5  &&  d.scheme==4){  // Euler Model
+     dt=d.CFL*Param.Euler.eps[0]*h;
+   }
+  if(Param.Model == 6 && d.nTest <3 ){  // M1 Model
+     dt=d.CFL*h*h;
+   }
+  if (Param.Model == 7) // M1 Model with matter
+  {
+    cout << "M1 Model with matter not define in semi implicite configuration"<< endl ;
+    exit(1) ;
+  }
+ }
+
+ if(d.Typetime=='E'){
+ 
+  if(Param.Model ==1){
+    dt=(d.CFL*(Param.Diff.D[0])*h*h); // Diffusion model
+  }
+
+  if(Param.Model == 2){
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Init/InitAdvection.cpp

@@ -1,0 +1,31 @@
+#include <iostream>
+#include <cassert>
+#include <cstdlib>
+#include <cmath>
+#include "Initialisation.hpp"
+#include <math.h>
+#include "AnalyticSolutions.hpp"
+#include "Diagnostics.hpp"
+#include "Functions.hpp"
+#include "Flux.hpp"
+#include "ParamPhys.hpp"
+
+void Initadv(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param){
+    /** function which construct the initial datas 
+      for the advection model
+  **/
+  int in=0;
+
+  switch(d.nTest)
+    {
+    case 1 :
+      
+      in=centerdomain(d,Mh);
+      for(int j=0;j<Mh.nc;j++){
+	v.var[0][j]=TransportSol(d,Param,Mh.xj(j),0,Mh.xj(in));
+      }
+      break;
+      
+    }
+
+}

### 2015-03-23 code_FVFSHS_2D_matter/Init/InitDiff.cpp

@@ -1,0 +1,47 @@
+#include <iostream>
+#include <cassert>
+#include <cstdlib>
+#include <cmath>
+#include "Initialisation.hpp"
+#include <math.h>
+#include "AnalyticSolutions.hpp"
+#include "Diagnostics.hpp"
+#include "Functions.hpp"
+#include "Flux.hpp"
+#include "ParamPhys.hpp"
+
+void InitDiff(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param){
+   /** function which construct the initial datas 
+      for the diffusion model
+  **/
+  int in=0;
+
+  switch(d.nTest)
+    {
+    case 1 : 
+   	       
+      in=centerdomain(d,Mh);
+      for(int j=0;j<Mh.nc;j++){
+	v.var[0][j]=0;
+      }
+      v.var[0][in]=1/(Mh.area(in));
+      break;
+      
+      case 2 :
+
+	 in=centerdomain(d,Mh);
+
+	 for(int j=0;j<Mh.nc;j++){
+	   v.var[0][j]=SolFon(d,Param,Mh.xj(j),0,Mh.xj(in),0);
+	 }
+      break;
+
+      case 3 :
+	 
+	 for(int j=0;j<Mh.nc;j++){
+	   v.var[0][j]=cos(M_PI*Mh.xj(j).y)*cos(M_PI*Mh.xj(j).x);
+	 }
+	 break;
+    }
+}
+  

### 2015-03-23 code_FVFSHS_2D_matter/Init/InitEuler.cpp

@@ -1,0 +1,175 @@
+#include <iostream>
+#include <cassert>
+#include <cstdlib>
+#include <cmath>
+#include "Initialisation.hpp"
+#include <math.h>
+#include "AnalyticSolutions.hpp"
+#include "Diagnostics.hpp"
+#include "Functions.hpp"
+#include "Flux.hpp"
+#include "ParamPhys.hpp"
+
+ void InitE(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param){
+ /** function which construct the initial datas 
+      for the Euler model
+  **/
+   int in=0;
+   double lambda=0.001;
+   double norm2=0;
+   R2 g(0,0);
+  g=GravityVector(d,Param.Euler);
+
+     switch(d.nTest)
+    {
+    case 1 : 		
+      //condition initiale
+      for(int j=0;j<Mh.nc;j++){
+        if(Param.Euler.LHO <2) {
+	  v.var[0][j]=SolFon(d,Param,Mh.xj(j),0,Mh.xj(in),0);
+	  v.var[1][j]=SolFon(d,Param,Mh.xj(j),0,Mh.xj(in),1);
+	  v.var[2][j]=SolFon(d,Param,Mh.xj(j),0,Mh.xj(in),2);
+	  v.var[3][j]=SolFon(d,Param,Mh.xj(j),0,Mh.xj(in),3);
+        }
+	else {
+	  v.var[0][j]=SolFonEulerAverage(d,Mh,Param,Mh.xj(j),0,Mh.xj(in),j,0);
+          v.var[1][j]=SolFonEulerAverage(d,Mh,Param,Mh.xj(j),0,Mh.xj(in),j,1);
+	  v.var[2][j]=SolFonEulerAverage(d,Mh,Param,Mh.xj(j),0,Mh.xj(in),j,2);
+	  v.var[3][j]=SolFonEulerAverage(d,Mh,Param,Mh.xj(j),0,Mh.xj(in),j,3);
+        }
+
+      }
+    
+      break;
+ 
+    case 2 : 
+      for(int j=0;j<Mh.nc;j++){
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Init/InitM1.cpp

@@ -1,0 +1,63 @@
+#include <iostream>
+#include <cassert>
+#include <cstdlib>
+#include <cmath>
+#include "Initialisation.hpp"
+#include <math.h>
+#include "AnalyticSolutions.hpp"
+#include "Diagnostics.hpp"
+#include "Functions.hpp"
+#include "Flux.hpp"
+#include "ParamPhys.hpp"
+
+  void InitM1(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param){
+     /** function which construct the initial datas 
+      for the M1 model
+  **/
+    int in=0;
+    in=centerdomain(d,Mh);
+    
+       switch(d.nTest)
+       { 
+
+      case 1 : 	
+      in=centerdomain(d,Mh);
+      for(int j=0;j<Mh.nc;j++){
+	v.var[0][j]=SolFonM1(d,Param,Mh.xj(j),0,Mh.xj(in),0);
+	v.var[1][j]=SolFonM1(d,Param,Mh.xj(j),0,Mh.xj(in),1);
+	v.var[2][j]=SolFonM1(d,Param,Mh.xj(j),0,Mh.xj(in),2);
+      }
+
+      break;
+     
+       case 2: 
+
+      for(int j=0;j<Mh.nc;j++){
+	v.var[0][j]=SolFonM1(d,Param,Mh.xj(j),0,Mh.xj(in),0);
+	v.var[1][j]=SolFonM1(d,Param,Mh.xj(j),0,Mh.xj(in),1);
+	v.var[2][j]=SolFonM1(d,Param,Mh.xj(j),0,Mh.xj(in),2);
+      }
+            
+
+      break;
+	case 3 :
+	 in=centerdomain(d,Mh);
+	 for(int j=0;j<Mh.nc;j++){
+	   v.var[0][j]=SolFonM1(d,Param,Mh.xj(j),0,Mh.xj(in),0);
+	   v.var[1][j]=SolFonM1(d,Param,Mh.xj(j),0,Mh.xj(in),1);
+	   v.var[2][j]=SolFonM1(d,Param,Mh.xj(j),0,Mh.xj(in),2);
+	   
+	 }
+	
+	 break; 
+       case 4:	 
+	 for(int j=0;j<Mh.nc;j++){
+	   
+	   v.var[0][j]=SolFonM1(d,Param,Mh.xj(j),0,Mh.xj(in),0);
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Init/InitM1Matter.cpp

@@ -1,0 +1,53 @@
+#include <iostream>
+#include <cassert>
+#include <cstdlib>
+#include <cmath>
+#include "Initialisation.hpp"
+#include <math.h>
+#include "AnalyticSolutions.hpp"
+#include "Diagnostics.hpp"
+#include "Functions.hpp"
+#include "Flux.hpp"
+#include "ParamPhys.hpp"
+
+void InitM1Matter(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param){
+    /** function which construct the initial datas
+     for the p1 model with matter
+     **/
+    double T=0;
+    
+    switch(d.nTest)
+    {
+            
+        case 1 :
+            // Marshak linear
+            T=300;
+            for(int j=0;j<Mh.nc;j++){
+                v.var[0][j]=Param.M1M.a_value*pow(T,4.);
+                v.var[1][j]=0;
+                v.var[2][j]=0;
+                v.var[2][j]=T;
+            }
+            break;
+            
+        case 2 :
+            // Oslon
+            T=0.056234;
+            for(int j=0;j<Mh.nc;j++){
+                v.var[0][j]=Param.M1M.a_value*pow(T,4.);
+                v.var[1][j]=0;
+                v.var[2][j]=0;
+                v.var[3][j]=T;
+            }
+            break;
+            
+    }
+}
+
+
+
+
+
+
+
+

### 2015-03-23 code_FVFSHS_2D_matter/Init/InitP1.cpp

@@ -1,0 +1,84 @@
+#include <iostream>
+#include <cassert>
+#include <cstdlib>
+#include <cmath>
+#include "Initialisation.hpp"
+#include <math.h>
+#include "AnalyticSolutions.hpp"
+#include "Diagnostics.hpp"
+#include "Functions.hpp"
+#include "Flux.hpp"
+#include "ParamPhys.hpp"
+
+  void InitP1(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param){
+     /** function which construct the initial datas 
+      for the P1 model
+  **/
+  
+    int in=0;
+    in=centerdomain(d,Mh);
+     switch(d.nTest)
+    {
+   
+       case 1 : 	
+      for(int j=0;j<Mh.nc;j++){
+	v.var[0][j]=CasTestOnde(d,Param,Mh.xj(j),0,0);
+	v.var[1][j]=CasTestOnde(d,Param,Mh.xj(j),0,1);
+	v.var[2][j]=CasTestOnde(d,Param,Mh.xj(j),0,2);
+      }
+      break;
+
+       case 2 : 
+		
+      for(int j=0;j<Mh.nc;j++){
+	v.var[0][j]=CasTestTelegraph(d,Param,Mh.xj(j),0,0);
+	v.var[1][j]=CasTestTelegraph(d,Param,Mh.xj(j),0,1);
+	v.var[2][j]=CasTestTelegraph(d,Param,Mh.xj(j),0,2);
+      }
+      break;
+      
+      
+    case 3 : 
+	
+	for(int j=0;j<Mh.nc;j++){
+	  v.var[0][j]=SolFonChaleur(d,Param,Mh.xj(j),0,Mh.xj(in));
+	  v.var[1][j]=0.;
+	  v.var[2][j]=0.; 
+	}
+      break;
+      
+     case 4 :
+      for(int j=0;j<Mh.nc;j++){	
+	v.var[0][j]=UniformSolution(d,Param,Mh.xj(j),0,0);
+	v.var[1][j]=UniformSolution(d,Param,Mh.xj(j),0,1);
+	v.var[2][j]=UniformSolution(d,Param,Mh.xj(j),0,2);
+      }
+      break;
+
+      case 5 :
+      double norm;
+      for(int j=0;j<Mh.nc;j++){
+	norm=sqrt(pow(Mh.xj(j).x,2.)+pow(Mh.xj(j).y,2.));
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Init/Initialisation.cpp

@@ -1,0 +1,50 @@
+#include <iostream>
+#include <cassert>
+#include <cstdlib>
+#include <cmath>
+#include "Initialisation.hpp"
+#include <math.h>
+#include "AnalyticSolutions.hpp"
+#include "Diagnostics.hpp"
+#include "Functions.hpp"
+#include "Flux.hpp"
+#include "ParamPhys.hpp"
+#include "WriteData.hpp"
+
+using namespace std;
+
+void ChoiceInit(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,double & InitTime){
+  /** functions which call the functions which construct the initial datas 
+      for the dfferent model
+  **/
+  if(d.restart==0) {
+    if(Param.Model == 1) {InitDiff(d,Mh,v,Param);}
+    
+    if(Param.Model == 2) {Initadv(d,Mh,v,Param);}
+    
+    if(Param.Model == 3) {InitP1(d,Mh,v,Param);}
+
+    if(Param.Model == 4) {InitP1Matter(d,Mh,v,Param);}
+    
+    if(Param.Model == 5) {InitE(d,Mh,v,Param);}
+   
+    if(Param.Model == 6) {InitM1(d,Mh,v,Param);}
+      
+    if(Param.Model == 7) {InitM1Matter(d,Mh,v,Param);}
+
+  }
+  else{
+    LoadRestart(d,Mh,v,Param,InitTime);
+  }
+}
+
+
+
+
+
+
+
+
+
+
+

### 2015-03-23 code_FVFSHS_2D_matter/Mesh/Functionsgeo.cpp

@@ -1,0 +1,441 @@
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "ClassMesh.hpp"
+#include "math.h"
+#include "Functionsgeo.hpp"
+#include "Data.hpp"
+
+/** File with Geometric functions **/
+
+
+R2 GravityCenter(cell cc,int nbnode){
+  /** function which compute the gravity center of the cell "cc" **/
+  R2 res;
+  Vertex A,B,C,D;
+  if(nbnode==4){
+    A=cc.vertices[0];
+    B=cc.vertices[1];
+    C=cc.vertices[2];
+    D=cc.vertices[3];
+
+    res.x=(1/(6*cc.area))*((A.x+B.x)*(A^B)+(B.x+C.x)*(B^C)+(C.x+D.x)*(C^D)+(D.x+A.x)*(D^A));
+    res.y=(1/(6*cc.area))*((A.y+B.y)*(A^B)+(B.y+C.y)*(B^C)+(C.y+D.y)*(C^D)+(D.y+A.y)*(D^A));
+  }
+  if(nbnode==3){
+    A=cc.vertices[0];
+    B=cc.vertices[1];
+    C=cc.vertices[2];
+
+    res.x=(1/(6*cc.area))*((A.x+B.x)*(A^B)+(B.x+C.x)*(B^C)+(C.x+A.x)*(C^A));                        
+    res.y=(1/(6*cc.area))*((A.y+B.y)*(A^B)+(B.y+C.y)*(B^C)+(C.y+A.y)*(C^A));
+  }
+  return res;
+}
+
+
+
+
+
+
+R2 ChoiceCenterCell(Data & d,cell cc, int nbnode){
+  R2 res;
+
+     res=GravityCenter(cc,nbnode);
+  return res;
+}
+
+
+int centerdomain(Data & d,Mesh & Mh){
+  /** Function which compute the center of mesh for the gaussian function **/
+  int in=0;
+ if(Mh.nbnodelocal==4){
+       in=(Mh.nc+d.Nx)/2;}
+  if(Mh.nbnodelocal==3){
+    in=(Mh.nc+2*d.Nx)/2;}
+   if(!strcmp(d.NameMesh,"KershawMesh")){
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Mesh/Tensor.cpp

@@ -1,0 +1,114 @@
+
+#include <cassert>
+#include <iostream>
+#include <cmath>
+#include<cstdlib>
+#include "Data.hpp"
+#include "ClassMesh.hpp"
+#include "Tensor.hpp"
+#include "Functions.hpp"
+#include "Functionsinit.hpp"
+#include "Flux.hpp"
+
+tensor inittensor(Data & d,Mesh & Mh,variable & v, TabConnecInv & tab,char c,int numGr,int numCell){
+  tensor t(d,c);
+   R2 xj1(0,0);
+  R2 xj2(0,0);
+  R2 w(0,0);
+  R2 vv(0,0);
+  double T;
+  double coP1=1;
+  int xg,xd,e1,e2,r;
+  int ts,th;
+  double ld=geomCorrection(d,Mh,numCell);
+  ts = 3;
+  th = 2; 
+
+  if (c=='s'){ t.num = ts; }
+  if (c=='h'){ t.num = th; }
+   
+  r=NodeGtoL(Mh,numCell,numGr);
+
+
+  if(c=='s'){
+
+    if(ts==1){
+      t.ten[0][0]=coP1*(Mh.xr(numCell,r).x-Mh.xj(numCell).x)*Mh.njr(numCell,r).x;
+      t.ten[0][1]=coP1*(Mh.xr(numCell,r).y-Mh.xj(numCell).y)*Mh.njr(numCell,r).x;
+      t.ten[1][0]=coP1*(Mh.xr(numCell,r).x-Mh.xj(numCell).x)*Mh.njr(numCell,r).y;
+      t.ten[1][1]=coP1*(Mh.xr(numCell,r).y-Mh.xj(numCell).y)*Mh.njr(numCell,r).y;
+      
+    }
+
+      if(ts==2){   
+
+	/////////////// Cas quadrangle //////////////
+	T=Vjr(Mh,numCell,numGr);
+	
+	t.ten[0][0]=T/Mh.ljr(numCell,r);
+	t.ten[0][1]=0;
+	t.ten[1][0]=0;
+	t.ten[1][1]=T/Mh.ljr(numCell,r);      
+      }
+      if(ts==3){
+	double a11=0,a12=0,a21=0,a22=0;
[…]

### 2015-03-23 code_FVFSHS_2D_matter/ParamPhysic/ParamAdvection.cpp

@@ -1,0 +1,94 @@
+#include <cmath>
+#include <cstdlib>
+#include <iostream> 
+#include "ParamAdvection.hpp"
+#include <cassert>
+#include <fstream>
+#include <string.h>
+#include <stdlib.h>
+using namespace std;
+
+/** File which contained some functions to intitialize the paramater of advection model **/ 
+
+void ParamAdv_Init(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamAdvection & Adv, const char * filename){
+  /** Initialization of advection parameter **/
+  ParamAdv_Initwithfile(Adv,filename);
+  ParamAdv_InitTab(d,Mh,v,tab,Adv);
+
+}
+
+void ParamAdv_Initwithfile(ParamAdvection & Adv, const char * filename){
+  /** Use the file ParamAdv.dat to initialize the advection parameter **/
+  
+    FILE* f = fopen(filename,"rb");
+    if(!f){cout << "Error when we open file"<<filename<<endl;exit(1);}
+     cout <<"Reading of file\"" << filename << "\""<<endl;
+    char string[255];
+
+  /* velocity_y */
+  fgets(string,255,f);
+  fscanf(f,"%lf\n",&Adv.velocity.x);
+
+  /* velocity_y */
+  fgets(string,255,f);
+  fscanf(f,"%lf\n",&Adv.velocity.y);
+
+  /* order */
+  fgets(string,255,f);
+  fscanf(f,"%d\n",&Adv.OrderAdv);
+
+  /*limitor */
+  fgets(string,255,f);
+  fscanf(f,"%d\n",&Adv.Nlim);
+  
+  cout << "End of reading ParamAdv.dat "<<endl;
+ 
+  }
+
+void ParamAdv_InitTab(Data & d,Mesh & Mh,variable  & v,TabConnecInv & tab,ParamAdvection & Adv){
+/** Function which initialize the table of advection velocity using the given value (paramAdv.dat)
+or the test case if the velocity is variable **/
+  
+  if (Adv.velocity.x != -100000 || Adv.velocity.y != -100000){
+     for(int i=0;i<Mh.nc;i++){
+      Adv.a[i].x=Adv.velocity.x;
+      Adv.a[i].y=Adv.velocity.y;
+    }
+  }
+ }
+
+
+
+
[…]

### 2015-03-23 code_FVFSHS_2D_matter/ParamPhysic/ParamDiff.cpp

@@ -1,0 +1,106 @@
+#include <cmath>
+#include <cstdlib>
+#include <iostream> 
+#include "ParamDiff.hpp"
+#include <cassert>
+#include <fstream>
+#include <string.h>
+#include <stdlib.h>
+using namespace std;
+
+/** File which contained some functions to intitialize the paramater of diffusion model **/ 
+
+void ParamDiff_Init(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab, ParamDiff & Diff, const char * filename){
+/** Initialization of diffusion parameter **/
+  ParamDiff_Initwithfile(Diff,filename);
+  ParamDiff_InitTab(d,Mh,v,tab,Diff);
+  ParamDiff_InitPhysicalTestcase(d,Mh,v,tab,Diff);
+
+}
+
+void ParamDiff_Initwithfile(ParamDiff & Diff, const char * filename){
+  /** Use the file ParamDiff.dat to initialize the diffusion parameter **/
+  
+    FILE* f = fopen(filename,"rb");
+    if(!f){cout << "Error when we open file"<<filename<<endl;exit(1);}
+     cout <<"Reading of file\"" << filename << "\""<<endl;
+    char string[255];
+
+  /* coef diff */
+  fgets(string,255,f);
+  fscanf(f,"%d\n",&Diff.Coefdiff_value);
+  
+  cout << "End of reading ParamDiff.dat "<<endl;
+ 
+  }
+
+void ParamDiff_InitTab(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamDiff & Diff){
+/** Function which initialize the table of diffusion coefficient using the given value (paramDiff.dat)
+or the test case if the diffusion coefficient is variable **/
+  
+  if (Diff.Coefdiff_value != -1){
+     for(int i=0;i<Mh.nc;i++){
+      Diff.D[i]=Diff.Coefdiff_value;
+    }
+  }
+ }
+
+
+void ParamDiff_InitPhysicalTestcase(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamDiff & Diff){
+  // This function modify the parameter to have parameter consistant with the test case
+ 
+  if (d.nTest == 1 && Diff.Coefdiff_value==0.){
+    Diff.Coefdiff_value=1.; 
[…]

### 2015-03-23 code_FVFSHS_2D_matter/ParamPhysic/ParamEuler.cpp

@@ -1,0 +1,191 @@
+#include <cmath>
+#include <cstdlib>
+#include <iostream> 
+#include "ParamEuler.hpp"
+#include <cassert>
+#include <fstream>
+#include <string.h>
+#include <stdlib.h>
+
+using namespace std;
+
+/** File which contained some functions to intitialize the paramater of Euler model **/ 
+
+void ParamEuler_Init(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab, ParamEuler & Euler, const char * filename){
+/** Initialization of Euler parameter **/
+   ParamEuler_Initwithfile(Euler,filename);
+   ParamEuler_InitPhysicalTestcase(d,Mh,v,tab,Euler);
+   ParamEuler_InitTab(d,Mh,v,tab,Euler);
+}
+
+void ParamEuler_Initwithfile(ParamEuler & Euler, const char * filename){
+ /** Use the file ParamEuler.dat to initialize the Euler parameter **/
+  
+    FILE* f = fopen(filename,"rb");
+    if(!f){cout << "Error when we open file"<<filename<<endl;exit(1);}
+     cout <<"Reading of file\"" << filename << "\""<<endl;
+    char string[255];
+
+  /* Pressure law*/
+  fgets(string,255,f);
+  fscanf(f,"%d\n",&Euler.lp);
+
+   /* gamma*/
+  fgets(string,255,f);
+  fscanf(f,"%lf\n",&Euler.gamma);
+
+   /* Local high order*/
+  fgets(string,255,f);
+  fscanf(f,"%d\n",&Euler.LHO);
+
+  /* sigma*/
+  fgets(string,255,f);
+  fscanf(f,"%lf\n",&Euler.sig_value);
+
+   /* eps*/
+  fgets(string,255,f);
+  fscanf(f,"%lf\n",&Euler.eps_value);
+
+   /* gx */
+  fgets(string,255,f);
+  fscanf(f,"%lf\n",&Euler.gx);
+
+  /* gy */
+  fgets(string,255,f);
+  fscanf(f,"%lf\n",&Euler.gy);
+
+  /* Order advection */
+  fgets(string,255,f);
+  fscanf(f,"%d\n",&Euler.OrderAdv); 
+  
+  cout << "End of reading ParamEuler.dat "<<endl;
+
+  fclose(f); 
+  
+  }
+
[…]

### 2015-03-23 code_FVFSHS_2D_matter/ParamPhysic/ParamM1.cpp

@@ -1,0 +1,219 @@
+#include <cmath>
+#include <cstdlib>
+#include <iostream> 
+#include "ParamM1.hpp"
+#include <cassert>
+#include <fstream>
+#include <string.h>
+#include <stdlib.h>
+
+using namespace std;
+
+/** File which contained some functions to intitialize the paramater of M1 model **/ 
+
+void ParamM1_Init(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamM1 & M1, const char * filename){
+/** Initialization of M1 parameter **/
+  ParamM1_Initwithfile(M1,filename);
+  ParamM1_InitTab(d,Mh,v,tab,M1);
+  ParamM1_InitPhysicalTestcase(d,Mh,v,tab,M1);
+
+}
+
+void ParamM1_Initwithfile(ParamM1 & M1, const char * filename){
+ /** Use the file ParamM1.dat to initialize the M1 parameter **/
+  
+    FILE* f = fopen(filename,"rb");
+    if(!f){cout << "Error when we open file"<<filename<<endl;exit(1);}
+     cout <<"Reading of file\"" << filename << "\""<<endl;
+    char string[255];
+
+  /* sigma*/
+  fgets(string,255,f);
+  fscanf(f,"%lf\n",&M1.sig_value);
+
+   /* eps*/
+  fgets(string,255,f);
+  fscanf(f,"%lf\n",&M1.eps_value);
+
+    /* order advection*/
+  fgets(string,255,f);
+  fscanf(f,"%d\n",&M1.OrderAdv);
+  
+  cout << "End of reading ParamM1.dat "<<endl;
+ 
+  }
+
+void ParamM1_InitTab(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamM1 & M1){
+/** Function which initialize the table of M1 quantities using the given value (paramM1.dat)
+or the test case if the eps, sigma are variables **/
+  
+  if (M1.eps_value != -1){
+     for(int i=0;i<M1.nbcell;i++){
+      M1.eps[i]=M1.eps_value;
+    }
+  }
+   if (M1.sig_value != -1){
+     for(int i=0;i<M1.nbcell;i++){
+      M1.sigma[i]=M1.sig_value;
+    }
+  }
+ }
+
[…]

### 2015-03-23 code_FVFSHS_2D_matter/ParamPhysic/ParamM1Matter.cpp

@@ -1,0 +1,238 @@
+#include <cmath>
+#include <cstdlib>
+#include <iostream> 
+#include "ParamM1Matter.hpp"
+#include <cassert>
+#include <fstream>
+#include <string.h>
+#include <stdlib.h>
+
+using namespace std;
+
+/** File which contained some functions to intitialize the paramater of M1 model **/ 
+
+void ParamM1M_Init(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamM1Matter & M1M, const char * filename){
+/** Initialization of M1M parameter **/
+  ParamM1M_Initwithfile(M1M,filename);
+  ParamM1M_InitTab(d,Mh,v,tab,M1M);
+  ParamM1M_InitPhysicalTestcase(d,Mh,v,tab,M1M);
+
+}
+
+void ParamM1M_Initwithfile(ParamM1Matter & M1M, const char * filename){
+ /** Use the file ParamM1M.dat to initialize the M1 with matter parameters **/
+  
+    FILE* f = fopen(filename,"rb");
+    if(!f){cout << "Error when we open file"<<filename<<endl;exit(1);}
+     cout <<"Reading of file\"" << filename << "\""<<endl;
+    char string[255];
+
+  /* sigma*/
+  fgets(string,255,f);
+  fscanf(f,"%lf\n",&M1M.sig_value);
+
+  /* sigma_A*/
+  fgets(string,255,f);
+  fscanf(f,"%lf\n",&M1M.sigA_value);
+
+  /* eps*/
+  fgets(string,255,f);
+  fscanf(f,"%lf\n",&M1M.eps_value);
+
+  /* order advection*/
+  fgets(string,255,f);
+  fscanf(f,"%d\n",&M1M.OrderAdv);
+  
+  /* valeur de 1/mc2, propre au Compton */
+  fgets(string,255,f);
+  fscanf(f,"%lf\n",&M1M.mc2value);
+    
+  /* Temp_BB (Black Body temperature)*/
+  fgets(string,255,f);
+  fscanf(f,"%lf\n",&M1M.TempBB);
+    
+  /* a (stefan constant)*/
+  fgets(string,255,f);
+  fscanf(f,"%lf\n",&M1M.a_value);
+
+
+  cout << "End of reading ParamM1.dat "<<endl;
+ 
+  }
+
[…]

### 2015-03-23 code_FVFSHS_2D_matter/ParamPhysic/ParamP1.cpp

@@ -1,0 +1,203 @@
+#include <cmath>
+#include <cstdlib>
+#include <iostream> 
+#include "ParamP1.hpp"
+#include <cassert>
+#include <fstream>
+#include <string.h>
+#include <stdlib.h>
+using namespace std;
+
+/** File which contained some functions to intitialize the paramater of P1 model **/ 
+
+void ParamP1_Init(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamP1 & P1, const char * filename){
+/** Initialization of P1 parameter **/
+  ParamP1_Initwithfile(P1,filename);
+  ParamP1_InitPhysicalTestcase(d,Mh,v,tab,P1);
+  ParamP1_InitTab(d,Mh,v,tab,P1);
+
+}
+
+void ParamP1_Initwithfile(ParamP1 & P1, const char * filename){
+ /** Use the file ParamP1.dat to initialize the P1 parameter **/
+  
+    FILE* f = fopen(filename,"rb");
+    if(!f){cout << "Error when we open file"<<filename<<endl;exit(1);}
+     cout <<"Reading of file\"" << filename << "\""<<endl;
+    char string[255];
+
+  /* sigma*/
+  fgets(string,255,f);
+  fscanf(f,"%lf\n",&P1.sig_value);
+
+   /* eps*/
+  fgets(string,255,f);
+  fscanf(f,"%lf\n",&P1.eps_value);
+
+  
+  
+  cout << "End of reading ParamP1.dat  "<<endl;
+ 
+  }
+
+void ParamP1_InitTab(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamP1 & P1){
+/** Function which initialize the table of P1 quantities using the given values (paramP1.dat)
+or the test case if the eps, sigma or phi are variables **/
+  
+  if (P1.eps_value != -1){
+     for(int i=0;i<P1.nbcell;i++){
+      P1.eps[i]=P1.eps_value;
+    }
+  }
+   if (P1.sig_value != -1){
+     for(int i=0;i<P1.nbcell;i++){
+      P1.sigma[i]=P1.sig_value;
+    }
+  }
+   if (P1.sig_value == -1 && d.nTest == 5){
+     for(int i=0;i<P1.nbcell;i++){
+       if(Mh.cells[i].lab==0){
+	 P1.sigma[i]=1;
+       }
[…]

### 2015-03-23 code_FVFSHS_2D_matter/ParamPhysic/ParamP1Matter.cpp

@@ -1,0 +1,207 @@
+#include <cmath>
+#include <cstdlib>
+#include <iostream> 
+#include "ParamP1Matter.hpp"
+#include <cassert>
+#include <fstream>
+#include <string.h>
+#include <stdlib.h>
+using namespace std;
+
+
+/** File which contained some functions to intitialize the paramater of P1 model with matter **/ 
+
+void ParamP1Matter_Init(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamP1Matter & P1M, const char * filename){
+/** Initialization of P1 with matter parameter **/
+  ParamP1Matter_Initwithfile(P1M,filename);
+  ParamP1Matter_InitTab(d,Mh,v,tab,P1M);
+  ParamP1Matter_InitPhysicalTestcase(d,Mh,v,tab,P1M); 
+
+}
+
+void ParamP1Matter_Initwithfile(ParamP1Matter & P1M, const char * filename){
+ /** Use the file ParamP1M.dat to initialize the P1 with matter parameter **/
+
+  
+    FILE* f = fopen(filename,"rb");
+    if(!f){cout << "Error when we open file"<<filename<<endl;exit(1);}
+     cout <<"Reading of file\"" << filename << "\""<<endl;
+    char string[255];
+
+  /* sigma*/
+  fgets(string,255,f);  fscanf(f,"%lf\n",&P1M.sig_value);
+
+   /* eps*/
+  fgets(string,255,f);
+  fscanf(f,"%lf\n",&P1M.eps_value);
+
+  /* sigma absorbtion*/
+  fgets(string,255,f);
+  fscanf(f,"%lf\n",&P1M.sigA_value);
+
+   /* a (stefan constant)*/
+  fgets(string,255,f);
+  fscanf(f,"%lf\n",&P1M.a_value);
+
+  /* Cv (matter constant)*/
+  fgets(string,255,f);
+  fscanf(f,"%lf\n",&P1M.Cv_value); 
+
+   /* Temp_BB (Black Body temperature)*/
+  fgets(string,255,f);
+  fscanf(f,"%lf\n",&P1M.TempBB);
+  
+  cout << "End of reading Paramp1M.dat "<<endl;
+ 
+  }
+
[…]

### 2015-03-23 code_FVFSHS_2D_matter/ParamPhysic/ParamPhysic.cpp

@@ -1,0 +1,64 @@
+#include <cmath>
+#include <cstdlib>
+#include <iostream> 
+#include "ParamPhys.hpp"
+#include <cassert>
+#include <fstream>
+#include <string.h>
+#include <stdlib.h>
+using namespace std;
+
+
+/** File which contained some generic functions to intitialize the paramater of the model **/ 
+
+void ParamPhysic_Init(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamPhysic & Param){
+ /** Initialization of the model parameters **/
+  if (Param.Model == 1){
+    ParamDiff_Init(d,Mh,v,tab,Param.Diff,"ParamPhysic/ParamDiff.dat");
+  }
+  if (Param.Model == 2){
+    ParamAdv_Init(d,Mh,v,tab,Param.Adv,"ParamPhysic/ParamAdv.dat");
+  }  
+  if (Param.Model == 3){
+    ParamP1_Init(d,Mh,v,tab,Param.P1,"ParamPhysic/ParamP1.dat");
+  } 
+  if (Param.Model == 4){
+    ParamP1Matter_Init(d,Mh,v,tab,Param.P1M,"ParamPhysic/ParamP1Matter.dat");
+  } 
+  if (Param.Model == 5){
+    ParamEuler_Init(d,Mh,v,tab,Param.Euler,"ParamPhysic/ParamEuler.dat");
+  } 
+  if (Param.Model == 6){
+    ParamM1_Init(d,Mh,v,tab,Param.M1,"ParamPhysic/ParamM1.dat");
+  }
+  if (Param.Model == 7){
+    ParamM1M_Init(d,Mh,v,tab,Param.M1M,"ParamPhysic/ParamM1Matter.dat");
+  }
+  
+}
+
+void ParamPhysic_InitTab(Data & d,Mesh & Mh,variable &v,TabConnecInv & tab, ParamPhysic & Param){
+  /** Function which initialize the table of quantities using the given values **/
+  if (Param.Model == 1){
+    ParamDiff_InitTab(d,Mh,v,tab,Param.Diff);
+  }
+  if (Param.Model == 2){
+    ParamAdv_InitTab(d,Mh,v,tab,Param.Adv);
+  }  
+  if (Param.Model == 3){
+    ParamP1_InitTab(d,Mh,v,tab,Param.P1);
+  } 
[…]

### 2015-03-23 code_FVFSHS_2D_matter/PlotDatas/WriteData.cpp

@@ -1,0 +1,382 @@
+#include <iostream>
+#include <cassert>
+#include "Data.hpp"
+#include "WriteData.hpp"
+#include "Functions.hpp"
+#include "AnalyticSolutions.hpp"
+#include "Diagnostics.hpp"
+#include "Flux.hpp"
+
+using namespace std;
+
+/** File which contains the functions for the plot **/
+
+
+void SaveData(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,int ntAnim){
+  /** Function which find the numbers of the variables plotted **/
+  int TabNumVar[300];
+  int NbVarWrite;
+  int c=0,j=0;
+  char *copie = new char[4];
+  for(int i=0;i<300;i++){
+    if(d.NumVar[i]=='E') break;
+    else if(d.NumVar[i]==',') {
+      copie[c]='\0';
+      TabNumVar[j]=atoi(copie);
+      j++;
+      c=0;}
+    
+    else {
+      copie[c]=d.NumVar[i];
+      c++;}
+      
+  }
+    delete [] copie;
+    NbVarWrite=j;
+    
+    for(j=0;j<NbVarWrite;j++){
+      if(TabNumVar[j] > v.nbvar) {
+	cout<<"the variable that you want plot does not exist"<<endl;
+	exit(1);
+      } 
+      if(d.dimsave==2){
+	if(d.Typewrite=='N'){
+	  SaveOneData(d,Mh,v,Param,TabNumVar[j],ntAnim);
+	}
+	if(d.Typewrite=='C'){
+	  SaveOneDatacentercell(d,Mh,v,Param,TabNumVar[j],ntAnim);
+	}
+      }
+      if(d.dimsave==1 && d.Ny == 1){
+	SaveOneData1D(d,Mh,v,Param,TabNumVar[j],ntAnim);
+	
+      }
+    }
+
+  
+  if(Param.Model == 5) {
+    SaveInterEner(d,Mh,v,Param,ntAnim); 
+  }
+
+}
+
+
+void SaveOneData(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,int Num,int ntAnim){
[…]

### 2015-03-23 code_FVFSHS_2D_matter/PlotDatas/WriteData_Euler.cpp

@@ -1,0 +1,143 @@
+#include <iostream>
+#include <cassert>
+#include "Data.hpp"
+#include "WriteData.hpp"
+#include "Functions.hpp"
+#include "AnalyticSolutions.hpp"
+#include "Diagnostics.hpp"
+#include "Flux.hpp"
+
+/** File which contains the functions for the plot of Euler quantities **/
+
+
+void SaveInterEner(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,int ntAnim){
+/** Function which plot the internal energy for Eler model **/
+  char string[255];
+  FILE *fileresult=NULL;
+  int j,n;
+  
+  if(d.Anim=='y'){ sprintf(string,"%s%s%04d.%s","./DATA/","InterEner",ntAnim,d.suffixe);}
+
+  else { sprintf(string,"%s%s%s","./DATA/","var",d.suffixe);}
+  fileresult=fopen(string,"w");
+  for(j=0;j<Mh.nc;j++){
+     if(Mh.cells[j].lab!=-1){
+      
+      if(Mh.nbnodelocal==4)
+	{n=Mh(j,0);
+	  fprintf(fileresult,"%e %e %e\n",Mh.xr(n).x,Mh.xr(n).y,EnergyIn(d,Mh,v,Param.Euler,j));
+	n=Mh(j,1);
+	fprintf(fileresult,"%e %e %e\n\n",Mh.xr(n).x,Mh.xr(n).y,EnergyIn(d,Mh,v,Param.Euler,j));
+	n=Mh(j,3);
+	fprintf(fileresult,"%e %e %e\n",Mh.xr(n).x,Mh.xr(n).y,EnergyIn(d,Mh,v,Param.Euler,j));
+	n=Mh(j,2);
+	fprintf(fileresult,"%e %e %e\n\n\n",Mh.xr(n).x,Mh.xr(n).y,EnergyIn(d,Mh,v,Param.Euler,j));
+       
+	
+	}
+      if(Mh.nbnodelocal==3)
+	{n=Mh(j,0);
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Prog.cpp

@@ -1,0 +1,254 @@
+#include <cmath>
+#include <cstdlib>
+#include <iostream>
+#include "Flux.hpp"
+#include "Initialisation.hpp"
+#include "WriteData.hpp"
+#include "AnalyticSolutions.hpp"
+#include "Diagnostics.hpp"
+#include <fstream>
+#include "Functions.hpp"
+#include "TimeDiscret.hpp"
+#include "Functionsgeo.hpp"
+#include "Functionsinit.hpp"
+#include "ParamPhys.hpp"
+
+using namespace std;
+
+/** Following works :**/
+/** 1) Check test case for 2 and 6 for P1, 1 and 2 for P1 matter **/
+/** 2) Droniou nonlinear diffusion scheme (Manu) **/
+/** 3) P3 model (Manu) **/
+/** 4) Generic Sn models  (Manu) **/
+/** 5) Second order extension. For now just write for P1 system without source term and works only without limiting **/
+/** 6) Multi-groupes models (Thomas) **/
+
+
+
+int main() { 
+  /** Parameter of the code initialized **/
+  Data d("parametre.dat"); 
+ 
+  /** Mesh construction **/
+  Mesh Mh(d);    
+  Mh=ChoiceMesh(d);
+
+  
+  R2 p;
+  for(int i=0;i<Mh.nc;i++){
+    p=GravityCenter(Mh.cells[i],Mh.nbnodelocal);
+    Mh.cells[i].initCC(p,1);
+  }
+  int in=centerdomain(d,Mh);
+  
+      
+  /** Connectivity table construction **/
+  struct TabConnecInv TConnectInv;
+  CreateTabInv(Mh,TConnectInv);  
+
+  /** Physical parameters construction **/
+  ParamPhysic Param(d,Mh);
+  
+  /** Variable contruction and initialization **/
+  variable v(d,Mh.nc,Mh.nv);
+  
+  /** Physical parameter initialization **/
+  double time=0.;
+  double dt=0.;
+  ParamPhysic_Init(d,Mh,v,TConnectInv,Param);
+  ChoiceInit(d,Mh,v,Param,time);
+  cout <<"End of parameters and variables construction"<<endl;
+
+  /** Plot informations of the run and plot mesh **/
+  WriteDataToMain(d,Param);
+  SaveMesh(d,Mh);
+ 
+  /** definition of the time quantities **/
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Source/Source.cpp

@@ -1,0 +1,69 @@
+
+#include <iostream>
+#include <cmath>
+#include <cstdlib>
+#include "Source.hpp"
+
+
+/** File which contains the functions for the source terms **/
+
+
+vectorflux ChoiceSource(Data & d ,int numCell,Mesh & Mh, variable & v, TabConnecInv & tab,ParamPhysic & Param,R2* ur){
+ /**  Function which gives the explicit source term associated with your model and your scheme (in Data) **/
+vectorflux res(d);
+
+  if(Param.Model ==1){      
+    res=SourceDiff(d,numCell,Mh,v,Param);    /** Diffusion source term **/
+  }
+
+  if(Param.Model ==2){      
+    res=Sourceadv(d,numCell,Mh,v,Param);    /** Advection source term **/
+  }
+    
+  if(Param.Model ==3){  
+    res=SourceP1(d,numCell,Mh,v,tab,Param); /** P1 source term **/
+  }
+
+ if(Param.Model ==4){
+    res=SourceP1Matter(d,numCell,Mh,v,tab,Param); /** P1 with matter source term **/
+  }
+  
+  if(Param.Model ==5){
+    res=SourceE(d,numCell,Mh,v,tab,Param,ur); /** Euler source term **/
+  }
+
+  if(Param.Model ==6){
+    res=SourceM1(d,numCell,Mh,v,tab,Param); /** M1 source term **/
+  }
+
+  if(Param.Model ==7){
+    res=SourceM1Matter(d,numCell,Mh,v,tab,Param); /** M1 with Matter source term **/
+  }
+
+  
+  return res;
+}
+
+
+R2 SemiImplicitPart(Data & d ,int numCell,Mesh & Mh, variable & v,variable & temp, TabConnecInv & tab,ParamPhysic & Param,double dt){
+/**  Function which gives the implicit source term (scattering or friction source term)
+ associated with your model and your scheme (in Data) **/
+  R2 res(0,0);
+
+  if(Param.Model ==3){
+    res=SolveurImpliciteP1(d,numCell,Mh,v,tab,Param,dt,temp.var[1][numCell],temp.var[2][numCell]);
+  }
+  
+  if(Param.Model ==4){
+      res=SolveurImpliciteP1Matter(d,numCell,Mh,v,tab,Param,dt,temp.var[1][numCell],temp.var[2][numCell]);
+  }
+  
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Source/SourceAdvection.cpp

@@ -1,0 +1,21 @@
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "Flux.hpp"
+#include "Source.hpp"
+#include "Variables.hpp"
+#include "Functions.hpp"
+#include <stdio.h>
+#include "Tensor.hpp"
+#include "BoundaryCondition.hpp"
+#include "Functionsinit.hpp"
+
+
+vectorflux Sourceadv(Data & d,int numCell, Mesh & Mh, variable & v,ParamPhysic & Param) {
+  /** Function wich compute the explicit source term for advection **/
+  vectorflux res(d);
+  res.vflux[0]=0;
+ 
+    return res;
+ 
+}

### 2015-03-23 code_FVFSHS_2D_matter/Source/SourceDiff.cpp

@@ -1,0 +1,20 @@
+
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "Flux.hpp"
+#include "Variables.hpp"
+#include "Functions.hpp"
+#include <stdio.h>
+#include "Tensor.hpp"
+#include "BoundaryCondition.hpp"
+#include "Functionsinit.hpp"
+#include "Source.hpp"
+
+vectorflux SourceDiff(Data & d,int numCell,Mesh & Mh, variable & v,ParamPhysic & Param){
+  /** Function wich compute the explicit source term for diffusion **/
+  vectorflux res(1);
+
+  res.vflux[0]=0;
+  return res;
+}

### 2015-03-23 code_FVFSHS_2D_matter/Source/SourceEuler.cpp

@@ -1,0 +1,408 @@
+ #include <iostream>
+#include <cmath>
+#include <cassert>
+#include "Flux.hpp"
+#include "Variables.hpp"
+#include "Functions.hpp"
+#include <stdio.h>
+#include "Tensor.hpp"
+#include "BoundaryCondition.hpp"
+#include "Functionsinit.hpp"
+#include "Source.hpp"
+
+
+
+vectorflux SourceE(Data & d,int numCell,Mesh & Mh, variable & v, TabConnecInv & tab,ParamPhysic & Param,R2 * ur){
+/** Function wich compute the explicit source terms for Euler **/
+  
+  vectorflux res(4);
+  R2 g(0,0);
+  g=GravityVector(d,Param.Euler);
+
+  if((d.scheme==1 || d.scheme==4) && d.Typetime=='E'){
+    res.vflux[0]=0.;
+    res.vflux[1]=-(Mh.area(numCell)/Param.Euler.eps[numCell])*(v.var[0][numCell]*g.x+(Param.Euler.sigma[numCell]/Param.Euler.eps[numCell])*v.var[1][numCell]);
+    res.vflux[2]=-(Mh.area(numCell)/Param.Euler.eps[numCell])*(v.var[0][numCell]*g.y+(Param.Euler.sigma[numCell]/Param.Euler.eps[numCell])*v.var[2][numCell]);
+    res.vflux[3]=-(Mh.area(numCell)/Param.Euler.eps[numCell])*((g.x*v.var[1][numCell]+g.y*v.var[2][numCell])+(Param.Euler.sigma[numCell]/Param.Euler.eps[numCell])*((pow(v.var[1][numCell],2.)+pow(v.var[2][numCell],2.))/v.var[0][numCell]));
+  }
+
+  if((d.scheme==1 || d.scheme==4) && d.Typetime=='S'){
+    res.vflux[0]=0.;
+    res.vflux[1]=-(Mh.area(numCell)/Param.Euler.eps[numCell])*v.var[0][numCell]*g.x;
+    res.vflux[2]=-(Mh.area(numCell)/Param.Euler.eps[numCell])*v.var[0][numCell]*g.y;
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Source/SourceM1.cpp

@@ -1,0 +1,183 @@
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "Variables.hpp"
+#include "Flux.hpp"
+#include "Source.hpp"
+#include "BoundaryCondition.hpp"
+#include "Tensor.hpp"
+#include "FunctionsAdvection.hpp"
+
+
+
+vectorflux SourceM1(Data & d,int numCell,Mesh & Mh, variable & v, TabConnecInv & tab, ParamPhysic & Param){
+ /** Function wich compute the explicit source terms for M1 **/
+
+  
+  vectorflux res(d);
+  double kj=0;
+  double Mr[2][2];
+  R2 uj(0,0);
+    
+  int compton_scattering = 1 ; //(1 if taken into account, 0 if not)
+
+  kj=coefk(d,Param.M1,v.var[0][numCell],v.var[1][numCell],v.var[2][numCell]);
+  Calcul_u(d,Mh,v,tab,Param.M1,uj,numCell);
+  
+  if(d.Typetime == 'E')
+  {
+    if( d.scheme==1 )
+    {
+      res.vflux[0] = 0. ;
+      res.vflux[1] = -((Param.M1.sigma[numCell])/(Param.M1.eps[numCell]*Param.M1.eps[numCell]))*Mh.area(numCell)*v.var[1][numCell];
+      res.vflux[2] = -((Param.M1.sigma[numCell])/(Param.M1.eps[numCell]*Param.M1.eps[numCell]))*Mh.area(numCell)*v.var[2][numCell];
+      
+      if (compton_scattering == 1)
+      {
+          
+          double T = 1. ; // temperature electron
+          double sigma_a = Param.M1.sigma[numCell] ;
+          
+          double temp = 0. ;
+          double source_E = 0. ;
+          double source_F = 0. ;
+          R2 g ;
+          
+          g.x = v.var[1][numCell] / v.var[0][numCell] ;
+          g.y = v.var[2][numCell] / v.var[0][numCell] ;
+                    
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Source/SourceM1Matter.cpp

@@ -1,0 +1,98 @@
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "Variables.hpp"
+#include "Flux.hpp"
+#include "Source.hpp"
+#include "BoundaryCondition.hpp"
+#include "Tensor.hpp"
+#include "FunctionsAdvection.hpp"
+
+
+
+vectorflux SourceM1Matter(Data & d,int numCell,Mesh & Mh, variable & v, TabConnecInv & tab, ParamPhysic & Param){
+    /** Function wich compute the explicit source terms for M1 **/
+    
+    
+    vectorflux res(d);
+    double kj=0;
+    double Mr[2][2];
+    R2 uj(0,0);
+    
+    int compton_scattering = 1 ; //(1 if taken into account, 0 if not)
+    
+    kj=coefk(d,Param.M1,v.var[0][numCell],v.var[1][numCell],v.var[2][numCell]);
+    Calcul_u(d,Mh,v,tab,Param.M1,uj,numCell);
+    
+    if(d.Typetime == 'E')
+    {
+        if( d.scheme==1 )
+        {
+            res.vflux[0] = 0. ;
+            res.vflux[1] = -((Param.M1.sigma[numCell])/(Param.M1.eps[numCell]*Param.M1.eps[numCell]))*Mh.area(numCell)*v.var[1][numCell];
+            res.vflux[2] = -((Param.M1.sigma[numCell])/(Param.M1.eps[numCell]*Param.M1.eps[numCell]))*Mh.area(numCell)*v.var[2][numCell];
+            res.vflux[3] = 0. ;
+            
+            if (compton_scattering == 1)
+            {
+                
+                double T = 1. ; // temperature electron
+                double sigma_a = Param.M1.sigma[numCell] ;
+                
+                double temp = 0. ;
+                double source_E = 0. ;
+                double source_F = 0. ;
+                R2 g ;
+                
+                g.x = v.var[1][numCell] / v.var[0][numCell] ;
+                g.y = v.var[2][numCell] / v.var[0][numCell] ;
+                
+                temp = 2. + sqrt(4.-3.*(g,g)) ;
+                
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Source/SourceP1.cpp

@@ -1,0 +1,139 @@
+#include <iostream>
+#include <cmath>
+#include <cstdlib>
+#include "Variables.hpp"
+#include "Flux.hpp"
+#include "Source.hpp"
+#include "BoundaryCondition.hpp"
+#include "Tensor.hpp"
+
+
+
+R2 SolveurImpliciteP1(Data & d,int numCell,Mesh & Mh, variable & v, TabConnecInv & tab,ParamPhysic & Param, double dt,double b1, double b2){
+     /** Function wich compute the implicit contribution to the source term for P1 **/
+  R2 res(0,0);
+  double a11=0,a12=0,a21=0,a22=0,Det=0;
+  double Mr[2][2];
+  tensor alpha(d,'h');
+  int numGr=0;
+
+  if(d.scheme == 1 ){
+    
+    a11=1.+dt*((Param.P1.sigma[numCell])/(Param.P1.eps[numCell]*Param.P1.eps[numCell]));
+    a12=0;
+    a21=0;
+    a22=1.+dt*((Param.P1.sigma[numCell])/(Param.P1.eps[numCell]*Param.P1.eps[numCell]));
+  }
+
+  if(d.scheme == 3){
+    
+    for(int r=0;r<Mh.nbnodelocal;r++){
+      
+      numGr=Mh(numCell,r);
+      alpha=inittensor(d,Mh,v,tab,'h',numGr,numCell);
+      MrConstructP1(d,numGr,Mh,v,tab,Param,Mr);
+      a11=a11+Mh.ljr(numCell,r)*(alpha.ten[0][0]*(1.-Mr[0][0])+alpha.ten[0][1]*(-Mr[1][0]));
+      a12=a12+Mh.ljr(numCell,r)*(alpha.ten[0][0]*(-Mr[0][1])+alpha.ten[0][1]*(1.-Mr[1][1]));
+      a21=a21+Mh.ljr(numCell,r)*(alpha.ten[1][0]*(1.-Mr[0][0])+alpha.ten[1][1]*(-Mr[1][0]));
+      a22=a22+Mh.ljr(numCell,r)*(alpha.ten[1][0]*(-Mr[0][1])+alpha.ten[1][1]*(1.-Mr[1][1]));
+
+    }
+    
+    
+    a11=(dt/(Mh.area(numCell)*Param.P1.eps[numCell]))*a11+1.;
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Source/SourceP1Matter.cpp

@@ -1,0 +1,195 @@
+#include <iostream>
+#include <cmath>
+#include <cstdlib>
+#include "Variables.hpp"
+#include "Flux.hpp"
+#include "Source.hpp"
+#include "BoundaryCondition.hpp"
+#include "Tensor.hpp"
+#include "FunctionsAdvection.hpp"
+
+vectorflux SourceP1Matter(Data & d,int numCell,Mesh & Mh, variable & v, TabConnecInv & tab,ParamPhysic & Param) {
+  /** Function wich compute the explicit source terms for P1 with matter**/
+  vectorflux res(d);
+  R2 sol(0,0);
+
+  if( d.Typetime=='E' ){
+    if( d.scheme==1 ){
+      res.vflux[0]=0;
+      res.vflux[1]=-((Param.P1M.sigmaA[numCell])/(Param.P1M.eps[numCell]*Param.P1M.eps[numCell]))*Mh.area(numCell)*v.var[1][numCell];
+      res.vflux[2]=-((Param.P1M.sigmaA[numCell])/(Param.P1M.eps[numCell]*Param.P1M.eps[numCell]))*Mh.area(numCell)*v.var[2][numCell];
+    }
+    
+    if( d.scheme==2 ){
+      res.vflux[0]=0;
+      res.vflux[1]=0;
+      res.vflux[2]=0;  
+    }
+    
+    if(d.scheme==3){
+      double Mr[2][2];
+      MatrixSourceP1Matter(d,numCell,Mh,v,tab,Param,Mr);
+      res.vflux[0]=0;
+      res.vflux[1]=Mr[0][0]*v.var[1][numCell]+Mr[0][1]*v.var[2][numCell];
+      res.vflux[2]=Mr[1][0]*v.var[1][numCell]+Mr[1][1]*v.var[2][numCell];
+    }
+    
+    res.vflux[0]=((Param.P1M.sigmaA[numCell])/(Param.P1M.eps[numCell]*Param.P1M.eps[numCell]))*(Param.P1M.a_value*pow(v.var[v.nbvar-1][numCell],4.)-v.var[0][numCell]);
+    
+    if(Param.P1M.Cv_value!=0){
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Timeschemes/ExplicitScheme.cpp

@@ -1,0 +1,109 @@
+#include <cmath>
+#include <cstdlib>
+#include <iostream>
+#include "TimeDiscret.hpp"
+#include <fstream>
+#include "Flux.hpp"
+#include "BoundaryCondition.hpp"
+#include "AnalyticSolutions.hpp"
+#include "Diagnostics.hpp"
+#include "FunctionsAdvection.hpp"
+#include "HOfunctions.hpp"
+#include <assert.h>
+
+using namespace std;
+
+/** Explicit scheme 
+ **/
+void ExplicitDiscret(Data & d,Mesh & Mh, variable & v,TabConnecInv & TConnectInv, ParamPhysic & Param,double dt,int & ntAnim,double & time){
+  
+  int nt=0;
+  variable temp(d,Mh.nc,Mh.nv);
+  vectorflux flux(d);
+  vectorflux source(d);
+  temp=v;
+  R2 *ur =new R2[Mh.nv];  
+  double c=0;
+
+  
+  /** computaion of the table for variables parameters  **/ 
+  ParamPhysic_InitTab(d,Mh,v,TConnectInv,Param);
+
+
+  if(Param.Model == 5 && Param.Euler.LHO >1 ){
+    for(int r=0;r<Mh.nv;r++){
+      if(Mh.xr(r).lab>-1){
+	/** We constructt the mean square problem for high order reconstruction 
+        only for the node of the physical domain (not for the ghost node)**/
+	LSInit(d,Mh,v,TConnectInv,Param.Euler,Param.Euler.TabLS[r],Param.Euler.LHO,r);
+      }    
+    }
+  } 
+   
+   while(time<d.Tf)
+     {
+       if(time+dt>d.Tf) {
+	 dt=d.Tf-time;
+       }
+
+       /** apply boundary condition (phantom cell) **/ 
+       BoundaryCondition(d,Mh,v,Param,time);
+       
+       if(d.Anim=='y' && time>=d.dtAnim*ntAnim){
+	  SaveRestart(d,Mh,v,Param,nt,time);
+	 SaveData(d,Mh,v,Param,ntAnim);
+	 ntAnim++;
+       } 
+
+       /** Diagnostic : masse, velocity etc **/
+        Diagnostics_Quantities(d,Mh,v,Param,nt,time);   
+
+       /** Computation of the nodal flux solving nodal system **/
+       if(Param.Model !=1 && d.Typescheme == 'N' ){	 
[…]

### 2015-03-23 code_FVFSHS_2D_matter/Timeschemes/SemiExScheme.cpp

@@ -1,0 +1,209 @@
+
+#include <cmath>
+#include <cstdlib>
+#include <iostream>
+#include "TimeDiscret.hpp"
+#include <fstream>
+#include "Flux.hpp"
+#include "BoundaryCondition.hpp"
+#include "AnalyticSolutions.hpp"
+#include "Diagnostics.hpp"
+#include "FunctionsAdvection.hpp"
+#include "HOfunctions.hpp"
+#include <assert.h>
+
+using namespace std;
+
+
+int SIschemeImplemented(Data & d,Mesh & Mh, variable & v,TabConnecInv & TConnectInv, ParamPhysic & Param){
+  /** function which allows to known if the semi implicit scheme exist or not **/
+  int res=0;
+  
+  /** if res=0 the semi implicit scheme does not exist, if res=1 the semi implicit scheme exist **/
+
+  
+  if(Param.Model == 1) {
+    res=0;  
+  }
+
+  if(Param.Model == 2) {
+    res=0;
+  }
+
+  if(Param.Model == 3) {
+     switch(d.scheme){
+    case 1:
+      res=1;
+      break;
+    case 2:
+      res=0;
+      break;  
+    case 3:
+      res=1;
+      break;  
+    default: cout <<" the scheme associated with the number"<<d.scheme<<" does not exist "<<endl;
+    }
+  }
+
+  if(Param.Model == 4) {
+       switch(d.scheme){
+    case 1:
+      res=1;
+      break;
+    case 2:
+      res=0;
+      break;  
+    case 3:
+      res=1;
+      break;  
+    default: cout <<" the scheme associated with the number"<<d.scheme<<" does not exist "<<endl;
+    }
+
+  }
+
+  if(Param.Model == 5) {
+       switch(d.scheme){
+    case 1:
+      res=1;
+      break;
+    case 2:
+      res=0;
+      break;  
+    case 3:
+      res=1;
+      break;
+    case 4:
+      res=1;
+      break;  
+    default: cout <<" the scheme associated with the number"<<d.scheme<<" does not exist "<<endl;
+    }
+
+  }
+
+  if(Param.Model == 6) {
+       switch(d.scheme){
+    case 1:
+      res=1;
[…]

### 2015-03-23 code_FVFSHS_2D_matter/hppParam/ParamAdvection.hpp

@@ -1,0 +1,103 @@
+#ifndef PARAMADVECTION_HPP
+#define PARAMADVECTION_HPP
+
+#include <cmath>
+#include <cstdlib>
+#include <iostream> 
+#include "R2.hpp"
+#include "Data.hpp"
+#include "ClassMesh.hpp"
+#include <cassert>
+#include "FunctionsConnect.hpp"
+#include "Variables.hpp"
+#include <fstream>
+#include <string.h>
+#include <stdlib.h>
+
+using namespace std;
+
+/** Class: physical parameter for advection model 
+    - nbvar: number of variable for the model
+    - nbcell: number of cells
+    - a: table of velocity coefficient for each cell
+    - Nlim : number of limiter
+    - OrderAdv : order of advection scheme (MUSCL for the second order)
+    - velocity : advection velocity (-100000 if the velocity is variable)
+
+**/ 
+
+class ParamAdvection {
+public:
+  int nbvar;
+  R2 *a;
+  R2 velocity;
+  int Nlim;
+  int OrderAdv;
+  int nbcell; 
+  
+  ParamAdvection(){
+    nbvar=1;
+    nbcell=0;
+    velocity.x=0.;
+    velocity.y=0.;
+    a=NULL;
+    OrderAdv=1;
+    Nlim=1;
+  }
+  
+  ParamAdvection(Data & d,Mesh & Mh){ 
+    nbvar=1;
+    nbcell=Mh.nc;
+    velocity.x=0.;
+    velocity.y=0.;    
+    a=new R2[nbcell];
+    OrderAdv=1;
+    Nlim=1;
+  }
+
+  ParamAdvection(const ParamAdvection & pa){
+    nbvar=pa.nbvar;
+    nbcell=pa.nbcell;
+    velocity.x=pa.velocity.x;
+    velocity.y=pa.velocity.y;
+    OrderAdv=pa.OrderAdv;
+    Nlim=pa.Nlim;
+    a = new R2[nbcell];
+    for(int i=0;i<nbvar;i++){
+      a[i]= pa.a[i];
+    }    
+  }
+  
+  ~ParamAdvection(){
+      if(a!=NULL){
+      delete [] a;
+      }      
+  }
+	
+ ParamAdvection & operator=( ParamAdvection pa){
+    nbvar=pa.nbvar;
+    nbcell=pa.nbcell;
+    OrderAdv=pa.OrderAdv;
[…]

### 2015-03-23 code_FVFSHS_2D_matter/hppParam/ParamDiff.hpp

@@ -1,0 +1,87 @@
+#ifndef PARAMDIFF_HPP
+#define PARAMDIFF_HPP
+
+#include <cmath>
+#include <cstdlib>
+#include <iostream> 
+#include "R2.hpp"
+#include "Data.hpp"
+#include "ClassMesh.hpp"
+#include "Variables.hpp"
+#include "FunctionsConnect.hpp"
+#include <cassert>
+#include <fstream>
+#include <string.h>
+#include <stdlib.h>
+using namespace std;
+
+/** Class: physical parameter for diffusion model 
+    - nbvar: number of variable for the model
+    - nbcell: number of cells
+    - D: table of diffusion coefficient for each cell
+    - Coefdiff_value :diffusion coefficient (-100000 if the coefficient is variable)
+
+**/
+
+class ParamDiff {
+public:
+  int nbvar;
+  int nbcell;
+  double *D;
+  int Coefdiff_value;
+  
+  ParamDiff(){
+    nbvar=1;
+    nbcell=0;
+    Coefdiff_value=0;
+    D=NULL;
+  }
+  
+  ParamDiff(Data & d,Mesh & Mh){ 
+    nbvar=1;
+    nbcell=Mh.nc;
+    Coefdiff_value=0;
+    D=new double[nbcell];
+  }
+
+  ParamDiff(const ParamDiff & pd){
+    nbvar=pd.nbvar;
+    nbcell=pd.nbcell;
+    Coefdiff_value=pd.Coefdiff_value;
+    D = new double[nbcell];
+    for(int i=0;i<nbcell;i++){
+      D[i]= pd.D[i];
+    }    
+  }
+  
+  ~ParamDiff(){
+      if(D!=NULL){
+      delete [] D;
+      }      
+  }
+	
+ ParamDiff & operator=( ParamDiff pd){
+    nbvar=pd.nbvar;
+    nbcell=pd.nbcell;
+    Coefdiff_value=pd.Coefdiff_value;
+    if(D==NULL){
+      D = new double[nbcell];
+    } 
+    for(int i=0;i<nbcell;i++){
+      D[i]= pd.D[i];
+    }    
+    return *this;
+ }    
+}; 
+
+
+void ParamDiff_Init(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab, ParamDiff & Diff, const char * filename);
+
[…]

### 2015-03-23 code_FVFSHS_2D_matter/hppParam/ParamM1.hpp

@@ -1,0 +1,123 @@
+#ifndef PARAMM1_HPP
+#define PARAMM1_HPP
+
+#include <cmath>
+#include <cstdlib>
+#include <iostream> 
+#include "R2.hpp"
+#include "Data.hpp"
+#include "ClassMesh.hpp"
+#include "FunctionsConnect.hpp"
+#include "Variables.hpp"
+#include <cassert>
+#include <fstream>
+#include <string.h>
+#include <stdlib.h>
+using namespace std;
+
+/** Class: physical parameter for M1 model 
+    - nbvar: number of variable for the model
+    - nbcell: number of cells
+    - eps: table of epsilon coefficient for each cell
+    - sigma: table of sigma coefficient for each cell
+    - eps_value : epsilon value (-100000 if eps is variable)
+    - sig_value : sigma value (-100000 if sig is variable)
+    - OrderAdv : order of remap scheme (MUSCL for the second order)
+**/
+
+
+class ParamM1 {
+public:
+  int nbvar;
+  double *eps;
+  double *sigma;
+  int nbcell;
+  double eps_value;
+  double sig_value;
+  int OrderAdv;
+  
+  ParamM1(){
+    nbvar=3;
+    eps_value=0;
+    sig_value=0;
+    nbcell=0;
+    OrderAdv=0; 
+    eps=NULL;
+    sigma=NULL;
+  }
+  
+  ParamM1(Data & d,Mesh & Mh){ 
+    nbvar=3;
+    nbcell=Mh.nc;
+    OrderAdv=1;
+    eps_value=0;
+    sig_value=0;
+    eps=new double[nbcell];
+    sigma=new double[nbcell];
+  }
+
+  ParamM1(const ParamM1 & pm){
+    nbvar=pm.nbvar;
+    nbcell=pm.nbcell;
+    OrderAdv=pm.OrderAdv;
+    eps_value=pm.eps_value;
+    sig_value=pm.sig_value;
+    eps = new double[nbcell];
+    for(int i=0;i<nbcell;i++){
+      eps[i]= pm.eps[i];
+    }    
+    sigma = new double[nbcell];
+    for(int i=0;i<nbcell;i++){
+      sigma[i]= pm.sigma[i];
+    }  
+  }
+  
+  ~ParamM1(){
+      if(eps!=NULL){
+	delete [] eps;
+      }     
[…]

### 2015-03-23 code_FVFSHS_2D_matter/hppParam/ParamM1Matter.hpp

@@ -1,0 +1,160 @@
+#ifndef PARAMM1M_HPP
+#define PARAMM1M_HPP
+
+#include <cmath>
+#include <cstdlib>
+#include <iostream>
+#include "R2.hpp"
+#include "Data.hpp"
+#include "ClassMesh.hpp"
+#include "FunctionsConnect.hpp"
+#include "Variables.hpp"
+#include <cassert>
+#include <fstream>
+#include <string.h>
+#include <stdlib.h>
+using namespace std;
+
+/** Class: physical parameter for M1 model
+ - nbvar: number of variable for the model
+ - nbcell: number of cells
+ - eps: table of epsilon coefficient for each cell
+ - sigma: table of sigma coefficient for each cell
+ - sigma_A: table of sigma absorption coefficient for each cell
+ - eps_value : epsilon value (-100000 if eps is variable)
+ - sig_value : sigma value (-100000 if sig is variable)
+ - mc2value: value of 1/mc2 for compton scattering
+ - OrderAdv : order of remap scheme (MUSCL for the second order)
+ **/
+
+
+class ParamM1Matter {
+public:
+    int nbvar;
+    double *eps;
+    double *sigma;
+    double *sigmaA ;
+    int nbcell;
+    double eps_value;
+    double sig_value;
+    double sigA_value;
+    double a_value;
+    double mc2value ;
+    int OrderAdv;
+    double TempBB;
+    
+    ParamM1Matter(){
+        nbvar=4;
+        eps_value=0;
+        sig_value=0;
+        sigA_value=0;
+        mc2value=0;
+        a_value=0.;
+        nbcell=0;
+        OrderAdv=0;
+        eps=NULL;
+        sigma=NULL;
+        sigmaA=NULL;
+        TempBB=0.;
+    }
+    
+    ParamM1Matter(Data & d,Mesh & Mh){
+        nbvar=4;
+        nbcell=Mh.nc;
+        OrderAdv=1;
+        eps_value=0;
+        sig_value=0;
+        sigA_value=0;
+        mc2value=0;
+        a_value=0.;
+        TempBB=0.;
+        eps=new double[nbcell];
+        sigma=new double[nbcell];
+        sigmaA=new double[nbcell];
+    }
+    
+    ParamM1Matter(const ParamM1Matter & pm){
+        nbvar=pm.nbvar;
[…]

### 2015-03-23 code_FVFSHS_2D_matter/hppParam/ParamP1.hpp

@@ -1,0 +1,113 @@
+#ifndef PARAMP1_HPP
+#define PARAMP1_HPP
+
+#include <cmath>
+#include <cstdlib>
+#include <iostream> 
+#include "R2.hpp"
+#include "Data.hpp"
+#include "ClassMesh.hpp"
+#include "FunctionsConnect.hpp"
+#include "Variables.hpp"
+#include <cassert>
+#include <fstream>
+#include <string.h>
+#include <stdlib.h>
+using namespace std;
+
+/** Class: physical parameter for P1 model 
+    - nbvar: number of variable for the model
+    - nbcell: number of cells
+    - eps: table of epsilon coefficient for each cell
+    - sigma: table of sigma coefficient for each cell
+    - eps_value : epsilon value (-100000 if eps is variable)
+    - sig_value : sigma value (-100000 if sig is variable)  
+**/
+
+
+class ParamP1 {
+public:
+  int nbvar;
+  double *eps;
+  double *sigma;
+  int nbcell;
+  double eps_value;
+  double sig_value;
+  
+  ParamP1(){
+    nbvar=3;
+    eps_value=0;
+    sig_value=0;
+    nbcell=0;
+    eps=NULL;
+    sigma=NULL;
+  }
+  
+  ParamP1(Data & d,Mesh & Mh){ 
+    nbvar=3;
+    nbcell=Mh.nc;
+    eps_value=0;
+    sig_value=0;
+    eps=new double[nbcell];
+    sigma=new double[nbcell];
+  }
+
+  ParamP1(const ParamP1 & pp){
+    nbvar=pp.nbvar;
+    nbcell=pp.nbcell;
+    eps_value=pp.eps_value;
+    sig_value=pp.sig_value;
+    eps = new double[nbcell];
+    for(int i=0;i<nbcell;i++){
+      eps[i]= pp.eps[i];
+    }    
+    sigma = new double[nbcell];
+    for(int i=0;i<nbcell;i++){
+      sigma[i]= pp.sigma[i];
+    }  
+  }
+  
+  ~ParamP1(){
+      if(eps!=NULL){
+	delete [] eps;
+      }     
+       if(sigma!=NULL){
+	 delete [] sigma;
+      }  
+  }
+	
+ ParamP1 & operator=( ParamP1 pp){
+    nbvar=pp.nbvar;
+    nbcell=pp.nbcell;
+    eps_value=pp.eps_value;
[…]

### 2015-03-23 code_FVFSHS_2D_matter/hppParam/ParamPhys.hpp

@@ -1,0 +1,135 @@
+#ifndef PARAMPHYS_HPP
+#define PARAMPHYS_HPP
+
+#include <cmath>
+#include <cstdlib>
+#include <iostream> 
+#include "ParamP1.hpp"
+#include "ParamP1Matter.hpp"
+#include "ParamDiff.hpp"
+#include "ParamAdvection.hpp"
+#include "ParamEuler.hpp"
+#include "ParamM1.hpp"
+#include "ParamM1Matter.hpp"
+#include "ClassMesh.hpp"
+#include <cassert>
+#include <fstream>
+#include <string.h>
+#include <stdlib.h>
+using namespace std;
+
+
+/** Class : generic class which contain the parameter associated with the model. 
+All the subclass are construct but only the sub class associated with the model use 
+is initialize.
+
+Model is an integer associated with the model. This integer is use to avoid the test 
+with string.
+
+Model :
+-Diffusion : Model = 1
+-Advection : Model = 2
+-P1 : Model = 3
+-P1 with matter : Model = 4
+-Euler : Model = 5
+-M1 : Model = 6
+-M1 with matter : Model = 7
+ **/
+
+class ParamPhysic {
+public:
+  ParamAdvection Adv;
+  ParamDiff Diff;
+  ParamP1 P1;
+  ParamEuler Euler; 
+  ParamM1 M1;
+  ParamM1Matter M1M ;
+  ParamP1Matter P1M;
+  int Model;
+
+   ParamPhysic(){
+     ParamP1();
+     ParamDiff();
+     ParamAdvection();
+     ParamEuler();
+     ParamM1();
+     ParamM1Matter();
+     ParamP1Matter();
+     Model=0; 
+  }
+
+  ParamPhysic(Data & d, Mesh & Mh){
+    if (!strcmp(d.Typemodel,"Diffusion")){
+      ParamDiff Diff_temp(d,Mh);
+      Diff = Diff_temp;
+      Model=1;
+    }
+    if (!strcmp(d.Typemodel,"Advection")){
+      ParamAdvection Adv_temp(d,Mh);
+      Adv = Adv_temp;
+      Model=2;
+    }  
+    if (!strcmp(d.Typemodel,"P1")){
+      ParamP1 P1_temp(d,Mh);
[…]

### 2015-03-23 code_FVFSHS_2D_matter/hppfiles/AnalyticSolutions.hpp

@@ -1,0 +1,73 @@
+#ifndef ANALYTICSOLUTIONS_HPP
+#define ANALYTICSOLUTIONS_HPP
+
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "ClassMesh.hpp"
+#include "math.h"
+#include "Functions.hpp"
+#include "Variables.hpp"
+#include "Data.hpp"
+#include "Flux.hpp"
+#include "Source.hpp"
+#include "ParamPhys.hpp"
+
+///////// general fucntions //////
+
+double SolFon(Data & d,ParamPhysic & Param,Vertex p,double t,Vertex center,int var);
+
+double FinalTime(Data & d,ParamPhysic & Param);
+
+int TraceSolfond(Data & d,ParamPhysic & Param);
+
+double Heaviside(Vertex y);
+
+////////// Euler functions ///////
+
+double SolFonEuler(Data & d,ParamPhysic & Param,Vertex p,double t,Vertex center,int var);
+
+double SolFonEulerAverage(Data & d,Mesh & Mh, ParamPhysic & Param,Vertex p,double t,Vertex center,int numCell,int var);
+
+
+////////// Euler functions ///////
+
+double SolFonM1(Data & d,ParamPhysic & Param,Vertex p,double t,Vertex center,int var);
+
+double CasTestM1Diff(Data & d, ParamPhysic & Param,Vertex p, double t,Vertex center, int var );
+
+double CasTestM1DiffPeriodic(Data & d, ParamPhysic & Param,Vertex p, double t,Vertex center,int var);
+
+double CasTestM1TransportSmooth(Data & d, ParamPhysic & Param,Vertex p, double t,Vertex center,int var);
+
+double CasTestM1Transport(Data & d, ParamPhysic & Param,Vertex p, double t,Vertex center,int var);
+
+
+///////// Diffusion functions //////
+
+double SolFonDiff(Data & d,ParamPhysic & Param,Vertex p,double t,Vertex center);
+
+double SolFonChaleur(Data & d,ParamPhysic & Param,Vertex p,double t,Vertex center);
+
+double SolNeumannChaleur(Data & d,ParamPhysic & Param,Vertex p,double t);
+
+
+//////// Advection functions ////////
+
+double SolFonAdvection(Data & d,ParamPhysic & Param,Vertex p,double t,Vertex center);
+
[…]

### 2015-03-23 code_FVFSHS_2D_matter/hppfiles/BoundaryCondition.hpp

@@ -1,0 +1,94 @@
+#ifndef BOUNDARYCONDITION_HPP
+#define BOUNDARYCONDITION_HPP
+
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "ClassMesh.hpp"
+#include "math.h"
+#include <cstdlib>
+#include "Variables.hpp"
+#include "Data.hpp"
+#include "Functions.hpp"
+#include "AnalyticSolutions.hpp"
+#include "Diagnostics.hpp"
+#include "Flux.hpp"
+#include "Source.hpp"
+#include "ParamPhys.hpp"
+
+//////// General functions ///////////
+
+R2 Norext(Data & d,Mesh & Mh, int numGr);
+
+void BoundaryCondition(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time);
+
+//////// Advection functions ////////
+
+void BoundaryConditionAdvection(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time);
+
+void BCDirichlet_SolExact_Advection(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time);
+
+/////// Diffusion functions /////////
+
+void BoundaryConditionDiff(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time);
+
+void BCDirichlet_SolExact_diff(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time);
+
+void BC_Periodic_diff(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time);
+
+/////////// P1 functions ////////////
+
+void BoundaryConditionP1(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time);
+
+void BCNeumann_P1(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time);
+
+void BC_Periodic_P1(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time);
+
+void BCDirichlet_P1(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time);
+
+/////////// P1 Matter functions ////////////
+
+void BoundaryConditionP1Matter(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time);
+
+void BC_Neumann_P1Matter(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time);
+
[…]

### 2015-03-23 code_FVFSHS_2D_matter/hppfiles/ClassMesh.hpp

@@ -1,0 +1,496 @@
+#ifndef CLASSMESH_HPP
+#define CLASSMESH_HPP
+
+#include <cmath>
+#include <cstdlib>
+#include <iostream> 
+#include "R2.hpp"
+#include <cassert>
+#include <fstream>
+#include "Variables.hpp"
+using namespace std;
+/**
+Class : Vertex
+
+contains:
+- lab : Vertex label (uselful for different sub domain)
+- R2 which correspond to the vertex
+
+**/
+class Vertex : public R2{
+public:
+  int lab;
+  Vertex(){ R2(); lab=0; }
+
+  Vertex(R2 P, int r,Data d){
+    vectorflux vec(d);
+    x=P.x;
+    y=P.y; 
+    lab=r;
+  }
+  Vertex(R2 P,Data d){
+    vectorflux vec(d);
+    x=P.x;
+    y=P.y;
+    lab=0;
+  }
+  Vertex(Data d){
+    R2(0,0);
+    lab=0;
+  }
+  ~Vertex(){}
+
+  Vertex(const Vertex & v){
+    lab=v.lab;
+    x=v.x;
+    y=v.y;
+  }
+
+   Vertex & operator =( Vertex  v){
+    lab=v.lab;
+    x=v.x;
+    y=v.y;
+    return *this; 
+  }
+  
+};
+
+/**
+Class : cell
+
+- nbnodelocal : number of vertex in the cell
+- vertices : table of vertex
+- numver : local intex of vertex
+- area : area of the cell
+- normevertex : table of nodal normal njr for the cell j
+- lvertex : table of nodal lenght ljr for the cell j
+- normeedge : table of edge normal njk for the cell j
+- ledge : table of edge normal ljk for the cell j
+- lab : label of the cell (for subdomain)
+
+**/
+
+class cell : public R2{
+public:
+  int nbnodelocal;
+  Vertex *vertices;
+  int *numver;
+  R area;
+  Vertex centercell;
+  R2 *normvertex;     
+  double *lvertex;          
+  R2 *normedge;       
+  double *ledge;
+  int lab;
+  cell(){
+    nbnodelocal=0;
+    vertices=NULL;
+    area=0;
+    normvertex=NULL;
+    lvertex=NULL;
+    normedge=NULL;
+    ledge=NULL;
+    numver=NULL;
+    lab=0;
+  };
[…]

### 2015-03-23 code_FVFSHS_2D_matter/hppfiles/Data.hpp

@@ -1,0 +1,243 @@
+#ifndef DATA_HPP
+#define DATA_HPP
+
+#include <cmath>
+#include <cstdlib>
+#include <iostream> 
+#include "R2.hpp"
+#include <cassert>
+#include <fstream>
+#include <string.h>
+#include <stdlib.h>
+using namespace std;
+
+/**
+ @brief Class: this class contains the parameters of the code.
+**/
+
+class Data {
+  public :
+  /**Number of cells in the x direction**/
+  int Nx;
+  /**Number of cells in the y direction **/
+  int Ny;
+  /** Lenght of the domain in the x direction **/
+  float Tx;
+  /** Lenght of the domain in the y direction **/
+  float Ty;
+  
+  /** Scheme number **/
+  int scheme;
+   /** Type of scheme (N for nodal scheme, E for edge scheme) **/
+  char Typescheme;
+  /** Test case number **/
+  int nTest; 
+  /** Final time**/
+  float Tf;
+  /** CFL **/
+  int Total_order;
+  /** CFL **/
+  float CFL;
+  
+  /** Mesh name **/
+  char *NameMesh;  
+  /** the number of variable that we plot **/
+  char *NumVar;
+  /** Suffix for the output file **/
+  char *suffixe;
+  
+  /** Model :
+   - Diffusion : diffusion equation
+   - P1 : P1 model
+   - M1 : M1 model
+   - M1Matter : M1 model with matter
+   - Advection : advection
+   - Euler : Euler
+   - P1Matter : P1 model with matter**/
+  char *Typemodel;
+  
+  /** Time discretization
+      - E : explicit
+      - S : Semi-implicit.**/
+  char Typetime;
+
+
+  /** Mesh type
+   - T : triangular
+   - Q : quandrangular **/
+  char Typemesh;
+
+  
+  /** Time step for the plot **/
+  float dtAnim;
+  /** Plot solutions: yes (y) or not (n)**/
+  char Anim;
+  
+  /** plot using the cell (N) or the center of the cell (C)**/
+  char Typewrite;
+  /** plot in 1D or 2D **/
[…]

### 2015-03-23 code_FVFSHS_2D_matter/hppfiles/Diagnostics.hpp

@@ -1,0 +1,34 @@
+#ifndef DIAGNOSTICS_HPP
+#define DIAGNOSTICS_HPP
+
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "ClassMesh.hpp"
+#include "math.h"
+#include "Functions.hpp"
+#include "Variables.hpp"
+#include "Data.hpp"
+#include "Flux.hpp"
+#include "Source.hpp"
+#include "ParamPhys.hpp"
+
+double NormLP_Error_One_variable(Data & d, Mesh & Mh,variable & v,ParamPhysic & Param,double p,double t,int var);
+
+double NormLP_Error_All_variables_Euler(Data & d, Mesh & Mh,variable & v,ParamPhysic & Param,double p,double t);
+
+double NormLP_Error_All_variables(Data & d, Mesh & Mh,variable & v,ParamPhysic & Param,double p,double t);
+
+double NormLP_Stability(Data & d, Mesh & Mh,variable & v,ParamPhysic & Param,double p);
+
+double Mass(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,double time); 
+
+void Diagnostics_Quantities(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,int nt,double time); 
+
+double Diagnostics_Error(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,double time, double p);
+
+//////////// Diagnostics Euler ///////
+
+double NormLP_Velocity(Data & d, Mesh & Mh,variable & v,ParamPhysic & Param,double p,double t);
+
+#endif

### 2015-03-23 code_FVFSHS_2D_matter/hppfiles/Flux.hpp

@@ -1,0 +1,145 @@
+#ifndef FLUX_HPP
+#define FLUX_HPP
+#include <iostream>
+#include <cmath>
+#include <cstdlib>
+#include "Variables.hpp"
+#include "ClassMesh.hpp"
+#include "Functions.hpp"
+#include "Initialisation.hpp"
+#include "Functionsinit.hpp"
+#include "AnalyticSolutions.hpp"
+#include "Diagnostics.hpp"
+#include "ParamPhys.hpp"
+
+
+
+vectorflux ChoiceFluxE(Data & d ,int numCell,Mesh &  Mh, variable & v, TabConnecInv & tab,ParamPhysic & Param);
+
+vectorflux FluxVF4Diff(Data & d,int numCell, Mesh & Mh,  variable & v,  TabConnecInv & tab,ParamPhysic & Param);
+
+vectorflux FluxEdgeAdv(Data & d,int numCell,Mesh &  Mh,variable & v, TabConnecInv & tab,ParamPhysic & Param);
+
+vectorflux ChoiceFluxN(Data & d ,int numCell,Mesh & Mh, variable & v,TabConnecInv & tab,ParamPhysic & Param,R2 * ur);
+
+R2 SolveurNodal(Data & d,int numGr,Mesh & Mh, variable & v, TabConnecInv & tab,ParamPhysic & Param);
+
+
+///////// flux d'advection/////////
+
+vectorflux FluxVertexadv(Data & d,int numCell, Mesh &  Mh, variable & v,TabConnecInv & tab,ParamPhysic & Param);
+
+
+/////////////// flux de diffusion/////////
+
+
+vectorflux FluxVertexDiff(Data & d,int numCell,Mesh &  Mh,variable & v, TabConnecInv & tab,ParamPhysic & Param,R2 * ur);
+
+vectorflux FluxVertexNlDiff(Data & d,int numCell,Mesh &  Mh,variable & v, TabConnecInv & tab,ParamPhysic & Param,R2 * ur);
+
+double FluxadvectionDiff(Data & d,int numCell,int r,Mesh &  Mh,variable & v, TabConnecInv & tab,ParamPhysic & Param,R2 a,R2* ur);
+
+void MatrixDiff(Data & d,Mesh & Mh,variable & v, TabConnecInv & tab,ParamPhysic & Param,int numGr,double &a11,double &a12,double &a21,double &a22,double &b1,double &b2); 
+
+////////////// flux du modèle P1//////////////////
+
+
[…]

### 2015-03-23 code_FVFSHS_2D_matter/hppfiles/Functions.hpp

@@ -1,0 +1,37 @@
+#ifndef FUNCTIONS_HPP
+#define FUNCTIONS_HPP
+
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "ClassMesh.hpp"
+#include "math.h"
+#include "Variables.hpp"
+#include "Functionsgeo.hpp"
+#include "FunctionsConnect.hpp" 
+
+#include "ParamPhys.hpp"
+
+
+
+void WriteDataToMain(Data & d,ParamPhysic & Param);
+
+void Tri(int * tableau, int longueur);
+
+void Tridouble(double * tableau, int longueur);
+
+void echanger(int * tableau, int i, int j);
+
+void echangerd(double * tableau, int i, int j);
+
+double positivepart(double x);
+
+
+double Valabs(double x);
+
+
+
+#endif
+      
+	  
+	 

### 2015-03-23 code_FVFSHS_2D_matter/hppfiles/FunctionsAdvection.hpp

@@ -1,0 +1,34 @@
+#ifndef FUNCTIONSADVECTION_HPP
+#define FUNCTIONSADVECTION_HPP
+#include <iostream>
+#include <cmath>
+#include <cstdlib>
+#include "Variables.hpp"
+#include "ClassMesh.hpp"
+#include "Functions.hpp"
+#include "Initialisation.hpp"
+#include "Functionsinit.hpp"
+#include "Tensor.hpp"
+#include "R2.hpp"
+#include "ParamPhys.hpp"
+
+
+int EnsembleR(Data & d,Mesh & Mh, variable & v,ParamPhysic & Param,int r,int numCell, R2 a);
+
+double variablekr(Data & d,Mesh & Mh, variable & v,int var,TabConnecInv & tab,ParamPhysic & Param,int numCell,int numGr, R2 a,int ordre);
+
+double VertexUpwind(Data & d,Mesh & Mh, variable & v,int var,TabConnecInv & tab,ParamPhysic & Param,int numCell,int r, R2 a);
+
+double EdgeUpwind(Data & d,Mesh & Mh, variable & v,int var,TabConnecInv & tab,ParamPhysic & Param,int numCell,int k,int r, R2 a);
+
+R2 Gradiant(Data & d,Mesh & Mh,variable & v,int var,TabConnecInv & tab,ParamPhysic & Param,int numGr);
+
+double VertexSlope(Data & d,Mesh & Mh,variable & v,int var,TabConnecInv & tab,ParamPhysic & Param,int numCell,R2 Grad);
+
+double EdgeSlope(Data & d,Mesh & Mh,variable & v,int var,TabConnecInv & tab,ParamPhysic & Param,int numCell,R2 Grad);
+
+double Limiter(ParamPhysic & Param,double m);
+
+double InterLineVertex(Data d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamPhysic & Param,int var,int ordre,int j,int r);
+
+#endif

### 2015-03-23 code_FVFSHS_2D_matter/hppfiles/FunctionsConnect.hpp

@@ -1,0 +1,42 @@
+#ifndef FUNCTIONSCONNECT_HPP
+#define FUNCTIONSCONNECT_HPP
+
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "ClassMesh.hpp"
+#include "math.h"
+
+/** Structure qui contient les mailles associées a un noeud
+    @brief Structure qui contient les mailles associées a un noeud**/
+struct TabCellLocal{
+  int taille;
+  int *TabCell;
+};
+
+/** Structure pour la table de connectivité 
+@brief Structure pour la table de connectivité **/
+ struct TabConnecInv{
+  int nbvertex;
+  TabCellLocal *TabInv;
+};
+
+void CellLocal( Mesh & Mh,int numnode, TabCellLocal & CellOfNode);
+
+int InverseEdge( Mesh & Mh,int node1,int node2,int numcell,TabConnecInv & tab);
+
+int tabVF9(Mesh & Mh, TabConnecInv & tab,int *& tabVF9,int cell);
+
+int PresenceNodetoTab(int * tab,int i,int taille); 
+
+void CreateTabInv(Mesh & Mh, TabConnecInv & tab);
+
+int NodeGtoL(Mesh & Mh,int  numCell,int numNode);
+
+double StepMesh(Mesh & Mh);
+
+int NextNodeLocal(Mesh & Mh,int r);
+
+int PreviousNodeLocal(Mesh & Mh,int r);
+
+#endif

### 2015-03-23 code_FVFSHS_2D_matter/hppfiles/Functionsgeo.hpp

@@ -1,0 +1,32 @@
+#ifndef FUNCTIONSGEO_HPP
+#define FUNCTIONSGEO_HPP
+
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "ClassMesh.hpp"
+#include "math.h"
+#include "Variables.hpp"
+#include "Data.hpp"
+#include "FunctionsConnect.hpp" 
+#include "ParamPhys.hpp"
+R2 GravityCenter(cell cc,int nbnode);
+
+int centerdomain(Data & d,Mesh & Mh);
+
+double AverageQuantity(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamPhysic & Param,int numGr,int var);
+
+double Vjr(Mesh & Mh,int j,int r);
+
+double Vr(Mesh & Mh,int r, TabConnecInv & tab);
+
+double geomCorrection(Data & d,Mesh & Mh,int j);
+
+cell ControlVolume(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,int numGr);
+
+cell SubControlVolume(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,int numGr,int j);
+
+void OneLayerStencilNodeQ(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,int *& Stencil,int NStencil,int numGr);
+
+void TwoLayerStencilNodeQ(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,int *& Stencil,int NStencil,int numGr);
+#endif

### 2015-03-23 code_FVFSHS_2D_matter/hppfiles/Functionsinit.hpp

@@ -1,0 +1,21 @@
+#ifndef FUNCTIONSINIT_HPP
+#define FUNCTIONSINIT_HPP
+
+#include <iostream>
+#include <cmath>
+#include <cassert>
+#include "ClassMesh.hpp"
+#include "math.h"
+#include "Variables.hpp"
+#include "Functionsgeo.hpp"
+#include "Functions.hpp"
+#include "ParamPhys.hpp"
+
+double CFL(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamPhysic & Param);
+
+
+
+
+
+
+#endif

### 2015-03-23 code_FVFSHS_2D_matter/hppfiles/HOfunctions.hpp

@@ -1,0 +1,30 @@
+#ifndef HOFUNCTIONS_HPP
+#define HOFUNCTIONS_HPP
+#include "UsualMesh.hpp"
+#include "Data.hpp"
+#include "ClassMesh.hpp"
+#include "Variables.hpp"
+#include "svd_solver.hpp"
+#include "ParamEuler.hpp"
+
+using namespace std;
+
+void ConstructionLSMatrix(Data & d, Mesh & Mh, variable & v,TabConnecInv & tab,ParamEuler & Euler, LSProblem & LS,int PolynomialOrder,int numGr);
+
+void ConstructionLSRHS(Data & d, Mesh & Mh, variable & v,TabConnecInv & tab,ParamEuler & Euler, LSProblem & LS,int PolynomialOrder,int numGr);
+
+void SolverLSProblem(Data & d, Mesh & Mh, variable & v,TabConnecInv & tab,ParamEuler & Euler, LSProblem & LS,int PolynomialOrder,int numGr);
+
+void ConstructionLSStencil(Data & d, Mesh & Mh, variable & v,TabConnecInv & tab,ParamEuler & Euler, LSProblem & LS,int PolynomialOrder,int numGr);
+
+void LSInit(Data & d, Mesh & Mh, variable & v,TabConnecInv & tab,ParamEuler & Euler, LSProblem & LS,int PolynomialOrder,int numGr);
+
+void QuadratureUnitSquare(double & p, double & w, int nb, int Order);
+
+double Mapping(Data & d, Mesh & Mh,R2 & p, double & J,double px, double py,cell & C);
+
+double ComputeMatrixcoefficent(Data & d, Mesh & Mh,int d1, int d2, int numCell,int numGr,int Order);
+
+void LocalDegreePolynomial(int & d1, int & d2, int j,int PolynomialOrder);
+
+#endif

### 2015-03-23 code_FVFSHS_2D_matter/hppfiles/R2.hpp

@@ -1,0 +1,124 @@
+// ORIG-DATE:     Dec 2007
+// -*- Mode : c++ -*-
+//
+// SUMMARY  :  Model of $\mathbb{R}^2$    
+// USAGE    : LGPL      
+// ORG      : LJLL Universite Pierre et Marie Curi, Paris,  FRANCE 
+// AUTHOR   : Frederic Hecht
+// E-MAIL   : frederic.hecht@ann.jussieu.fr
+//
+
+/*
+ 
+ This file is part of Freefem++
+ 
+ Freefem++ is free software; you can redistribute it and/or modify
+ it under the terms of the GNU Lesser General Public License as published by
+ the Free Software Foundation; either version 2.1 of the License, or
+ (at your option) any later version.
+ 
+ Freefem++  is distributed in the hope that it will be useful,
+ but WITHOUT ANY WARRANTY; without even the implied warranty of
+ MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ GNU Lesser General Public License for more details.
+ 
+ You should have received a copy of the GNU Lesser General Public License
+ along with Freefem++; if not, write to the Free Software
+ Foundation, Inc., 51 Franklin St, Fifth Floor, Boston, MA  02110-1301  USA
+
+ Thank to the ARN ()  FF2A3 grant
+ ref:ANR-07-CIS7-002-01 
+ */
+#ifndef R2_HPP
+#define  R2_HPP
+#include <cmath>
+#include <cstdlib>
+#include <iostream>
+// Definition de la class R2 
+//  sans compilation separe toute les fonctions 
+// sous defini dans ce R2.hpp avec des inline 
+//  
+// definition R (les nombres reals)
+// remarque la fonction abort est defini dans 
+// #include <cstdlib> 
+
+// The class R2
+
+class R2 {
+public:  
+  typedef double R;
+  static const int d=2;
+
+  R x,y;  // declaration de membre 
+  // les 3 constructeurs ---
+  R2 () :x(0.),y(0.) {} // rappel : x(0), y(0)  sont initialiser via le constructeur de double 
+  R2 (R a,R b):x(a),y(b)  {}
+  R2 (const R * a):x(a[0]),y(a[1])  {}
+  R2 ( R * a):x(a[0]),y(a[1])  {}
+
[…]

### 2015-03-23 code_FVFSHS_2D_matter/hppfiles/Tensor.hpp

@@ -1,0 +1,80 @@
+#ifndef TENSOR_HPP
+#define TENSOR_HPP
+#include <cassert>
+#include <iostream>
+#include <cmath>
+#include<cstdlib>
+#include "Data.hpp"
+#include "ClassMesh.hpp"
+#include "Functions.hpp"
+#include "Variables.hpp"
+
+
+class tensor {
+public:
+  double ten[2][2];
+  int num;
+  char type;
+
+  tensor(){
+  
+    num=0;
+    type='0';
+    ten[0][0]=0.;
+    ten[0][1]=0.;
+    ten[1][0]=0.;
+    ten[1][1]=0.;
+  }
+  
+  tensor(Data d,char c){
+    if(c=='h' || c=='s'){
+    type=c;
+    }
+    else{ cout <<"probleme dans le type de tenseur demander"<<endl;exit(1);}
+    num =0;
+  
+    ten[0][0]=0.;
+    ten[0][1]=0.;
+    ten[1][0]=0.;
+    ten[1][1]=0.;
+    
+  }
+  
+  
+  tensor(const tensor & t){
+    num=t.num;
+    type=t.type;
+    
+    for(int i=0;i<2;i++){
+      for(int j=0;j<2;j++){
+	ten[i][j]=t.ten[i][j];
+	
+      }
+      
+    }
+  }
+  
+  ~tensor(){}
+     
+	
+ tensor & operator=( tensor t){
+    num=t.num;
+    type=t.type;
+    
+    for(int i=0;i<2;i++){
+      for(int j=0;j<2;j++){
+	ten[i][j]=t.ten[i][j];
+      }
+      
+    }
+    
+
+    return *this;
+ } 
+
+};   
+
+tensor inittensor(Data & d,Mesh & Mh,variable & v, TabConnecInv & tab,char c,int numGr,int numCell);
+
+
+#endif

### 2015-03-23 code_FVFSHS_2D_matter/hppfiles/TimeDiscret.hpp

@@ -1,0 +1,25 @@
+#ifndef TIMEDISCRET_HPP
+#define TIMEDISCRET_HPP
+#include <cmath>
+#include <cstdlib>
+#include <iostream>
+#include "Flux.hpp"
+#include "Source.hpp"
+#include "Initialisation.hpp"
+#include <fstream>
+#include "Functions.hpp"
+#include "ClassMesh.hpp"
+#include "Variables.hpp"
+#include "WriteData.hpp"
+#include "ParamPhys.hpp"
+
+using namespace std;
+
+void ExplicitDiscret(Data & d,Mesh & Mh, variable & v,TabConnecInv & TConnectInv, ParamPhysic & Param,double dt,int & ntAnim, double & time);
+
+
+void SemiImplicit(Data & d,Mesh & Mh, variable & v,TabConnecInv & TConnectInv, ParamPhysic & Param,double dt,int & ntAnim, double & time);
+
+int SIschemeImplemented(Data & d,Mesh & Mh, variable & v,TabConnecInv & TConnectInv, ParamPhysic & Param);
+
+#endif

### 2015-03-23 code_FVFSHS_2D_matter/hppfiles/UsualMesh.hpp

@@ -1,0 +1,31 @@
+#ifndef USUALMESH_HPP
+#define USUALMESH_HPP
+#include "ClassMesh.hpp"
+#include "Variables.hpp"
+#include "Data.hpp"
+
+
+
+Mesh ChoiceMesh(Data & d);
+
+Mesh CartesianMeshT(Data & d);
+
+Mesh RandomCartesianMeshT(Data & d);
+
+Mesh KershawMesh(Data & d);
+
+Mesh CartesianMesh(Data & d);
+
+Mesh RandomCartesianMesh(Data & d);
+
+Mesh SmoothCartesianMesh(Data & d);
+
+Mesh CheckMesh(Data & d);
+
+Mesh DoubleSquareMeshQ(Data & d);
+
+#endif
+
+
+
+ 

### 2015-03-23 code_FVFSHS_2D_matter/hppfiles/Variables.hpp

@@ -1,0 +1,159 @@
+#ifndef VARIABLES_HPP
+#define VARIABLES_HPP
+#include <cassert>
+#include <iostream>
+#include <cmath>
+#include <cstdlib>
+#include "Data.hpp"
+
+using namespace std;
+
+
+
+class variable {
+public:
+  int nbvar;
+  int nbcell;
+  double **var; 
+
+  variable(){
+    nbvar=0;
+    nbcell=0;
+    var=NULL;
+  }
+  
+  variable(Data d,int nc,int nv){
+    nbvar=0;
+    if(!strcmp(d.Typemodel,"Diffusion")){nbvar=1;}
+    if(!strcmp(d.Typemodel,"Advection")){nbvar=1;}
+    if(!strcmp(d.Typemodel,"P1")) {nbvar=3;}
+    if(!strcmp(d.Typemodel,"Euler")) {nbvar=4;}
+    if(!strcmp(d.Typemodel,"M1")) {nbvar=3;}
+    if(!strcmp(d.Typemodel,"P1Matter")) {nbvar=4;}
+    if(!strcmp(d.Typemodel,"M1Matter")) {nbvar=4;}
+
+    nbcell=nc;
+     
+    var = new double*[nbvar];
+    for(int i=0;i<nbvar;i++){
+      var[i]= new double[nbcell];
+    }
+  
+  }
+
+  variable(const variable & v){
+    nbvar=v.nbvar;
+    nbcell=v.nbcell;
+  
+    var = new double*[nbvar];
+    for(int i=0;i<nbvar;i++){
+      var[i]= new double[nbcell];
+    }  
+    
+    for(int j=0;j<nbcell;j++){
+      for(int i=0;i<nbvar;i++){
+	var[i][j]=v.var[i][j];
+      }
+    }
+  }
+  
+  ~variable(){
+    if(var!=NULL){
+      for(int i=0;i<nbvar;i++){
+	if (var[i]!=NULL){
+	  delete [] var[i];}
+	
+      }
+    delete [] var;
+    }
+  }
+    
+	
+ variable & operator=(variable v){
+    nbvar=v.nbvar;
+    nbcell=v.nbcell;
+    
+    nbvar=v.nbvar;
+    nbcell=v.nbcell;
+    if(var==NULL){
+    var = new double*[nbvar];
+    }
+   
+    for(int i=0;i<nbvar;i++){
+      if(var[i]==NULL){
[…]

### 2015-03-23 code_FVFSHS_2D_matter/hppfiles/WriteData.hpp

@@ -1,0 +1,37 @@
+#ifndef WRITEDATA_HPP
+#define WRITEDATA_HPP
+
+#include <iostream>
+#include <cassert>
+#include "Data.hpp"
+#include "Variables.hpp"
+#include "ClassMesh.hpp"
+#include "Flux.hpp"
+
+using namespace std;
+
+void SaveData(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,int ntAnim);
+
+void SaveOneData(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,int Num,int ntAnim);
+
+void  SaveOneData1D(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,int Num,int ntAnim);
+
+void SaveOneDatacentercell(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,int Num,int ntAnim);
+
+void SaveMesh(Data & d,Mesh & Mh);
+
+void SaveFonction2D(Data & d,Mesh & Mh,ParamPhysic & Param,float t,Vertex c,int var);
+
+void SaveFonction2DEuler(Data & d,Mesh & Mh,ParamPhysic & Param,float t,Vertex c,int var);
+
+void SaveFonction1D(Data & d,Mesh & Mh,ParamPhysic & Param,float t,Vertex c,int var);
+
+void SaveFonction(Data & d,Mesh & Mh,ParamPhysic & Param,float t,Vertex c);
+
+void SaveInterEner(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,int ntAnim);
+
+void SaveRestart(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,int nstep, double time);
+
+void LoadRestart(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param, double & InitTime);
+
+#endif

### 2015-03-26 Corrected_version.tex
Gros changements jusqu'à début p34

@@
 
-We denote by $\V^{\eps}(t)=\left(p^{\eps}(x_j,t),
-u^{\eps}(x_j,t)\right)_{j\in \mathbb Z}$ the interpolation of the 
-solution of the hyperbolic heat equations $P^\eps$ and by
+We denote by $\V^{\eps}(t,x)=\left(p^{\eps}(x,t),
+u^{\eps}(x,t)\right)$ the solution of the hyperbolic heat equations $P^\eps$ and by
 $\V^{\eps}_h(t)=
-\left(p_j^{\eps}(t), u_j^{\eps}(t)   \right)_{j\in \mathbb Z}$ the
-solution of the JL-(b) scheme $P_h^\eps$. Similarly  we  reconstruct
+\left( \sum_{j\in \mathbb Z} p_j^{\eps}(t) {1}_{\Omega_j} ,  \sum_{j\in \mathbb Z} u_j^{\eps}(t) {1}_{\Omega_j} \right)$ the solution of the JL-(b) scheme $P_h^\eps$. Similarly  we  reconstruct
 similar quantities from the diffusion scheme: it yields 
-$\W^\eps(t)=\left(p(x_j,t),\varepsilon v(x_j,t)\right)_{j\in \mathbb Z}$ 
-which is the interpolation of the 
+$\W^\eps(t,x)=\left(p(x,t),\varepsilon v(x,t)\right)$ 
+which is the 
 solution of the diffusion limit
 $P^0$ (\ref{difffff})-(\ref{eq:diff-v}),
- and  $\W_h^\eps(t)=\left( p_j(t),  
-\varepsilon v_j(t)   \right)_{j\in \mathbb Z}$ which is
+ and  $\W_h^\eps(t)= \left( \sum_{j\in \mathbb Z} p_j(t) {1}_{\Omega_j} ,
+\varepsilon \sum_{j\in \mathbb Z} v_j(t)  {1}_{\Omega_j} \right)$ which is
 the
@@
 \|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
-\leq \sqrt{h\eps + 2t + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} }
+\leq \sqrt{h\eps + 2T + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} }
 \sqrt \frac{h}\eps 
@@
 \|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
-\leq \sqrt{h\eps + 2t + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} } \sqrt{ \frac{h}{\eps}}
+\leq \sqrt{h\eps + 2T + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} } \sqrt{ \frac{h}{\eps}}
 \| \V^{\eps}( 0)
@@
 \begin{equation*}
-\|\V_h^{\eps}-\W^\eps_h\|_{L^2([0,T]\times\mathbb R)} \leq  \eps e^{t/2} \bigg(  C_0h + \sqrt{ \frac{1}{\sigma C_{\mathcal{M}} } ( \frac12 + \frac{1}{\sigma^2} )} \|p_0\|_{H^2(\mathbb{R})} \bigg) ,
+\|\V_h^{\eps}-\W^\eps_h\|_{L^2([0,T]\times\mathbb R)} \leq  \eps e^{T/2} \bigg(  C_0h + \sqrt{ \frac{1}{\sigma C_{\mathcal{M}} } \big( \frac12 + \frac{1}{\sigma^2} \big) } \|p_0\|_{H^2(\mathbb{R})} \bigg) ,
 \end{equation*}
@@
 $
-\|\V_h^{\eps}-\W^\eps_h\|_{L^2([0,T]\times\mathbb{R})} \leq \eps e^{t/2} \big(  C_0h + \sqrt{ \frac{1}{\sigma C_{\mathcal{M}} } ( \frac12 + \frac{1}{\sigma^2} )} \|p_0\|_{H^2(\mathbb{R})} \big)$. 
+\|\V_h^{\eps}-\W^\eps_h\|_{L^2([0,T]\times\mathbb{R})} \leq \eps e^{T/2} \big(  C_0h + \sqrt{ \frac{1}{\sigma C_{\mathcal{M}} } ( \frac12 + \frac{1}{\sigma^2} )} \|p_0\|_{H^2(\mathbb{R})} \big)$. 
 The proof is ended.
@@
 \begin{equation}\label{ine3}
-\| p^\epsilon-p\|_{   L^\infty([0,T];H^n(\Omega))  }+
+\textcolor{red}{\| p^\epsilon-p\|_{   L^\infty([0,T];H^n(\Omega))  }+
 \| \mathbf{v} 
@@
 \|p_0 \|_{H^{3+n}(\Omega)},
-\qquad n \in \mathbb N.
+\qquad n \in \mathbb N.}
 \end{equation}
@@
 $\sum_r \alj$ is  symetric positive by definition of the $\alj$.
-
 \subsection{Definition of $\mathbf{DA}_h^\eps$}
@@
 \end{equation*}
-By definition  there exists  a constant $C>0$ such that 
+By definition  there exists  a constant $C_{\mathcal{M}}>0$ such that 
 \begin{equation} \label{eq:d7}
-l_{jr}\leq Ch , \qquad \forall j,r.
+\left\{
+\begin{aligned}
+&l_{jr}\leq C_{\mathcal{M}}h , \qquad \forall j,r , \\
+&|\Omega_j| \leq C_{\mathcal{M}}^2 h^2 , \qquad \forall j .
+\end{aligned}
+\right. 
 \end{equation}
@@
 
-\item  The matrix $B_r$ is positive and that there exists a
+\item  The matrix $B_r$ is positive and there exists a
 constant $\alpha >0 $ independent of r such that 
@@
 \begin{itemize}
-\item $\mathbf V_h^\eps=\left(p^\eps_j, \uu^\eps_j \right)_
-{j\in {\rm Cells}}$ is the solution of $\mathbf P_h^\eps$.
+\item $\mathbf V_h^\eps=\left(  \sum_{j\in Cells} p^\eps_j 1_{\Omega_j} , \sum_{j\in Cells} \uu^\eps_j  1_{\Omega_j} \right) $ is the solution of $\mathbf P_h^\eps$.
 \item 
-$\mathbf V^\eps=\left(p^\eps(\x_j), \uu^\eps(\x_j)  \right)_
-{j\in {\rm Cells}}$ is the solution of $\mathbf P^\eps$,
-\item $\mathbf W_h^\eps=\left(p^\eps_j, \uu^\eps_j \right)_
-{j\in {\rm Cells}}$ is the solution of $\mathbf{DA}_h^\eps$.
+$\mathbf V^\eps=\left(p^\eps, \uu^\eps  \right)$ is the solution of $\mathbf P^\eps$,
+\item $\mathbf W_h^\eps=\left(  \sum_{j\in Cells}  p^\eps_j 1_{\Omega_j} ,  \sum_{j\in Cells}  \uu^\eps_j  1_{\Omega_j}  \right) $ is the solution of $\mathbf{DA}_h^\eps$.
 Notice that an abuse of notations is been made with the solution
 of $\mathbf P_h^\eps$.
-\item $\mathbf W^\eps= \left(p(\x_j),-\frac\eps\sigma \nabla p(\x_j)  \right)_
-{j\in {\rm Cells}} $ is the solution of $\mathbf P^0$.
+\item $\mathbf W^\eps= \left( p ,-\frac\eps\sigma \nabla p  \right) $ is the solution of $\mathbf P^0$.
 \end{itemize}
@@
 _{ L^2([0,T]\times L^2(\Omega)   ) } \leq C \eps.
+\end{equation}
+The initialization stage yields 
+\begin{equation}\label{constant_init}
+\left\{
+\begin{aligned}
+&\| \mathbf{V}_0 - \mathbf{V}^{\eps}_h(0)\|_{L^2(\Omega)} \leq C_0 h \|  \mathbf V ^\eps_0 \|_  { H^1(\Omega)  } ,\\
+&\| \mathbf{W}_0 - \mathbf{W}^{\eps}_h(0)\|_{L^2(\Omega)} \leq C_0 h \|  \mathbf W ^\eps_0 \|_  { H^1(\Omega)  } .
+\end{aligned}
+\right.
 \end{equation}
@@
 \frac{\sigma}{\eps^2}\vert\vert \uu_r^{\eps} \vert\vert_{L^2([0,T]\times \Omega)}\leq
-C 
+\frac{1}{\alpha}
 \vert\vert
-V^{\eps}_h(0)\vert\vert_{L^2( \Omega)}, \qquad C>0,
+V^{\eps}_h(0)\vert\vert_{L^2( \Omega)},
 \end{equation}
@@
 \int_0^T\sum_j \sum_r
-l_{jr}(\njr,(\uj^\eps-\ur^\eps))^{2} dt\leq C  \eps \vert\vert
-\mathbf V^{\eps}_h(0)\vert\vert^2_{L^2( \Omega)}. 
-\qquad C>0.
+l_{jr}(\njr,(\uj^\eps-\ur^\eps))^{2} dt\leq \eps \vert\vert
+\mathbf V^{\eps}_h(0)\vert\vert^2_{L^2( \Omega)} .
 \end{equation}
@@
 \begin{proposition}[Convergence]\label{ein_prosit}
-There exists a constant $C(T, \sigma)>0$ 
-      such that the following estimate holds
+The following estimate holds
 \begin{equation} \label{eq:veps2}
 \|\V^{\eps}_h-\V^{\eps}\|_{L^\infty( [0,T]\times L^2  (\Omega) )}\leq
-C(T, \sigma)\|  \mathbf V ^\eps (0) \|_  { H^3(\Omega)  }
-\sqrt{\frac h \eps}.
-\end{equation}
+C \sqrt{\frac h \eps},
+\end{equation}
+where
+\begin{equation*}
+\begin{aligned}
+C = \|\mathbf{V}_0^\eps\|_{H^3(\Omega)}  \sqrt{2+T+\sigma } \: \hbox{max}\bigg\{ & \:  \frac{ C_{\mathcal{M}}^2 }{2}\sqrt{\frac{P}{C_1}} \bigg( \frac1{\alpha} + PC_{\delta}^2 \bigg) \: , \: \frac{C_{\mathcal{M}}^3P}{2C_1}  , \\
+&  C_{\mathcal{M}} C_{\delta} P \bigg( \frac{1+C_0^2h^2}{C_1} + C_{\delta}  + h \bigg) \: , \: C_0^2 + C_{\mathcal{M}}^2  P C_{\delta}\bigg( 1 + \frac{2C_{\mathcal{M}}^2P}{C_1\alpha} \bigg) \: \bigg\}^{\frac12} .
+\end{aligned}
+\end{equation*}
+The constants $P$, $C_{\delta}$, $C_{\mathcal{M}}$, $\alpha$, $C_0$ and $C_1$ are defined respectively in \eqref{nbmr}, (\ref{const_delta1}-\ref{const_delta2}), \eqref{eq:d7}, \eqref{geom3}, \eqref{constant_init} and \eqref{eq:d5.2}.
 \end{proposition}
@@
 \begin{equation*}
-\begin{array}{l}
-D_3 =\frac{1}{\eps} \sum_j \sum_r \bigg(
+\begin{aligned}
+D_3 &=\frac{1}{\eps} \sum_j \sum_r \bigg(
 l_{j,r}(\textbf{u}_r^{\eps}-\textbf{u}_j^{\eps}),\textbf{n}_{j,r} \bigg)
 \delta_{j,r}(p^{\eps})+\frac{1}{\eps} \sum_j \sum_r \bigg( 
-
 l_{jr} \mathbf n_{jr} (p_{j,r}^{\eps}
@@
 \:\delta_{j,r}(\uu^{\eps}) \bigg) \\
-\hspace{0.6cm}+ \frac{1}{\eps} \sum_j \sum_r \bigg(
+&+ \frac{1}{\eps} \sum_j \sum_r \bigg(
 l_{j,r}(\textbf{u}_r^{\eps}-\textbf{u}_j^{\eps}),\textbf{n}_{j,r} \bigg)
@@
 p_j^{\eps})  \: , \:  \uu^{\eps}(\textbf{x}_{r}) \bigg) \\
-\hspace{0.6cm}+\frac{\sigma}{\eps^2} \bigg( \sum_r \sum_j
+&+\frac{\sigma}{\eps^2} \bigg( \sum_r \sum_j
 \widehat{\beta}_{j,r}\textbf{u}_r^{\eps}  \: , \:
 \frac{1}{|\Omega_j|}\int_{\Omega_j} \uu^{\eps} d\x \bigg) .
-\end{array}
+\end{aligned}
 \end{equation*}
@@
 one has the inequalities
-\begin{equation}\label{}
+\begin{equation}\label{const_delta1}
  \vert \delta_{jr}(q) \vert
  \leq 
-  C  \| q \| _{ H^1(\Omega_j) }
+  C_{\delta}  \| q \| _{ H^1(\Omega_j) }
 \end{equation}
 and
-\begin{equation}
+\begin{equation}\label{const_delta2}
 \vert \widetilde \delta_{jr}(q)\vert
 \leq  
-  C h^{3/2}  \| q \| _{ H^3(\Omega_j) }
+  C_{\delta} h^{3/2}  \| q \| _{ H^3(\Omega_j) }
 \end{equation}
@@
 One has
-the bound with a constant $C$proportional to $  \|  \mathbf V ^\eps (0) \|^2_  { H^1(\Omega)  }$  
+the bound 
 \begin{equation} \label{eq:bound1}
@@
 _r^{\eps})^2 
-+Ch(  \frac T {\gamma } +1).
-\end{equation}
++ T \frac {P C_{\delta}^2 C_{\mathcal{M}} h }{2\gamma \eps} \vert \vert \mathbf{V}_0^{\eps} \vert\vert^2_{H^1(\Omega)}  +  \bigg( \frac1{\alpha} + PC_{\delta}^2 \bigg) \frac{ h C_{\mathcal{M}}^2 }{2}\sqrt{\frac{P}{C_1}}  \| \mathbf{V}_0^{\eps} \|_{H^1(\Omega)}^2,
+\end{equation}
+where the constants $P$, $C_{\delta}$, $C_{\mathcal{M}}$ and $C_1$ are defined respectively in \eqref{nbmr}, (\ref{const_delta1}-\ref{const_delta2}), \eqref{eq:d7} and \eqref{eq:d5.2}.
 \end{pro}
@@
 \end{equation*}
-
-We now look at the last term of (\ref{eq:bound1}), which we call $W$.
+We now look at the last term of this inequality, which we call $W$.
 One has, by definition of $\widehat{\beta}_{j,r}$
@@
 Using the assumptions of the mesh, there exist a 
-constant $C>0$ such that $|\xr -\xj|\leq Ch$.
- Using successively assumptions \eqref{eq:d5.2},\eqref{nbmr} and 
-\eqref{geom3}, we get
+constant $C_{\mathcal{M}}>0$ such that $|\xr -\xj|\leq C_{\mathcal{M}} h$ and $\ljr \leq C_{\mathcal{M}} h$.
+Since $| \njr\otimes(\xr -\xj) \textbf{u}_r^{\eps} |^2 = | (\xr -\xj) ,  \textbf{u}_r^{\eps} |^2$, one obtains by using successively assumptions \eqref{eq:d5.2} and \eqref{nbmr}
 \begin{equation*}\label{esti_beta}
 \vert W \vert
-\leq C \frac{\sigma h}{\eps^2}
-\bigg( \sum_r \big( B_{r}\textbf{u}_r^{\eps},\textbf{u}_r^{\eps}\big)\bigg)^{\frac12} \bigg(\sum_j \sum_r    | \delta_{j,r}(\uu^{\eps})|^2 \bigg)^{\frac12 }.
+\leq  \frac{\sigma h C_{\mathcal{M}}^2 }{\eps^2}\sqrt{\frac{P}{C_1}}
+\bigg( \sum_r |V_r| \big( \textbf{u}_r^{\eps},\textbf{u}_r^{\eps}\big)\bigg)^{\frac12} \bigg(\sum_j \sum_r    | \delta_{j,r}(\uu^{\eps})|^2 \bigg)^{\frac12 }.
 \end{equation*}
@@
 \vert W \vert
-\leq C \frac{\sigma h}{2\eps^2}
-\bigg( \sum_r \big( B_{r}\textbf{u}_r^{\eps},\textbf{u}_r^{\eps}\big)  +\sum_j \sum_r    | \delta_{j,r}(\uu^{\eps})|^2 \bigg).
+\leq \frac{\sigma h C_{\mathcal{M}}^2 }{2\eps^2}\sqrt{\frac{P}{C_1}}
+\bigg( \sum_r |V_r| \big( \textbf{u}_r^{\eps},\textbf{u}_r^{\eps}\big)  + \sum_j \sum_r    | \delta_{j,r}(\uu^{\eps})|^2 \bigg).
 \end{equation}
@@
 &+\frac{1}{2 \gamma \eps} \sum_j \sum_r l_{j,r}\bigg( \textbf{n}_{j,r} \: , \:
-\delta_{j,r}(\uu^{\eps}) \bigg)^2 + C \frac{\sigma h}{2\eps^2}
-\bigg( \sum_r \big( B_{r}\textbf{u}_r^{\eps},\textbf{u}_r^{\eps}\big)  +\sum_j \sum_r    | \delta_{j,r}(\uu^{\eps})|^2 \bigg)\\
+\delta_{j,r}(\uu^{\eps}) \bigg)^2 + \frac{\sigma h C_{\mathcal{M}}^2 }{2\eps^2}\sqrt{\frac{P}{C_1}} 
+\bigg( \sum_r |V_r|  \big( \textbf{u}_r^{\eps},\textbf{u}_r^{\eps}\big)  +\sum_j \sum_r    | \delta_{j,r}(\uu^{\eps})|^2 \bigg)\\
 \end{aligned}
 \end{equation}
-
-Furthermore, using the  classical interpolation results of proposition \ref{pro:interp} , there exists another constant $C\geq0$ such that 
+Furthermore, using the  classical interpolation results of proposition \ref{pro:interp} and once again the assumption  \eqref{nbmr}, one has 
 \[
-\sum_j \sum_r ( \delta_{j,r}\uu^{\eps})^2 \leq C \vert \vert \uu^\eps \vert\vert^2_{H^1(\Omega)}
+\sum_j \sum_r | \delta_{j,r}\uu^{\eps}|^2 \leq P C_{\delta}^2 \vert \vert \uu^\eps \vert\vert^2_{H^1(\Omega)}
 .
@@
 \[
-\sum_j \sum_r l_{j,r} ( \delta_{j,r}p^{\eps})^2 \leq C h \vert \vert p^\eps \vert\vert^2_{H^1(\Omega)}
+\sum_j \sum_r l_{j,r}  \delta_{j,r} ( p^{\eps})^2 \leq P C_{\delta}^2 C_{\mathcal{M}} h \vert \vert p^\eps \vert\vert^2_{H^1(\Omega)}
 .
 \]
-
-So we obtain, after redefinition of all the constants $C$
-
-$$
-\int_0^T E_1 dt\leq 
+So we obtain
+
+\begin{equation*}
+\begin{aligned}
+\int_0^T E_1 dt & \leq 
 \int_0^T \frac{\gamma}{\eps}
 \sum_{j,r}l_{j,r}(\textbf{n}_{j,r},\textbf{u}_j^{\eps}-\textbf{u}
-_r^{\eps})^2 
-+\frac {Ch }{2\gamma \eps}\bigg(\vert \vert \uu^\eps \vert\vert^2_{H^1(\Omega)} +\vert \vert p^\eps \vert\vert^2_{H^1(\Omega)}  \bigg)
-+C \frac{h\sigma}{2\eps^2}
-\bigg(\sum_r \big( B_{r}\mathbf{u}_r^{\eps},\mathbf{u}_r^{\eps}\big) +  \vert \vert \uu^\eps \vert\vert^2_{H^1(\Omega)}\bigg)dt.
-$$
-
+_r^{\eps})^2 dt  +  \frac {P C_{\delta}^2 C_{\mathcal{M}} h }{2\gamma \eps}\bigg(\vert \vert \uu^\eps \vert\vert^2_{L^2([0,T]; H^1(\Omega) )} +\vert \vert p^\eps \vert\vert^2_{L^2([0,T]; H^1(\Omega) )}  \bigg) \\
+&+\frac{\sigma h C_{\mathcal{M}}^2 }{2\eps^2}\sqrt{\frac{P}{C_1}}  \| \textbf{u}_r^{\eps} \|_{L^2([0,T]\times\Omega)}^2 + \frac{\sigma h C_{\mathcal{M}}^2  C_{\delta}^2 P^{3/2} }{2\sqrt{C_1} \eps^2}  \vert \vert \uu^\eps \vert\vert^2_{L^2([0,T]; H^1(\Omega) )} .
+\end{aligned}
+\end{equation*}
 Using  energy estimate (\ref{bee1})  for the the second  term of the rhs of the above inequality, (\ref{gggg}) for the third term   and   (\ref{bee2}) for the last term,
-one gets finally after simplifications and up to another redefinition  of the constant $C$(which is proportional to the $H^1(\Omega)$ norm of the initial data $\V_0$ and  is independent of the parameter $\sigma$)
+one gets finally after simplifications
 \begin{equation} \label{eq:si1}
@@
 _r^{\eps})^2 
-+Ch(  \frac 1 {\gamma } +1).
++ T \frac {P C_{\delta}^2 C_{\mathcal{M}} h }{2\gamma \eps} \vert \vert \mathbf{V}_0^{\eps} \vert\vert^2_{H^1(\Omega)}  +  \bigg( \frac1{\alpha} + PC_{\delta}^2 \bigg) \frac{ h C_{\mathcal{M}}^2 }{2}\sqrt{\frac{P}{C_1}}  \| \mathbf{V}_0^{\eps} \|_{H^1(\Omega)}^2 .
 \end{equation}
@@
 \begin{equation} \label{eq:si2}
-\int_0^T E_2(t) dt \leq  \frac{CTh}{\eps} .
-\end{equation}
-
-where the constant $C$ depends   on $\|  \mathbf V ^\eps (0) \|^2_  { H^3(\Omega)  }$
+\int_0^T E_2(t) dt \leq  \frac{hT}{\eps} C_{\mathcal{M}} C_{\delta} P \bigg( \frac{1+C_0^2h^2}{C_1} + h \bigg)   \|  \mathbf V ^\eps_0 \|^2_  { H^3(\Omega)  } ,
+\end{equation} 
+where the constants $P$, $C_{\delta}$, $C_{\mathcal{M}}$ and $C_0$ are defined respectively in \eqref{nbmr}, (\ref{const_delta1}-\ref{const_delta2}), \eqref{eq:d7} and \eqref{constant_init}.
+
 \end{pro}
@@
 Making use of the second set of inequalities
-of proposition \ref{pro:interp}, one gets concerning the first one
+of the proposition \ref{pro:interp} and the assumptions \eqref{eq:d7} and \eqref{nbmr}, one gets concerning the first one
 $$
@@
 \leq 
-\frac{C}{\eps}  \sum_j h^{5/2} | p_j  ^\eps |
+\frac{ C_{\mathcal{M}} C_{\delta} P }{\eps}  \sum_j h^{5/2} | p_j  ^\eps |
  \|  \mathbf V ^\eps (t) \|_  { H^3(\Omega_j)  }.
@@
 And using the inequality $ab\leq \frac{1}{2}(a^2+b^2)$ 
-
 $$
 | A|\leq 
-\frac{C_1}{\eps}  \sum_j h^{3} | p_j  ^\eps |^2 + \frac{C_2}{\eps} \sum_j h^{2} 
+\frac{ C_{\mathcal{M}} C_{\delta} P }{ 2\eps}  \sum_j h^{3} | p_j  ^\eps |^2 + \frac{C_{\mathcal{M}} C_{\delta} P}{2 \eps} \sum_j h^{2} 
  \|  \mathbf V ^\eps (t) \|^2_  { H^3(\Omega_j)  }
- \leq 
-\frac{hC_3}{\eps} \|  \mathbf V_h ^\eps (t) \|^2_  { L^2(\Omega)  } + \frac{C_2h^2}{\eps}  
+$$
+The assumption \eqref{eq:d5} yields
+$$
+| A| \leq 
+\frac{hC_{\mathcal{M}} C_{\delta} P}{2C_1 \eps} \|  \mathbf V_h ^\eps (t) \|^2_  { L^2(\Omega)  } + \frac{C_{\mathcal{M}} C_{\delta} P h^2}{2 \eps}  
  \|  \mathbf V ^\eps (t) \|^2_  { H^3(\Omega)  }.
@@
 The $L^2$ stability  (\ref{gggg})  of the scheme $\mathbf P_h ^\eps$ yields
-that $\|  \mathbf V_h ^\eps (t) \|^2_  { L^2(\Omega)  }\leq
-\|  \mathbf V_h ^\eps (0) \|^2_  { L^2(\Omega)  }\leq\|  \mathbf V ^\eps (0) \|^2_  { L^2(\Omega)  }+C \|  \mathbf V ^\eps (0) \|^2_  { H^1(\Omega)  } $.
-And with  the basic energy estimate (\ref{bee1}) , and since $h$ is bounded, we obtain with a constant $C_4$ proportional to  $   \|  \mathbf V ^\eps (0) \|^2_  { H^3(\Omega)  }$ 
-$$\int_0^T\vert A \vert dt \leq C_4 \frac{hT}{\eps}.$$
-
+that $
+\|  \mathbf V_h ^\eps (t) \|^2_  { L^2(\Omega)  }\leq
+\|  \mathbf V_h ^\eps (0) \|^2_  { L^2(\Omega)  }\leq\|  \mathbf V ^\eps_0 \|^2_  { L^2(\Omega)  }+C_0^2h^2 \|  \mathbf V ^\eps_0 \|^2_  { H^1(\Omega)  } $, where the last inequality comes from the initialization stage \eqref{constant_init}.
+With  the basic energy estimate (\ref{bee1}), and since $h$ is bounded, we obtain
+$$
+\int_0^T\vert A \vert dt \leq \frac{hT}{\eps} \frac{C_{\mathcal{M}} C_{\delta} P }{2 }\bigg( \frac{1+C_0^2h^2}{C_1} + h \bigg)   \|  \mathbf V ^\eps_0 \|^2_  { H^3(\Omega)  } .
+$$
 For the  second contribution$$
@@
 by similar calculations we obtain
-$$\int_0^T\vert B \vert dt \leq C_5 \frac{hT}{\eps},$$
-with a constant $C_5$ proportional to $  \|  \mathbf V ^\eps (0) \|^2_  { H^3(\Omega)  }$. Taking $C=2\max(C_4,C_5)$ yields (\ref{eq:si2}).
+$$
+\int_0^T\vert B \vert dt \leq \frac{hT}{\eps} \frac{C_{\mathcal{M}} C_{\delta} P }{2 }\bigg( \frac{1+C_0^2h^2}{C_1} + h \bigg)   \|  \mathbf V ^\eps_0 \|^2_  { H^3(\Omega)  },
+$$
+which concludes the proof.
 \end{proof}
@@
 \begin{pro}  \label{pro:conv2}
-There exists a constant $C>0$ proportional to $  \|  \mathbf V ^\eps (0) \|^2_  { H^1(\Omega)  }$ such that one has for all $\hat \gamma>0$ 
+For all $\widehat{\gamma}>0$, the following bound holds
 \begin{equation} \label{eq:bound3}
 \begin{aligned}
-\int_0^TSdt&\leq  C\left(  { h^2} +\frac{h}{ \widehat \gamma \eps}\right)
+\int _0^TS dt \leq 
+\frac{\widehat{\gamma} \sigma}{2\eps}\int_0^T\sum_r \sum_j \ljr \bigg( 
+\njr  \: , \: \textbf{u}_r^{\eps}-\textbf{u}_j^{\eps} \bigg)^2 dt 
 +
- \frac{\sigma\hat \gamma}{2\eps}\int_0^T\sum_r \sum_j \ljr \bigg(  \njr  \: , \:
-\mathbf{u}_r^{\eps}-\mathbf{u}_j^{\eps} \bigg)^2 dt
+C_{\mathcal{M}}^2  P \bigg\{ C_{\delta}\bigg( 1 + \frac{2C_{\mathcal{M}}^2P}{C_1\alpha} \bigg) h^2 
++
+\frac{ C_{\mathcal{M}} h}{2 C_1 \widehat{\gamma}\eps} \bigg\} \|  \mathbf{V}_0^{\eps} \|_{H^1(\Omega)}^2,
 \end{aligned}
 \end{equation}
+where the constants $P$, $C_{\delta}$, $C_{\mathcal{M}}$ and $C_1$ are defined respectively in \eqref{nbmr}, (\ref{const_delta1}-\ref{const_delta2}), \eqref{eq:d7} and \eqref{eq:d5.2}.
+
 \end{pro}
@@
 \begin{equation}\label{eq:s1}
-\begin{array}{ll | r}
+\left.
+\begin{aligned}
 S\leq &-\frac{\sigma}{\eps^2} \sum_r \sum_j  \bigg( \widehat{\beta}_{j,r}\bigg(
@@
 \textbf{u}^{\eps} d\x \bigg)
-&=S_1
  \\
@@
 \frac{1}{|\Omega_j|}\int_{\Omega_j} \textbf{u}^{\eps} d\x  \: , \:
-\textbf{u}_r^{\eps}-\textbf{u}_j^{\eps} \bigg). &=S_2
-\end{array}
+\textbf{u}_r^{\eps}-\textbf{u}_j^{\eps} \bigg)
+\end{aligned}
+\hspace{0.3cm}
+\right|
+\begin{aligned}
+:=S_1 \\
+\\
+:=S_2
+\end{aligned}
 \end{equation}
@@
 \end{equation}
-with the help of (\ref{geom3}).
-
-The second and third term in the identity (\ref{eq:bb1}) can be bounded
-by a Young's inequality with a convenient constant
+with the help of (\ref{geom3}). The second and third term in the identity (\ref{eq:bb1}) can be bounded
+by a Young's inequality with a convenient constant $C=\frac{C_1\alpha}{2C_{\mathcal{M}}^2P}$
 so that all terms containing $ \textbf{u}_r^{\eps}-u^\eps(\x_r)$
@@
 S_1
-\leq C\frac{h^2\sigma }{\eps^2}\sum_r \sum_j  \left|  \delta_{j,r}(\textbf{u}^{\eps}) \right|^2.
+\leq C_{\mathcal{M}}^2 \bigg( 1 + \frac{2C_{\mathcal{M}}^2P}{C_1\alpha} \bigg) \frac{h^2\sigma }{\eps^2}\sum_r \sum_j  \left|  \delta_{j,r}(\textbf{u}^{\eps}) \right|^2.
 \end{equation*}
@@
 $| \delta_{j,r}(\textbf{u}^{\eps}) |
- \leq C_1  \|\uu^\eps(t)\|^2_{H^1(\Omega_j)} $. 
+ \leq C_{\delta}  \|\uu^\eps(t)\|_{H^1(\Omega_j)} $. 
 So, taking into account energy estimate (\ref{bee2})
@@
 \begin{equation*} \label{eq:ss6}
-\int_0^T S_1dt \leq C_2 h^2  \|\V^\eps(0\|^2_{H^1(\Omega)}.
+\int_0^T S_1dt \leq C_{\mathcal{M}}^2 C_{\delta} P  \bigg( 1 + \frac{2C_{\mathcal{M}}^2P}{C_1\alpha} \bigg) h^2   \| \mathbf{V}_0^{\eps} \|_{H^1(\Omega)}^2 .
 \end{equation*}
@@
 $$
-Using one more time the energy estimate (\ref{bee2}) the second term in the right hand side of the above inequality  is bounded by $\frac{C_3h}{\widehat{\gamma}\eps}\|\V^\eps(0)\|^2_{ L^2(\Omega)}$.
-
+Using one more time the energy estimate (\ref{bee2}) the second term in the right hand side of the above inequality  is bounded by $\frac{ C_{\mathcal{M}}^3 P h}{2 C_1 \widehat{\gamma}\eps} \| \V^\eps_0\|^2_{ L^2(\Omega)}$.
 Thus
 $$
-\int _0^TS dt \leq 
-C_2 h^2  \|\V^\eps(0)\|^2_{H^1(\Omega)}
+\int _0^TS(t) dt \leq 
+\frac{\widehat{\gamma} \sigma}{2\eps}\int_0^T\sum_r \sum_j \ljr \bigg( 
+\njr  \: , \: \textbf{u}_r^{\eps}-\textbf{u}_j^{\eps} \bigg)^2 dt 
 +
-\frac{\widehat{\gamma} \sigma}{2\eps}\int_0^T\sum_r \sum_j \ljr \bigg( 
-\njr  \: , \: \textbf{u}_r^{\eps}-\textbf{u}_j^{\eps} \bigg)^2 dt\\
+C_{\mathcal{M}}^2  P \bigg\{ C_{\delta}\bigg( 1 + \frac{2C_{\mathcal{M}}^2P}{C_1\alpha} \bigg) h^2 
 +
-\frac{C_3h}{\widehat{\gamma}\eps}\|\V^\eps(0)\|^2_{ L^2(\Omega)}
-$$
-
-One finally obtains
-the claim
- with a new constant $C\geq0$ proportional to $\|\V^\eps(0)\|^2_{H^1(\Omega)} $.
+\frac{ C_{\mathcal{M}} h}{2 C_1 \widehat{\gamma}\eps} \bigg\} \|  \mathbf{V}_0^{\eps} \|_{H^1(\Omega)}^2 ,
+$$
+which is the expected result.
 \end{proof}
@@
 (\ref{eq:bound1}), (\ref{eq:si2}) and   
-(\ref{eq:bound3}).  Using $\mathscr{E}(0)=O(h)$,  it yields with some new constant $C$
-$$
-\begin{array}{ll}
-\mathscr{E}(T)& \leq Ch  \\
+(\ref{eq:bound3}).  Using equation \eqref{constant_init}, one finds
+\begin{equation*}
+\begin{aligned}
+\mathscr{E}(T)& \leq C_0^2h^2 \|\mathbf{V}_0^{\eps}\|_{H^1(\Omega)}^2 \\
 & 
-\displaystyle 
 -\frac1\eps \int_0^T \sum_{j,r}l_{j,r}(\textbf{n}_{j,r},\textbf{u}_j^{\eps}-\textbf{u}
 _r^{\eps})^2\\
-  & 
-    \displaystyle            +            \frac{\gamma}{\eps}
+&  +  \frac{\gamma}{\eps}
      \int_0^T \sum_{j,r}l_{j,r}(\textbf{n}_{j,r},\textbf{u}_j^{\eps}-\textbf{u}
 _r^{\eps})^2 
-+Ch(  \frac 1 {\gamma } +1) \\
-& \displaystyle  + C T
-\frac{h}{\eps}  \\
++ T \frac {P C_{\delta}^2 C_{\mathcal{M}} h }{2\gamma \eps} \vert \vert \mathbf{V}_0^{\eps} \vert\vert^2_{H^1(\Omega)}  +  \bigg( \frac1{\alpha} + PC_{\delta}^2 \bigg) \frac{ h C_{\mathcal{M}}^2 }{2}\sqrt{\frac{P}{C_1}}  \| \mathbf{V}_0 \|_{H^1(\Omega)}^2   \\
+& + \frac{hT}{\eps} C_{\mathcal{M}} C_{\delta} P \bigg( \frac{1+C_0^2h^2}{C_1} + h \bigg)   \|  \mathbf V ^\eps_0 \|^2_  { H^3(\Omega)  }  \\
 &
- \displaystyle +C(h^2+\frac{h}{ \widehat \gamma \eps})
++ \frac{\widehat{\gamma} \sigma}{2\eps}\int_0^T\sum_r \sum_j \ljr \bigg( 
+\njr  \: , \: \textbf{u}_r^{\eps}-\textbf{u}_j^{\eps} \bigg)^2 dt 
 +
- \frac{\sigma\hat \gamma}{2\eps} \int_0^T \sum_r \sum_j \ljr \bigg(  \njr  \: , \:
-\mathbf{u}_r^{\eps}-\mathbf{u}_j^{\eps} \bigg)^2
- \end{array}.
-$$
+C_{\mathcal{M}}^2  P \bigg\{ C_{\delta}\bigg( 1 + \frac{2C_{\mathcal{M}}^2P}{C_1\alpha} \bigg) h^2 
++
+\frac{ C_{\mathcal{M}} h}{2 C_1 \widehat{\gamma}\eps} \bigg\} \|  \mathbf{V}_0^{\eps} \|_{H^1(\Omega)}^2 
+ \end{aligned}.
+\end{equation*}
 Therefore
@@
 \mathscr{E}(T)\leq
-Ch\left( 2 + \frac{1}{\gamma} +\frac T \eps +h +\frac{1}{\eps \widehat{\gamma}}
+Ch\left( 1 +\frac T \eps +h +\frac{1}{\eps \widehat{\gamma}}
 \right)-
-\frac{1}{\eps}\bigg( 1-\frac1{\gamma} - \frac{\sigma \widehat{\gamma}}{2}
-\bigg)\int_0^T \sum_{j,r}l_{j,r}\bigg(\textbf{n}_{j,r},\textbf{u}_j^{\eps}-\textbf{u}_r^{\eps} \bigg)^2 dt.
-$$
+\frac{1}{\eps}\bigg( 1- \gamma - \frac{\sigma \widehat{\gamma}}{2}
+\bigg)\int_0^T \sum_{j,r}l_{j,r}\bigg(\textbf{n}_{j,r},\textbf{u}_j^{\eps}-\textbf{u}_r^{\eps} \bigg)^2 dt,
+$$
+where
+\begin{equation*}
+\begin{aligned}
+C = \|\mathbf{V}_0^\eps\|^2_{H^3(\Omega)}  \: \hbox{max}\bigg\{ & \:  \frac{ C_{\mathcal{M}}^2 }{2}\sqrt{\frac{P}{C_1}} \bigg( \frac1{\alpha} + PC_{\delta}^2 \bigg) \: , \: \frac{C_{\mathcal{M}}^3P}{2C_1}  , \\
+&  C_{\mathcal{M}} C_{\delta} P \bigg( \frac{1+C_0^2h^2}{C_1} +\frac{ C_{\delta} }{2 \gamma } + h \bigg) \: , \: C_0^2 + C_{\mathcal{M}}^2  P C_{\delta}\bigg( 1 + \frac{2C_{\mathcal{M}}^2P}{C_1\alpha} \bigg) \: \bigg\} .
+\end{aligned}
+\end{equation*}
 This estimate is fundamental, since it 
@@
 \mathscr{E}(T)\leq
-Ch\left( 3 +\frac T \eps +h +\frac{\sigma}{\eps}
+Ch\left( 1 +\frac T \eps +h +\frac{\sigma}{\eps}
 \right)$$
- Rereading the proof one can check that the constant $C$ is proportional to  $\|\V^\eps(0)\|^2_{H^3(\Omega)} $, and  if $\sigma=0$ one recovers the result of Mazeran \cite{Mazeran}, chapter 4.
+The constant $C$, uniform in $\eps$, is proportional to  $\|\V^\eps_0\|^2_{H^3(\Omega)} $, and  if $\sigma=0$ one recovers the result of Mazeran \cite{Mazeran}, chapter 4.
 The proof was more difficult to obtain due to the non standard discretization of the source term and its incorporation in  the approximate nodal Riemann solver.
-
 Since $h$ and $\eps$ can be taken less than 1, elementary comparison
@@
 \mathscr{E}(t) 
-\leq C' (T,\sigma)\nvhp \frac{h}{\eps}$.
+\leq  \frac{h}{\eps} C (2+T+\sigma) $.
 The proof is ended. 
@@
 diffusion approximation scheme (\ref{das:1})  is stable in the $L^2$
-norm, in the sense that $E'(t)\leq 0$. Moreover we have
+norm, in the sense that $E'(t)\leq 0$. Moreover, denoting $p_h=\left( p_j(0)\right)_{j\in Cells}$, we have
 \begin{equation}\label{das:gggg}
 \vert\vert \uu_r \vert\vert_{L^2([0,T]\times \Omega)}\leq
-C  \left\|  \left( p_j(0)\right)_j \right\|_{L^2(\Omega)}
+\frac{1}{\alpha}  \left\|  p_h(0) \right\|_{L^2(\Omega)}
 \end{equation}
@@
 l_{jr}(\njr,(\uj-\ur))^{2} \leq  
- \left\|  \left( p_j(0)\right)_j \right\|_{L^2(\Omega)}.
+ \left\|   p_h(0) \right\|_{L^2(\Omega)}.
 \end{equation}
@@
 \begin{equation*}\label{eq:ds6bis}
-E(T) + \alpha \int_{[0,T]}\sum_r  \vert V_r\vert \  \vert\vert\uu_r\vert\vert^2 
+E(T) + \alpha \int_{[0,T]}\sum_r  \vert V_r\vert \  \| \uu_r \|^2 
 + \int_{[0,T]}\eps\sum_j\sum_r \ljr \left( \uu_r- \uu_j,  \njr\right )^2\leq
@@
 \left\{ 
-\begin{array}{l}
-a_j=\displaystyle \frac{d}{dt} \pej+
+\begin{aligned}
+&a_j=\displaystyle \frac{d}{dt} \pej+
 \frac{1}{\mid\Omega_{j}\mid}\sum_{r}(l_{jr}\uer,\njr)\\
- \br=\frac{1}{\vert V_r\vert}\left (   \sigma B_r \uer- \sum_{j}\ljr
+& \br=\frac{1}{\vert V_r\vert}\left (   \sigma B_r \uer- \sum_{j}\ljr
 \pej\njr+ \eps\sum_j\alj(\uer-\uej)\right ), \\
-\cj= \frac{1}{h}\sum_{r}l_{jr} (\njr,\uer -\uej)\njr=0.
-\end{array}
+&\cj= \frac{1}{h}\sum_{r}l_{jr} (\njr,\uer -\uej)\njr .
+\end{aligned}
 \right.
@@
 Assume $p_0\in H^{4}(\Omega)$.
-Then there exists a constant $C>0$ such that the following 
+Then there exists a constant $C_c>0$ such that the following 
 estimates hold
 \begin{equation} \label{eq:d20}
-\left| a_j\right|\leq C h
+\left| a_j\right|\leq C_c h
 \quad
@@
 \begin{equation} \label{eq:d21}
-\left|  \br\right|  \leq C(h+\eps), \quad
+\left|  \br\right|  \leq C_c(h+\eps), \quad
 \mbox{for all } r   .
@@
 \begin{equation} \label{eq:d22}
-\left| \cj\right| \leq C h, \quad
+\left| \cj\right| \leq C_c h, \quad
 \mbox{for all } j   .
@@
 \end{lemma}
-
+In this result the constant $C_c$  is not explicitly given since it only depends on the regularity of $p_0$.
 \begin{proof} 
@@
 $$
-\partial_t p(\xj,t)=\frac{1}{\sigma}\frac{\int_{\Omega_j} \partial_t
+\partial_t p(\xj,t) = \frac{\int_{\Omega_j} \partial_t
 p(x,t)dx}{\left| \Omega_j \right|}+O(h)=
@@
  \| e \|_{L^\infty(  [0,T]: L^2(\Omega) )}
- \leq C(T)(h+\eps),
+ \leq C_e(T)(h+\eps),
 \end{equation}
 \begin{equation} \label{eq:dconv2}
- \| \ff \|_{L^2([0,T]\times \Omega)} \leq C(T) (h+\eps)  
+ \| \ff \|_{L^2([0,T]\times \Omega)} \leq C_f(T) (h+\eps)  
  ,
@@
 \begin{equation} \label{eq:dconv3}
-\eps \int_0^T \sum_j \sum_r    \ljr \left( \fr  -
-\fj ,\njr \right)^2\leq C(T) (h+\eps)^2, 
+\sqrt{\eps \int_0^T \sum_j \sum_r    \ljr \left( \fr  -
+\fj ,\njr \right)^2 } \leq C_h(T) (h+\eps), 
  \end{equation}
@@
 \end{equation}
-
+where
+\begin{equation*}
+\left\{
+\begin{aligned}
+&C_e(T) = \sqrt{2} e^{T/2} \max\bigg\{  \: C_0^2\|\mathbf{W}^{\eps}_0\|_{H^1(\Omega)}^2  \:  , \:  T\frac{2C_c^2|\Omega| }{\alpha \sigma} \max \bigg( 1 \: ,\: \frac{C_{\mathcal{M}}^2}{C_1^2\beta}\max\big(\alpha \sigma , C_{\mathcal{M}} P \big) \bigg)  \bigg\}^{\frac12}    ,\\
+&C_f(T) = 2\sqrt{\frac{T+e^{-T}}{\alpha}}C_e , \\
+&C_h(T) = \sqrt{2( T+e^{-T})}C_e , \\
+&C_g(T) = \sqrt{\frac{2}{\beta} } C_{\mathcal{M}} \max\bigg( C_h(T) , \frac{C_{\mathcal{M}}P}{C_1}C_f^2(T) \bigg)^{\frac12} .
+\end{aligned}
+\right.
+\end{equation*}
 \end{theorem}
@@
 \left\{ 
-\begin{array}{l}
-\displaystyle \mid\Omega_{j}\mid e'_{j}+
+\begin{aligned}
+& \mid\Omega_{j}\mid e'_{j}+
 \sum_{r}(l_{jr}\fr,\njr)=-\mid\Omega_{j}\mid a_j\\
- \left( \eps\sum_{j}\alj+  \sigma B_r\right)\fr-
+& \left( \eps\sum_{j}\alj+  \sigma B_r\right)\fr-
 \sum_{j}\ljr e_j\njr-\eps\sum_j\alj\fj=-\mid
 V_r\mid\br , \\
- \sum_{r}l_{jr} (\njr,\fr -\fj)\njr=-h\cj.
-\end{array}
+& \sum_{r}l_{jr} (\njr,\fr -\fj)\njr=-h\cj.
+\end{aligned}
 \right.
@@
 By proceeding as for the results of stability one has the identity
-$$
-E'(t)= \sum_j |\Omega_j| e_j e_j'=
+\begin{equation*}
+\begin{aligned}
+E'(t)&= \sum_j |\Omega_j| e_j e_j'=
 \sum_j  e_j\left(
@@
 \right)
-$$ 
-$$
 =- \sum_r \sum_j (  l_{jr}  \mathbf n_{jr} e_j , \mathbf f_r)
-- \sum_j\left| \Omega_j \right| e_j a_j 
-$$
-$$= -\sum_r \left (\fr, \left( \eps\sum_{j}\alj+  \sigma
+- \sum_j\left| \Omega_j \right| e_j a_j \\
+&= -\sum_r \left (\fr, \left( \eps\sum_{j}\alj+  \sigma
 B_r\right)\fr- \eps\sum_j\alj\fj\right )
 - \sum_j \left| \Omega_j \right| a_j e_j
-- \sum_r \left| V_r \right| \br \fr
-$$
-$$= -\sum_r \left (\sigma B_r \fr, \fr\right ) 
--\eps \sum_r\left( \fr, \sum_j \alj(\fr -\fj\right )
+- \sum_r \left| V_r \right| \br \fr \\
+&= -\sum_r \left (\sigma B_r \fr, \fr\right ) 
+-\eps \sum_r\left( \fr, \sum_j \alj(\fr -\fj ) \right )
 - \sum_j \left| \Omega_j \right| a_j e_j
-- \sum_r \left| V_r \right| \br \fr
-$$
-$$= -\sum_r \left (\sigma B_r \fr, \fr\right ) 
+- \sum_r \left| V_r \right| \br \fr \\
+&= -\sum_r \left (\sigma B_r \fr, \fr\right ) 
 -\eps\sum_j\sum_r \ljr \left( \fr- \fj,  \njr\right )^2
@@
 - \sum_r \left| V_r \right| \br \fr +\eps\sum_j h \fj\cj.
-$$
-Using a Young's inequality and the Cauchy-Schwarz inequality, one gets
+\end{aligned}
+\end{equation*}
+Using a Young's inequality, the Cauchy-Schwarz inequality and assumptions \eqref{eq:d5} and \eqref{geom3}, one gets
 \begin{equation} \label{eq:yi}
@@
 \right)
--  \alpha \|  \ff \|^2_{L^2(\Omega)}\\
+-  \alpha \sigma \|  \ff \|^2_{L^2(\Omega)}\\
 &
   -\eps\sum_j\sum_r \ljr \left( \fr- \fj,  \njr\right )^2 
-+\frac{\eps}{2h}\left (\eta||\gf ||^2_{L^2(\Omega)}
++\frac{\eps}{2h  C_1}\left (\eta||\gf ||^2_{L^2(\Omega)}
 +\frac{1}{\eta}||\cc||^2_{L^2(\Omega)} \right )
@@
 specified later. 
-Now using  (\ref{geom4})
+Now using  (\ref{geom4}) and \eqref{eq:d7},
 we have
 $$
-\vert \Omega_j\vert \ \vert \fj \vert^2\leq C h\sum_r\ljr(\njr,\fj)^2.
+\vert \Omega_j\vert \ \vert \fj \vert^2\leq \frac{C_{\mathcal{M}}^2}{\beta} h\sum_r\ljr(\njr,\fj)^2.
 $$
@@
 \vert \Omega_j\vert \ \vert\fj \vert^2\leq 
-Ch \left(2\sum_r\ljr(\njr,\fj-\fr)^2+2\sum_r \ljr \vert 
-\fr \vert^2\right ).
-$$
-So 
-there exists two constant $C_1$ and $C_2$ such that
+\frac{C_{\mathcal{M}}^2}{\beta} h \left(2\sum_r\ljr(\njr,\fj-\fr)^2+2\sum_r \ljr \vert 
+\fr \vert^2\right ),
+$$
+which yields, using \eqref{eq:d5.2} and \eqref{nbmr}
 \begin{equation}\label{gl2}
 \vert\vert\gf \vert\vert^2_{L^2(\Omega)} \leq 
-C_1 h\sum_{jr}\ljr(\njr,\fj-\fr)^2 +  C_2\vert\vert\ff \vert\vert^2_{L^2(\Omega)}.
+\frac{2C_{\mathcal{M}}^2}{\beta} h\sum_{jr}\ljr(\njr,\fj-\fr)^2 +  \frac{2C_{\mathcal{M}}^3P}{\beta C_1} \vert\vert\ff \vert\vert^2_{L^2(\Omega)}.
 \end{equation}
 So from (\ref{eq:yi}) we  obtain 
-$$
-E'(t) \leq  ||e||_{L^2(\Omega)}\ ||a||_{L^2(\Omega)} +
+\begin{equation*}
+\begin{aligned}
+E'(t) &\leq  ||e||_{L^2(\Omega)}\ ||a||_{L^2(\Omega)} +
  \frac{1}{2\mu} ||\bb||^2_{L^2(\Omega)} 
-+( \frac{\mu}{2} +\frac{C_2\eps\eta}{2h}- \alpha) \|  \ff \|^2_{L^2(\Omega)}
-$$
-$$
-+ (\frac{C_1}{2}\eta -1)\eps\sum_j\sum_r \ljr \left( \fr- \fj,  \njr\right )^2 
-+\frac{\eps}{2h\eta} ||\cc||^2, \qquad \forall \mu,\eta >0.
-$$
-Let us choose $\mu=\frac{\alpha}{2}$ and $\eta =\min(\frac{1}{C_1},\frac{\alpha h}{C_2
-\eps})$, so that
++\bigg( \frac{\mu}{2} + \frac{\eps\eta C_{\mathcal{M}}^3 P }{ h C_1^2 \beta} - \sigma \alpha \bigg) \|  \ff \|^2_{L^2(\Omega)}
+\\
+&+ \bigg(\frac{ C_{\mathcal{M}}^2 \eta}{C_1 \beta} -1 \bigg)\eps\sum_j\sum_r \ljr \left( \fr- \fj,  \njr\right )^2 
++\frac{\eps}{2h\eta C_1} ||\cc||^2, \qquad \forall \mu,\eta >0.
+\end{aligned}
+\end{equation*}
+Let us choose $\mu=\frac{\alpha\sigma}{2}$ and $\eta =\frac{C_1\beta}{2C_{\mathcal{M}}^2} \min\big(1,\frac{\alpha \sigma hC_1}{ \eps C_{\mathcal{M}} P} \big)$.
+It yields, using the inequality $ab\leq \frac12(a^2+b^2)$
 \begin{equation*} \label{eq:d40}
 \begin{aligned}
-E'(t) \leq & \sqrt{2}\sqrt{E(t)}\ ||a||_{L^2(\Omega)}  - \frac{\alpha}{4}  F'(t)
+E'(t) \leq & E(t) + \frac12  ||a||_{L^2(\Omega)}^2  - \frac{\alpha\sigma}{4}  F'(t)
 - \frac{\eps}{2}\sum_j\sum_r \ljr \left( \fr- \fj,  \njr\right )^2\\
-& +  \frac{1}{2 \alpha} ||\bb||^2_{L^2(\Omega)} +\max(\frac{\eps C_1}{2h},\frac{C_2
-\eps^2}{\alpha h^2}) ||\cc||^2_{L^2(\Omega)} .
+& +  \frac{1}{ \alpha\sigma } ||\bb||^2_{L^2(\Omega)}  +   \frac{C_{\mathcal{M}}^2}{C_1^2\beta} \max \bigg( \frac{\eps}{h} , \frac{\eps^2}{h^2} \frac{C_{\mathcal{M}} P}{ \alpha \sigma C_1 } \bigg) ||\cc||^2_{L^2(\Omega)} .
 \end{aligned}
@@
 By the consistency estimates (\ref{eq:d20}-\ref{eq:d21}-\ref{eq:d22}) 
- and since the domain $\Omega$ is bounded, one finds a constant C such that
+ and since the domain $\Omega$ is bounded, one finds
 \begin{equation} \label{eq:d40bis}
@@
 - \frac{\eps}{2}\sum_j\sum_r \ljr \left( \fr- \fj,  \njr\right )^2
-+  C\left (h+\eps\right )^2. 
-\end{equation}
++  C\left (h+\eps\right )^2,
+\end{equation}
+where
+\begin{equation*}
+C = \frac{2C_c^2|\Omega| }{\alpha \sigma} \max \bigg( 1 \: ,\: \frac{C_{\mathcal{M}}^2}{C_1^2\beta}\max\big(\alpha \sigma , C_{\mathcal{M}} P \big) \bigg).
+\end{equation*}
 Thus 
-$$
+\begin{equation}\label{esti_E_DA}
 E'(t) \leq  E(t)  
 +  C\left (h+\eps\right )^2. 
-$$
-By construction $E(0)=O(h^2)$ for a smooth initial data.
+\end{equation}
+By construction $E(0)\leq C_0^2h^2\|\mathbf{W}^{\eps}_0\|_{H^1(\Omega)}^2$ \eqref{constant_init}.
  So by the Gr\"onwall lemma 
 $
-E(t)\leq C(t) (h+\eps)^2
+E(t)\leq C_e^2(t) (h+\eps)^2,
 $
+ with $C_e(t) = \sqrt{2} \max ( C_0^2\|\mathbf{W}^{\eps}_0\|_{H^1(\Omega)}^2 , T C )^{\frac12}e^{T/2}$,
  which gives (\ref{eq:dconv1}).
@@
 \leq
- E(0)+ \int_0^t \left(  E(t)+ C(h+\eps)^2  \right) dt \leq C'(T) (h+\eps)^2.
-$$
-It shows   
+ E(0)+ \int_0^t \left(  E(s)+ C(h+\eps)^2  \right) ds .
+$$
+Using the estimate \eqref{esti_E_DA}, it shows   
 the  estimates (\ref{eq:dconv2}) and (\ref{eq:dconv3}).
-Using   (\ref{gl2}) 
-one gets
+Integrating  (\ref{gl2}) and using the estimates \eqref{eq:dconv2} and \eqref{eq:dconv3}, one gets
 \begin{equation*}\label{gl3}
 \int_0^T \vert\vert\gf \vert\vert^2_{L^2(\Omega)} \leq 
-C_1 h\int_0^T\sum_{jr}\ljr(\njr,\fj-\fr)^2 +  C_2\int_0^T\vert\vert\ff \vert\vert^2_{L^2(\Omega)}\leq
-C"(T)(h+\eps)^2(1+\frac h\eps)
+\frac{2C_{\mathcal{M}}^2}{\beta} h \int_0^T\sum_{jr}\ljr(\njr,\fj-\fr)^2 +  \frac{2C_{\mathcal{M}}^3P}{\beta C_1} \vert\vert\ff \vert\vert^2_{L^2([0,T]\times\Omega)}
+\leq
+C_g^2(T)(h+\eps)^2(1+\frac h\eps),
+\end{equation*}
+with
+\begin{equation*}
+C_g(T) = \sqrt{\frac{2}{\beta} } C_{\mathcal{M}} \max\bigg( C_h(T) , \frac{C_{\mathcal{M}}P}{C_1}C_f^2(T) \bigg)^{\frac12} . 
 \end{equation*}

### 2015-03-27 Corrected_version.tex
change thomas

@@
 \begin{equation}\label{init_1D}
- \| u_j^{\eps}(0)-\eps v_j(0)\|_{L^2(\mathbb{R})} \leq C_0 h\eps .
+ \| u_j^{\eps}(0)-\eps v_j(0)\|_{L^2(\mathbb{R})} \leq C_0 h\eps \|p_0\|_{H^2(\mathbb{R})}.
 \end{equation}
@@
 There exists a constant which depend of the time such that 
-\begin{equation*}
+\begin{equation}\label{esti_p_eps_p_0}
 \|\V^{\eps}-\W^\eps\|_{L^\infty([0,T];L^2(\mathbb{R}) )} \leq
  \eps \frac{T}{\sigma^2} \|\partial_{xxx}p_0\|_{L^2(\mathbb{R})}.
-\end{equation*}
+\end{equation}
 \end{proposition}
@@
 
-\begin{equation*}
+\begin{equation}\label{esti_naive_1d}
 \|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
@@
 \sqrt \frac{h}\eps 
-\left\| \V^{\eps}(0)
+\left\| \V^{\eps}_0
 \right\|_{H^1(\mathbb{R})}.
-\end{equation*}
+\end{equation}
 
@@
 For example by choosing $\alpha=\frac12$ and $\widehat{\alpha}=\frac12$, and coming back to $\mathscr{E}'(t) $ we get
-\begin{eqnarray} \label{eq:eqn1}
+\begin{eqnarray} 
 \mathscr{E}'(t)  & \leq & \sum_{j\in \mathbb{Z}} \bigg(
@@
 \delta_{j}^+(p^{\eps})^2+\delta_{j}^-(p^{\eps}
-)^2\right ) \bigg) \\
+)^2\right ) \bigg)\label{eq:eqn1} \\
 &+& \underset{j\in \mathbb{Z}}{\sum} \frac{1}{8\eps} \sigma \Delta x_j^2
@@
 u_{j+\frac12 }^{\eps})^2}{\eps}+\frac{\sigma^2}{4\eps^3} \sum_{j\in
-\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2.
+\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2.\label{eq:eqn2}
 \end{eqnarray} 
@@
 \end{equation}
-Finally the last term in (\ref{eq:eqn1}) can be bounded using a
-Cauchy-Schwarz inequality 
+Finally the last term in (\ref{eq:eqn2}) can be bounded using the Jensen inequality 
 $$
@@
 Under assumption \ref{geometrie1d}, the following estimate holds
-\begin{equation*}
+\begin{equation}\label{esti_p_h_0_p_0}
 \|\W_h^\eps-\W^\eps\|_{L^{\infty}([0,T];L^2(\mathbb{R}))} \leq
@@
 \eps \sqrt{\frac12 + \frac{4}{\mathcal{C}_M}\bigg( 3 + \frac{T}{\sigma}e^{T/\sigma} \bigg) } \bigg).
-\end{equation*}
+\end{equation}
 \end{proposition}
@@
 There exists a constant $C(T)>0$ such that the following estimate holds
-\begin{equation*}
-\|\V_h^{\eps}-\W^\eps_h\|_{L^2([0,T]\times\mathbb R)} \leq  \eps e^{T/2} \bigg(  C_0h + \sqrt{ \frac{1}{\sigma C_{\mathcal{M}} } \big( \frac12 + \frac{1}{\sigma^2} \big) } \|p_0\|_{H^2(\mathbb{R})} \bigg) ,
-\end{equation*}
+\begin{equation}\label{p_h_eps_p_h_0_1d}
+\|\V_h^{\eps}-\W^\eps_h\|_{L^2([0,T]\times\mathbb R)} \leq  \eps e^{T/2} \bigg(  C_0h + \sqrt{ \frac{1}{\sigma C_{\mathcal{M}} } \big( \frac12 + \frac{1}{\sigma^2} \big) } \bigg)  \|p_0\|_{H^2(\mathbb{R})},
+\end{equation}
 where $C_0$ is defined in \eqref{init_1D}.
@@
 $
-\|\V_h^{\eps}-\W^\eps_h\|_{L^2([0,T]\times\mathbb{R})} \leq \eps e^{T/2} \big(  C_0h + \sqrt{ \frac{1}{\sigma C_{\mathcal{M}} } ( \frac12 + \frac{1}{\sigma^2} )} \|p_0\|_{H^2(\mathbb{R})} \big)$. 
+\|\V_h^{\eps}-\W^\eps_h\|_{L^2([0,T]\times\mathbb{R})} \leq \eps e^{T/2} \big(  C_0h + \sqrt{ \frac{1}{\sigma C_{\mathcal{M}} } ( \frac12 + \frac{1}{\sigma^2} )}  \big) \|p_0\|_{H^2(\mathbb{R})} $.  
 The proof is ended.
@@
 \end{proof} 
+~~\\
+\begin{proof}[ALTERNATIVE PROOF]~~\\
+\\
+All the previous estimates
+show that (\ref{eq:mod3}-\ref{eq:mod4})  are true
+with
+$a=1$, $b=c=\frac12$ and $d=1$. More specifically, estimates \eqref{esti_naive_1d}, \eqref{p_h_eps_p_h_0_1d}, \eqref{esti_p_h_0_p_0} and \eqref{esti_p_eps_p_0} shows that
+\begin{equation*}
+\|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
+\leq C \min\bigg( \sqrt \frac{h}\eps  \: , \: \eps + h + \eps \bigg)
+\end{equation*}
+where
+\begin{equation*}
+\begin{aligned}
+C =  2 \max \bigg\{  & \sqrt{h\eps + 2T + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} }
+\left\| \V^{\eps}_0
+\right\|_{H^1(\mathbb{R})} \: ,  \\
+&\|p_0\|_{H^3(\mathbb{R})} \max\bigg( e^{T/2} \bigg(  C_0h + \sqrt{ \frac{1}{\sigma C_{\mathcal{M}} } \big( \frac12 + \frac{1}{\sigma^2} \big) }  \bigg) \: ,\\
+& \hspace{3cm} e^{T/2\sigma} + 
+\eps \sqrt{\frac12 + \frac{4}{\mathcal{C}_M}\bigg( 3 + \frac{T}{\sigma}e^{T/\sigma} \bigg) }  \: ,  \frac{T}{\sigma^2}  \bigg) \bigg\} .
+\end{aligned}
+\end{equation*}
+Using the general
+method described at the beginning of this work in proposition \ref{prop:1}, 
+one  obtains the convergence
+estimate of convergence
+$
+\|\mathbf V_h^\eps -\mathbf V^\eps   \|_{L^2([0,T]\times \mathbb{R}   )  }
+\leq C(T) h^{ q }
+$
+with the order of convergence
+$
+q=\frac{ac}{a+b}=\frac13$.
+
+\end{proof}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{equation}\label{ine3}
-\textcolor{red}{\| p^\epsilon-p\|_{   L^\infty([0,T];H^n(\Omega))  }+
+\| p^\epsilon-p\|_{   L^\infty([0,T];H^n(\Omega))  }+
 \| \mathbf{v} 
@@
  \leq
-C \eps
+\frac{T}{\sigma^2} \eps
 \|p_0 \|_{H^{3+n}(\Omega)},
-\qquad n \in \mathbb N.}
+\qquad n \in \mathbb N.
 \end{equation}
@@
 \leq
-\|  \tilde p(0)\|_{L^2(\Omega)} 
+\|  \tilde p(0)\|_{L^2(\Omega)}^2
 $$
@@
 By definition $\|\mathbf{R}\|_{L^2(\Omega)}= \|\frac{d}{dt}
-\uj\|_{L^2(\Omega)}$. Using the third line of \eqref{das}, one has
+\uj\|_{L^2(\Omega)}$. Using the second line of \eqref{das}, one has
 $\uj=A_j^{-1}\sum_r \alj\ur$ and thus $\|\frac{d}{dt}

### 2015-04-01 Answers_for_reviewers.tex
add a remark on time rate
last correction thomas

--- 2015-03-20 Answers_for_reviewers.tex
@@
 \section{Answers for the report 2M}
+
 \begin{itemize}
-\item Constant
+\item A massive overuse of ``Constant C'' and the issue of the estimates? time-dependence
 \begin{itemize}
@@
 \item We have correct the constant in the proposition 2.5 page 8
-\item 1 : we have corrected the constant in the proposition 2.2 page 7
-\item 2 :
-\item 3 :
-\item 4 :
-\item 5 : We have explicit the constant between the equation (32) and the end of the proof of the proposition 2.5
+\item Page 7 : we have corrected the constant in the proposition 2.2 page 7
+\item Point 2-1:
+\item Point 2-2:
+\item Page 8 : corrected.
+\item Page 11 -1: It is the mesh constant, now explicitly given.
+\item Page 11 -2: (28)$\to$(29), corrected.
+\item Page 11 -3: We have change ``the Cauchy-Schwarz inequality'' to ``the Jensen inequality''.
+\item Pages 11-12: all the constants have been given.
+\item Pages 20-27 -1:
+\item Pages 20-27 -2:
+\item Pages 20-27 -3:
+\item Page 36 : The conflict for the notation have been corrected.
+For the solution there are not reference, we have construct this solution using a separation of the variable.
+we have added the details.
+\item Last point: in 1D we have explicit all the constant.
+We obtain time-exponential rate as you expect.
+Numerically we constat a a time-linear rate, we have added a remark in the numerical part at this subject.
+\end{itemize}
 \end{itemize}

### 2015-04-01 Corrected_version.tex
last correction thomas

@@
 \eps^a
-\right)\leq \varepsilon_{\rm thresh} =h^{\frac{ac}{a+b}  }$, or 
+\right)\leq \varepsilon_{\rm thresh}^a =h^{\frac{ac}{a+b}  }$, or 
 $\eps\geq \varepsilon_{\rm thresh} $ and the same bound is obtained by 
@@
 u^{\eps}(x,t)\right)$ the solution of the hyperbolic heat equations $P^\eps$ and by
-$\V^{\eps}_h(t)=
-\left( \sum_{j\in \mathbb Z} p_j^{\eps}(t) {1}_{\Omega_j} ,  \sum_{j\in \mathbb Z} u_j^{\eps}(t) {1}_{\Omega_j} \right)$ the solution of the JL-(b) scheme $P_h^\eps$. Similarly  we  reconstruct
+$\V^{\eps}_h(t,x)=
+\left( \sum_{j\in \mathbb Z} p_j^{\eps}(t) {1}_{\Delta x_j}(x) ,  \sum_{j\in \mathbb Z} u_j^{\eps}(t) {1}_{\Delta x_j}(x) \right)$ the solution of the JL-(b) scheme $P_h^\eps$, in which ${1}_{\Delta x_j}(x)=1$ if $x\in\Delta x_j$ and $0$ elsewhere.
+We  reconstruct
 similar quantities from the diffusion scheme: it yields 
@@
 $P^0$ (\ref{difffff})-(\ref{eq:diff-v}),
- and  $\W_h^\eps(t)= \left( \sum_{j\in \mathbb Z} p_j(t) {1}_{\Omega_j} ,
-\varepsilon \sum_{j\in \mathbb Z} v_j(t)  {1}_{\Omega_j} \right)$ which is
+ and  $\W_h^\eps(t,x)= \left( \sum_{j\in \mathbb Z} p_j(t) {1}_{\Delta x_j}(x) ,
+\varepsilon \sum_{j\in \mathbb Z} v_j(t)  {1}_{\Delta x_j}(x) \right)$ which is
 the
@@
 \begin{itemize}
-\item $\mathbf V_h^\eps=\left(  \sum_{j\in Cells} p^\eps_j 1_{\Omega_j} , \sum_{j\in Cells} \uu^\eps_j  1_{\Omega_j} \right) $ is the solution of $\mathbf P_h^\eps$.
+\item $\mathbf V_h^\eps(t,\x)=\left(  \sum_{j\in Cells} p^\eps_j(t) 1_{\Omega_j}(\x) , \sum_{j\in Cells} \uu^\eps_j(t)  1_{\Omega_j}(\x) \right) $ is the solution of $\mathbf P_h^\eps$.
 \item 
-$\mathbf V^\eps=\left(p^\eps, \uu^\eps  \right)$ is the solution of $\mathbf P^\eps$,
-\item $\mathbf W_h^\eps=\left(  \sum_{j\in Cells}  p^\eps_j 1_{\Omega_j} ,  \sum_{j\in Cells}  \uu^\eps_j  1_{\Omega_j}  \right) $ is the solution of $\mathbf{DA}_h^\eps$.
+$\mathbf V^\eps(t,\x) =\left(p^\eps, \uu^\eps  \right)(t,\x)$ is the solution of $\mathbf P^\eps$,
+\item $\mathbf W_h^\eps(t,\x) =\left(  \sum_{j\in Cells}  p^\eps_j(t) 1_{\Omega_j}(\x) ,  \sum_{j\in Cells}  \uu^\eps_j(t)  1_{\Omega_j} (\x) \right) $ is the solution of $\mathbf{DA}_h^\eps$.
 Notice that an abuse of notations is been made with the solution
 of $\mathbf P_h^\eps$.
-\item $\mathbf W^\eps= \left( p ,-\frac\eps\sigma \nabla p  \right) $ is the solution of $\mathbf P^0$.
+\item $\mathbf W^\eps (t,\x) = \left( p ,-\frac\eps\sigma \nabla p  \right) (t,\x)$ is the solution of $\mathbf P^0$.
 \end{itemize}

### 2015-05-19 Answers_for_reviewers.tex
modif article

--- 2015-03-20 Answers_for_reviewers.tex
@@
 
+\section{Work done}
+
+The authors deeply thank the referees for their reviews.
+We understant that our work is judged interesting and worth of publications,
+but that the a more detailed of explanation of the estimates and a proof of the fully 
+discrete scheme were necessary.
+We have done this work, together with a reexamination line after line of all estimates.
+
+Our answer to the all question raised in the reports is below.
+In {\bf bold} are the questions/remarks, our answers follow immediately.
+
 \section{Answers for the report 2M}
+
 \begin{itemize}
-\item Constant
+\item {\bf A massive overuse of "Constant C" and the issue of the estimates' time-dependence \dots}
+
+In order to give a positive answer to the question of the "massive overuse of the constant $C$", we have
+completely re-examine all that concerns the constants.
+In order to clarify, we have adopted the following strategy:
+
+a)  the four main constants which correspond to the four branches of the AP diagram and the new AP diagram
+are denoted as $~_\downarrow C$, $C^\rightarrow$, $C_\downarrow$ and $C_\leftarrow$.
+Moreover the dependence with respect to the constant which measures the quality
+of the mesh, denoted as $C_\mathcal M$, and with respect to the Gronwall exponentials
+is indicated systematically {\bf in dimension $n=1$}.
+In 1D, it is now clear that the Gronwall exponentials have zero dependence with respect to $1/\varepsilon$.
+So they are perfectly bounded for a given time $T$. There is no exponential of exponential.
+
+In dimension two, we do not indicate the extra dependance 
+with respect to $C_\mathcal M$ and  the Gronwall-exponentials,
+since it would make the reading much heavier
+once again, and  it would bring almost zero with respect to the 1D case.
+
+The constant $S$ in section 3.5 is now renamed $E_3$.
+
+b) the "sub-sectioning" tries to be more rigorous. For example 
+a new subsection 3.4 now explains the various norms and approximation/interpolation estimates,
+subsection 3.5 is split into sub subsections entitled stability, consistency, ..., 
+subsection 3.6 is split into a rescaling sub subsection, and so on.
+
+c) The main inequality (one of the four branch) of the AP diagram yields a lemma
+which is written at the beginning of the main subsections (3.5, 3.6, 3.7).
+
+d) A new section (asked by the other referred) explains how to use a simple method
+(from Despres, Math of Comp 04) to obtained a $\sqrt{\Delta t}$ error term in time, uniformly
+with respect to $h$ and $\varepsilon$.
+It allows to formulate the  theorem 1.1 immediately in the introduction.
+
+In any cases, we mention to the referee that a huge  work has been done to fulfill his expections.
+It also seems to us more rigorous now.
+
 \begin{itemize}
-\item Page 5 we have modified the constant for the 1D regularity mesh
-\item We have correct the constant in the proposition 2.5 page 8
-\item 1 : we have corrected the constant in the proposition 2.2 page 7
-\item 2 :
-\item 3 :
-\item 4 :
-\item 5 : We have explicit the constant between the equation (32) and the end of the proof of the proposition 2.5
+
+\item {\bf Page 7, Proposition 2.2: as far as I understand, the proof yields C = T. So there's no need for this first constant. Agree ? Same for Prop. 3.1 ?}
+
+we have corrected the constant in the proposition 2.2 page 7
+
+\item {\bf The former comment may seem anecdotal, but it reveals (at least) 2 interesting things: }
+
+\begin{itemize}
+\item 
+{\bf 1.
+assuming p smooth, the approximation (on continuous solutions) is reliable mainly for $t <<\frac1 \epsilon$ }
+
+\item {\bf 2.
+all the remaining Propositions (pages 11-14) ask for the Gronwall lemma in their proofs: hence we obtain bounds growing exponentially in time, suggesting that numerical approximations (discrete solutions) are now r \dots}
+
 \end{itemize}
+
+{\bf Hence I think that the authors shouldn't try to hide this apparent discrepancy under the carpet, because it may be checked numerically rather easily: it suffices to run the code which produced the Figure 6 several times, and scrutinize whether we see a growth in time which is linear, polynomial or exponential.
+Moreover, this will give valuable information on the sharpness of the error bounds rigorously proven}
+
+Already answered: the  important parameters of the  constants are now fully detailed in dimension 1, and partially
+in dimension 2.
+
+\item {\bf Page 8, the estimate (27): the proof is quite easy, so why not displaying it in order to wipe off the C ? It suffices to set up a classical computation, from e.g. DiPerna,
+$$
+\frac12 \frac d {dt} \int_R p^2 dx + \frac1\sigma \int_R |\partial_x p |^2\leq 0 \Longrightarrow \|  p(t,\cdot) \|_{L^2}\leq  \|  p_0 \|_{L^2}.
+$$
+which yields, without introducing any C,
+$$
+\int_0^T \int_R |\partial_x p |^2 dt \leq \frac \sigma 2 \|  p_0 \|_{L^2}^2.
+$$
+}
+
+Corrected.
+
+\item {\bf Page 11, proof of (32)-(33)}
+
 \begin{itemize}
+
+\item {\bf 1.  one can find a constant $C \geq 0$ such that the next term $[\dots]$. Is this
+C the one of the grid introduced in Hypothesis 2.1 ?}
+
+It is the mesh constant, now explicitly given as $C_\mathcal M$ everywhere.
+
+\item {\bf 2. The last term in (28) $[\dots]$: seems like it's (29) instead }
+
+(28)$\to$(29), corrected.
+
+\item {\bf 3.  using a Cauchy-Schwarz inequality $[\dots]$: in my opinion, one should invoke instead Jensen's inequality. Indeed \dots}
+
+We have change ``the Cauchy-Schwarz inequality'' to ``the Jensen inequality''.
+
+\end{itemize}
+
+\item {\bf Pages 11-12, in Proposition 2.6, the C(T) is an exponential of the time T: it must be indicated and the discrepancy with respect to the linear growth found in Proposition 2.2 should be commented.
+Moreover, concerning the estimate (35): the statement is correct, except that it would require a little bit of explanations, as it relies on a bootstrap-type argument based on estimate (27), which wasn?t stated really correctly (as already seen).}
+
+Pages 11-12: all the constants have been given.
+
+\item 
+{\bf Pages 20-27: the statements and proofs of Props. 3.4 and 3.5 are A MESS!}
+
+Entirely reshaped as already mentioned above.
+
+\begin{itemize}
+\item
+
+{\bf 1. When studying the different terms in $E'(t)$, please use either itemize or enumerate, and perhaps forward heavy calculations to an 
+Appendix in order to lighten stuff,}
+
+Done.
+
+\item {\bf 2. Props. 3.6-8 are indeed "technical Lemmas" and should be stated accordingly (cf. comments on the 1D case of Prop. 2.8). Their proofs might be forwarded too.}
+
+\item {\bf 3. the 1D comment about Jensen's inequality appears to apply here again, bottom of page 26 }
+
+Jensen does not show up anymore.
+
+\end{itemize}
+
+\item {\bf Page 36, 4: perhaps a bibliographic reference for the solution of the telegraph's equation may be useful to the reader.
+Moreover, there is a conflict of notation between the $\gamma$ used here and the one invoked in the proofs on pages 25-26-27}
+
+Page 36 : The conflict for the notation have been corrected. For the solution there are not reference, we have construct this solution using a separation of the variable. we have added the details.
+
+\item {\bf As said before, there's a question which should be addressed, that is the rate of amplification in time of the errors: the Gronwall?s Lemma produces a time-exponential rate, so it's interesting to check out numerically if this feature is a discrepancy of the analysis, or if it holds practically.
+Such a point was addressed, in a totally different context of scalar balance laws.
+
+{\it D. Amadori, L. Gosse, Transient $L1$
+ error estimates for well-balanced schemes on non-resonant scalar balance laws, J. Differential Equations 255 (2013) 469-502}
+
+}
+
+\item Last point: in 1D we have explicit all the constant.
+We obtain time-exponential rate as you expect.
+Numerically we constat a a time-linear rate, we have added a remark in the numerical part at this subject.
+
+\item 
+Additional modifications: Page 5 we have modified the constant for the 1D regularity mesh;
+We have correct the constant in the proposition 2.5 page 8.
+\end{itemize}
+
+\end{itemize}
+
+\begin{itemize}
+
 \item Comments and suggestions
 \begin{itemize}
-\item 1: We have added two subsections : "Precisions on AP discretizations" and "Organisation of the proof"
-\item 2: we have added 2 sentences about the 2D Riemann problem and the nodal scheme. 
-\item 3: We have added a sentence to explain why we use this formulation of the scheme and not the classical Gosse-Toscani scheme.
+\item 
+{\bf Pages 2-': with an Introduction that long, it makes sense to insert "sub- sections" entitled "Precisions on AP discretizations" (right after Remark 1.2), and ?Organization of the paper?
+(right after the proof of Prop 1.3 }
+
+ We have added two subsections : "Precisions on AP discretizations" and "Organisation of the proof"
+
+\item {\bf Page 5: is there a connection between "nodal-based" FV schemes (advocated in the Intro.) and the classical Godunov scheme where 2D Riemann problems are to be solved at each node of the computational grid ?
+See for instance the elementary case of a non-resonant scalar balance law in,
+L. Gosse, A two-dimensional version of the Godunov scheme for scalar balance laws. SIAM J. Numer. Anal. 52 (2014) 626-652.
+If so, the sentence in the Introduction "it strongly questions ..." wouldn't be that surprising.
+Moreover, on page 27, the authors speak about the "incorporation in the approximate nodal Riemann solver", thus reinforcing this vague impression of similarity with 2D Riemann solvers}
+
+We  added 2 sentences about the 2D Riemann problem and the nodal scheme. 
+We agree that there is a similarity, but essentially concerning the final formula itself.
+The method is rather different.
+
+\item {\bf Page 6: The big footnote is confusing: in my opinion, it would be better to state clearly that, in order to build a discretization able to produce a 2D AP numerical process, the authors choose to renounce to the well- balanced property of the original 1D Gosse-Toscani scheme (except on uniform Cartesian grids) while retaining only its AP character.
+This ex- plains why the algebraic expressions differ from each other.}
+
+We have added a sentence to explain why we use this formulation of the scheme and not the classical Gosse-Toscani scheme.
+
 For the remark about " the authors choose to renounce to the well- balanced property of the original 1D Gosse-Toscani scheme (except on uniform Cartesian grids) while retaining only its AP character" it is not clear that we say that.
@@
 At the end we renounce only to the steady states associated to $\nabla{u}=\nabla\times \phi$ with $\phi$ a potential.
-\item 4: We have correct this part introducing $v$ to obtain a not confusing proof.
-\item 5: We have replaced is $\mathbf{u}^{\eps}$ by $u^{\eps}$
-\item 6 : We have replaced the proposition 2.8 by the Lemma 2.8
-\item 7 : We have added the reference on the paper "Time asymptotic high order ..." at the end of the 2D in the numerical results.
-\item 8 : We have corrected the proposition 
-\item 9 : We have added the missing "("
+
+\item {\bf Page 7, Proof of Prop. 2.2, the notation choice $u^\epsilon=-\frac\sigma \epsilon \partial _x p^\epsilon$  is confusing:
+according to (13), a notation like $v^\epsilon$ looks better.}
+
+ We have correct this part introducing $v$ to obtain a not confusing proof.
+
+\item {\bf Page 10, last lines, what is the definition of $\mathbf u^{\eps}$ ? This notation doesn?t
+appear previously.}
+
+ We have replaced is $\mathbf{u}^{\eps}$ by $u^{\eps}$
+
+\item {\bf Page 14, the Proposition 2.8 is indeed a (technical) Lemma, and this should be stated accordingly}
+
+We have replaced the proposition 2.8 by the Lemma 2.8
+
+\item {\bf Page 14, end of the 1D section: according to what is displayed numerically in the §4, Figure 6, we see a second-order accuracy
+ (in h) for $\epsilon \approx  h^2$. This appears to be an extension in 2D of an observation made in a paper devoted to 
+ "TAHO schemes", see especially §7.1.2 in,
+D. Aregba, M. Briani, R. Natalini, Time Asymptotic High Order Schemes for Dissipative BGK Hyperbolic Systems, arXiv:1207.6279}
+
+We have added the reference on the paper "Time asymptotic high order ..." at the end of the 2D in the numerical results.
+
+\item {\bf Page 15, Proposition 3.1: same comment than for Proposition 2.2}
+
+We have corrected the proposition
+
+\item {\bf Page 15, eqn. (45), there is a "(" missing in the first line.}
+
+We have added the missing "(".
 \end{itemize}
+
 \item Minor issues and Typos
@@
 \end{itemize}
+
+\section{Answers for the report 2C}
+
+Before answering to explain what we have done, we would like to make a general comment.
+
+We still consider that the space discretization is the most important, in the sense
+that such multiD method can be used by researchers and engineers only if they are proved
+to be convergent, in the usual sense.
+That it is converge for a family of smooth enough functions.
+The question of the boundary in time
+layer plays little role for the application we have in mind.
+On the contrary, discontinuity of the coefficients of the equations may generate 
+some boundary layers in space. For radiation equation this is called the Milne problem.
+This issue is of tremendous importance, but seems to us difficult to address in general, not only for the scheme that we develop.
+
+On the other hand our method is the first which is proved to be convergent: what we think is of real importance
+is the fact that usual Finite Volume technique through the edges are not able have a geometrical
+obstruction for AP on a general mesh. This is why our method for which fluxes are corner based 
+seems a real advance.
+
+Now we answer to 
+{\bf  The issue concerning the time
+discretization must be addressed correctly.
+}.
+
+This issue was not addressed at all because it seems to us that the convergence in space was the real point.
+Nevertheless we do agree with the referee.
+This is why was have now done the following.
+
+\begin{itemize}
+\item the theorem of convergence for a fully explicit scheme is written in the introduction, and proved
+in section  4b by the abstract method (the main idea was given in  despres 04, but
+the new proof is much more direct). This method easily give a uniform estimate 
+between the continuous and fully discrete solutions, so proves the theorem when combined with the previous results.
+
+\item Furthermore we have restructure most of the material. The proof of the naive estimate in 2D 
+is in two parts, the technical details being in the appendix is asked by the other referee.
+We also give a much more detailed presentation of the constants
+$~_\downarrow C$, $C^\rightarrow$, $C_\downarrow$ and $C_\leftarrow$ with the regularity of the initial data
+and other constants.
+
+\item We feel the entire work is more complete rigorous with these two modifications.
+
+\end{itemize}
+
+The proposed method has already been applied to to a non linear diffusion equation in  (see references):
+{\it C. Buet, B. Despr\'es, E. Franck, \emph{An asymptotic
+preserving scheme with the maximum principle for the $M_1$ model on distorted
+meshes}, C.R. Acad. Sci., Paris, S\'er. I, Math., Vol 350,  11-12
+pp 633-638,  2012.}
+
+The propose references are relevant. They have been added and discussed with the other references in the introduction.
+
 \end{document}

### 2015-05-19 code_FVFSHS_2D_matter/BC/BoundaryConditionP1.cpp
correction code :)

@@ -42,9 +42,26 @@ For triangular mesh only the Boundary conditions based on th exact solutions are
 	break;
 
       case 6 : BC_Periodic_P1(d,Mh,v,Param,time);
-       
+
+	break;
+
+      case 7 : BC_2DRiemann_P1(d,Mh,v,Param,time);
 	
-	break;}
+	break;
+
+      case 8 : BC_2DRiemann_P1(d,Mh,v,Param,time);
+	
+	break;
+
+      case 9 : BC_2DRiemann_P1(d,Mh,v,Param,time);
+	
+	break;
+
+      case 10 : BC_2DRiemann_P1(d,Mh,v,Param,time);
+	
+	break;
+
+      }
   }
 
   if (d.Typemesh=='T'){
@@ -119,6 +136,70 @@ void BCNeumann_P1(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double ti
   }
 }
 
+
+void BC_2DRiemann_P1(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time){
+ /** Function which initialize the phantom cells to have Neumann condition **/
+  for(int j=0;j<Mh.nc;j++){
+    if(Mh.cells[j].lab==-1){
+
+	    //cote gauche
+
+	    if((Mh.xj(j).x < 0) && (Mh.xj(j).y> 0 && Mh.xj(j).y< d.Ty)){
+	     v.var[0][j]=v.var[0][j+1];
+	     v.var[1][j]=v.var[1][j+1];	//-
+	     v.var[2][j]=v.var[2][j+1];
+	   }
+	    //cote droit
+	    if(Mh.xj(j).x> d.Tx && (Mh.xj(j).y> 0 && Mh.xj(j).y< d.Ty)){
+	     v.var[0][j]=v.var[0][j-1];
+	     v.var[1][j]=v.var[1][j-1];
+	     v.var[2][j]=v.var[2][j-1]; //-
+	   }
+	    //cote bas
+	    if(Mh.xj(j).y< 0 && (Mh.xj(j).x> 0  && Mh.xj(j).x< d.Tx)){
+	      v.var[0][j]=v.var[0][j+(d.Nx+2)];
+	      v.var[1][j]=v.var[1][j+(d.Nx+2)];
[…]

### 2015-05-19 code_FVFSHS_2D_matter/Diagnostics/Diagnostics.cpp

@@ -113,6 +113,20 @@ double NormLP_Stability(Data & d, Mesh & Mh,variable & v,ParamPhysic & Param,dou
      return res;	 
 }
 
+double NormLP_One_variable_Stability(Data & d, Mesh & Mh,variable & v,ParamPhysic & Param,double p,int ivar){
+   /** Function which compute the Lp norm associated with one discrete quantity for the different models **/
+  double res=0.;
+  double sum=0;
+  
+
+  for(int j=0;j<Mh.nc;j++){
+     if(Mh.cells[j].lab!=-1){
+    res=res+Mh.area(j)*pow(Valabs(v.var[ivar][j]),p);
+     }
+  }		  
+  res=pow(res,1/p);
+     return res;	 
+}
 
 double Mass(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,double time){
   /** Function which compute the mass associated with the first quantity for the different models **/
@@ -131,13 +145,19 @@ double Mass(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,double time){
 void Diagnostics_Quantities(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,int nt,double time){
   /** Function which gives the diagnostics for the numerical stability **/
   double Mass_0=0;
-  double p=1.;
   
-    if((nt%20)==0) {
-      Mass_0 = Mass(d,Mh,v,Param,time);
+    if((nt%50)==0) {
       cout<<"Iteration n "<<nt<<" correspondant au temps :"<<time<<endl;
-      cout<<"masse "<<pow(Mass_0,1./p)<<endl;
-
+      cout<<"masse "<<Mass(d,Mh,v,Param,time)<<endl;
+      cout<<"norme L2 :"<<NormLP_Stability(d,Mh,v,Param,2.)<<endl;
+      if( TraceSolfond(d,Param) == 1){
+	cout<<"Error L1 :"<<Diagnostics_Error(d,Mh,v,Param,time,1.)<<endl;
+	cout<<"Error L2 :"<<Diagnostics_Error(d,Mh,v,Param,time,2.)<<endl;
+	cout<<"Error L2 relative :"<<Diagnostics_Error(d,Mh,v,Param,time,2.)/NormLP_Stability(d,Mh,v,Param,2)<<endl;
+      }
[…]

### 2015-05-19 code_FVFSHS_2D_matter/Flux/FluxP1Vertex.cpp

@@ -23,7 +23,7 @@ vectorflux FluxVertexP1(Data & d,int numCell,Mesh & Mh, variable & v, TabConnecI
   int z=0;
   double signode=0;
   double epsnode=0;
-  double var0jr=0, var1jr=0, var2jr=0;
+
 
   if(d.scheme==1){
     z=1;} /** JL-(a) scheme**/
@@ -41,21 +41,11 @@ vectorflux FluxVertexP1(Data & d,int numCell,Mesh & Mh, variable & v, TabConnecI
      signode=AverageSigNodeP1(d,Mh,v,tab,Param.P1,numGr,numCell);
      epsnode=AverageEpsNodeP1(d,Mh,v,tab,Param.P1,numGr,numCell);
 
-     var0jr=InterLineVertex(d,Mh,v,tab,Param,0,d.Total_order,numCell,r);
-     var1jr=InterLineVertex(d,Mh,v,tab,Param,1,d.Total_order,numCell,r);
-     var2jr=InterLineVertex(d,Mh,v,tab,Param,2,d.Total_order,numCell,r);
-       
-     Fu1=var0jr*Mh.njr(numCell,r).x+alpha.ten[0][0]*(var1jr-sol.x)+alpha.ten[0][1]*(var2jr-sol.y)
-       -z*(signode/epsnode)*(sol.x*beta.ten[0][0]+sol.y*beta.ten[0][1]);
+      Fu1=v.var[0][numCell]*Mh.njr(numCell,r).x+alpha.ten[0][0]*(v.var[1][numCell]-sol.x)+alpha.ten[0][1]*(v.var[2][numCell]-sol.y)
+      -z*(signode/epsnode)*(sol.x*beta.ten[0][0]+sol.y*beta.ten[0][1]);
      
-     Fu2=var0jr*Mh.njr(numCell,r).y+alpha.ten[1][0]*(var1jr-sol.x)+alpha.ten[1][1]*(var2jr-sol.y)
+      Fu2=v.var[0][numCell]*Mh.njr(numCell,r).y+alpha.ten[1][0]*(v.var[1][numCell]-sol.x)+alpha.ten[1][1]*(v.var[2][numCell]-sol.y)
        -z*(signode/epsnode)*(sol.x*beta.ten[1][0]+sol.y*beta.ten[1][1]);
-
[…]

### 2015-05-19 code_FVFSHS_2D_matter/Flux/FluxVertexM1.cpp

@@ -264,20 +264,22 @@ vectorflux FluxVertexClassicM1(Data & d,int numCell,Mesh & Mh, variable & v, Tab
   for(int r=0;r<Mh.nbnodelocal;r++){
 
      numGr=Mh(numCell,r);
-     sol=ur[numGr];
+     sol=ur[numGr]; // Lagrangian Velocity flux
      beta=inittensor(d,Mh,v,tab,'s',numGr,numCell);
      alpha=inittensor(d,Mh,v,tab,'h',numGr,numCell);
      
-     qj=q(d,Param.M1,v.var[0][numCell],v.var[1][numCell],v.var[2][numCell]);
-     Calcul_u(d,Mh,v,tab,Param.M1,uj,numCell);
-     rjr=(4./sqrt(3.))*(v.var[0][numCell]/(3+(uj,uj)));
+     qj=q(d,Param.M1,v.var[0][numCell],v.var[1][numCell],v.var[2][numCell]); // pressure in the cell
+     Calcul_u(d,Mh,v,tab,Param.M1,uj,numCell); // velocity in the cell
+     rjr=(4./sqrt(3.))*(v.var[0][numCell]/(3+(uj,uj))); // speed velocity 
      
      Gjr.x=Mh.ljr(numCell,r)*(qj*Mh.njr(numCell,r).x+rjr*(alpha.ten[0][0]*(uj.x-sol.x)+alpha.ten[0][1]*(uj.y-sol.y)));
 			      
-     Gjr.y=Mh.ljr(numCell,r)*(qj*Mh.njr(numCell,r).y+rjr*(alpha.ten[1][0]*(uj.x-sol.x)+alpha.ten[1][1]*(uj.y-sol.y)));						          
-     s[0]=s[0]+remap(d,Mh,v,0,tab,Param,numCell,r,ur,sol)+(sol,Gjr);
-     s[1]=s[1]+remap(d,Mh,v,1,tab,Param,numCell,r,ur,sol)+Gjr.x;                    
-     s[2]=s[2]+remap(d,Mh,v,2,tab,Param,numCell,r,ur,sol)+Gjr.y;
+     Gjr.y=Mh.ljr(numCell,r)*(qj*Mh.njr(numCell,r).y+rjr*(alpha.ten[1][0]*(uj.x-sol.x)+alpha.ten[1][1]*(uj.y-sol.y)));
+     // pressure flux lagrangian 
+     
[…]

### 2015-05-19 code_FVFSHS_2D_matter/Flux/FluxVertexM1Matter.cpp

@@ -9,6 +9,82 @@
 #include "FunctionsAdvection.hpp"
 
 
+/** Calcul de la pression q**/
+double q_M1M(Data & d, ParamM1Matter & M1Matter,double E,double F1, double F2){
+    /**  function which compute the isotorpic pressure of the M1 model **/
+  double res;
+  R2 f;
+  if(E==0){
+    res=0;
+  }
+  else{
+    f.x=F1/(E);
+    f.y=F2/(E);
+      double khi=(3.+4.*(f,f))/(5.+2.*sqrt(4.-3.*(f,f)));
+      res=0.5*(1.-khi)*E;
+  }
+  return res;
+}
+
+/** Calcul du coefficient kr**/
+double coefk_M1M(Data & d, ParamM1Matter & M1Matter,double E,double F1, double F2){
+    /**  function which compute the coefficienty k define by F=k U, with F the flux and U the velocity in the euler description **/
+  double res=0.;
+  R2 f(0,0);
+ 
+  if(E==0){
+    res=0;
+  }
+  else{
+    f.x=F1/(E);
+    f.y=F2/(E);
+    if(f.x==0 && f.y==0){
+       res=(4./3.)*E;
+     }
+     
+     else{
+       double khi=(3.+4.*(f,f))/(5.+2.*sqrt(4.-3.*(f,f)));
+         if(khi < (1./3.)+0.000001 && khi >(1./3.)-0.000001){
+        res=(4./3.)*E;
+       }
+       else{
+	res=(2.*E*(f,f))/(3.*khi-1.);
+       }     
+     }
+  }
+  return res;
+
+}
+
+void  Calcul_u_M1M(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab, ParamM1Matter & M1Matter,R2 & u,int numCell){
+    /** Function which compute the velocity U in cell "numcell" **/
+  R2 f;
+  double khi;
+
+    if(v.var[0][numCell]==0){
+      u.x=0;
+      u.y=0;
+    }
+    else{
+      f.x=v.var[1][numCell]/(v.var[0][numCell]);
+      f.y=v.var[2][numCell]/(v.var[0][numCell]);
+       if((f.x==0 && f.y==0)){
+	u.x=0;
[…]

### 2015-05-19 code_FVFSHS_2D_matter/Flux/FunctionsAdvection.cpp

@@ -227,7 +227,7 @@ double InterLineVertex(Data d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamPhy
    /** function which compute the value used by the scheme. Cell average for the order 1, linear reconstruction for the order 2 **/
   double res=0;
   int numGr;
-
+  
   if(ordre==1){
     res=v.var[var][j];
   }
@@ -238,6 +238,7 @@ double InterLineVertex(Data d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamPhy
       Grad=Gradiant(d,Mh,v,var,tab,Param,numGr);
       m=VertexSlope(d,Mh,v,var,tab,Param,j,Grad);
       res=v.var[var][j]-m*((Mh.xr(j,r)-Mh.xj(j)),Grad);
+
     }
   
   return res;

### 2015-05-19 code_FVFSHS_2D_matter/Init/InitM1Matter.cpp

@@ -20,13 +20,19 @@ void InitM1Matter(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param){
     {
             
         case 1 :
-            // Marshak linear
-            T=300;
             for(int j=0;j<Mh.nc;j++){
-                v.var[0][j]=Param.M1M.a_value*pow(T,4.);
-                v.var[1][j]=0;
-                v.var[2][j]=0;
-                v.var[2][j]=T;
+	      if(Mh.xj(j).x < 0.5*d.Tx){
+		v.var[0][j]=2;
+		v.var[1][j]=0;
+		v.var[2][j]=0;
+		v.var[3][j]=1.e-14;
+	      }
+	      else {
+		v.var[0][j]=1.e-14;
+		v.var[1][j]=0;
+		v.var[2][j]=0;
+		v.var[3][j]=2;
+	      }
             }
             break;
             

### 2015-05-19 code_FVFSHS_2D_matter/Init/InitP1.cpp

@@ -16,6 +16,7 @@
   **/
   
     int in=0;
+    double a=0;
     in=centerdomain(d,Mh);
      switch(d.nTest)
     {
@@ -72,7 +73,63 @@
 	v.var[2][j]=0; /// A verifier
       }     
       break;
-    
+
+       case 7 :
+      for(int j=0;j<Mh.nc;j++){
+	if( ((Mh.xj(j).x -1.0) * (Mh.xj(j).y -1.0))>0.0){
+	  a=1;
+	}  
+	else  {
+	  a=-1;
+	} 
+	v.var[0][j]=0;
+	v.var[1][j]=0;
+	v.var[2][j]=a; /// A verifier
+      }     
+      break;
+
+       case 8 :
+      for(int j=0;j<Mh.nc;j++){
+	if( ((Mh.xj(j).x -1.0) * (Mh.xj(j).y -1.0))>0.0){
+		  a=1;
+	}  
+	else  {
+	  a=-1;
+	} 
+	v.var[0][j]=0;
+	v.var[1][j]=a;
+	v.var[2][j]=a; /// A verifier
+      }     
+      break;
+
+       case 9 :
+      for(int j=0;j<Mh.nc;j++){
+	if( ((Mh.xj(j).x -1.0) * (Mh.xj(j).y -1.0))>0.0){
+	  a=1;
+	}  
+	else  {
+	  a=-1;
+	}     
+	v.var[0][j]=a;
+	v.var[1][j]=a;
+	v.var[2][j]=a; /// A verifier
+      }     
+      break;
+
+      case 10 :
+      for(int j=0;j<Mh.nc;j++){
+	if( ((Mh.xj(j).x -1.0) * (Mh.xj(j).y -1.0))>0.0 && Mh.xj(j).x>1.0){
+	  a=1;
+	}  
+	else  {
+	  a=0;
+	}     
+	v.var[0][j]=a;
+	v.var[1][j]=0;
+	v.var[2][j]=0; /// A verifier
+      }     
+      break;
+
   }
 }
 

### 2015-05-19 code_FVFSHS_2D_matter/Init/InitP1Matter.cpp

@@ -26,7 +26,7 @@ void InitP1Matter(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param){
 	v.var[0][j]=Param.P1M.a_value*pow(T,4.);
 	v.var[1][j]=0;
 	v.var[2][j]=0;
-	v.var[2][j]=T;
+	v.var[3][j]=T;
       }
       break;
       

### 2015-05-19 code_FVFSHS_2D_matter/Mesh/UsualMesh.cpp

@@ -985,7 +985,7 @@ Mesh CheckMesh(Data & d){
     if (d.Nx==630){ mod=90;}
     if (d.Nx==700){ mod=100;}
     
-    Mesh Mh(d);
+     Mesh Mh(d);
     Dx=d.Tx/(double)d.Nx; // uniform step mesh in the x direction
     Dy=d.Ty/(double)d.Ny;
     

### 2015-05-19 code_FVFSHS_2D_matter/PlotDatas/WriteData.cpp

@@ -12,7 +12,7 @@ using namespace std;
 /** File which contains the functions for the plot **/
 
 
-void SaveData(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,int ntAnim){
+void SaveData(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamPhysic & Param,int ntAnim){
   /** Function which find the numbers of the variables plotted **/
   int TabNumVar[300];
   int NbVarWrite;
@@ -41,27 +41,110 @@ void SaveData(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,int ntAnim){
       } 
       if(d.dimsave==2){
 	if(d.Typewrite=='N'){
-	  SaveOneData(d,Mh,v,Param,TabNumVar[j],ntAnim);
+	  SaveOneData(d,Mh,v,tab,Param,TabNumVar[j],ntAnim);
 	}
 	if(d.Typewrite=='C'){
-	  SaveOneDatacentercell(d,Mh,v,Param,TabNumVar[j],ntAnim);
+	  SaveOneDatacentercell(d,Mh,v,tab,Param,TabNumVar[j],ntAnim);
 	}
       }
       if(d.dimsave==1 && d.Ny == 1){
-	SaveOneData1D(d,Mh,v,Param,TabNumVar[j],ntAnim);
+	SaveOneData1D(d,Mh,v,tab,Param,TabNumVar[j],ntAnim);
 	
       }
     }
 
   
   if(Param.Model == 5) {
-    SaveInterEner(d,Mh,v,Param,ntAnim); 
+    SaveInterEner(d,Mh,v,tab,Param,ntAnim); 
+  }
+  if(Param.Model == 3) {
+    Save_vorticity(d,Mh,v,tab,Param,ntAnim); 
   }
 
 }
 
 
-void SaveOneData(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,int Num,int ntAnim){
+void Save_vorticity(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamPhysic & Param,int ntAnim){
+ /** Function which plot in 2D the variable "num" using the average in the cell**/
+  char string[255];
+  FILE *fileresult=NULL;
+  int j,n;
+  int in=0;
[…]

### 2015-05-19 code_FVFSHS_2D_matter/PlotDatas/WriteData_Euler.cpp

@@ -10,7 +10,7 @@
 /** File which contains the functions for the plot of Euler quantities **/
 
 
-void SaveInterEner(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,int ntAnim){
+void SaveInterEner(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamPhysic & Param,int ntAnim){
 /** Function which plot the internal energy for Eler model **/
   char string[255];
   FILE *fileresult=NULL;
@@ -55,7 +55,7 @@ void SaveInterEner(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,int ntAni
 }
 
 
-void SaveFonction2DEuler(Data & d,Mesh & Mh,ParamPhysic & Param,float t,Vertex c,int Num){
+void SaveFonction2DEuler(Data & d,Mesh & Mh,TabConnecInv & tab,ParamPhysic & Param,float t,Vertex c,int Num){
 /** Function which plot the non conservative quantities for Euler**/
   char string[255];
   FILE *fileresult=NULL;

### 2015-05-19 code_FVFSHS_2D_matter/Prog.cpp

@@ -45,10 +45,10 @@ int main() {
   /** Connectivity table construction **/
   struct TabConnecInv TConnectInv;
   CreateTabInv(Mh,TConnectInv);  
-
+  
   /** Physical parameters construction **/
   ParamPhysic Param(d,Mh);
-  
+
   /** Variable contruction and initialization **/
   variable v(d,Mh.nc,Mh.nv);
   
@@ -61,7 +61,7 @@ int main() {
 
   /** Plot informations of the run and plot mesh **/
   WriteDataToMain(d,Param);
-  SaveMesh(d,Mh);
+  SaveMesh(d,Mh,TConnectInv);
  
   /** definition of the time quantities **/
   int SI=0;
@@ -69,7 +69,7 @@ int main() {
   int ntAnim=0;
 
  
- 
+  cout << "Time step: "<<dt<<endl;
 
 
   /** Time loop **/    
@@ -95,7 +95,7 @@ int main() {
 
   /** Save final data **/
   SaveRestart(d,Mh,v,Param,0,time);
-  SaveData(d,Mh,v,Param,ntAnim);   
+  SaveData(d,Mh,v,TConnectInv,Param,ntAnim);   
  
   /** free memory **/
   for(int i=0;i<TConnectInv.nbvertex;i++){
@@ -106,9 +106,10 @@ int main() {
   
   /** Computation and plot of exact solutions. Computation of errors **/
   if(TraceSolfond(d,Param)==1){
+    cout<< "Final error"<<endl;
     cout <<"The L"<<1<<" norm is : "<<Diagnostics_Error(d,Mh,v,Param,d.Tf,1.)<<endl;     
     cout <<"The L"<<2<<" norm is : "<<Diagnostics_Error(d,Mh,v,Param,d.Tf,2.)<<endl;
-    SaveFonction(d,Mh,Param,d.Tf,Mh.cells[in].centercell); 
+    SaveFonction(d,Mh,TConnectInv,Param,d.Tf,Mh.cells[in].centercell); 
   }  
   cout <<" The step mesh is :"<<StepMesh(Mh)<<endl;
  

### 2015-05-19 code_FVFSHS_2D_matter/Source/SourceM1Matter.cpp

@@ -21,72 +21,41 @@ vectorflux SourceM1Matter(Data & d,int numCell,Mesh & Mh, variable & v, TabConne
     
     int compton_scattering = 1 ; //(1 if taken into account, 0 if not)
     
-    kj=coefk(d,Param.M1,v.var[0][numCell],v.var[1][numCell],v.var[2][numCell]);
-    Calcul_u(d,Mh,v,tab,Param.M1,uj,numCell);
-    
-    if(d.Typetime == 'E')
-    {
-        if( d.scheme==1 )
-        {
-            res.vflux[0] = 0. ;
-            res.vflux[1] = -((Param.M1.sigma[numCell])/(Param.M1.eps[numCell]*Param.M1.eps[numCell]))*Mh.area(numCell)*v.var[1][numCell];
-            res.vflux[2] = -((Param.M1.sigma[numCell])/(Param.M1.eps[numCell]*Param.M1.eps[numCell]))*Mh.area(numCell)*v.var[2][numCell];
-            res.vflux[3] = 0. ;
+ 
+    res.vflux[0] = 0. ;
+    res.vflux[1] = -(4./3.)*((Param.M1M.sigma[numCell])/(Param.M1M.eps[numCell]*Param.M1M.eps[numCell]))*Mh.area(numCell)*v.var[1][numCell];
+    res.vflux[2] = -(4./3.)*((Param.M1M.sigma[numCell])/(Param.M1M.eps[numCell]*Param.M1M.eps[numCell]))*Mh.area(numCell)*v.var[2][numCell];
+    res.vflux[3] = 0. ;
             
-            if (compton_scattering == 1)
-            {
+    if (compton_scattering == 1)
+      {
                 
-                double T = 1. ; // temperature electron
-                double sigma_a = Param.M1.sigma[numCell] ;
-                
-                double temp = 0. ;
-                double source_E = 0. ;
-                double source_F = 0. ;
-                R2 g ;
-                
-                g.x = v.var[1][numCell] / v.var[0][numCell] ;
-                g.y = v.var[2][numCell] / v.var[0][numCell] ;
-                
-                temp = 2. + sqrt(4.-3.*(g,g)) ;
-                
[…]

### 2015-05-19 code_FVFSHS_2D_matter/Timeschemes/ExplicitScheme.cpp

@@ -45,16 +45,18 @@ void ExplicitDiscret(Data & d,Mesh & Mh, variable & v,TabConnecInv & TConnectInv
        if(time+dt>d.Tf) {
 	 dt=d.Tf-time;
        }
+      
 
        /** apply boundary condition (phantom cell) **/ 
        BoundaryCondition(d,Mh,v,Param,time);
-       
+  
        if(d.Anim=='y' && time>=d.dtAnim*ntAnim){
-	  SaveRestart(d,Mh,v,Param,nt,time);
-	 SaveData(d,Mh,v,Param,ntAnim);
+   
+	 SaveRestart(d,Mh,v,Param,nt,time);   
+	 SaveData(d,Mh,v,TConnectInv,Param,ntAnim);
+	    
 	 ntAnim++;
-       } 
-
+       }  
        /** Diagnostic : masse, velocity etc **/
         Diagnostics_Quantities(d,Mh,v,Param,nt,time);   
 
@@ -75,7 +77,7 @@ void ExplicitDiscret(Data & d,Mesh & Mh, variable & v,TabConnecInv & TConnectInv
        /** Computation of the flux and source term and update of the time solution **/
        #pragma omp parallel for private(flux,source) 
        for( j=0;j<Mh.nc;j++){
-       if(Mh.cells[j].lab!=-1){
+	  if(Mh.cells[j].lab!=-1){
             if(d.Typescheme == 'N' ){
 	      flux=ChoiceFluxN(d,j,Mh,v,TConnectInv,Param,ur);
             }  
@@ -87,6 +89,7 @@ void ExplicitDiscret(Data & d,Mesh & Mh, variable & v,TabConnecInv & TConnectInv
 	    source=ChoiceSource(d,j,Mh,v,TConnectInv,Param,ur);
 	 for(int i=0;i<v.nbvar;i++){
 	   temp.var[i][j]=v.var[i][j]+(dt/Mh.area(j))*(flux.vflux[i]+source.vflux[i]);
+	   //cout<<" ppp "<<flux.vflux[i]<<" "<<source.vflux[i]<<endl;
 	   if (v.var[0][j]<0){
 	     c++; 
 	   }   

### 2015-05-19 code_FVFSHS_2D_matter/Timeschemes/SemiExScheme.cpp

@@ -110,7 +110,9 @@ void SemiImplicit(Data & d,Mesh & Mh, variable & v,TabConnecInv & TConnectInv, P
   temp=v;
   R2 *ur =new R2[Mh.nv];
   double c=0;
- 
+  FILE *fileresult=NULL;
+  char string[255];
+  
   /** computaion of the table for variables parameters  **/ 
   ParamPhysic_InitTab(d,Mh,v,TConnectInv,Param);
 
@@ -122,6 +124,9 @@ void SemiImplicit(Data & d,Mesh & Mh, variable & v,TabConnecInv & TConnectInv, P
     }
   }
 
+  //sprintf(string,"TimeError.dat");
+  //fileresult=fopen(string,"w");
+  
    while(time<d.Tf)
      {
        if(time+dt>d.Tf) {
@@ -129,8 +134,11 @@ void SemiImplicit(Data & d,Mesh & Mh, variable & v,TabConnecInv & TConnectInv, P
        }
 
        if(d.Anim=='y' && time>=d.dtAnim*ntAnim){
+	 
+	 //	 fprintf(fileresult,"%e %e %e %e\n",time,Diagnostics_Error(d,Mh,v,Param,time,1.),Diagnostics_Error(d,Mh,v,Param,time,2.),Diagnostics_Error(d,Mh,v,Param,time,2.)/NormLP_Stability(d,Mh,v,Param,2));
+
          SaveRestart(d,Mh,v,Param,nt,time);
-	 SaveData(d,Mh,v,Param,ntAnim);
+	 SaveData(d,Mh,v,TConnectInv,Param,ntAnim);
  
 	 ntAnim++;
        } 
@@ -201,7 +209,8 @@ void SemiImplicit(Data & d,Mesh & Mh, variable & v,TabConnecInv & TConnectInv, P
 	  
      }
    delete [] ur;
-    cout<<"negative coefficients " <<c<<" "<<" dt "<<dt<<endl;
+   
+   // fclose(fileresult);
 }
 
 

### 2015-05-19 code_FVFSHS_2D_matter/hppParam/ParamEuler.hpp

@@ -113,50 +113,7 @@ public:
  LSProblem & operator=(const LSProblem & ls){
    NColum=ls.NColum;
    NLign=ls.NLign;
-   /**
-   if(A==NULL){
-     A = new double[ls.NLign*ls.NColum];
-   }
-
-   for(int i=0;i<ls.NLign*ls.NColum;i++){
-     A[i]= ls.A[i];
-     }
-   
-   if(b_rho==NULL){
-     b_rho = new double[ls.NLign];
-   }
-   for(int i=0;i<ls.NLign;i++){
-     b_rho[i]= ls.b_rho[i];
-   }
-   
-    if(b_pressure==NULL){
-     b_pressure = new double[ls.NLign];
-   }
-   for(int i=0;i<ls.NLign;i++){
-     b_pressure[i]= ls.b_pressure[i];
-     }
-   
-   if(Sol_rho==NULL){
-     Sol_rho = new double[ls.NColum];
-   }
-   for(int i=0;i<ls.NColum;i++){
-     Sol_rho[i]= ls.Sol_rho[i];
-   }
-   
-   if(Sol_pressure==NULL){
-     Sol_pressure = new double[ls.NColum];
-   }
-   for(int i=0;i<ls.NColum;i++){
-     Sol_pressure[i]= ls.Sol_pressure[i];
-   }
-   
-   if(Stencil==NULL){
-     Stencil= new int[ls.NLign];
-   }
-   for(int i=0;i<ls.NLign;i++){
-     Stencil[i]= ls.Stencil[i];
-   }
-   **/
+  
    
    if(A!=NULL){
      delete [] A;

### 2015-05-19 code_FVFSHS_2D_matter/hppfiles/BoundaryCondition.hpp

@@ -46,6 +46,8 @@ void BC_Periodic_P1(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double 
 
 void BCDirichlet_P1(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time);
 
+void BC_2DRiemann_P1(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time);
+
 /////////// P1 Matter functions ////////////
 
 void BoundaryConditionP1Matter(Data & d,Mesh & Mh,variable & v, ParamPhysic & Param,double time);

### 2015-05-19 code_FVFSHS_2D_matter/hppfiles/ClassMesh.hpp

@@ -348,7 +348,7 @@ class Mesh { public :
     
      
    }
-  Mesh(const Mesh & M){
+  Mesh(const Mesh &  M){
     
      
      nv=M.nv; nc=M.nc; nbnodelocal=M.nbnodelocal;

### 2015-05-19 code_FVFSHS_2D_matter/hppfiles/Data.hpp

@@ -12,7 +12,7 @@
 using namespace std;
 
 /**
- @brief Class: this class contains the parameters of the code.
+ @brief Class: this class contains the parameter of the code.
 **/
 
 class Data {
@@ -30,14 +30,14 @@ class Data {
   int scheme;
    /** Type of scheme (N for nodal scheme, E for edge scheme) **/
   char Typescheme;
-  /** Test case number **/
+  /** Test case number**/
   int nTest; 
   /** Final time**/
   float Tf;
   /** CFL **/
-  int Total_order;
-  /** CFL **/
   float CFL;
+  /** total order **/
+  int Total_order;
   
   /** Mesh name **/
   char *NameMesh;  
@@ -49,8 +49,7 @@ class Data {
   /** Model :
    - Diffusion : diffusion equation
    - P1 : P1 model
-   - M1 : M1 model
-   - M1Matter : M1 model with matter
+   - M1 : M1 odel
    - Advection : advection
    - Euler : Euler
    - P1Matter : P1 model with matter**/

### 2015-05-19 code_FVFSHS_2D_matter/hppfiles/Flux.hpp

@@ -139,7 +139,11 @@ void MatrixM1Matter(Data & d,Mesh & Mh,variable & v, TabConnecInv & tab,ParamPhy
 vectorflux FluxVertexClassicM1Matter(Data & d,int numCell,Mesh & Mh, variable & v, TabConnecInv & tab, ParamPhysic & Param,R2 * ur);
 
 
+double q_M1M(Data & d, ParamM1Matter & M1Matter,double E,double F1, double F2);
 
+void  Calcul_u_M1M(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab, ParamM1Matter & M1Matter,R2 & u,int numCell);
+
+double coefk_M1M(Data & d, ParamM1Matter & M1Matter,double E,double F1, double F2);
 
 
 

### 2015-05-19 code_FVFSHS_2D_matter/hppfiles/WriteData.hpp

@@ -10,25 +10,27 @@
 
 using namespace std;
 
-void SaveData(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,int ntAnim);
+void SaveData(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamPhysic & Param,int ntAnim);
 
-void SaveOneData(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,int Num,int ntAnim);
+void SaveOneData(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamPhysic & Param,int Num,int ntAnim);
 
-void  SaveOneData1D(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,int Num,int ntAnim);
+void  SaveOneData1D(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamPhysic & Param,int Num,int ntAnim);
 
-void SaveOneDatacentercell(Data & d,Mesh & Mh,variable & v,ParamPhysic & Param,int Num,int ntAnim);
+void SaveOneDatacentercell(Data & d,Mesh & Mh,variable & v,TabConnecInv & tab,ParamPhysic & Param,int Num,int ntAnim);
 
-void SaveMesh(Data & d,Mesh & Mh);
+void SaveMesh(Data & d,Mesh & Mh,TabConnecInv & tab);
 
-void SaveFonction2D(Data & d,Mesh & Mh,ParamPhysic & Param,float t,Vertex c,int var);
+void SaveFonction2D(Data & d,Mesh & Mh,TabConnecInv & tab,ParamPhysic & Param,float t,Vertex c,int var);
 
-void SaveFonction2DEuler(Data & d,Mesh & Mh,ParamPhysic & Param,float t,Vertex c,int var);
+void SaveFonction2DEuler(Data & d,Mesh & Mh,TabConnecInv & tab,ParamPhysic & Param,float t,Vertex c,int var);
 
-void SaveFonction1D(Data & d,Mesh & Mh,ParamPhysic & Param,float t,Vertex c,int var);
+void SaveFonction1D(Data & d,Mesh & Mh,TabConnecInv & tab,ParamPhysic & Param,float t,Vertex c,int var);
 
-void SaveFonction(Data & d,Mesh & Mh,ParamPhysic & Param,float t,Vertex c);
[…]
